### 2019-05-24 meta-analysis.Rmd
added analysis rmd

---
title: "Accuracy of zero heat flux temperature measurements"
output: html_document
---

Functions for calculating Bland-Altman meta-analysis

```{r echo=FALSE}
meta <-  function(Te,V_T){
m <- length(Te)
wt_FE=1/V_T
T_FE <- sum(Te*wt_FE)/sum(wt_FE)
Q <- sum(wt_FE*(Te - T_FE)^2)
S1 <- sum(wt_FE)
S2 <- sum(wt_FE^2)
o2 <- (Q - (m - 1))/(S1 - S2/S1)
wt_RE <- 1/(V_T + o2)
T_RE <- sum(Te*wt_RE)/sum(wt_RE)
V_T_RE_mod <- 1/sum(wt_RE)
V_T_RE_rve <- (m/(m-1))*sum(wt_RE^2*(Te - T_RE)^2)/(sum(wt_RE))^2
c(m,T_RE,o2,V_T_RE_mod, V_T_RE_rve)
}
loa_maker <- function(bias,V_bias,logs2,V_logs2) {
bias_row=meta(bias, V_bias)
logs2_row=meta(logs2, V_logs2)
bias_mean <- bias_row[2]
sd2_est <- exp(logs2_row[2])
tau_est <- bias_row[3]
LOA_L <- bias_mean - 2*sqrt(sd2_est + tau_est)
LOA_U <- bias_mean + 2*sqrt(sd2_est + tau_est)
m <- bias_row[1]
tcrit <- qt(1-.05/2,m-1)
B1 <- sd2_est^2/(sd2_est + tau_est)
B2 <- tau_est^2/(sd2_est + tau_est)
wt <- 1/V_bias
S1 <- sum(wt)
S2 <- sum(wt^2)
S3 <- sum(wt^3)
A0 <- 2*(m-1)/(S1-S2/S1)^2
A1 <- 4/(S1 - S2/S1)
A2 <- 2*(S2-2*S3/S1+S2^2/S1^2)/(S1-S2/S1)^2
V_logT2 <- A0/tau_est^2 + A1/tau_est + A2
V_logT2 <- 2/sum((V_bias + tau_est)^(-2))
V_LOA_mod <- bias_row[4] + B1*logs2_row[4] + B2*V_logT2
V_LOA_rve <- bias_row[5] + B1*logs2_row[5] + B2*V_logT2
CI_L_mod <- LOA_L - tcrit*sqrt(V_LOA_mod)
CI_U_mod <- LOA_U + tcrit*sqrt(V_LOA_mod)
CI_L_rve <- LOA_L - tcrit*sqrt(V_LOA_rve)
CI_U_rve <- LOA_U + tcrit*sqrt(V_LOA_rve)
c(m, bias_mean,sqrt(sd2_est), tau_est, LOA_L, LOA_U, CI_L_mod, CI_U_mod, CI_L_rve, CI_U_rve)}
```

##Legend:

Bias=pooled estimate of mean differences calculated as PaCO2-TcCO2 in mmHg

SD=pooled standard deviation of differences

tau2=Variation in bias between studies

LoA_L LoA_U = Lower and upper 95% limit of agreement calculated from pooled estimates of bias and standard deviation of differences

CI_Lm CI_Um = Model-based random-effects meta-analysis estimate of CI for LOA

CI_Lr CI_Ur = Robust variance estimation meta-analysis estimate of CI for LOA

#Primary meta-analysis (all included studies)
```{r}
library(tidyverse)
data <- readxl::read_xlsx("ZHF.xlsx")

#variance
data <- data %>% 
  mutate(s2 = ((upper - bias)/1.96)^2)

data <- data %>% 
  mutate(V_bias = s2/n)

data <- data %>% 
  mutate(logs2 = log(s2)+1/(n-1))

data <- data %>% 
  mutate(V_logs2 = 2/(n-1))

data_NPA <- data %>% 
  filter(comparison=="NPA")

data_es <- data %>% 
  filter(comparison=="Es")

data_PA <- data %>% 
  filter(comparison=="PA")

data_core <- data %>% 
  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Es")

```

```{r}
out <- loa_maker(data_core$bias,data_core$V_bias,data_core$logs2,data_core$V_logs2)
names(out) <- c("studies","bias","sd","tau2","LOA_L","LOA_U","CI_Lm","CI_Um","CI_Lr","CI_Ur")
out[1:10]
```

```{r}
out <- loa_maker(data_es$bias,data_es$V_bias,data_es$logs2,data_es$V_logs2)
names(out) <- c("studies","bias","sd","tau2","LOA_L","LOA_U","CI_Lm","CI_Um","CI_Lr","CI_Ur")
out[1:10]
```

```{r}
out <- loa_maker(data_PA$bias,data_PA$V_bias,data_PA$logs2,data_PA$V_logs2)
names(out) <- c("studies","bias","sd","tau2","LOA_L","LOA_U","CI_Lm","CI_Um","CI_Lr","CI_Ur")
out[1:10]
```

```{r}
out <- loa_maker(data_NPA$bias,data_NPA$V_bias,data_NPA$logs2,data_NPA$V_logs2)
names(out) <- c("studies","bias","sd","tau2","LOA_L","LOA_U","CI_Lm","CI_Um","CI_Lr","CI_Ur")
out[1:10]
```

### 2019-05-24 revtools/analysis.Rmd
added analysis rmd

---
title: "Untitled"
author: "Aaron Conway"
date: "29/04/2019"
output: html_document
---

```{r}
library(revtools)
library(tidyverse)
library(vroom)
```

# Search pubmed with phrase "zero heat flux"

```{r}
data <- read_bibliography("citations.bib")
```

# Screen abstracts

*It is essential that data is saved as .csv before exiting webpaage*

```{r}
screen_abstracts(data)
```

# Load in results from reviewers

```{r message=FALSE}
reviewer_1 <- read_csv("reviewer_1.csv") %>% 
  mutate(reviewer_one = selected)

reviewer_2 <- read_csv("reviewer_2.csv") %>% 
  mutate(reviewer_two = selected)

abstract_review <- right_join(reviewer_1, reviewer_2, by = "label")
abstract_review <- abstract_review %>% 
  select(label, title.x, abstract.x, doi.x, author.x, reviewer_one, reviewer_two)
names <- c("label", "title", "abstract", "doi", "author", "reviewer_one", "reviewer_two")
colnames(abstract_review) <- names
```

# Compare results between reviewers

```{r}
# Identify inclusions (both reviewers selected include)

inclusions <- abstract_review %>% 
  filter(reviewer_one == "selected" & reviewer_two == "selected")

# Identify exclusions (both reviewers selected include)

exclusions <- abstract_review %>% 
   filter(reviewer_one == "excluded" & reviewer_two == "excluded")

# Identify conflicts (diagreement among reviewers)

conflicts <- abstract_review %>% 
  filter((reviewer_one == "excluded" & reviewer_two == "selected") | (reviewer_one == "selected" & reviewer_two == "excluded"))

# Third reviewer to resolve conflicts

screen_abstracts(as.data.frame(conflicts))

# Add inclusions and exclusions after resolution of conflicts

reviewer_3 <- read_csv("reviewer_2.csv")

inclusions_3 <- reviewer_3 %>% 
  filter(selected == "selected")

exclusions_3 <- reviewer_3 %>% 
  filter(selected == "excluded")

```

# Full text screening

```{r}
library(BibScan)
```

```{r}
library(crminer)
x <- "6c00c459-ddeb8bce-425652b1-aa68cd58"
Sys.setenv(CROSSREF_TDM=x)
e <- "aaron.conway@utoronto.ca"
Sys.setenv(CROSSREF_EMAIL=e)
```

```{r}
indir <- here::here("full-texts", "savedrecs.bib")
outdir <- here::here('full-texts')
article_pdf_download(indir, outdir)
```

```{r}
df_citations <- bibfile_reader(indir, bib_format)
```

### 2019-08-12 zhf_manuscript/flow_nomnoml.Rmd
study inclusion flow chart

---
title: "flow diagram"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(nomnoml)
```
```{nomnoml}
#import: my-common-styles.nomnoml
#stroke: black
#.blob: fill=#DBDBDB visual=italic
#direction: down
#arrowSize: 0.6
#bendSize: 0.3
#fillArrows: true

  [129 references imported for screening]->[94 studies screened against title and abstract]

  [129 references imported for screening]-->[<blob> 35 duplicates removed]

  [94 studies screened against title and abstract]->[23 studies assessed for full-text eligibility]
  [94 studies screened against title and abstract]-->[<blob> 71 studies excluded]

[23 studies assessed for full-text eligibility] -> [17 studies included]

 [23 studies assessed for full-text eligibility] --> [<blob> 7 studies excluded | 4 Wrong intervention

                                                      1 Wrong comparator

                                                      1 Wrong study design]
```

### 2019-08-12 zhf_manuscript/ggplotflow/ggplot.Rmd
study inclusion flow chart

---
title: "ggplot2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tibble)
library(tidyverse)

data <- tibble(x= 1:100, y= 1:100)

data %>% 
  ggplot(aes(x, y)) +
  scale_x_continuous(minor_breaks = seq(10, 100, 10)) +
  scale_y_continuous(minor_breaks = seq(10, 100, 10)) +
  theme_linedraw() -> p

p<-p +
  geom_rect(xmin = 29, xmax=71, ymin=93, ymax=101, color='black',
            fill='white', size=0.25, size=0.25) +
  annotate('text', x= 50, y=97,label= '129 references imported for screening as 129 studies', size=2.5)

p<- p + geom_rect(xmin = 32, xmax=68, ymin=74, ymax=82, color='black',
            fill='white', size=0.25) +
  annotate('text', x= 50, y=78,label= '94 studies screened against title and abstract', size=2.5) +
  geom_rect(xmin = 74, xmax=93, ymin=84, ymax=92, color='black',
            fill='white', size=0.25) +
  annotate('text', x= 83.5, y=88,label= '35 duplicates removed', size=2.5)

p<- p + geom_segment(
    x=50, xend=50, y=92, yend=83.3, 
    size=0.15, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(1, "mm"), type= "closed")) +
  geom_segment(
    x=50, xend=73, y=88, yend=88, 
    size=0.15, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(1, "mm"), type= "closed")) +
  geom_segment(
    x=50, xend=50, y=73, yend=65, 
    size=0.15, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(1, "mm"), type= "closed")) +
  geom_segment(
    x=50, xend=73, y=69, yend=69, 
    size=0.15, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(1, "mm"), type= "closed"))

p <- p+ geom_rect(xmin = 33, xmax=67, ymin=55, ymax=63, color='black',
            fill='white', size=0.25) +
  annotate('text', x= 50, y=59,label= '24 studies assessed for full-text eligibility', size=2.5) +
  geom_rect(xmin = 74, xmax=91, ymin=65, ymax=73, color='black',
            fill='white', size=0.25) +
  annotate('text', x= 82, y=69,label= ' 70 studies excluded', size=2.5)

p <- p + geom_rect(xmin = 42, xmax=58, ymin=38, ymax=45, color='black',
            fill='white', size=0.25) +
annotate('text', x= 50, y=41.5,label= '17 studies included', size=2.5) +

  geom_rect(xmin = 74, xmax=103, ymin=26, ymax=52, color='black',
            fill='white', size=0.25) +
  annotate('text', x= 82, y=39,label= 
  '7 studies excluded
            3 Wrong intervention
                                    1 Abstract only (full paper included)
    1 Tcore not ZHF
           1 Wrong comparator
             1 Wrong study design', size=2.5) #weird spacing to help indent
p <- p +   geom_segment(
    x=50, xend=50, y=54, yend=46, 
    size=0.15, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(1, "mm"), type= "closed")) +
  geom_segment(
    x=50, xend=73, y=50, yend=50, 
    size=0.15, linejoin = "mitre", lineend = "butt",
    arrow = arrow(length = unit(1, "mm"), type= "closed"))
```
```{r}
p + theme_void()
```

129 references imported for screening as 129 studies 
	35 duplicates removed
94 studies screened against title and abstract
	70 studies excluded
24 studies assessed for full-text eligibility
	7 studies excluded
		3  Wrong intervention
		1  Abstract - full paper included
		1  Tcore not ZHF
		1  Wrong comparator
		1  Wrong study design
	0 studies ongoing
	0 studies awaiting classification
17 studies included

### 2019-08-20 meta-analysis.Rmd
new dashboard_app.R

@@
 library(tidyverse)
-data <- readxl::read_xlsx("ZHF.xlsx")
+data <- readxl::read_xlsx("zhf_extracted.xlsx")
+sum_findings <- readxl::read_xlsx("sum_findings.xlsx")
+
+data <- data %>%
+
+  mutate(c = N/n)
 
 #variance
-data <- data %>% 
-  mutate(s2 = ((upper - bias)/1.96)^2)
+
+data <-  if (data$corrected == "Yes"){
+
+  mutate(data, s2 = ((upper - bias)/1.96)^2)
+
+  } else {
+
+    mutate(data, s2 = ((upper - bias)/1.96)^2)*((N-1)/(N-c))
+
+    }
 
@@
 data_NPA <- data %>% 
-  filter(comparison=="NPA")
+  filter(comparison == "NPA")
 
-data_es <- data %>% 
-  filter(comparison=="Es")
+data_SL <- data %>% 
+  filter(comparison == "Sublingual")
 
-data_PA <- data %>% 
-  filter(comparison=="PA")
+data_core <- data %>% #need to adjust for Eshragi, want overall only
+  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac")
 
-data_core <- data %>% 
-  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Es")
+data_core_lowrisk <- data_core %>% # need to adjust for eshragi, want overall only
+  filter(RoB_selection == "low" & RoB_spoton == "low" & RoB_comparator == "low" & RoB_flow =="low" & (comments != "Intraoperative, off cardiopulmonary bypass" | comments != "Postoperative"))
+
+data_core_op <- data_core %>% 
+  filter(clinical_setting=="Intraoperative" & (clinical_setting != "Postoperative" | clinical_setting != "Intra- and Postoperative"))
+
+data_core_icu <- data_core %>% 
+  filter(clinical_setting=="ICU" | clinical_setting=="Postoperative")
 
@@
 out <- loa_maker(data_core$bias,data_core$V_bias,data_core$logs2,data_core$V_logs2)
-names(out) <- c("studies","bias","sd","tau2","LOA_L","LOA_U","CI_Lm","CI_Um","CI_Lr","CI_Ur")
-out[1:10]
-```
-
-```{r}
-out <- loa_maker(data_es$bias,data_es$V_bias,data_es$logs2,data_es$V_logs2)
-names(out) <- c("studies","bias","sd","tau2","LOA_L","LOA_U","CI_Lm","CI_Um","CI_Lr","CI_Ur")
-out[1:10]
-```
-
-```{r}
-out <- loa_maker(data_PA$bias,data_PA$V_bias,data_PA$logs2,data_PA$V_logs2)
-names(out) <- c("studies","bias","sd","tau2","LOA_L","LOA_U","CI_Lm","CI_Um","CI_Lr","CI_Ur")
-out[1:10]
+out <- round(out, digits=3)
+out <- append(out, sum(data_core$n_count, na.rm=T))
+out <- append(out, sum(data_core$N, na.rm = T))
+names(out) <- c("studies","bias","sd","tau2","LOA_L","LOA_U","CI_Lm","CI_Um","CI_Lr","CI_Ur", "n", "N")
+out[1:12]
 ```
@@
 out <- loa_maker(data_NPA$bias,data_NPA$V_bias,data_NPA$logs2,data_NPA$V_logs2)
-names(out) <- c("studies","bias","sd","tau2","LOA_L","LOA_U","CI_Lm","CI_Um","CI_Lr","CI_Ur")
-out[1:10]
+out <- round(out, digits=3)
+out <- append(out, sum(data_NPA$n_count, na.rm=T))
+out <- append(out, sum(data_NPA$N, na.rm = T))
+names(out) <- c("studies","bias","sd","tau2","LOA_L","LOA_U","CI_Lm","CI_Um","CI_Lr","CI_Ur", "n", "N")
+out[1:12]
 ```
+
+```{r}
+out <- loa_maker(data_SL$bias,data_SL$V_bias,data_SL$logs2,data_SL$V_logs2)
+out <- round(out, digits=3)
+out <- append(out, sum(data_SL$n_count, na.rm=T))
+out <- append(out, sum(data_SL$N, na.rm = T))
+names(out) <- c("studies","bias","sd","tau2","LOA_L","LOA_U","CI_Lm","CI_Um","CI_Lr","CI_Ur", "n", "N")
+out[1:12]
+```
+
+```{r}
+out <- loa_maker(data_core_lowrisk$bias,data_core_lowrisk$V_bias,data_core_lowrisk$logs2,data_core_lowrisk$V_logs2)
+out <- round(out, digits=3) 
+out <- append(out, sum(data_core_lowrisk$n_count, na.rm=T))
+out <- append(out, sum(data_core_lowrisk$N, na.rm = T))
+names(out) <- c("studies","bias","sd","tau2","LOA_L","LOA_U","CI_Lm","CI_Um","CI_Lr","CI_Ur", "n", "N")
+out[1:12]
+```
+```{r}
+out <- loa_maker(data_core_op$bias,data_core_op$V_bias,data_core_op$logs2,data_core_op$V_logs2)
+out <- round(out, digits=3) 
+out <- append(out, sum(data_core_op$n_count, na.rm=T))
+out <- append(out, sum(data_core_op$N, na.rm = T))
+names(out) <- c("studies","bias","sd","tau2","LOA_L","LOA_U","CI_Lm","CI_Um","CI_Lr","CI_Ur", "n", "N")
+out[1:12]
+```
+```{r}
+out <- loa_maker(data_core_icu$bias,data_core_icu$V_bias,data_core_icu$logs2,data_core_icu$V_logs2)
+out <- round(out, digits=3) 
+out <- append(out, sum(data_core_icu$n_count, na.rm=T))
+out <- append(out, sum(data_core_icu$N, na.rm = T))
+names(out) <- c("studies","bias","sd","tau2","LOA_L","LOA_U","CI_Lm","CI_Um","CI_Lr","CI_Ur", "n", "N")
+out[1:12]
+```

### 2019-08-20 zhf_manuscript/flow_nomnoml.Rmd
new dashboard_app.R

@@
 #direction: down
+#edges: rounded
 #arrowSize: 0.6
@@
 
-[23 studies assessed for full-text eligibility] -> [17 studies included]
+[23 studies assessed for full-text eligibility] -> [16 studies included]
 
- [23 studies assessed for full-text eligibility] --> [<blob> 7 studies excluded | 4 Wrong intervention
+ [23 studies assessed for full-text eligibility] --> [<blob> 6 studies excluded | 4 wrong intervention
+                                                      1 wrong comparator
+                                                      1 wrong study design]
+ [23 studies assessed for full-text eligibility] --> [<blob> 1 study awaiting classification]
+```
 
-                                                      1 Wrong comparator
+The objective for the meta-analysis was to estimate the population limits of agreement between temperature measurements by the ZHF sensor and established core temperature measurement tools.
+The framework for meta-analysis of Bland-Altman method comparison studies based on limits of agreement (LoA) approach was used [@tipton2017framework].
+This method was selected because it parallels the approach used in primary Bland-Altman studies, whereby an estimate is generated for the pooled LoAs in the population (not just in the samples studied).
+The ‘population LoA’ is more broad than the LoA commonly reported in the meta-analyses of Bland-Altman studies [@tipton2017framework].
+In these instances, the pooled LoAs are calculated using $δ±2√(σ2+τ2)$, where $δ$ is the average bias across studies, $σ2$ is the average within-study variation in differences and $τ2$ is the variation in bias across studies.
+Estimations of $δ$ and $σ2$ were made using a weighted least-squares model (similar to a random-effects approach), with the associated SEs estimated using robust variance estimation (RVE).
+RVE was used alternatively to model-based SEs as several studies included in the systematic review used repeated-measures designs without accommodating for the correlation between measurements [@hedges2010robust; @tanner2016handling; @tipton2015small].
+We used the method-of-moments estimator from ref 16 for the $τ2$ parameter.
+In accordance with ref 12, (1) measures of uncertainty were included when interpreting the LoA estimates by calculating the outer $95\%$ CIs for pooled LoA; and (2) repeated measurements were adjusted if improperly adjusted for in individual studies (by using weights proportional to the number of samples, not the total number of measurements).
+The formulas for the above calculations from ref 12 can be found in [file 1]().
+The R statistical program was use to conduct all analyses[@team2017r].
+All data and R code (provided in ref 12) used in the meta-analyses can be located [here](https://doi.org).
 
-                                                      1 Wrong study design]
-```
+Prior to conducting the meta-analyses, the results from each study were converted into a standard format, with bias meaning ECT - ZHF measured in $˚C$.
+In two of the studies, the results were reported for two separate groups of participants, so these were treated in the meta-analyses as separate ‘studies’.
+Other studies reported separate results for analyses conducted using different TcCO2 device types or sensor locations performed on the same patients.
+Only the result with the largest number of paired measurements between PaCO2 and TcCO2 was selected for inclusion in the main analysis, with others included in subgroup meta-analyses where appropriate.
+For the studies that reported results for patients while receiving both two-lung and one-lung ventilation during thoracic surgery, we used the result for two-lung ventilation in the main analysis.
+The conventionally cited clinically acceptable agreement between ECT and ZHF sensors is 0.5 $˚C$(ref).
+It was deemed that outer confidence bounds for 95% LoA between ECT and ZHF (termed as ‘population limits of agreement’) outside of these bounds would be clinically unacceptable.
+Sensitivity analysis for the primary meta-analysis was performed based on risk of bias, whereby ‘unclear risk of bias’ was treated as ‘high risk’ and ‘high risk of bias’ studies were excluded from analyses.
+Subgroup analyses were conducted according to the comparator device used to monitor temperature (eg, pulmonary artery, esophagus, rectal and bladder thermostats) to allow clinicians to identify the accuracy of the ZHF temperature sensor relative to their typical core temperature monitoring tools.
+
+|Table 1 Results of meta-analysis of agreement between transcutaneous and arterial carbon dioxide|
+|---|---|---|---|---|---|---|---|---|---|---|---|---|
+|---|Studies|N|n|Bias|SD|tau2|LoAL|LoAU|CIL|CIU|
+|---|---|---|---|---|---|---|---|---|---|---|---|---|
+|Subset|Stu-content|N-content|n-content|Bias-content|SD-content|tau2-content|LoAL-content|LoAU-content|CIL-content|CIU-content|
+|Subset|Stu-content|N-content|n-content|Bias-content|SD-content|tau2-content|LoAL-content|LoAU-content|CIL-content|CIU-content|
+
+|Table 2 Summary of findings for accuracy and precision of ZHF core temperature monitoring|
+|---|---|---|---|---|---|
+|Outcome|Summary accuracy and precision (C)|Participants|Study characteristics|Quality|Implications|
+|---|---|---|---|---|---|
+|Out-content|Sum-content|Par-content|Char-content|Qual-content|Impl-content|
+|Out-content|Sum-content|Par-content|Char-content|Qual-content|Impl-content|
+|Out-content|Sum-content|Par-content|Char-content|Qual-content|Impl-content|
+|Out-content|Sum-content|Par-content|Char-content|Qual-content|Impl-content|

### 2019-08-20 zhf_manuscript/zhf_manuscript.Rmd
new dashboard_app.R

---
title: "Accuracy and precision of zero-heat-flux temperature monitoring: a systematic review and meta- analysis"
titlerunning: Short form of title (if too long for head)
authorrunning: Conway,
thanks: | 
    Grants or other notes about the article that should go on the front 
    page should be placed here. General acknowledgments should be placed at the
    end of the article.

authors: 
- name: Aaron Conway
  address: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  email: aaron.conway@utoronto.ca

- name: Âuthóř 2
  address: Department of ZZZ, University of WWW
  email: djf@wef

keywords:
- key
- dictionary
- word

#PACS: 
#- PAC1
#- superPAC

MSC:
- MSC code 1
- MSC code 2

abstract: |
  The text of your abstract.  150 -- 250 words.

bibliography: bibliography.bib
output: rticles::springer_article

---

  ```{r echo=FALSE, include=FALSE}
library(redcapAPI)
library(tidyverse)
library(kableExtra)
library(purrr)
library(ggplot2)
library(dplyr)
library(qwraps2)
library(rticles)
```
# Introduction

Core temperature monitoring is an important intervention within perioperative and intensive care settings$(ref)$. Thermoregulatory dysfunction is commonly associated with the induction of anesthesia and can lead to adverse outcomes including cardiac dysrhythmias, altered hemostasis and increased risk of surgical site infection [@frank1997perioperative; @kurz1996perioperative; @michelson1994reversible; @rohrer1992effect]. The pulmonary artery catheter is the reference standard for continuous core temperature monitoring$(ref)$, however, the invasive nature of this method renders an increased risk of bloodstream infections and damage to surrounding tissue[@hadian2006evidence]. Although clinically accurate relative to pulmonary artery thermometry, surrogate measures of core temperature via esophageal, rectal, and bladder sites remain mildly invasive interventions$(ref)$.

Zero-heat-flux (ZHF) thermometry is an alternative non-invasive method that allows for continuous monitoring of core temperature. Originally developed in the 1970s, ZHF technology was recently implemented in the 3M SpotOn (3M, St Paul, MN), a single-use, disposable sensor $(ref)$. In practice, the ZHF sensor, such as the 3M SpotOn, is placed on the lateral surface of the forehead and initially warmed to equilibrate the temperature of the skin surface to the underlaying core tissues$(ref)$. Equipped with a thermal insulator, the ZHF sensor eliminates heat loss to the environment $(thereby creating an isothermal pathway between the skin surface and underlaying core tissues)$ to allow for changes in core temperature to be directly reflected by a change in skin surface temperature $(ref)$.

The agreement between ZHF and established core temperature measures has been investigated in several studies conducted within the clinical setting, each with varied results. Appraisal of these studies and synthesis of the results would aid $clinical decision-making regarding the appropriate circumstances in which ZHF monitoring may be used.$

We aimed to determine if the ZHF sensor has clinically acceptable accuracy and precision compared with established core temperature tools. Accuracy is defined as the average difference between the ZHF sensor and established core temperature instrument and precisions as the variance (typically reported as the SD) in the differences.

# Methods

A systematic review was conducted in accordance with a predetermined protocol (PROSPERO trial registration number: ################).

## Data sources and searches

Published studies were found by searching Medline and EMBASE from January 2000 to July 2019, $as well as the reference lists of articles identified to be relevant to the review.  This search strategy is an efficient approach for systematic reviews of diagnostic test accuracy studies [@preston2015improving]. Unpublished and ongoing studies were located by searching the International Clinical Trials Platform.$ Published conference abstracts were included if there was enough information reported to appraise the quality of the study. There were no language restrictions applied during the search. $The Cochrane-recommended search strategy combining terms for the ‘target condition’ and ‘index test’ was used [@mann2012should]$. The search strategies used for each data base can be located in [file 1]().

The selection of studies was undertaken by two independent reviewers. Studies were included if reported measures from a ZHF sensor and another established core temperature tool coincided.  Studies involving a case control design were excluded due to potential for overestimation of the intervention performance. Studies were excluded if conducted on non-human subjects or outside of a clinical healthcare setting. Studies were excluded if conducted earlier than the year 2000 as prior studies evaluated outdated technology that is no longer relevant to current clinical practice.

## Data extraction and quality assessment

$Information was extracted regarding study characteristics(author, year of publication, country, design, sample size, clinical setting, numbers studied and analyses for each outcome), population characteristics (inclusion and exclusion criteria) and ZHF characteristics (timing and methods of measurements, and methods of calibration).$ The outcomes that were extracted included the mean bias (eg, accuracy) and variance (eg, SD, precision) in temperature between the ZHF sensor and established core temperature measurement tool. $Information was extracted about how repeated measurements were handled: (1) analysed each pair of data separately; (2) treated each pair of data as independent; or (3) used either analysis of variance or a random effects model as a way to control for the dependent nature of the repeated measures data [@myles2007using].$

Using the revised Quality Assessment of Diagnostic Accuracy Studies (QUADAS-2), each reviewer independently assessed the risk of bias for the included studies [@whiting2011quadas]. $Reviewers used guiding questions to rate the risk of bias for patient selection$, conduct of the ZHF measurements, conduct of the established core temperature measurement tools, and timing and flow (eg, timing of ZHF and established core temperature measurements, dropouts) as “high”, “low” or “unclear”. We worked to minimize the risk of publication bias by conducting a comprehensive search of multiple databases as well as an international clinical trial registry [@glasziou2001systematic]. $Statistical analyses to detect reporting bias were not conducted due to lack of validated methods [@begg2005systematic]. Although some meta-analyses of method comparison studies have used tests for detecting funnel plot asymmetry [@niven2015accuracy], simulations have revealed that such tests will result in publication bias being incorrectly identified too often [@deeks2005performance]$. In order to rate the quality of evidence, we applied the Grading Quality of Evidence and Strength of Recommendation methodology [@schunemann2008grading]. Evidence was downgraded in accordance with study limitations, inconsistency and imprecision. There were no circumstances in which evidence was downgraded for indirectness as this systematic review only included relevant studies. Although the possibility of publication bias was not excluded, this bias was not formally assessed as it was not considered sufficient enough to reason downgrading the quality of evidence.

## Data synthesis and analysis

The objective $for the meta-analysis was to estimate the population limits of agreement between$ temperature measurements by the ZHF sensor and established core temperature measurement tools. $The framework for meta-analysis of Bland-Altman method comparison studies based on limits of agreement (LoA) approach was used [@tipton2017framework]$. This method was selected because it parallels the approach used in primary Bland-Altman studies, whereby an estimate is generated for the pooled LoAs in the population (not just in the samples studied). The ‘population LoA’ is more broad than the LoA commonly reported in the meta-analyses of Bland-Altman studies [@tipton2017framework]. In these instances, $the pooled LoAs are calculated using $\delta\pm2\sqrt{\sigma2+\tau2}$, where $\delta$ is the average bias across studies, $\sigma2$ is the average within-study variation in differences and $\tau2$ is the variation in bias across studies.$ Estimations of $\delta$ and $\sigma2$ were made using a weighted least-squares model (similar to a random-effects approach), with the associated SEs estimated using robust variance estimation (RVE). RVE was used alternatively to model-based SEs as several studies included in the systematic review used repeated-measures designs without accommodating for the correlation between measurements [@hedges2010robust; @tanner2016handling; @tipton2015small]. We used the $method-of-moments estimator from ref 16 for the $\tau2$ parameter$. In accordance with ref 12, (1) measures of uncertainty were included $when interpreting the LoA estimates by calculating the outer $95\%$ CIs for pooled LoA$; and (2) repeated measurements were adjusted if improperly adjusted for in $individual studies (by using weights proportional to the number of samples, not the total number of measurements)$. The formulas for the above calculations from ref 12 can be found in [file 1](). The R statistical program was use to conduct all analyses [@team2017r]. All data and R code (provided in ref 12) used in the meta-analyses can be located [here](https://doi.org).

Prior to conducting the meta-analyses, the results from each study were converted into a standard format, with bias meaning $ECT - ZHF$ measured in $^\circ C$. In two of the studies, the results were reported for two separate groups of participants, so these were treated in the meta-analyses as separate ‘studies’. $Other studies reported separate results for analyses conducted using different TcCO2 device types or sensor locations performed on the same patients. Only the result with the largest number of paired measurements between PaCO2 and TcCO2 was selected for inclusion in the main analysis, with others included in subgroup meta-analyses where appropriate. For the studies that reported results for patients while receiving both two-lung and one-lung ventilation during thoracic surgery, we used the result for two-lung ventilation in the main analysis. The conventionally cited clinically acceptable agreement between$ ECT and ZHF sensors is 0.5 $^\circ C$(ref). $It was deemed that outer confidence bounds for $95\%$ LoA between ECT and ZHF (termed as ‘population limits of agreement’) outside of these bounds would$ be clinically unacceptable. Sensitivity analysis for the primary meta-analysis was performed based on risk of bias, whereby ‘unclear risk of bias’ was treated as ‘high risk’ and ‘high risk of bias’ studies were excluded from analyses. $As clinicians would be interested in the accuracy of$ ZHF relative to temperature monitoring devices they use, and within the clinical setting in which they use it we conducted subgroup analyses according to the comparator device used (eg, core, peripheral, nasopharangeal) and clinical setting (eg, intraoperative, intensuve care unit).

# Results

<!-- Table 1  -->
<!-- |---|---|---|---|---|---|---|---|---|---|---|---|---| -->
<!-- |Table 1 Results of meta-analysis of agreement between transcutaneous and arterial carbon dioxide| -->
<!-- |---|---|---|---|---|---|---|---|---|---|---|---|---| -->
<!-- |---|Studies|N|n|Bias|SD|tau2|LoA_L|LoA_U|CI_L|CI_U| -->
<!-- |---|---|---|---|---|---|---|---|---|---|---|---|---| -->
<!-- |Subset|Stu-content|N-content|n-content|Bias-content|SD-content|tau2-content|LoAL-content|LoAU-content|CIL-content|CIU-content| -->
<!-- |Subset|Stu-content|N-content|n-content|Bias-content|SD-content|tau2-content|LoAL-content|LoAU-content|CIL-content|CIU-content| -->

<!-- Table 2 -->
<!-- |Outcome|Summary accuracy and precision (C)|Participants|Study characteristics|Quality|Implications| -->
<!-- |---|---|---|---|---|---| -->
<!-- |Out-content|Sum-content|Par-content|Char-content|Qual-content|Impl-content| -->
<!-- |Out-content|Sum-content|Par-content|Char-content|Qual-content|Impl-content| -->
<!-- |Out-content|Sum-content|Par-content|Char-content|Qual-content|Impl-content| -->
<!-- |Out-content|Sum-content|Par-content|Char-content|Qual-content|Impl-content| -->

| test1 | test2 | test3 | test4 | test5 |
|-------|-------|-------|-------|-------|
| a     | b     | c     | d     | e     |
| a     | b     | c     | d     | e     |
| a     | b     | c     | d     | e     |

## Study selection and description

## Agreement between ZHF and core temperature measurements

# Discussion

## Limitations

# Conclusion

# References

### 2019-08-20 zhf_manuscript/zhf_manuscript.tex
new dashboard_app.R

% !TeX program = pdfLaTeX
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}

\usepackage[hyphens]{url} % not crucial - just used below for the URL
\usepackage{hyperref}
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%

%% load any required packages here

\begin{document}

\title{Accuracy and precision of zero-heat-flux temperature monitoring: a
systematic review and meta- analysis \thanks{Grants or other notes about the article that should go on the front page
should be placed here. General acknowledgments should be placed at the
end of the article.} }

    \titlerunning{Short form of title (if too long for head)}

\author{  Aaron Conway \and  Âuthóř 2 \and  }

    \authorrunning{ Conway, }

\institute{
        Aaron Conway \at
     Peter Munk Cardiac Centre, UHN \& Lawrence S. Bloomberg Faculty of
 Nursing, University of Toronto \\
     \email{\href{mailto:aaron.conway@utoronto.ca}{\nolinkurl{aaron.conway@utoronto.ca}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Âuthóř 2 \at
     Department of ZZZ, University of WWW \\
     \email{\href{mailto:djf@wef}{\nolinkurl{djf@wef}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
    }

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
The text of your abstract. 150 -- 250 words.
\\
\keywords{
        key \and
        dictionary \and
        word \and
    }

    \subclass{
                    MSC code 1 \and
                    MSC code 2 \and
            }

\end{abstract}

\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Core temperature monitoring is an important intervention within
perioperative and intensive care settings\((ref)\). Thermoregulatory
dysfunction is commonly associated with the induction of anesthesia and
can lead to adverse outcomes including cardiac dysrhythmias, altered
hemostasis and increased risk of surgical site infection (Frank et al.
1997; Kurz, Sessler, and Lenhardt 1996; Michelson et al. 1994; Rohrer
and Natale 1992). The pulmonary artery catheter is the reference
standard for continuous core temperature monitoring\((ref)\), however,
the invasive nature of this method renders an increased risk of
bloodstream infections and damage to surrounding tissue(Hadian and
Pinsky 2006). Although clinically accurate relative to pulmonary artery
thermometry, surrogate measures of core temperature via esophageal,
rectal, and bladder sites remain mildly invasive interventions\((ref)\).

Zero-heat-flux (ZHF) thermometry is an alternative non-invasive method
that allows for continuous monitoring of core temperature. Originally
developed in the 1970s, ZHF technology was recently implemented in the
3M SpotOn (3M, St Paul, MN), a single-use, disposable sensor \((ref)\).
In practice, the ZHF sensor, such as the 3M SpotOn, is placed on the
lateral surface of the forehead and initially warmed to equilibrate the
temperature of the skin surface to the underlaying core
tissues\((ref)\). Equipped with a thermal insulator, the ZHF sensor
eliminates heat loss to the environment
\((thereby creating an isothermal pathway between the skin surface and underlaying core tissues)\)
to allow for changes in core temperature to be directly reflected by a
change in skin surface temperature \((ref)\).

The agreement between ZHF and established core temperature measures has
been investigated in several studies conducted within the clinical
setting, each with varied results. Appraisal of these studies and
synthesis of the results would aid
\(clinical decision-making regarding the appropriate circumstances in which ZHF monitoring may be used.\)

We aimed to determine if the ZHF sensor has clinically acceptable
accuracy and precision compared with established core temperature tools.
Accuracy is defined as the average difference between the ZHF sensor and
established core temperature instrument and precisions as the variance
(typically reported as the SD) in the differences.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

A systematic review was conducted in accordance with a predetermined
protocol (PROSPERO trial registration number:
\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#).

\hypertarget{data-sources-and-searches}{%
\subsection{Data sources and searches}\label{data-sources-and-searches}}

Published studies were found by searching Medline and EMBASE from
January 2000 to July 2019,
\(as well as the reference lists of articles identified to be relevant to the review. This search strategy is an efficient approach for systematic reviews of diagnostic test accuracy studies [@preston2015improving]. Unpublished and ongoing studies were located by searching the International Clinical Trials Platform.\)
Published conference abstracts were included if there was enough
information reported to appraise the quality of the study. There were no
language restrictions applied during the search.
\(The Cochrane-recommended search strategy combining terms for the ‘target condition’ and ‘index test’ was used [@mann2012should]\).
The search strategies used for each data base can be located in
\href{}{file 1}.

The selection of studies was undertaken by two independent reviewers.
Studies were included if reported measures from a ZHF sensor and another
established core temperature tool coincided. Studies involving a case
control design were excluded due to potential for overestimation of the
intervention performance. Studies were excluded if conducted on
non-human subjects or outside of a clinical healthcare setting. Studies
were excluded if conducted earlier than the year 2000 as prior studies
evaluated outdated technology that is no longer relevant to current
clinical practice.

\hypertarget{data-extraction-and-quality-assessment}{%
\subsection{Data extraction and quality
assessment}\label{data-extraction-and-quality-assessment}}

\(Information was extracted regarding study characteristics(author, year of publication, country, design, sample size, clinical setting, numbers studied and analyses for each outcome), population characteristics (inclusion and exclusion criteria) and ZHF characteristics (timing and methods of measurements, and methods of calibration).\)
The outcomes that were extracted included the mean bias (eg, accuracy)
and variance (eg, SD, precision) in temperature between the ZHF sensor
and established core temperature measurement tool.
\(Information was extracted about how repeated measurements were handled: (1) analysed each pair of data separately; (2) treated each pair of data as independent; or (3) used either analysis of variance or a random effects model as a way to control for the dependent nature of the repeated measures data [@myles2007using].\)

Using the revised Quality Assessment of Diagnostic Accuracy Studies
(QUADAS-2), each reviewer independently assessed the risk of bias for
the included studies (Whiting et al. 2011).
\(Reviewers used guiding questions to rate the risk of bias for patient selection\),
conduct of the ZHF measurements, conduct of the established core
temperature measurement tools, and timing and flow (eg, timing of ZHF
and established core temperature measurements, dropouts) as ``high'',
``low'' or ``unclear''. We worked to minimize the risk of publication
bias by conducting a comprehensive search of multiple databases as well
as an international clinical trial registry (Glasziou et al. 2001).
\(Statistical analyses to detect reporting bias were not conducted due to lack of validated methods [@begg2005systematic]. Although some meta-analyses of method comparison studies have used tests for detecting funnel plot asymmetry [@niven2015accuracy], simulations have revealed that such tests will result in publication bias being incorrectly identified too often [@deeks2005performance]\).
In order to rate the quality of evidence, we applied the Grading Quality
of Evidence and Strength of Recommendation methodology (Schünemann et
al. 2008). Evidence was downgraded in accordance with study limitations,
inconsistency and imprecision. There were no circumstances in which
evidence was downgraded for indirectness as this systematic review only
included relevant studies. Although the possibility of publication bias
was not excluded, this bias was not formally assessed as it was not
considered sufficient enough to reason downgrading the quality of
evidence.

\hypertarget{data-synthesis-and-analysis}{%
\subsection{Data synthesis and
analysis}\label{data-synthesis-and-analysis}}

The objective
\(for the meta-analysis was to estimate the population limits of agreement between\)
temperature measurements by the ZHF sensor and established core
temperature measurement tools.
\(The framework for meta-analysis of Bland-Altman method comparison studies based on limits of agreement (LoA) approach was used [@tipton2017framework]\).
This method was selected because it parallels the approach used in
primary Bland-Altman studies, whereby an estimate is generated for the
pooled LoAs in the population (not just in the samples studied). The
`population LoA' is more broad than the LoA commonly reported in the
meta-analyses of Bland-Altman studies (Tipton and Shuster 2017). In
these instances, \$the pooled LoAs are calculated using
\(\delta\pm2\sqrt{\sigma2+\tau2}\), where \(\delta\) is the average bias
across studies, \(\sigma2\) is the average within-study variation in
differences and \(\tau2\) is the variation in bias across studies.\$
Estimations of \(\delta\) and \(\sigma2\) were made using a weighted
least-squares model (similar to a random-effects approach), with the
associated SEs estimated using robust variance estimation (RVE). RVE was
used alternatively to model-based SEs as several studies included in the
systematic review used repeated-measures designs without accommodating
for the correlation between measurements (Hedges, Tipton, and Johnson
2010; Tanner-Smith, Tipton, and Polanin 2016; Tipton 2015). We used the
\$method-of-moments estimator from ref 16 for the \(\tau2\) parameter\$.
In accordance with ref 12, (1) measures of uncertainty were included
\$when interpreting the LoA estimates by calculating the outer \(95\%\)
CIs for pooled LoA\$; and (2) repeated measurements were adjusted if
improperly adjusted for in
\(individual studies (by using weights proportional to the number of samples, not the total number of measurements)\).
The formulas for the above calculations from ref 12 can be found in
\href{}{file 1}. The R statistical program was use to conduct all
analyses (Team 2017). All data and R code (provided in ref 12) used in
the meta-analyses can be located \href{https://doi.org}{here}.

Prior to conducting the meta-analyses, the results from each study were
converted into a standard format, with bias meaning \(ECT - ZHF\)
measured in \(^\circ C\). In two of the studies, the results were
reported for two separate groups of participants, so these were treated
in the meta-analyses as separate `studies'.
\(Other studies reported separate results for analyses conducted using different TcCO2 device types or sensor locations performed on the same patients. Only the result with the largest number of paired measurements between PaCO2 and TcCO2 was selected for inclusion in the main analysis, with others included in subgroup meta-analyses where appropriate. For the studies that reported results for patients while receiving both two-lung and one-lung ventilation during thoracic surgery, we used the result for two-lung ventilation in the main analysis. The conventionally cited clinically acceptable agreement between\)
ECT and ZHF sensors is 0.5 \(^\circ C\)(ref). \$It was deemed that outer
confidence bounds for \(95\%\) LoA between ECT and ZHF (termed as
`population limits of agreement') outside of these bounds would\$ be
clinically unacceptable. Sensitivity analysis for the primary
meta-analysis was performed based on risk of bias, whereby `unclear risk
of bias' was treated as `high risk' and `high risk of bias' studies were
excluded from analyses.
\(As clinicians would be interested in the accuracy of\) ZHF relative to
temperature monitoring devices they use, and within the clinical setting
in which they use it we conducted subgroup analyses according to the
comparator device used (eg, core, peripheral, nasopharangeal) and
clinical setting (eg, intraoperative, intensuve care unit).

\hypertarget{results}{%
\section{Results}\label{results}}

\begin{longtable}[]{@{}lllll@{}}
\toprule
test1 & test2 & test3 & test4 & test5\tabularnewline
\midrule
\endhead
a & b & c & d & e\tabularnewline
a & b & c & d & e\tabularnewline
a & b & c & d & e\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{study-selection-and-description}{%
\subsection{Study selection and
description}\label{study-selection-and-description}}

\hypertarget{agreement-between-zhf-and-core-temperature-measurements}{%
\subsection{Agreement between ZHF and core temperature
measurements}\label{agreement-between-zhf-and-core-temperature-measurements}}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{limitations}{%
\subsection{Limitations}\label{limitations}}

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-frank1997perioperative}{}%
Frank, Steven M, Lee A Fleisher, Michael J Breslow, Michael S Higgins,
Krista F Olson, Susan Kelly, and Charles Beattie. 1997. ``Perioperative
Maintenance of Normothermia Reduces the Incidence of Morbid Cardiac
Events: A Randomized Clinical Trial.'' \emph{Jama} 277 (14). American
Medical Association: 1127--34.

\leavevmode\hypertarget{ref-glasziou2001systematic}{}%
Glasziou, Paul, Les Irwig, Chris Bain, and Graham Colditz. 2001.
\emph{Systematic Reviews in Health Care: A Practical Guide}. Cambridge
University Press.

\leavevmode\hypertarget{ref-hadian2006evidence}{}%
Hadian, Mehrnaz, and Michael R Pinsky. 2006. ``Evidence-Based Review of
the Use of the Pulmonary Artery Catheter: Impact Data and
Complications.'' \emph{Critical Care} 10 (3). BioMed Central: S8.

\leavevmode\hypertarget{ref-hedges2010robust}{}%
Hedges, Larry V, Elizabeth Tipton, and Matthew C Johnson. 2010. ``Robust
Variance Estimation in Meta-Regression with Dependent Effect Size
Estimates.'' \emph{Research Synthesis Methods} 1 (1). Wiley Online
Library: 39--65.

\leavevmode\hypertarget{ref-kurz1996perioperative}{}%
Kurz, Andrea, Daniel I Sessler, and Rainer Lenhardt. 1996.
``Perioperative Normothermia to Reduce the Incidence of Surgical-Wound
Infection and Shorten Hospitalization.'' \emph{New England Journal of
Medicine} 334 (19). Mass Medical Soc: 1209--16.

\leavevmode\hypertarget{ref-michelson1994reversible}{}%
Michelson, Alan D, Hollace MacGregor, Marc R Barnard, Anita S Kestin,
Michael J Rohrer, and C Robert Valeri. 1994. ``Reversible Inhibition of
Human Platelet Activation by Hypothermia in Vivo and in Vitro.''
\emph{Thrombosis and Haemostasis} 72 (05). Schattauer GmbH: 633--40.

\leavevmode\hypertarget{ref-rohrer1992effect}{}%
Rohrer, Michael J, and ANITA M Natale. 1992. ``Effect of Hypothermia on
the Coagulation Cascade.'' \emph{Critical Care Medicine} 20 (10):
1402--5.

\leavevmode\hypertarget{ref-schunemann2008grading}{}%
Schünemann, Holger J, Andrew D Oxman, Jan Brozek, Paul Glasziou, Roman
Jaeschke, Gunn E Vist, John W Williams, et al. 2008. ``Grading Quality
of Evidence and Strength of Recommendations for Diagnostic Tests and
Strategies.'' \emph{Bmj} 336 (7653). British Medical Journal Publishing
Group: 1106--10.

\leavevmode\hypertarget{ref-tanner2016handling}{}%
Tanner-Smith, Emily E, Elizabeth Tipton, and Joshua R Polanin. 2016.
``Handling Complex Meta-Analytic Data Structures Using Robust Variance
Estimates: A Tutorial in R.'' \emph{Journal of Developmental and
Life-Course Criminology} 2 (1). Springer: 85--112.

\leavevmode\hypertarget{ref-team2017r}{}%
Team, R Core. 2017. ``R Core Team (2017). R: A Language and Environment
for Statistical Computing.'' \emph{R Found. Stat. Comput. Vienna,
Austria. URL Http://Www. R-Project. Org/., Page R Foundation for
Statistical Computing}.

\leavevmode\hypertarget{ref-tipton2015small}{}%
Tipton, Elizabeth. 2015. ``Small Sample Adjustments for Robust Variance
Estimation with Meta-Regression.'' \emph{Psychological Methods} 20 (3).
American Psychological Association: 375.

\leavevmode\hypertarget{ref-tipton2017framework}{}%
Tipton, Elizabeth, and Jonathan Shuster. 2017. ``A Framework for the
Meta-Analysis of Bland--Altman Studies Based on a Limits of Agreement
Approach.'' \emph{Statistics in Medicine} 36 (23). Wiley Online Library:
3621--35.

\leavevmode\hypertarget{ref-whiting2011quadas}{}%
Whiting, Penny F, Anne WS Rutjes, Marie E Westwood, Susan Mallett,
Jonathan J Deeks, Johannes B Reitsma, Mariska MG Leeflang, Jonathan AC
Sterne, and Patrick MM Bossuyt. 2011. ``QUADAS-2: A Revised Tool for the
Quality Assessment of Diagnostic Accuracy Studies.'' \emph{Annals of
Internal Medicine} 155 (8). Am Coll Physicians: 529--36.

\bibliographystyle{spbasic}
\bibliography{bibliography.bib}

\end{document}

### 2019-08-20 app.R

@@ -1,0 +1,301 @@
+library(shiny)
+library(tidyverse)
+library(ggplot2)
+library(DT)
+
+
+
+# Load data ----
+
+data <- readxl::read_xlsx("zhf_extracted.xlsx")
+
+# Functions for calculating the Bland-Altman meta-analysis ----
+
+meta <-  function(Te,V_T){
+  m <- length(Te)
+  wt_FE=1/V_T
+  T_FE <- sum(Te*wt_FE)/sum(wt_FE)
+  Q <- sum(wt_FE*(Te - T_FE)^2)
+  S1 <- sum(wt_FE)
+  S2 <- sum(wt_FE^2)
+  o2 <- (Q - (m - 1))/(S1 - S2/S1)
+  wt_RE <- 1/(V_T + o2)
+  T_RE <- sum(Te*wt_RE)/sum(wt_RE)
+  V_T_RE_mod <- 1/sum(wt_RE)
+  V_T_RE_rve <- (m/(m-1))*sum(wt_RE^2*(Te - T_RE)^2)/(sum(wt_RE))^2
+  c(m,T_RE,o2,V_T_RE_mod, V_T_RE_rve)
+}
+loa_maker <- function(bias,V_bias,logs2,V_logs2) {
+  bias_row=meta(bias, V_bias)
+  logs2_row=meta(logs2, V_logs2)
+  bias_mean <- bias_row[2]
+  sd2_est <- exp(logs2_row[2])
+  tau_est <- bias_row[3]
+  LOA_L <- bias_mean - 2*sqrt(sd2_est + tau_est)
+  LOA_U <- bias_mean + 2*sqrt(sd2_est + tau_est)
+  m <- bias_row[1]
+  tcrit <- qt(1-.05/2,m-1)
+  B1 <- sd2_est^2/(sd2_est + tau_est)
+  B2 <- tau_est^2/(sd2_est + tau_est)
+  wt <- 1/V_bias
+  S1 <- sum(wt)
+  S2 <- sum(wt^2)
+  S3 <- sum(wt^3)
+  A0 <- 2*(m-1)/(S1-S2/S1)^2
+  A1 <- 4/(S1 - S2/S1)
+  A2 <- 2*(S2-2*S3/S1+S2^2/S1^2)/(S1-S2/S1)^2
+  V_logT2 <- A0/tau_est^2 + A1/tau_est + A2
+  V_logT2 <- 2/sum((V_bias + tau_est)^(-2))
[…]

### 2019-08-20 dashboard_app.R

@@ -1,0 +1,326 @@
+devtools::install_github("rstudio/shinydashboard")
+library(shiny)
+library(shinydashboard)
+library(tidyverse)
+library(ggplot2)
+library(DT)
+
+# Load data ----
+
+data <- readxl::read_xlsx("zhf_extracted.xlsx")
+sum_findings <- readxl::read_xlsx("sum_findings.xlsx")
+
+
+# Functions for calculating the Bland-Altman meta-analysis ----
+
+meta <-  function(Te,V_T){
+  m <- length(Te)
+  wt_FE=1/V_T
+  T_FE <- sum(Te*wt_FE)/sum(wt_FE)
+  Q <- sum(wt_FE*(Te - T_FE)^2)
+  S1 <- sum(wt_FE)
+  S2 <- sum(wt_FE^2)
+  o2 <- (Q - (m - 1))/(S1 - S2/S1)
+  wt_RE <- 1/(V_T + o2)
+  T_RE <- sum(Te*wt_RE)/sum(wt_RE)
+  V_T_RE_mod <- 1/sum(wt_RE)
+  V_T_RE_rve <- (m/(m-1))*sum(wt_RE^2*(Te - T_RE)^2)/(sum(wt_RE))^2
+  c(m,T_RE,o2,V_T_RE_mod, V_T_RE_rve)
+}
+loa_maker <- function(bias,V_bias,logs2,V_logs2) {
+  bias_row=meta(bias, V_bias)
+  logs2_row=meta(logs2, V_logs2)
+  bias_mean <- bias_row[2]
+  sd2_est <- exp(logs2_row[2])
+  tau_est <- bias_row[3]
+  LOA_L <- bias_mean - 2*sqrt(sd2_est + tau_est)
+  LOA_U <- bias_mean + 2*sqrt(sd2_est + tau_est)
+  m <- bias_row[1]
+  tcrit <- qt(1-.05/2,m-1)
+  B1 <- sd2_est^2/(sd2_est + tau_est)
+  B2 <- tau_est^2/(sd2_est + tau_est)
+  wt <- 1/V_bias
+  S1 <- sum(wt)
+  S2 <- sum(wt^2)
+  S3 <- sum(wt^3)
+  A0 <- 2*(m-1)/(S1-S2/S1)^2
+  A1 <- 4/(S1 - S2/S1)
[…]

### 2019-08-23 meta-analysis.Rmd
navy shinydashboard

@@
 
-data_core <- data %>% #need to adjust for Eshragi, want overall only
-  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac")
+data_core <- data %>% #eshragi overall
+  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
+  filter(comments != "Intraoperative, off cardiopulmonary bypass" & comments != "Postoperative")
 
-data_core_lowrisk <- data_core %>% # need to adjust for eshragi, want overall only
-  filter(RoB_selection == "low" & RoB_spoton == "low" & RoB_comparator == "low" & RoB_flow =="low" & (comments != "Intraoperative, off cardiopulmonary bypass" | comments != "Postoperative"))
+data_core_lowrisk <- data_core %>% #eshragi overall
+  filter(RoB_selection == "low" & RoB_spoton == "low" & RoB_comparator == "low" & RoB_flow =="low")
 
-data_core_op <- data_core %>% 
-  filter(clinical_setting=="Intraoperative" & (clinical_setting != "Postoperative" | clinical_setting != "Intra- and Postoperative"))
+data_core_op <- data%>% #eshragi intraop
+    filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
+  filter (clinical_setting=="Intraoperative")
 
-data_core_icu <- data_core %>% 
+data_core_icu <- data %>% #eshragi postop
+      filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
   filter(clinical_setting=="ICU" | clinical_setting=="Postoperative")
@@
 ```
+,#end fluid Row
+            column(12,
+                   htmlOutput("selected_subset"),
+                   DT::dataTableOutput("summary"))),

### 2019-08-23 dashboard_app.R

@@ -1,6 +1,7 @@
-devtools::install_github("rstudio/shinydashboard")
+
 library(shiny)
 library(shinydashboard)
+library(shinydashboardPlus)
 library(tidyverse)
 library(ggplot2)
 library(DT)
@@ -82,17 +83,20 @@ data_NPA <- data %>%
 data_SL <- data %>% 
   filter(comparison == "Sublingual")
 
-data_core <- data %>% 
-  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac")
+data_core <- data %>% #eshragi overall
+  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
+  filter(comments != "Intraoperative, off cardiopulmonary bypass" & comments != "Postoperative")
 
-data_core_lowrisk <- data_core %>% 
-  filter((RoB_selection == "low" & RoB_spoton == "low" & RoB_comparator == "low" & RoB_flow =="low") & clinical_setting != "Intra- and Postoperative")
+data_core_lowrisk <- data_core %>% #eshragi overall
+  filter(RoB_selection == "low" & RoB_spoton == "low" & RoB_comparator == "low" & RoB_flow =="low")
 
-data_core_op <- data_core %>% 
-  filter(clinical_setting=="Intraoperative")
+data_core_op <- data%>% #eshragi intraop
+  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
+  filter (clinical_setting=="Intraoperative")
 
-data_core_icu <- data_core %>% 
-  filter(clinical_setting=="ICU" | clinical_setting =="Postoperative")
+data_core_icu <- data %>% #eshragi postop
+  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
+  filter(clinical_setting=="ICU" | clinical_setting=="Postoperative")
 
 #clean up comparison
 data$comparison <- sub("NPA", "Nasopharyngeal", data$comparison) 
@@ -102,7 +106,7 @@ data$comparison <- sub("Ax", "Axillary artery", data$comparison)
[…]

### 2019-08-27 meta-analysis.Rmd
final summer submission of app.R and zhf_manuscript

@@
 
+# meta-analyses categories
+
 data_NPA <- data %>% 
@@
 
+# ROB
+
+data_RoB_sel <- data %>% 
+  filter(RoB_selection == "high" | RoB_selection == "unclear")
+
+data_RoB_spot <- data %>% 
+  filter(RoB_spoton == "high" | RoB_spoton == "unclear")
+
+data_RoB_comp <- data %>% 
+  filter(RoB_comparator == "high" | RoB_comparator == "unclear")
+
+data_RoB_flow <- data %>%
+  filter(RoB_flow == "high" | RoB_flow == "unclear")
+
+# conflict of interests
+
+data_conflict <- data %>% 
+  filter(`Funding/equipment/conflict with ZHF company` == "Yes")
+
+```
+```{r}
+out <- loa_maker(data_RoB_sel$bias,data_RoB_sel$V_bias,data_RoB_sel$logs2,data_RoB_sel$V_logs2)
+out <- round(out, digits=3)
+out <- append(out, sum(data_core$n_count, na.rm=T))
+out <- append(out, sum(data_core$N, na.rm = T))
+names(out) <- c("studies","bias","sd","tau2","LOA_L","LOA_U","CI_Lm","CI_Um","CI_Lr","CI_Ur", "n", "N")
+out[1:12]
+```
+```{r}
+out <- loa_maker(data_RoB_spot$bias,data_RoB_spot$V_bias,data_RoB_spot$logs2,data_RoB_spot$V_logs2)
+out <- round(out, digits=3)
+out <- append(out, sum(data_core$n_count, na.rm=T))
+out <- append(out, sum(data_core$N, na.rm = T))
+names(out) <- c("studies","bias","sd","tau2","LOA_L","LOA_U","CI_Lm","CI_Um","CI_Lr","CI_Ur", "n", "N")
+out[1:12]
+```
+```{r}
+out <- loa_maker(data_RoB_comp$bias,data_RoB_comp$V_bias,data_RoB_comp$logs2,data_RoB_comp$V_logs2)
+out <- round(out, digits=3)
+out <- append(out, sum(data_core$n_count, na.rm=T))
+out <- append(out, sum(data_core$N, na.rm = T))
+names(out) <- c("studies","bias","sd","tau2","LOA_L","LOA_U","CI_Lm","CI_Um","CI_Lr","CI_Ur", "n", "N")
+out[1:12]
+```
+```{r}
+out <- loa_maker(data_RoB_flow$bias,data_RoB_flow$V_bias,data_RoB_flow$logs2,data_RoB_flow$V_logs2)
+out <- round(out, digits=3)
+out <- append(out, sum(data_core$n_count, na.rm=T))
+out <- append(out, sum(data_core$N, na.rm = T))
+names(out) <- c("studies","bias","sd","tau2","LOA_L","LOA_U","CI_Lm","CI_Um","CI_Lr","CI_Ur", "n", "N")
+out[1:12]
 ```

### 2019-08-27 zhf_manuscript/flow_nomnoml.Rmd
final summer submission of app.R and zhf_manuscript

@@
 ```
-```{nomnoml}
+```{nomnoml, echo=F}
 #import: my-common-styles.nomnoml

### 2019-08-27 zhf_manuscript/zhf_manuscript.Rmd
final summer submission of app.R and zhf_manuscript

@@
 
-Core temperature monitoring is an important intervention within perioperative and intensive care settings$(ref)$.
+Core temperature monitoring is an important intervention within perioperative and intensive care settings.
 Thermoregulatory dysfunction is commonly associated with the induction of anesthesia and can lead to adverse outcomes including cardiac dysrhythmias, altered hemostasis and increased risk of surgical site infection [@frank1997perioperative; @kurz1996perioperative; @michelson1994reversible; @rohrer1992effect].
-The pulmonary artery catheter is the reference standard for continuous core temperature monitoring$(ref)$, however, the invasive nature of this method renders an increased risk of bloodstream infections and damage to surrounding tissue[@hadian2006evidence].
-Although clinically accurate relative to pulmonary artery thermometry, surrogate measures of core temperature via esophageal, rectal, and bladder sites remain mildly invasive interventions$(ref)$.
+The pulmonary artery catheter is the reference standard for continuous core temperature monitoring$(ref - trouble finding a statement regarding this in the literature)$, however, the invasive nature of this method renders an increased risk of bloodstream infections and damage to surrounding tissue[@hadian2006evidence].
+Although clinically accurate relative to pulmonary artery temperature measurements, surrogate measures of core temperature at esophageal, rectal, and bladder locations remain mildly invasive interventions$(ref)$.
 
@@
 In practice, the ZHF sensor, such as the 3M SpotOn, is placed on the lateral surface of the forehead and initially warmed to equilibrate the temperature of the skin surface to the underlaying core tissues$(ref)$.
-Equipped with a thermal insulator, the ZHF sensor eliminates heat loss to the environment $(thereby creating an isothermal pathway between the skin surface and underlaying core tissues)$ to allow for changes in core temperature to be directly reflected by a change in skin surface temperature $(ref)$.
+Equipped with a thermal insulator, the ZHF sensor eliminates heat loss to the environment to allow for changes in core temperature to be directly reflected by a change in skin surface temperature $(ref)$.
 
-The agreement between ZHF and established core temperature measures has been investigated in several studies conducted within the clinical setting, each with varied results.
-Appraisal of these studies and synthesis of the results would aid $clinical decision-making regarding the appropriate circumstances in which ZHF monitoring may be used.$
+The agreement between ZHF and established core temperature devices has been investigated in several studies conducted within the clinical setting, each with varied results.
+Appraisal of these studies and synthesis of the results would aid clinicians in deciding the appropriate circumstances in which ZHF may be used.
 
-We aimed to determine if the ZHF sensor has clinically acceptable accuracy and precision compared with established core temperature tools.
-Accuracy is defined as the average difference between the ZHF sensor and established core temperature instrument and precisions as the variance (typically reported as the SD) in the differences.
+We aimed to determine if ZHF has clinically acceptable accuracy and precision relative to established core temperature measurement devices.
+Accuracy is defined as the average difference between temperature measurements from the ZHF and comparator device and precisions as the variance (typically reported as the SD) in the differences.
 
@@
 
-Published studies were found by searching Medline and EMBASE from January 2000 to July 2019, $as well as the reference lists of articles identified to be relevant to the review.
+Published studies were found by searching Medline and EMBASE from January 2000 to July 2019, 
+>as well as the reference lists of articles identified to be relevant to the review.
 This search strategy is an efficient approach for systematic reviews of diagnostic test accuracy studies [@preston2015improving].
-Unpublished and ongoing studies were located by searching the International Clinical Trials Platform.$ Published conference abstracts were included if there was enough information reported to appraise the quality of the study.
-There were no language restrictions applied during the search.
-$The Cochrane-recommended search strategy combining terms for the ‘target condition’ and ‘index test’ was used [@mann2012should]$.
+Unpublished and ongoing studies were located by searching the International Clinical Trials Platform.
+
+Published conference abstracts were included if there was enough information reported to appraise the quality of the study. There were no language restrictions applied during the search. 
+>The Cochrane-recommended search strategy combining terms for the ‘target condition’ and ‘index test’ was used [@mann2012should].
+
 The search strategies used for each data base can be located in [file 1]().
@@
 The selection of studies was undertaken by two independent reviewers.
-Studies were included if reported measures from a ZHF sensor and another established core temperature tool coincided.
+Studies were included if reported measures from a ZHF and comparator device coincided.
 Studies involving a case control design were excluded due to potential for overestimation of the intervention performance.
@@
 
-$Information was extracted regarding study characteristics(author, year of publication, country, design, sample size, clinical setting, numbers studied and analyses for each outcome), population characteristics (inclusion and exclusion criteria) and ZHF characteristics (timing and methods of measurements, and methods of calibration).$ The outcomes that were extracted included the mean bias (eg, accuracy) and variance (eg, SD, precision) in temperature between the ZHF sensor and established core temperature measurement tool.
-$Information was extracted about how repeated measurements were handled: (1) analysed each pair of data separately; (2) treated each pair of data as independent; or (3) used either analysis of variance or a random effects model as a way to control for the dependent nature of the repeated measures data [@myles2007using].$
+Information was extracted regarding study characteristics (author, year of publication, country, design, sample size, clinical setting, numbers studied and analyses for each outcome), population characteristics (inclusion and exclusion criteria) and ZHF characteristics (placement of sensor, timing and methods of measurements).
+The outcomes that were extracted included the mean bias (eg, accuracy) and variance (eg, SD, precision) in temperature measurement between the ZHF sensor and comparator device.
+>Information was extracted about how repeated measurements were handled: (1) analysed each pair of data separately; (2) treated each pair of data as independent; or (3) used either analysis of variance or a random effects model as a way to control for the dependent nature of the repeated measures data [@myles2007using].
 
 Using the revised Quality Assessment of Diagnostic Accuracy Studies (QUADAS-2), each reviewer independently assessed the risk of bias for the included studies [@whiting2011quadas].
-$Reviewers used guiding questions to rate the risk of bias for patient selection$, conduct of the ZHF measurements, conduct of the established core temperature measurement tools, and timing and flow (eg, timing of ZHF and established core temperature measurements, dropouts) as “high”, “low” or “unclear”.
+Using guiding questions, reviewers rated the risk of bias for patient selection, conduct of the ZHF measurements, conduct of the comparator device measurements, and timing and flow (eg, timing of ZHF and established core temperature measurements, dropouts) as “high”, “low” or “unclear”.
 We worked to minimize the risk of publication bias by conducting a comprehensive search of multiple databases as well as an international clinical trial registry [@glasziou2001systematic].
-$Statistical analyses to detect reporting bias were not conducted due to lack of validated methods [@begg2005systematic].
-Although some meta-analyses of method comparison studies have used tests for detecting funnel plot asymmetry [@niven2015accuracy], simulations have revealed that such tests will result in publication bias being incorrectly identified too often [@deeks2005performance]$.
+>Statistical analyses to detect reporting bias were not conducted due to lack of validated methods [@begg2005systematic].
+Although some meta-analyses of method comparison studies have used tests for detecting funnel plot asymmetry [@niven2015accuracy], simulations have revealed that such tests will result in publication bias being incorrectly identified too often [@deeks2005performance].
+
 In order to rate the quality of evidence, we applied the Grading Quality of Evidence and Strength of Recommendation methodology [@schunemann2008grading].
@@
 
-The objective $for the meta-analysis was to estimate the population limits of agreement between$ temperature measurements by the ZHF sensor and established core temperature measurement tools.
-$The framework for meta-analysis of Bland-Altman method comparison studies based on limits of agreement (LoA) approach was used [@tipton2017framework]$.
+The objective for the meta-analysis was to estimate the population limits of agreement between temperature measurements from the ZHF and established comparator devices.
+>The framework for meta-analysis of Bland-Altman method comparison studies based on limits of agreement (LoA) approach was used [@tipton2017framework].
+
 This method was selected because it parallels the approach used in primary Bland-Altman studies, whereby an estimate is generated for the pooled LoAs in the population (not just in the samples studied).
 The ‘population LoA’ is more broad than the LoA commonly reported in the meta-analyses of Bland-Altman studies [@tipton2017framework].
-In these instances, $the pooled LoAs are calculated using $\delta\pm2\sqrt{\sigma2+\tau2}$, where $\delta$ is the average bias across studies, $\sigma2$ is the average within-study variation in differences and $\tau2$ is the variation in bias across studies.$ Estimations of $\delta$ and $\sigma2$ were made using a weighted least-squares model (similar to a random-effects approach), with the associated SEs estimated using robust variance estimation (RVE).
+In these instances,
+>the pooled LoAs are calculated using $\delta\pm2\sqrt{\sigma2+\tau2}$, where $\delta$ is the average bias across studies, $\sigma2$ is the average within-study variation in differences and $\tau2$ is the variation in bias across studies.
+
+Estimations of $\delta$ and $\sigma2$ were made using a weighted least-squares model (similar to a random-effects approach), with the associated SEs estimated using robust variance estimation (RVE).
 RVE was used alternatively to model-based SEs as several studies included in the systematic review used repeated-measures designs without accommodating for the correlation between measurements [@hedges2010robust; @tanner2016handling; @tipton2015small].
-We used the $method-of-moments estimator from ref 16 for the $\tau2$ parameter$.
-In accordance with ref 12, (1) measures of uncertainty were included $when interpreting the LoA estimates by calculating the outer $95\%$ CIs for pooled LoA$; and (2) repeated measurements were adjusted if improperly adjusted for in $individual studies (by using weights proportional to the number of samples, not the total number of measurements)$.
+We used the
+>method-of-moments estimator from ref 16 for the $\tau2$ parameter.
+
+In accordance with ref 12, (1) measures of uncertainty were included 
+>when interpreting the LoA estimates by calculating the outer $95\%$ CIs for pooled LoA;
+
+and (2) repeated measurements were adjusted if improperly adjusted for in 
+>individual studies (by using weights proportional to the number of participants, not the total number of measurements).
+
 The formulas for the above calculations from ref 12 can be found in [file 1]().
-The R statistical program was use to conduct all analyses [@team2017r].
+The R statistical program was used to conduct all analyses [@team2017r].
 All data and R code (provided in ref 12) used in the meta-analyses can be located [here](https://doi.org).
 
-Prior to conducting the meta-analyses, the results from each study were converted into a standard format, with bias meaning $ECT - ZHF$ measured in $^\circ C$.
-In two of the studies, the results were reported for two separate groups of participants, so these were treated in the meta-analyses as separate ‘studies’.
-$Other studies reported separate results for analyses conducted using different TcCO2 device types or sensor locations performed on the same patients.
-Only the result with the largest number of paired measurements between PaCO2 and TcCO2 was selected for inclusion in the main analysis, with others included in subgroup meta-analyses where appropriate.
-For the studies that reported results for patients while receiving both two-lung and one-lung ventilation during thoracic surgery, we used the result for two-lung ventilation in the main analysis.
-The conventionally cited clinically acceptable agreement between$ ECT and ZHF sensors is 0.5 $^\circ C$(ref).
-$It was deemed that outer confidence bounds for $95\%$ LoA between ECT and ZHF (termed as ‘population limits of agreement’) outside of these bounds would$ be clinically unacceptable.
+Prior to conducting the meta-analyses, the results from each study were converted into a standard format, with bias meaning $comparator-ZHF$ measured in $^\circ C$.
+In several studies, results were reported for multiple groups of participants, therefore in the meta-analysis each of these groups was treated as a separate 'comparison'.
+Other studies reported multiple sets of results, whereby analyses were conducted between ZHF and various comparator devices used on the same participant.
+These instances were also treated as a separate 'comparison' if the comparator devices were apart of separate meta-analyses groups.
+One study reported intraoperative, postoperative and overall results for the same participants.
+Only the paired measurements from the overall results were included in the main and low risk bias analyses, leaving paired measurements exclusively from the intraoperative and postoperative timepoints to be included in respective meta-analyses subgroups.
+The conventionally cited clinically acceptable agreement between ZHF and comparator devices is 0.5 $^\circ C$ $(ref - most of the studies site this range from Eshragi...)$.
+>It was deemed that outer confidence bounds for 95\% LoA between ECT and ZHF (termed as ‘population limits of agreement’) outside of these bounds would
+
+be clinically unacceptable.
 Sensitivity analysis for the primary meta-analysis was performed based on risk of bias, whereby ‘unclear risk of bias’ was treated as ‘high risk’ and ‘high risk of bias’ studies were excluded from analyses.
-$As clinicians would be interested in the accuracy of$ ZHF relative to temperature monitoring devices they use, and within the clinical setting in which they use it we conducted subgroup analyses according to the comparator device used (eg, core, peripheral, nasopharangeal) and clinical setting (eg, intraoperative, intensuve care unit).
+As clinicians would be interested in the accuracy of ZHF relative to the thermometer devices they use, and within the clinical setting in which they use it we conducted subgroup analyses according to the comparator device used (eg, core, peripheral, nasopharangeal) and clinical setting (eg, intraoperative, intensuve care unit).
 
@@
 
-<!-- Table 1  -->
-<!-- |---|---|---|---|---|---|---|---|---|---|---|---|---| -->
-<!-- |Table 1 Results of meta-analysis of agreement between transcutaneous and arterial carbon dioxide| -->
-<!-- |---|---|---|---|---|---|---|---|---|---|---|---|---| -->
-<!-- |---|Studies|N|n|Bias|SD|tau2|LoA_L|LoA_U|CI_L|CI_U| -->
-<!-- |---|---|---|---|---|---|---|---|---|---|---|---|---| -->
-<!-- |Subset|Stu-content|N-content|n-content|Bias-content|SD-content|tau2-content|LoAL-content|LoAU-content|CIL-content|CIU-content| -->
-<!-- |Subset|Stu-content|N-content|n-content|Bias-content|SD-content|tau2-content|LoAL-content|LoAU-content|CIL-content|CIU-content| -->
+Sixteen studies were eligible for inclusion in this systematic review. 
+>The characteristics of each study are in online supplementary [file 1](link to file 1).
 
-<!-- Table 2 -->
-<!-- |Outcome|Summary accuracy and precision (C)|Participants|Study characteristics|Quality|Implications| -->
-<!-- |---|---|---|---|---|---| -->
-<!-- |Out-content|Sum-content|Par-content|Char-content|Qual-content|Impl-content| -->
-<!-- |Out-content|Sum-content|Par-content|Char-content|Qual-content|Impl-content| -->
-<!-- |Out-content|Sum-content|Par-content|Char-content|Qual-content|Impl-content| -->
-<!-- |Out-content|Sum-content|Par-content|Char-content|Qual-content|Impl-content| -->
+Using these studies, we conducted 6 different meta-analyses.
+The first group compared ZHF to core (eg, arterial, bladder, esophageal, rectal) temperature measurements and included 22 (73%) comparisons from 14 (%) studies, and enrolled 607 participants with 179,821 paired measurements.
+The second group compared ZHF to core temperature measurements in low risk bias studies studies that scored a low risk of bias in all categories) and included 10 (%) comparisons from 5 (%) studies, and enrolled 273 participants with 104,294 paired measurements.
+The third group compared ZHF to core temperature measurements in ICU patients and included 7 (23%) comparisons from 5 (31%) studies, and enrolled 246 participants with 155,598 paired measurements.
+The fourth group compared ZHF to core temperature measurement in intraoperative patients and included 16 (53%) comparisons from  10 (63%) studies, and enrolled 464 participants with 24,223 paired measurements.
+The fifth group compared ZHF to nasopharyngeal temperature measurements and included 4 (13%) comparisons from  4 (25%) studies, and enrolled 297 participants with 109,819 paired measurements.
+The sixth group compared ZHF to sublingual temperature measurement and included 2 (7%) comparisons from  2 (13%) studies, and enrolled 107 participants with 22731 paired measurements.
+The studies included in this systematic review evaluated a ZHF temperature monitoring system manufactured by 3M.
+Previously known as the SpotOn Temperature Monitoring System, the 3M ZHF device is now referred to as the Bair Hugger Temperature Monitoring System.
+All comparisons reported adherence to the ZHF device manufacturer instructions and placed the sensor on the forehead of the participants.
+High risk of bias was associated with patient selection for 13 (43%) comparisons from 9 (56%) studies, conduct of ZHF and comparator measurements in 10(33%) comparisons from 8 (50%) studies and 12 (40%) comparisons 9 (30%) studies, respectively (mostly due to ZHF measurements being taken with knowledge of the comparator measurements and vice versa) and participant flow for 13 (43%) studies.
+In 19 (50%) comparisons from 8 (50%) studies, the authors had declared a conflict of interest or receipt of funding or equipment from the manufacturer of the ZHF device under evaluation.
 
-| test1 | test2 | test3 | test4 | test5 |
-|-------|-------|-------|-------|-------|
-| a     | b     | c     | d     | e     |
-| a     | b     | c     | d     | e     |
-| a     | b     | c     | d     | e     |
+Table 1
+|---|---|---|---|---|---|---|---|---|---|---|---|---|
+|Table 1 Results of meta-analysis of agreement between transcutaneous and arterial carbon dioxide|
+|---|---|---|---|---|---|---|---|---|---|---|---|---|
+|---|Studies|N|n|Bias|SD|tau2|LoA_L|LoA_U|CI_L|CI_U|
+|---|---|---|---|---|---|---|---|---|---|---|---|---|
+|Subset|Stu-content|N-content|n-content|Bias-content|SD-content|tau2-content|LoAL-content|LoAU-content|CIL-content|CIU-content|
+|Subset|Stu-content|N-content|n-content|Bias-content|SD-content|tau2-content|LoAL-content|LoAU-content|CIL-content|CIU-content|
+
+Table 2
+|Outcome|Summary accuracy and precision (C)|Participants|Study characteristics|Quality|Implications|
+|---|---|---|---|---|---|
+|Out-content|Sum-content|Par-content|Char-content|Qual-content|Impl-content|
+|Out-content|Sum-content|Par-content|Char-content|Qual-content|Impl-content|
+|Out-content|Sum-content|Par-content|Char-content|Qual-content|Impl-content|
+|Out-content|Sum-content|Par-content|Char-content|Qual-content|Impl-content|
 

### 2019-08-27 zhf_manuscript/zhf_manuscript.tex
final summer submission of app.R and zhf_manuscript

@@
 tissues\((ref)\). Equipped with a thermal insulator, the ZHF sensor
-eliminates heat loss to the environment
-\((thereby creating an isothermal pathway between the skin surface and underlaying core tissues)\)
-to allow for changes in core temperature to be directly reflected by a
-change in skin surface temperature \((ref)\).
+eliminates heat loss to the environment to allow for changes in core
+temperature to be directly reflected by a change in skin surface
+temperature \((ref)\).
 
@@
 synthesis of the results would aid
-\(clinical decision-making regarding the appropriate circumstances in which ZHF monitoring may be used.\)
+\textbackslash{}\clinical {decision-making regarding the appropriate circumstances in which ZHF monitoring may be used.}
 
@@
 Published studies were found by searching Medline and EMBASE from
-January 2000 to July 2019,
-\(as well as the reference lists of articles identified to be relevant to the review.
-This search strategy is an efficient approach for systematic reviews of diagnostic test accuracy studies [@preston2015improving].
-Unpublished and ongoing studies were located by searching the International Clinical Trials Platform.\)
+January 2000 to July 2019, \textgreater{}as well as the reference lists
+of articles identified to be relevant to the review. This search
+strategy is an efficient approach for systematic reviews of diagnostic
+test accuracy studies (Preston et al. 2015). Unpublished and ongoing
+studies were located by searching the International Clinical Trials
+Platform.
+
 Published conference abstracts were included if there was enough
 information reported to appraise the quality of the study. There were no
-language restrictions applied during the search.
-\(The Cochrane-recommended search strategy combining terms for the ‘target condition’ and ‘index test’ was used [@mann2012should]\).
+language restrictions applied during the search. \textgreater{}The
+Cochrane-recommended search strategy combining terms for the `target
+condition' and `index test' was used (Mann and Gilbody 2012).
+
 The search strategies used for each data base can be located in
@@
 
-\(Information was extracted regarding study characteristics(author, year of publication, country, design, sample size, clinical setting, numbers studied and analyses for each outcome), population characteristics (inclusion and exclusion criteria) and ZHF characteristics (timing and methods of measurements, and methods of calibration).\)
+\begin{quote}
+Information was extracted regarding study characteristics(author, year
+of publication, country, design, sample size, clinical setting, numbers
+studied and analyses for each outcome), population characteristics
+(inclusion and exclusion criteria) and ZHF characteristics (timing and
+methods of measurements, and methods of calibration).
+\end{quote}
+
 The outcomes that were extracted included the mean bias (eg, accuracy)
@@
 and established core temperature measurement tool.
-\(Information was extracted about how repeated measurements were handled: (1) analysed each pair of data separately; (2) treated each pair of data as independent; or (3) used either analysis of variance or a random effects model as a way to control for the dependent nature of the repeated measures data [@myles2007using].\)
+\textgreater{}Information was extracted about how repeated measurements
+were handled: (1) analysed each pair of data separately; (2) treated
+each pair of data as independent; or (3) used either analysis of
+variance or a random effects model as a way to control for the dependent
+nature of the repeated measures data (Myles and Cui 2007).
 
@@
 (QUADAS-2), each reviewer independently assessed the risk of bias for
-the included studies (Whiting et al. 2011).
-\(Reviewers used guiding questions to rate the risk of bias for patient selection\),
+the included studies (Whiting et al. 2011). \textgreater{}Reviewers used
+guiding questions to rate the risk of bias for patient selection,
+
 conduct of the ZHF measurements, conduct of the established core
@@
 as an international clinical trial registry (Glasziou et al. 2001).
-\(Statistical analyses to detect reporting bias were not conducted due to lack of validated methods [@begg2005systematic].
-Although some meta-analyses of method comparison studies have used tests for detecting funnel plot asymmetry [@niven2015accuracy], simulations have revealed that such tests will result in publication bias being incorrectly identified too often [@deeks2005performance]\).
+\textgreater{}Statistical analyses to detect reporting bias were not
+conducted due to lack of validated methods (Begg 2005). Although some
+meta-analyses of method comparison studies have used tests for detecting
+funnel plot asymmetry (Niven et al. 2015), simulations have revealed
+that such tests will result in publication bias being incorrectly
+identified too often (Deeks, Macaskill, and Irwig 2005).
+
 In order to rate the quality of evidence, we applied the Grading Quality
@@
 The objective
-\(for the meta-analysis was to estimate the population limits of agreement between\)
+\textgreater{}\(for the meta-analysis was to estimate the population limits of agreement between\)
+
 temperature measurements by the ZHF sensor and established core
-temperature measurement tools.
-\(The framework for meta-analysis of Bland-Altman method comparison studies based on limits of agreement (LoA) approach was used [@tipton2017framework]\).
+temperature measurement tools. \textgreater{}The framework for
+meta-analysis of Bland-Altman method comparison studies based on limits
+of agreement (LoA) approach was used (Tipton and Shuster 2017).
+
 This method was selected because it parallels the approach used in
@@
 meta-analyses of Bland-Altman studies (Tipton and Shuster 2017). In
-these instances, \$the pooled LoAs are calculated using
+these instances, \textgreater{}the pooled LoAs are calculated using
 \(\delta\pm2\sqrt{\sigma2+\tau2}\), where \(\delta\) is the average bias
 across studies, \(\sigma2\) is the average within-study variation in
-differences and \(\tau2\) is the variation in bias across studies.\$
+differences and \(\tau2\) is the variation in bias across studies.
+
 Estimations of \(\delta\) and \(\sigma2\) were made using a weighted
@@
 2010; Tanner-Smith, Tipton, and Polanin 2016; Tipton 2015). We used the
-\$method-of-moments estimator from ref 16 for the \(\tau2\) parameter\$.
+\textgreater{}method-of-moments estimator from ref 16 for the \(\tau2\)
+parameter.
+
 In accordance with ref 12, (1) measures of uncertainty were included
-\$when interpreting the LoA estimates by calculating the outer \(95\%\)
-CIs for pooled LoA\$; and (2) repeated measurements were adjusted if
-improperly adjusted for in
-\(individual studies (by using weights proportional to the number of samples, not the total number of measurements)\).
+\textgreater{}when interpreting the LoA estimates by calculating the
+outer \(95\%\) CIs for pooled LoA;
+
+and (2) repeated measurements were adjusted if improperly adjusted for
+in \textgreater{}individual studies (by using weights proportional to
+the number of samples, not the total number of measurements).
+
 The formulas for the above calculations from ref 12 can be found in
-\href{}{file 1}. The R statistical program was use to conduct all
+\href{}{file 1}. The R statistical program was used to conduct all
 analyses (Team 2017). All data and R code (provided in ref 12) used in
@@
 reported for two separate groups of participants, so these were treated
-in the meta-analyses as separate `studies'.
-\(Other studies reported separate results for analyses conducted using different TcCO2 device types or sensor locations performed on the same patients.
-Only the result with the largest number of paired measurements between PaCO2 and TcCO2 was selected for inclusion in the main analysis, with others included in subgroup meta-analyses where appropriate.
-For the studies that reported results for patients while receiving both two-lung and one-lung ventilation during thoracic surgery, we used the result for two-lung ventilation in the main analysis.
-The conventionally cited clinically acceptable agreement between\)
-ECT and ZHF sensors is 0.5 \(^\circ C\)(ref). \$It was deemed that outer
-confidence bounds for \(95\%\) LoA between ECT and ZHF (termed as
-`population limits of agreement') outside of these bounds would\$ be
-clinically unacceptable. Sensitivity analysis for the primary
+in the meta-analyses as separate `studies'. \textgreater{}Other studies
+reported separate results for analyses conducted using different TcCO2
+device types or sensor locations performed on the same patients. Only
+the result with the largest number of paired measurements between PaCO2
+and TcCO2 was selected for inclusion in the main analysis, with others
+included in subgroup meta-analyses where appropriate. For the studies
+that reported results for patients while receiving both two-lung and
+one-lung ventilation during thoracic surgery, we used the result for
+two-lung ventilation in the main analysis. The conventionally cited
+clinically acceptable agreement between
+
+ECT and ZHF sensors is 0.5 \(^\circ C\)(ref).
+\textgreater{}\(It was deemed that outer confidence bounds for 95\% LoA between ECT and ZHF (termed as ‘population limits of agreement’) outside of these bounds would\)
+
+be clinically unacceptable. Sensitivity analysis for the primary
 meta-analysis was performed based on risk of bias, whereby `unclear risk
 of bias' was treated as `high risk' and `high risk of bias' studies were
-excluded from analyses.
-\(As clinicians would be interested in the accuracy of\) ZHF relative to
-temperature monitoring devices they use, and within the clinical setting
-in which they use it we conducted subgroup analyses according to the
-comparator device used (eg, core, peripheral, nasopharangeal) and
+excluded from analyses. \textgreater{}As clinicians would be interested
+in the accuracy of
+
+ZHF relative to thermometer devices they use, and within the clinical
+setting in which they use it we conducted subgroup analyses according to
+the comparator device used (eg, core, peripheral, nasopharangeal) and
 clinical setting (eg, intraoperative, intensuve care unit).
@@
 
-\begin{longtable}[]{@{}lllll@{}}
-\toprule
-test1 & test2 & test3 & test4 & test5\tabularnewline
-\midrule
-\endhead
-a & b & c & d & e\tabularnewline
-a & b & c & d & e\tabularnewline
-a & b & c & d & e\tabularnewline
-\bottomrule
-\end{longtable}
+Sixteen studies were eligible for inclusion in this systematic review.
+\textgreater{}The characteristics of each study are in online
+supplementary \href{link\%20to\%20file\%201}{file 1}.
+
+Using these studies, we conducted 6 different meta-analyses. The first
+group compared ZHF to core (eg, arterial, bladder, esophageal, rectal)
+temperature measurements and included 22 (73\%) comparisons from 14 (\%)
+studies, and enrolled 607 participants with 179,821 paired measurements.
+\textgreater{}The second group compared ZHF to core temperature
+measurements in low risk bias studies studies that scored a low risk of
+bias in all categories) and included 10 (\%) comparisons from 5 (\%)
+studies, and enrolled 273 participants with 104,294 paired measurements.
+
+The third group compared ZHF to core temperature measurements in ICU
+patients and included 7 (23\%) comparisons from 5 (31\%) studies, and
+enrolled 246 participants with 155,598 paired measurements. The fourth
+group compared ZHF to core temperature measurement in intraoperative
+patients and included 16 (53\%) comparisons from 10 (63\%) studies, and
+enrolled 464 participants with 24,223 paired measurements. The fifth
+group compared ZHF to nasopharyngeal temperature measurements and
+included 4 (13\%) comparisons from 4 (25\%) studies, and enrolled 297
+participants with 109,819 paired measurements. The sixth group compared
+ZHF to sublingual temperature measurement and included 2 (7\%)
+comparisons from 2 (13\%) studies, and enrolled 107 participants with
+22731 paired measurements. The studies included in this systematic
+review evaluated a ZHF temperature monitoring system manufactured by 3M.
+Previously known as the SpotOn Temperature Monitoring System, the 3M ZHF
+device is now referred to as the Bair Hugger Temperature Monitoring
+System. All comparisons reported adherence to the ZHF device
+manufacturer instructions and placed the sensor on the forehead of the
+participants. High risk of bias was associated with patient selection
+for 13 (43\%) comparisons from 9 (56\%) studies, conduct of ZHF and
+comparator measurements in 10(33\%) comparisons from 8 (50\%) studies
+and 12 (40\%) comparisons 9 (30\%) studies, respectively (mostly due to
+ZHF measurements being taken with knowledge of the comparator
+measurements and vice versa) and participant flow for 13 (43\%) studies.
+In 19 (50\%) comparisons from 8 (50\%) studies, the authors had declared
+a conflict of interest or receipt of funding or equipment from the
+manufacturer of the ZHF device under evaluation.
+
+Table 1
+\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}
+\textbar{}Table 1 Results of meta-analysis of agreement between
+transcutaneous and arterial carbon dioxide\textbar{}
+\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}
+\textbar{}---\textbar{}Studies\textbar{}N\textbar{}n\textbar{}Bias\textbar{}SD\textbar{}tau2\textbar{}LoA\_L\textbar{}LoA\_U\textbar{}CI\_L\textbar{}CI\_U\textbar{}
+\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}
+\textbar{}Subset\textbar{}Stu-content\textbar{}N-content\textbar{}n-content\textbar{}Bias-content\textbar{}SD-content\textbar{}tau2-content\textbar{}LoAL-content\textbar{}LoAU-content\textbar{}CIL-content\textbar{}CIU-content\textbar{}
+\textbar{}Subset\textbar{}Stu-content\textbar{}N-content\textbar{}n-content\textbar{}Bias-content\textbar{}SD-content\textbar{}tau2-content\textbar{}LoAL-content\textbar{}LoAU-content\textbar{}CIL-content\textbar{}CIU-content\textbar{}
+
+Table 2 \textbar{}Outcome\textbar{}Summary accuracy and precision
+(C)\textbar{}Participants\textbar{}Study
+characteristics\textbar{}Quality\textbar{}Implications\textbar{}
+\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}
+\textbar{}Out-content\textbar{}Sum-content\textbar{}Par-content\textbar{}Char-content\textbar{}Qual-content\textbar{}Impl-content\textbar{}
+\textbar{}Out-content\textbar{}Sum-content\textbar{}Par-content\textbar{}Char-content\textbar{}Qual-content\textbar{}Impl-content\textbar{}
+\textbar{}Out-content\textbar{}Sum-content\textbar{}Par-content\textbar{}Char-content\textbar{}Qual-content\textbar{}Impl-content\textbar{}
+\textbar{}Out-content\textbar{}Sum-content\textbar{}Par-content\textbar{}Char-content\textbar{}Qual-content\textbar{}Impl-content\textbar{}
+
+Table 3 \textbar{} test1 \textbar{} test2 \textbar{} test3 \textbar{}
+test4 \textbar{} test5 \textbar{}
+\textbar{}-------\textbar{}-------\textbar{}-------\textbar{}-------\textbar{}-------\textbar{}
+\textbar{} a \textbar{} b \textbar{} c \textbar{} d \textbar{} e
+\textbar{} \textbar{} a \textbar{} b \textbar{} c \textbar{} d
+\textbar{} e \textbar{} \textbar{} a \textbar{} b \textbar{} c
+\textbar{} d \textbar{} e \textbar{}
+
+\# simple table creation here \textbar{} Tables \textbar{} Are
+\textbar{} Cool \textbar{}
+\textbar{}---------------\textbar{}:-------------:\textbar{}------:\textbar{}
+\textbar{} col 3 is \textbar{} right-aligned \textbar{} \$1600
+\textbar{} \textbar{} col 2 is \textbar{} centered \textbar{} \$12
+\textbar{} \textbar{} zebra stripes \textbar{} are neat \textbar{} \$1
+\textbar{}
 
@@
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-begg2005systematic}{}%
+Begg, Colin B. 2005. ``Systematic Reviews of Diagnostic Accuracy Studies
+Require Study by Study Examination: First for Heterogeneity, and Then
+for Sources of Heterogeneity.'' \emph{Journal of Clinical Epidemiology}
+58 (9). Elsevier Limited: 865.
+
+\leavevmode\hypertarget{ref-deeks2005performance}{}%
+Deeks, Jonathan J, Petra Macaskill, and Les Irwig. 2005. ``The
+Performance of Tests of Publication Bias and Other Sample Size Effects
+in Systematic Reviews of Diagnostic Test Accuracy Was Assessed.''
+\emph{Journal of Clinical Epidemiology} 58 (9). Elsevier: 882--93.
+
 \leavevmode\hypertarget{ref-frank1997perioperative}{}%
@@
 
+\leavevmode\hypertarget{ref-mann2012should}{}%
+Mann, Rachel, and Simon M Gilbody. 2012. ``Should Methodological Filters
+for Diagnostic Test Accuracy Studies Be Used in Systematic Reviews of
+Psychometric Instruments? A Case Study Involving Screening for Postnatal
+Depression.'' \emph{Systematic Reviews} 1 (1). BioMed Central: 9.
+
 \leavevmode\hypertarget{ref-michelson1994reversible}{}%
@@
 \emph{Thrombosis and Haemostasis} 72 (05). Schattauer GmbH: 633--40.
+
+\leavevmode\hypertarget{ref-myles2007using}{}%
+Myles, PS, and James Cui. 2007. ``I. Using the Bland--Altman Method to
+Measure Agreement with Repeated Measures.'' Oxford University Press.
+
+\leavevmode\hypertarget{ref-niven2015accuracy}{}%
+Niven, Daniel J, Jonathan E Gaudet, Kevin B Laupland, Kelly J Mrklas,
+Derek J Roberts, and Henry Thomas Stelfox. 2015. ``Accuracy of
+Peripheral Thermometers for Estimating Temperature: A Systematic Review
+and Meta-Analysis.'' \emph{Annals of Internal Medicine} 163 (10).
+American College of Physicians: 768--77.
+
+\leavevmode\hypertarget{ref-preston2015improving}{}%
+Preston, Louise, Christopher Carroll, Paolo Gardois, Suzy Paisley, and
+Eva Kaltenthaler. 2015. ``Improving Search Efficiency for Systematic
+Reviews of Diagnostic Test Accuracy: An Exploratory Study to Assess the
+Viability of Limiting to Medline, Embase and Reference Checking.''
+\emph{Systematic Reviews} 4 (1). BioMed Central: 82.
 

### 2019-08-27 app.R

@@ -1,13 +1,23 @@
+
 library(shiny)
+library(shinydashboard)
+library(shinydashboardPlus)
 library(tidyverse)
 library(ggplot2)
 library(DT)
 
+# Manuscript screenshot resolution ----
+# resolution to be set to 600 DP for springer articles
+# screenshot image and open in preview, then go to tools > adjust size... 
+# 1. enter new desired resolution 
+# 2. check box for 'resample image' to ensure new image is created with additional pixels
+# note that this will new image retains the same dimensions as original picture but has extra pixels
 
 
 # Load data ----
 
 data <- readxl::read_xlsx("zhf_extracted.xlsx")
+sum_findings <- readxl::read_xlsx("sum_findings.xlsx")
 
 # Functions for calculating the Bland-Altman meta-analysis ----
 
@@ -73,38 +83,42 @@ data <- data %>%
 
 data <- data %>% 
   mutate(V_logs2 = 2/(n-1))
-  
+
 data_NPA <- data %>% 
   filter(comparison == "NPA")
 
 data_SL <- data %>% 
   filter(comparison == "Sublingual")
 
-data_core <- data %>% 
-  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac")
+data_core <- data %>% #eshragi overall
+  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
+  filter(comments != "Intraoperative, off cardiopulmonary bypass" & comments != "Postoperative")
 
-data_core_lowrisk <- data_core %>% 
-  filter((RoB_selection == "low" & RoB_spoton == "low" & RoB_comparator == "low" & RoB_flow =="low") & clinical_setting != "Intra- and Postoperative")
+data_core_lowrisk <- data_core %>% #eshragi overall
+  filter(RoB_selection == "low" & RoB_spoton == "low" & RoB_comparator == "low" & RoB_flow =="low")
 
-data_core_op <- data_core %>% 
-  filter(clinical_setting=="Intraoperative")
+data_core_op <- data%>% #eshragi intraop
+  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
[…]

### 2019-08-27 dashboard_app.R

@@ -1,518 +1,0 @@
-
-library(shiny)
-library(shinydashboard)
-library(shinydashboardPlus)
-library(tidyverse)
-library(ggplot2)
-library(DT)
-
-# Load data ----
-
-data <- readxl::read_xlsx("zhf_extracted.xlsx")
-sum_findings <- readxl::read_xlsx("sum_findings.xlsx")
-
-
-# Functions for calculating the Bland-Altman meta-analysis ----
-
-meta <-  function(Te,V_T){
-  m <- length(Te)
-  wt_FE=1/V_T
-  T_FE <- sum(Te*wt_FE)/sum(wt_FE)
-  Q <- sum(wt_FE*(Te - T_FE)^2)
-  S1 <- sum(wt_FE)
-  S2 <- sum(wt_FE^2)
-  o2 <- (Q - (m - 1))/(S1 - S2/S1)
-  wt_RE <- 1/(V_T + o2)
-  T_RE <- sum(Te*wt_RE)/sum(wt_RE)
-  V_T_RE_mod <- 1/sum(wt_RE)
-  V_T_RE_rve <- (m/(m-1))*sum(wt_RE^2*(Te - T_RE)^2)/(sum(wt_RE))^2
-  c(m,T_RE,o2,V_T_RE_mod, V_T_RE_rve)
-}
-loa_maker <- function(bias,V_bias,logs2,V_logs2) {
-  bias_row=meta(bias, V_bias)
-  logs2_row=meta(logs2, V_logs2)
-  bias_mean <- bias_row[2]
-  sd2_est <- exp(logs2_row[2])
-  tau_est <- bias_row[3]
-  LOA_L <- bias_mean - 2*sqrt(sd2_est + tau_est)
-  LOA_U <- bias_mean + 2*sqrt(sd2_est + tau_est)
-  m <- bias_row[1]
-  tcrit <- qt(1-.05/2,m-1)
-  B1 <- sd2_est^2/(sd2_est + tau_est)
-  B2 <- tau_est^2/(sd2_est + tau_est)
-  wt <- 1/V_bias
-  S1 <- sum(wt)
-  S2 <- sum(wt^2)
-  S3 <- sum(wt^3)
-  A0 <- 2*(m-1)/(S1-S2/S1)^2
-  A1 <- 4/(S1 - S2/S1)
-  A2 <- 2*(S2-2*S3/S1+S2^2/S1^2)/(S1-S2/S1)^2
[…]

### 2019-08-29 zhf_manuscript/zhf_manuscript.Rmd
prisma diagram

@@
 
-Sixteen studies were eligible for inclusion in this systematic review. 
+Sixteen studies were eligible for inclusion in this systematic review (Figure 1).
+
+```{r echo=FALSE, fig.height=4.5}
+knitr::include_graphics("figure_one.png")
+```
+
 >The characteristics of each study are in online supplementary [file 1](link to file 1).
@@
 
-Table 1
-|---|---|---|---|---|---|---|---|---|---|---|---|---|
-|Table 1 Results of meta-analysis of agreement between transcutaneous and arterial carbon dioxide|
-|---|---|---|---|---|---|---|---|---|---|---|---|---|
-|---|Studies|N|n|Bias|SD|tau2|LoA_L|LoA_U|CI_L|CI_U|
-|---|---|---|---|---|---|---|---|---|---|---|---|---|
-|Subset|Stu-content|N-content|n-content|Bias-content|SD-content|tau2-content|LoAL-content|LoAU-content|CIL-content|CIU-content|
-|Subset|Stu-content|N-content|n-content|Bias-content|SD-content|tau2-content|LoAL-content|LoAU-content|CIL-content|CIU-content|
-
-Table 2
-|Outcome|Summary accuracy and precision (C)|Participants|Study characteristics|Quality|Implications|
-|---|---|---|---|---|---|
-|Out-content|Sum-content|Par-content|Char-content|Qual-content|Impl-content|
-|Out-content|Sum-content|Par-content|Char-content|Qual-content|Impl-content|
-|Out-content|Sum-content|Par-content|Char-content|Qual-content|Impl-content|
-|Out-content|Sum-content|Par-content|Char-content|Qual-content|Impl-content|
-
 ## Study selection and description

### 2019-08-29 zhf_manuscript/zhf_manuscript.tex
prisma diagram

@@
 Core temperature monitoring is an important intervention within
-perioperative and intensive care settings\((ref)\). Thermoregulatory
-dysfunction is commonly associated with the induction of anesthesia and
-can lead to adverse outcomes including cardiac dysrhythmias, altered
-hemostasis and increased risk of surgical site infection (Frank et al.
-1997; Kurz, Sessler, and Lenhardt 1996; Michelson et al. 1994; Rohrer
-and Natale 1992). The pulmonary artery catheter is the reference
-standard for continuous core temperature monitoring\((ref)\), however,
-the invasive nature of this method renders an increased risk of
+perioperative and intensive care settings. Thermoregulatory dysfunction
+is commonly associated with the induction of anesthesia and can lead to
+adverse outcomes including cardiac dysrhythmias, altered hemostasis and
+increased risk of surgical site infection (Frank et al. 1997; Kurz,
+Sessler, and Lenhardt 1996; Michelson et al. 1994; Rohrer and Natale
+1992). The pulmonary artery catheter is the reference standard for
+continuous core temperature
+monitoring\((ref - trouble finding a statement regarding this in the literature)\),
+however, the invasive nature of this method renders an increased risk of
 bloodstream infections and damage to surrounding tissue(Hadian and
 Pinsky 2006). Although clinically accurate relative to pulmonary artery
-thermometry, surrogate measures of core temperature via esophageal,
-rectal, and bladder sites remain mildly invasive interventions\((ref)\).
+temperature measurements, surrogate measures of core temperature at
+esophageal, rectal, and bladder locations remain mildly invasive
+interventions\((ref)\).
 
@@
 
-The agreement between ZHF and established core temperature measures has
+The agreement between ZHF and established core temperature devices has
 been investigated in several studies conducted within the clinical
 setting, each with varied results. Appraisal of these studies and
-synthesis of the results would aid
-\textbackslash{}\clinical {decision-making regarding the appropriate circumstances in which ZHF monitoring may be used.}
+synthesis of the results would aid clinicians in deciding the
+appropriate circumstances in which ZHF may be used.
 
-We aimed to determine if the ZHF sensor has clinically acceptable
-accuracy and precision compared with established core temperature tools.
-Accuracy is defined as the average difference between the ZHF sensor and
-established core temperature instrument and precisions as the variance
-(typically reported as the SD) in the differences.
+We aimed to determine if ZHF has clinically acceptable accuracy and
+precision relative to established core temperature measurement devices.
+Accuracy is defined as the average difference between temperature
+measurements from the ZHF and comparator device and precisions as the
+variance (typically reported as the SD) in the differences.
 
@@
 The selection of studies was undertaken by two independent reviewers.
-Studies were included if reported measures from a ZHF sensor and another
-established core temperature tool coincided. Studies involving a case
-control design were excluded due to potential for overestimation of the
-intervention performance. Studies were excluded if conducted on
-non-human subjects or outside of a clinical healthcare setting. Studies
-were excluded if conducted earlier than the year 2000 as prior studies
-evaluated outdated technology that is no longer relevant to current
-clinical practice.
+Studies were included if reported measures from a ZHF and comparator
+device coincided. Studies involving a case control design were excluded
+due to potential for overestimation of the intervention performance.
+Studies were excluded if conducted on non-human subjects or outside of a
+clinical healthcare setting. Studies were excluded if conducted earlier
+than the year 2000 as prior studies evaluated outdated technology that
+is no longer relevant to current clinical practice.
 
@@
 
-\begin{quote}
-Information was extracted regarding study characteristics(author, year
+Information was extracted regarding study characteristics (author, year
 of publication, country, design, sample size, clinical setting, numbers
 studied and analyses for each outcome), population characteristics
-(inclusion and exclusion criteria) and ZHF characteristics (timing and
-methods of measurements, and methods of calibration).
-\end{quote}
-
-The outcomes that were extracted included the mean bias (eg, accuracy)
-and variance (eg, SD, precision) in temperature between the ZHF sensor
-and established core temperature measurement tool.
-\textgreater{}Information was extracted about how repeated measurements
-were handled: (1) analysed each pair of data separately; (2) treated
-each pair of data as independent; or (3) used either analysis of
-variance or a random effects model as a way to control for the dependent
-nature of the repeated measures data (Myles and Cui 2007).
+(inclusion and exclusion criteria) and ZHF characteristics (placement of
+sensor, timing and methods of measurements). The outcomes that were
+extracted included the mean bias (eg, accuracy) and variance (eg, SD,
+precision) in temperature measurement between the ZHF sensor and
+comparator device. \textgreater{}Information was extracted about how
+repeated measurements were handled: (1) analysed each pair of data
+separately; (2) treated each pair of data as independent; or (3) used
+either analysis of variance or a random effects model as a way to
+control for the dependent nature of the repeated measures data (Myles
+and Cui 2007).
 
@@
 (QUADAS-2), each reviewer independently assessed the risk of bias for
-the included studies (Whiting et al. 2011). \textgreater{}Reviewers used
-guiding questions to rate the risk of bias for patient selection,
-
-conduct of the ZHF measurements, conduct of the established core
-temperature measurement tools, and timing and flow (eg, timing of ZHF
-and established core temperature measurements, dropouts) as ``high'',
-``low'' or ``unclear''. We worked to minimize the risk of publication
-bias by conducting a comprehensive search of multiple databases as well
-as an international clinical trial registry (Glasziou et al. 2001).
-\textgreater{}Statistical analyses to detect reporting bias were not
-conducted due to lack of validated methods (Begg 2005). Although some
-meta-analyses of method comparison studies have used tests for detecting
-funnel plot asymmetry (Niven et al. 2015), simulations have revealed
-that such tests will result in publication bias being incorrectly
-identified too often (Deeks, Macaskill, and Irwig 2005).
+the included studies (Whiting et al. 2011). Using guiding questions,
+reviewers rated the risk of bias for patient selection, conduct of the
+ZHF measurements, conduct of the comparator device measurements, and
+timing and flow (eg, timing of ZHF and established core temperature
+measurements, dropouts) as ``high'', ``low'' or ``unclear''. We worked
+to minimize the risk of publication bias by conducting a comprehensive
+search of multiple databases as well as an international clinical trial
+registry (Glasziou et al. 2001). \textgreater{}Statistical analyses to
+detect reporting bias were not conducted due to lack of validated
+methods (Begg 2005). Although some meta-analyses of method comparison
+studies have used tests for detecting funnel plot asymmetry (Niven et
+al. 2015), simulations have revealed that such tests will result in
+publication bias being incorrectly identified too often (Deeks,
+Macaskill, and Irwig 2005).
 
@@
 
-The objective
-\textgreater{}\(for the meta-analysis was to estimate the population limits of agreement between\)
-
-temperature measurements by the ZHF sensor and established core
-temperature measurement tools. \textgreater{}The framework for
+The objective for the meta-analysis was to estimate the population
+limits of agreement between temperature measurements from the ZHF and
+established comparator devices. \textgreater{}The framework for
 meta-analysis of Bland-Altman method comparison studies based on limits
@@
 in \textgreater{}individual studies (by using weights proportional to
-the number of samples, not the total number of measurements).
+the number of participants, not the total number of measurements).
 
@@
 Prior to conducting the meta-analyses, the results from each study were
-converted into a standard format, with bias meaning \(ECT - ZHF\)
-measured in \(^\circ C\). In two of the studies, the results were
-reported for two separate groups of participants, so these were treated
-in the meta-analyses as separate `studies'. \textgreater{}Other studies
-reported separate results for analyses conducted using different TcCO2
-device types or sensor locations performed on the same patients. Only
-the result with the largest number of paired measurements between PaCO2
-and TcCO2 was selected for inclusion in the main analysis, with others
-included in subgroup meta-analyses where appropriate. For the studies
-that reported results for patients while receiving both two-lung and
-one-lung ventilation during thoracic surgery, we used the result for
-two-lung ventilation in the main analysis. The conventionally cited
-clinically acceptable agreement between
-
-ECT and ZHF sensors is 0.5 \(^\circ C\)(ref).
-\textgreater{}\(It was deemed that outer confidence bounds for 95\% LoA between ECT and ZHF (termed as ‘population limits of agreement’) outside of these bounds would\)
+converted into a standard format, with bias meaning \(comparator-ZHF\)
+measured in \(^\circ C\). In several studies, results were reported for
+multiple groups of participants, therefore in the meta-analysis each of
+these groups was treated as a separate `comparison'. Other studies
+reported multiple sets of results, whereby analyses were conducted
+between ZHF and various comparator devices used on the same participant.
+These instances were also treated as a separate `comparison' if the
+comparator devices were apart of separate meta-analyses groups. One
+study reported intraoperative, postoperative and overall results for the
+same participants. Only the paired measurements from the overall results
+were included in the main and low risk bias analyses, leaving paired
+measurements exclusively from the intraoperative and postoperative
+timepoints to be included in respective meta-analyses subgroups. The
+conventionally cited clinically acceptable agreement between ZHF and
+comparator devices is 0.5 \(^\circ C\)
+\((ref - most of the studies site this range from Eshragi...)\).
+\textgreater{}It was deemed that outer confidence bounds for 95\% LoA
+between ECT and ZHF (termed as `population limits of agreement') outside
+of these bounds would
 
@@
 of bias' was treated as `high risk' and `high risk of bias' studies were
-excluded from analyses. \textgreater{}As clinicians would be interested
-in the accuracy of
-
-ZHF relative to thermometer devices they use, and within the clinical
-setting in which they use it we conducted subgroup analyses according to
-the comparator device used (eg, core, peripheral, nasopharangeal) and
-clinical setting (eg, intraoperative, intensuve care unit).
+excluded from analyses. As clinicians would be interested in the
+accuracy of ZHF relative to the thermometer devices they use, and within
+the clinical setting in which they use it we conducted subgroup analyses
+according to the comparator device used (eg, core, peripheral,
+nasopharangeal) and clinical setting (eg, intraoperative, intensuve care
+unit).
 
@@
 
-Sixteen studies were eligible for inclusion in this systematic review.
-\textgreater{}The characteristics of each study are in online
-supplementary \href{link\%20to\%20file\%201}{file 1}.
+Sixteen studies were eligible for inclusion in this systematic review
+(Figure 1).
+
+\includegraphics[width=53.08in]{figure_one}
+
+\begin{quote}
+The characteristics of each study are in online supplementary
+\href{link\%20to\%20file\%201}{file 1}.
+\end{quote}
 
@@
 studies, and enrolled 607 participants with 179,821 paired measurements.
-\textgreater{}The second group compared ZHF to core temperature
-measurements in low risk bias studies studies that scored a low risk of
-bias in all categories) and included 10 (\%) comparisons from 5 (\%)
-studies, and enrolled 273 participants with 104,294 paired measurements.
-
-The third group compared ZHF to core temperature measurements in ICU
-patients and included 7 (23\%) comparisons from 5 (31\%) studies, and
-enrolled 246 participants with 155,598 paired measurements. The fourth
-group compared ZHF to core temperature measurement in intraoperative
-patients and included 16 (53\%) comparisons from 10 (63\%) studies, and
-enrolled 464 participants with 24,223 paired measurements. The fifth
-group compared ZHF to nasopharyngeal temperature measurements and
-included 4 (13\%) comparisons from 4 (25\%) studies, and enrolled 297
-participants with 109,819 paired measurements. The sixth group compared
-ZHF to sublingual temperature measurement and included 2 (7\%)
-comparisons from 2 (13\%) studies, and enrolled 107 participants with
-22731 paired measurements. The studies included in this systematic
-review evaluated a ZHF temperature monitoring system manufactured by 3M.
-Previously known as the SpotOn Temperature Monitoring System, the 3M ZHF
-device is now referred to as the Bair Hugger Temperature Monitoring
-System. All comparisons reported adherence to the ZHF device
-manufacturer instructions and placed the sensor on the forehead of the
-participants. High risk of bias was associated with patient selection
-for 13 (43\%) comparisons from 9 (56\%) studies, conduct of ZHF and
-comparator measurements in 10(33\%) comparisons from 8 (50\%) studies
-and 12 (40\%) comparisons 9 (30\%) studies, respectively (mostly due to
-ZHF measurements being taken with knowledge of the comparator
-measurements and vice versa) and participant flow for 13 (43\%) studies.
-In 19 (50\%) comparisons from 8 (50\%) studies, the authors had declared
-a conflict of interest or receipt of funding or equipment from the
-manufacturer of the ZHF device under evaluation.
-
-Table 1
-\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}
-\textbar{}Table 1 Results of meta-analysis of agreement between
-transcutaneous and arterial carbon dioxide\textbar{}
-\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}
-\textbar{}---\textbar{}Studies\textbar{}N\textbar{}n\textbar{}Bias\textbar{}SD\textbar{}tau2\textbar{}LoA\_L\textbar{}LoA\_U\textbar{}CI\_L\textbar{}CI\_U\textbar{}
-\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}
-\textbar{}Subset\textbar{}Stu-content\textbar{}N-content\textbar{}n-content\textbar{}Bias-content\textbar{}SD-content\textbar{}tau2-content\textbar{}LoAL-content\textbar{}LoAU-content\textbar{}CIL-content\textbar{}CIU-content\textbar{}
-\textbar{}Subset\textbar{}Stu-content\textbar{}N-content\textbar{}n-content\textbar{}Bias-content\textbar{}SD-content\textbar{}tau2-content\textbar{}LoAL-content\textbar{}LoAU-content\textbar{}CIL-content\textbar{}CIU-content\textbar{}
-
-Table 2 \textbar{}Outcome\textbar{}Summary accuracy and precision
-(C)\textbar{}Participants\textbar{}Study
-characteristics\textbar{}Quality\textbar{}Implications\textbar{}
-\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}---\textbar{}
-\textbar{}Out-content\textbar{}Sum-content\textbar{}Par-content\textbar{}Char-content\textbar{}Qual-content\textbar{}Impl-content\textbar{}
-\textbar{}Out-content\textbar{}Sum-content\textbar{}Par-content\textbar{}Char-content\textbar{}Qual-content\textbar{}Impl-content\textbar{}
-\textbar{}Out-content\textbar{}Sum-content\textbar{}Par-content\textbar{}Char-content\textbar{}Qual-content\textbar{}Impl-content\textbar{}
-\textbar{}Out-content\textbar{}Sum-content\textbar{}Par-content\textbar{}Char-content\textbar{}Qual-content\textbar{}Impl-content\textbar{}
-
-Table 3 \textbar{} test1 \textbar{} test2 \textbar{} test3 \textbar{}
-test4 \textbar{} test5 \textbar{}
-\textbar{}-------\textbar{}-------\textbar{}-------\textbar{}-------\textbar{}-------\textbar{}
-\textbar{} a \textbar{} b \textbar{} c \textbar{} d \textbar{} e
-\textbar{} \textbar{} a \textbar{} b \textbar{} c \textbar{} d
-\textbar{} e \textbar{} \textbar{} a \textbar{} b \textbar{} c
-\textbar{} d \textbar{} e \textbar{}
-
-\# simple table creation here \textbar{} Tables \textbar{} Are
-\textbar{} Cool \textbar{}
-\textbar{}---------------\textbar{}:-------------:\textbar{}------:\textbar{}
-\textbar{} col 3 is \textbar{} right-aligned \textbar{} \$1600
-\textbar{} \textbar{} col 2 is \textbar{} centered \textbar{} \$12
-\textbar{} \textbar{} zebra stripes \textbar{} are neat \textbar{} \$1
-\textbar{}
+The second group compared ZHF to core temperature measurements in low
+risk bias studies studies that scored a low risk of bias in all
+categories) and included 10 (\%) comparisons from 5 (\%) studies, and
+enrolled 273 participants with 104,294 paired measurements. The third
+group compared ZHF to core temperature measurements in ICU patients and
+included 7 (23\%) comparisons from 5 (31\%) studies, and enrolled 246
+participants with 155,598 paired measurements. The fourth group compared
+ZHF to core temperature measurement in intraoperative patients and
+included 16 (53\%) comparisons from 10 (63\%) studies, and enrolled 464
+participants with 24,223 paired measurements. The fifth group compared
+ZHF to nasopharyngeal temperature measurements and included 4 (13\%)
+comparisons from 4 (25\%) studies, and enrolled 297 participants with
+109,819 paired measurements. The sixth group compared ZHF to sublingual
+temperature measurement and included 2 (7\%) comparisons from 2 (13\%)
+studies, and enrolled 107 participants with 22731 paired measurements.
+The studies included in this systematic review evaluated a ZHF
+temperature monitoring system manufactured by 3M. Previously known as
+the SpotOn Temperature Monitoring System, the 3M ZHF device is now
+referred to as the Bair Hugger Temperature Monitoring System. All
+comparisons reported adherence to the ZHF device manufacturer
+instructions and placed the sensor on the forehead of the participants.
+High risk of bias was associated with patient selection for 13 (43\%)
+comparisons from 9 (56\%) studies, conduct of ZHF and comparator
+measurements in 10(33\%) comparisons from 8 (50\%) studies and 12 (40\%)
+comparisons 9 (30\%) studies, respectively (mostly due to ZHF
+measurements being taken with knowledge of the comparator measurements
+and vice versa) and participant flow for 13 (43\%) studies. In 19 (50\%)
+comparisons from 8 (50\%) studies, the authors had declared a conflict
+of interest or receipt of funding or equipment from the manufacturer of
+the ZHF device under evaluation.
 

### 2019-08-29 zhf_manuscript/prisma_nomnoml.R

@@ -1,0 +1,22 @@
+nomnoml::nomnoml("#import: my-common-styles.nomnoml
+#stroke: black
+#.blob: fill=#DBDBDB visual=italic
+#direction: down
+#edges: rounded
+#arrowSize: 0.6
+#bendSize: 0.3
+#fillArrows: true
+
+  [129 references imported for screening]->[94 studies screened against title and abstract]
+
+  [129 references imported for screening]-->[<blob> 35 duplicates removed]
+
+  [94 studies screened against title and abstract]->[23 studies assessed for full-text eligibility]
+  [94 studies screened against title and abstract]-->[<blob> 71 studies excluded]
+
+[23 studies assessed for full-text eligibility] -> [16 studies included]
+
+ [23 studies assessed for full-text eligibility] --> [<blob> 6 studies excluded | 4 wrong intervention
+                                                      1 wrong comparator
+                                                      1 wrong study design]
+ [23 studies assessed for full-text eligibility] --> [<blob> 1 study awaiting classification]", png = here::here("zhf_manuscript", "figure_one.png"))

### 2019-09-18 zhf_manuscript/zhf_manuscript.Rmd
prisma right size
dataframe ma output

@@
 title: "Accuracy and precision of zero-heat-flux temperature monitoring: a systematic review and meta- analysis"
-titlerunning: Short form of title (if too long for head)
-authorrunning: Conway,
+titlerunning: Accuracy of zero-heat-flux temperature monitoring
+authorrunning: Conway
 thanks: | 
@@
   email: aaron.conway@utoronto.ca
-
-- name: Âuthóř 2
-  address: Department of ZZZ, University of WWW
-  email: djf@wef
 
@@
 ```{r echo=FALSE, include=FALSE}
-library(redcapAPI)
 library(tidyverse)
@@
 library(qwraps2)
-library(rticles)
 ```
@@
 
-Zero-heat-flux (ZHF) thermometry is an alternative non-invasive method that allows for continuous monitoring of core temperature.
-Originally developed in the 1970s, ZHF technology was recently implemented in the 3M SpotOn (3M, St Paul, MN), a single-use, disposable sensor $(ref)$.
-In practice, the ZHF sensor, such as the 3M SpotOn, is placed on the lateral surface of the forehead and initially warmed to equilibrate the temperature of the skin surface to the underlaying core tissues$(ref)$.
-Equipped with a thermal insulator, the ZHF sensor eliminates heat loss to the environment to allow for changes in core temperature to be directly reflected by a change in skin surface temperature $(ref)$.
+Zero-heat-flux thermometry is an alternative non-invasive method that allows for continuous monitoring of core temperature.
+Originally developed in the 1970s, zero-heat-flux technology was recently implemented in the 3M SpotOn (3M, St Paul, MN), a single-use, disposable sensor $(ref)$.
+In practice, the zero-heat-flux sensor, such as the 3M SpotOn, is placed on the lateral surface of the forehead and initially warmed to equilibrate the temperature of the skin surface to the underlaying core tissues$(ref)$.
+Equipped with a thermal insulator, the zero-heat-flux sensor eliminates heat loss to the environment to allow for changes in core temperature to be directly reflected by a change in skin surface temperature $(ref)$.
 
-The agreement between ZHF and established core temperature devices has been investigated in several studies conducted within the clinical setting, each with varied results.
-Appraisal of these studies and synthesis of the results would aid clinicians in deciding the appropriate circumstances in which ZHF may be used.
-
-We aimed to determine if ZHF has clinically acceptable accuracy and precision relative to established core temperature measurement devices.
-Accuracy is defined as the average difference between temperature measurements from the ZHF and comparator device and precisions as the variance (typically reported as the SD) in the differences.
+The agreement between zero-heat-flux thermometers and core as well as other peripheral thermometers has been investigated in several studies conducted within clinical settings.
+Appraisal of these studies and synthesis of the results would aid clinicians in deciding the appropriate circumstances in which zero-heat-flux thermometers may be used.
+We aimed to determine if zero-heat-flux thermometers have clinically acceptable accuracy and precision relative to established core and peripheral temperature measurement devices.
+Accuracy is defined as the average difference between temperature measurements from the zero-heat-flux and comparator device and precision as the variance (standard deviation) in the differences.
 
@@
 
-A systematic review was conducted in accordance with a predetermined protocol (PROSPERO trial registration number: ################).
+A systematic review was conducted in accordance with a predetermined protocol.
+The protocol was submitted to PROSPERO for registration but due to delays in processing we had started data extraction by the time it was reviewed.
+Therefore, the protocol did not meet the requirements for registration.
+A copy of the submitted protocol can be accessed [here](insert link).
+The primary comparison for this review was temperature measured from a zero-heat-flux thermometer versus a temperature measured from a core site, which we defined as arterial, esophaeal, bladder and rectal sites.
+Secondary comparisons were made between zero-heat-flux thermometers and temperatures taken at peripheral sites.
+
+## Inclusion criteria
+
+Observational studies that reported temperature measurements from a zero-heat-flux thermometer and comparator thermometer were included.
+Studies involving a case control design were excluded due to potential for overestimation of the intervention performance.
+Studies were excluded if conducted on non-human subjects or outside of a clinical healthcare setting.
+No publication date restrictions were applied.Published conference abstracts were included if there was enough information reported to appraise the quality of the study.
+There were no language restrictions applied during the search.
 
@@
 
-Published studies were found by searching Medline and EMBASE from January 2000 to July 2019, 
->as well as the reference lists of articles identified to be relevant to the review.
-This search strategy is an efficient approach for systematic reviews of diagnostic test accuracy studies [@preston2015improving].
-Unpublished and ongoing studies were located by searching the International Clinical Trials Platform.
-
-Published conference abstracts were included if there was enough information reported to appraise the quality of the study. There were no language restrictions applied during the search. 
->The Cochrane-recommended search strategy combining terms for the ‘target condition’ and ‘index test’ was used [@mann2012should].
-
+Published studies were found by searching Medline and EMBASE from January 2000 to July 2019.
+The Cochrane-recommended search strategy combining terms for the ‘target condition’ and ‘index test’ was used [@mann2012should].
+This search strategy is an efficient approach for systematic reviews of diagnostic test accuracy studies.[@preston2015improving] We also conducted forward citation searching, by using Google Scholar to search the citations of the first article published on the accuracy of zero-heat-flux thermometers.
 The search strategies used for each data base can be located in [file 1]().
-
-The selection of studies was undertaken by two independent reviewers.
-Studies were included if reported measures from a ZHF and comparator device coincided.
-Studies involving a case control design were excluded due to potential for overestimation of the intervention performance.
-Studies were excluded if conducted on non-human subjects or outside of a clinical healthcare setting.
-Studies were excluded if conducted earlier than the year 2000 as prior studies evaluated outdated technology that is no longer relevant to current clinical practice.
+Selection of studies was undertaken independently by two reviewers using [Covidence](https://www.covidence.org).
 
@@
 
-Information was extracted regarding study characteristics (author, year of publication, country, design, sample size, clinical setting, numbers studied and analyses for each outcome), population characteristics (inclusion and exclusion criteria) and ZHF characteristics (placement of sensor, timing and methods of measurements).
-The outcomes that were extracted included the mean bias (eg, accuracy) and variance (eg, SD, precision) in temperature measurement between the ZHF sensor and comparator device.
->Information was extracted about how repeated measurements were handled: (1) analysed each pair of data separately; (2) treated each pair of data as independent; or (3) used either analysis of variance or a random effects model as a way to control for the dependent nature of the repeated measures data [@myles2007using].
+Information was extracted regarding study characteristics (author, year of publication, country, design, sample size, clinical setting, numbers studied and analyses for each outcome), population characteristics (inclusion and exclusion criteria) and temperature measurement characteristics (placement of sensor, timing and methods of measurements).
+The outcomes that were extracted included the mean bias (eg, accuracy) and variance (eg, SD, precision) in temperature measurement between the zero-heat-flux and comparator thermometers.
+We also extracted information about how repeated measurements were handled.
+In particular we assessed whether studies: (1) analysed each pair of data separately; (2) treated each pair of data as independent; or (3) used either analysis of variance or a random effects model as a way to control for the dependent nature of the repeated measures data [@myles2007using].
 
-Using the revised Quality Assessment of Diagnostic Accuracy Studies (QUADAS-2), each reviewer independently assessed the risk of bias for the included studies [@whiting2011quadas].
-Using guiding questions, reviewers rated the risk of bias for patient selection, conduct of the ZHF measurements, conduct of the comparator device measurements, and timing and flow (eg, timing of ZHF and established core temperature measurements, dropouts) as “high”, “low” or “unclear”.
+Two reviewers independently assessed the risk of bias for the included studies using the revised Quality Assessment of Diagnostic Accuracy Studies (QUADAS-2) [@whiting2011quadas].
+Reviewers rated the risk of bias for patient selection, conduct of the zero-heat-flux measurements, conduct of the comparator thermometer measurements, and timing and flow (eg, timing of ZHF and established core temperature measurements, dropouts) as “high”, “low” or “unclear” risk of bias.
 We worked to minimize the risk of publication bias by conducting a comprehensive search of multiple databases as well as an international clinical trial registry [@glasziou2001systematic].
->Statistical analyses to detect reporting bias were not conducted due to lack of validated methods [@begg2005systematic].
-Although some meta-analyses of method comparison studies have used tests for detecting funnel plot asymmetry [@niven2015accuracy], simulations have revealed that such tests will result in publication bias being incorrectly identified too often [@deeks2005performance].
+Statistical approaches for detection of reporting bias were not conducted due to lack of validated methods [@begg2005systematic].
+ASimulations have revealed that tests for detecting funnel plot asymmetry will result in publication bias being incorrectly identified too often [@deeks2005performance].
 
@@
 
-The objective for the meta-analysis was to estimate the population limits of agreement between temperature measurements from the ZHF and established comparator devices.
->The framework for meta-analysis of Bland-Altman method comparison studies based on limits of agreement (LoA) approach was used [@tipton2017framework].
-
+The objective for the meta-analysis was to estimate the population limits of agreement between temperature measurements from the ZHF and established comparator thermometers.
+A framework for meta-analysis of Bland-Altman method comparison studies developed by @tipton2017framework based on limits of agreement approach was used.
 This method was selected because it parallels the approach used in primary Bland-Altman studies, whereby an estimate is generated for the pooled LoAs in the population (not just in the samples studied).
 The ‘population LoA’ is more broad than the LoA commonly reported in the meta-analyses of Bland-Altman studies [@tipton2017framework].
-In these instances,
->the pooled LoAs are calculated using $\delta\pm2\sqrt{\sigma2+\tau2}$, where $\delta$ is the average bias across studies, $\sigma2$ is the average within-study variation in differences and $\tau2$ is the variation in bias across studies.
+Pooled limits of agreement were calculated using $\delta\pm2\sqrt{\sigma2+\tau2}$, where $\delta$ is the average bias across studies, $\sigma2$ is the average within-study variation in differences and $\tau2$ is the variation in bias across studies.
 
-Estimations of $\delta$ and $\sigma2$ were made using a weighted least-squares model (similar to a random-effects approach), with the associated SEs estimated using robust variance estimation (RVE).
-RVE was used alternatively to model-based SEs as several studies included in the systematic review used repeated-measures designs without accommodating for the correlation between measurements [@hedges2010robust; @tanner2016handling; @tipton2015small].
-We used the
->method-of-moments estimator from ref 16 for the $\tau2$ parameter.
+Estimations of $\delta$ and $\sigma2$ were made using a weighted least-squares model (similar to a random-effects approach), with the associated standard errors estimated using robust variance estimation.
+Robust variance estimation was used alternatively to model-based standard errors as some studies included in the systematic review used repeated-measures designs without accommodating for the correlation between measurements [@hedges2010robust; @tanner2016handling; @tipton2015small].
+We used the method-of-moments estimator from @dersimonian1986meta for the $\tau2$ parameter.
 
-In accordance with ref 12, (1) measures of uncertainty were included 
->when interpreting the LoA estimates by calculating the outer $95\%$ CIs for pooled LoA;
+Measures of uncertainty were included in our meta-analyses by calculating the outer $95\%$ confidence intervals for pooled limits of agreement.
+We also accounted for repeated measurements if they were not properly adjusted for in individual studies.
+This was achieved by using weights proportional to the number of participants, not the total number of measurements.
+The R statistical program was used to conduct all analyses [@team2017r].
+All data and R code used in the meta-analyses can be located [here]().
 
-and (2) repeated measurements were adjusted if improperly adjusted for in 
->individual studies (by using weights proportional to the number of participants, not the total number of measurements).
-
-The formulas for the above calculations from ref 12 can be found in [file 1]().
-The R statistical program was used to conduct all analyses [@team2017r].
-All data and R code (provided in ref 12) used in the meta-analyses can be located [here](https://doi.org).
-
-Prior to conducting the meta-analyses, the results from each study were converted into a standard format, with bias meaning $comparator-ZHF$ measured in $^\circ C$.
+Prior to conducting the meta-analyses, the results from each study were converted into a standard format, with bias meaning $comparator thermometer-ZHF thermometer$ measured in $^\circ C$.
 In several studies, results were reported for multiple groups of participants, therefore in the meta-analysis each of these groups was treated as a separate 'comparison'.
@@
 Only the paired measurements from the overall results were included in the main and low risk bias analyses, leaving paired measurements exclusively from the intraoperative and postoperative timepoints to be included in respective meta-analyses subgroups.
+
 The conventionally cited clinically acceptable agreement between ZHF and comparator devices is 0.5 $^\circ C$ $(ref - most of the studies site this range from Eshragi...)$.
->It was deemed that outer confidence bounds for 95\% LoA between ECT and ZHF (termed as ‘population limits of agreement’) outside of these bounds would
+It was deemed that outer confidence bounds for 95% LoA between zero-heat-flux and core temperature measurements (termed as ‘population limits of agreement’) outside of these bounds wouldbe clinically unacceptable.
 
-be clinically unacceptable.
-Sensitivity analysis for the primary meta-analysis was performed based on risk of bias, whereby ‘unclear risk of bias’ was treated as ‘high risk’ and ‘high risk of bias’ studies were excluded from analyses.
-As clinicians would be interested in the accuracy of ZHF relative to the thermometer devices they use, and within the clinical setting in which they use it we conducted subgroup analyses according to the comparator device used (eg, core, peripheral, nasopharangeal) and clinical setting (eg, intraoperative, intensuve care unit).
+A sensitivity analysis for the primary comparison (ZHF versus temperature measurement at core site) was performed based on risk of bias, whereby ‘unclear risk of bias’ was treated as ‘high risk’ and ‘high risk of bias’ studies were excluded from analyses.
+As clinicians would be interested in the accuracy of ZHF relative to the thermometer devices they use, and within the clinical setting in which they use it, we conducted subgroup analyses according to the comparator device used (either core, sublingual or nasopharangeal) and clinical setting (either intraoperative or intensive care unit).
 
@@
 
-Sixteen studies were eligible for inclusion in this systematic review (Figure 1).
+Fifteen studies were included in this systematic review (Figure 1).
+Two studies reported only in abstract form were not included and assigned as 'studies awaiting classification' because there was insufficient information provided.
 
-```{r echo=FALSE, fig.height=4.5}
-knitr::include_graphics("figure_one.png")
+```{r fig-1, fig.align="center", fig.cap="PRISMA Flow Diagram", echo=FALSE}
+img <- magick::image_read("figure_one.png")
+img %>% magick::image_scale("350")
+```
+
+```{r meta-function, echo=FALSE}
+meta <-  function(Te,V_T){
+m <- length(Te)
+wt_FE=1/V_T
+T_FE <- sum(Te*wt_FE)/sum(wt_FE)
+Q <- sum(wt_FE*(Te - T_FE)^2)
+S1 <- sum(wt_FE)
+S2 <- sum(wt_FE^2)
+o2 <- (Q - (m - 1))/(S1 - S2/S1)
+wt_RE <- 1/(V_T + o2)
+T_RE <- sum(Te*wt_RE)/sum(wt_RE)
+V_T_RE_mod <- 1/sum(wt_RE)
+V_T_RE_rve <- (m/(m-1))*sum(wt_RE^2*(Te - T_RE)^2)/(sum(wt_RE))^2
+c(m,T_RE,o2,V_T_RE_mod, V_T_RE_rve)
+}
+loa_maker <- function(bias,V_bias,logs2,V_logs2) {
+bias_row=meta(bias, V_bias)
+logs2_row=meta(logs2, V_logs2)
+bias_mean <- bias_row[2]
+sd2_est <- exp(logs2_row[2])
+tau_est <- bias_row[3]
+LOA_L <- bias_mean - 2*sqrt(sd2_est + tau_est)
+LOA_U <- bias_mean + 2*sqrt(sd2_est + tau_est)
+m <- bias_row[1]
+tcrit <- qt(1-.05/2,m-1)
+B1 <- sd2_est^2/(sd2_est + tau_est)
+B2 <- tau_est^2/(sd2_est + tau_est)
+wt <- 1/V_bias
+S1 <- sum(wt)
+S2 <- sum(wt^2)
+S3 <- sum(wt^3)
+A0 <- 2*(m-1)/(S1-S2/S1)^2
+A1 <- 4/(S1 - S2/S1)
+A2 <- 2*(S2-2*S3/S1+S2^2/S1^2)/(S1-S2/S1)^2
+V_logT2 <- A0/tau_est^2 + A1/tau_est + A2
+V_logT2 <- 2/sum((V_bias + tau_est)^(-2))
+V_LOA_mod <- bias_row[4] + B1*logs2_row[4] + B2*V_logT2
+V_LOA_rve <- bias_row[5] + B1*logs2_row[5] + B2*V_logT2
+CI_L_mod <- LOA_L - tcrit*sqrt(V_LOA_mod)
+CI_U_mod <- LOA_U + tcrit*sqrt(V_LOA_mod)
+CI_L_rve <- LOA_L - tcrit*sqrt(V_LOA_rve)
+CI_U_rve <- LOA_U + tcrit*sqrt(V_LOA_rve)
+data.frame(m, bias_mean,sqrt(sd2_est), tau_est, LOA_L, LOA_U, CI_L_mod, CI_U_mod, CI_L_rve, CI_U_rve)
+}
+```
+
+```{r load-data, include=FALSE}
+library(tidyverse)
+data <- readxl::read_xlsx(here::here("data","zhf_extracted.xlsx"))
+```
+
+```{r meta-analysis-prep, include=FALSE}
+data <- data %>%
+
+  mutate(c = N/n)
+
+#variance
+
+data <-  if (data$corrected == "Yes"){
+
+  mutate(data, s2 = ((upper - bias)/1.96)^2)
+
+  } else {
+
+    mutate(data, s2 = ((upper - bias)/1.96)^2)*((N-1)/(N-c))
+
+    }
+
+data <- data %>% 
+  mutate(V_bias = s2/n)
+
+data <- data %>% 
+  mutate(logs2 = log(s2)+1/(n-1))
+
+data <- data %>% 
+  mutate(V_logs2 = 2/(n-1))
+```
+
+```{r subgroups, include=FALSE}
+# meta-analyses categories
+
+data_NPA <- data %>% 
+  filter(comparison == "NPA")
+
+data_SL <- data %>% 
+  filter(comparison == "Sublingual")
+
+data_core <- data %>% #eshragi overall
+  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
+  filter(comments != "Intraoperative, off cardiopulmonary bypass" & comments != "Postoperative")
+
+data_core_op <- data%>% #eshragi intraop
+    filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
+  filter (clinical_setting=="Intraoperative")
+
+data_core_icu <- data %>% #eshragi postop
+      filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
+  filter(clinical_setting=="ICU" | clinical_setting=="Postoperative")
+
+# ROB
+
+data_core_lowrisk <- data_core %>% #eshragi overall
+  filter(RoB_selection == "low" & RoB_spoton == "low" & RoB_comparator == "low" & RoB_flow =="low")
+
+# conflict of interests
+
+data_conflict <- data_core %>% 
+  filter(`Funding/equipment/conflict with ZHF company` == "Yes")
+
+```
+
+```{r format-result-function, include=FALSE}
+format_results <- function(group){
+out <- loa_maker(group$bias,group$V_bias, group$logs2, group$V_logs2)
+out <- round(out, digits=1)
+out <- out %>% 
+  mutate(Participants = sum(group$n_count, na.rm=T)) %>% 
+  mutate(Measurements = sum(group$N, na.rm = T)) %>% 
+  mutate(Studies = length(unique(group$Study))) %>% 
+  select(Studies, m, Participants, Measurements, bias_mean, tau_est, LOA_L, LOA_U, CI_L_rve, CI_U_rve) %>% 
+  rename("Comparisons" = m, "Mean bias" = bias_mean, "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, "Upper bound for 95% limits of agreement" = LOA_U, "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve)
+out
+}
+```
+
+```{r primary, include=FALSE}
+primary <- format_results(data_core)
+```
+
+```{r sensitivity-low-risk, include=FALSE}
+low_risk <- format_results(data_core_lowrisk)
+```
+
+```{r NPA, include=FALSE}
+NPA  <- format_results(data_NPA)
+```
+
+```{r SL, include=FALSE}
+SL  <- format_results(data_SL)
+```
+
+```{r OT, include=FALSE}
+OT  <- format_results(data_core_op)
+```
+
+```{r ICU, include=FALSE}
+ICU  <- format_results(data_core_icu)
+```
+
+```{r conflict, include=FALSE}
+conflict  <- format_results(data_conflict)
 ```
@@
 
-Using these studies, we conducted 6 different meta-analyses.
-The first group compared ZHF to core (eg, arterial, bladder, esophageal, rectal) temperature measurements and included 22 (73%) comparisons from 14 (%) studies, and enrolled 607 participants with 179,821 paired measurements.
-The second group compared ZHF to core temperature measurements in low risk bias studies studies that scored a low risk of bias in all categories) and included 10 (%) comparisons from 5 (%) studies, and enrolled 273 participants with 104,294 paired measurements.
-The third group compared ZHF to core temperature measurements in ICU patients and included 7 (23%) comparisons from 5 (31%) studies, and enrolled 246 participants with 155,598 paired measurements.
+The primary comparison of zero-heat-flux versus core temperature measurements (eg, arterial, bladder, esophageal or rectal) consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies.
+In total, data from `r primary$Participants` participants with `r format(primary$Measurements, scientfic=F)` paired measurements were included in this comparison (two studies did not report the total number of measurements included in their analysis).
+The sensitivity analysis for the primary comparison with only studies that were judged as low risk of bias across all domains included `r low_risk$Comparisons` comparisons from `r low_risk$Studies` studies that enrolled `r low_risk$Participants` participants with `r format(low_risk$Measurements, scientific=F)` paired measurements (two studies did not report the total number of measurements included in their analysis).
+The third group compared zero-heat-flux to core temperature measurements in ICU patients and included 7 (23%) comparisons from 5 (31%) studies, and enrolled 246 participants with 155,598 paired measurements.
 The fourth group compared ZHF to core temperature measurement in intraoperative patients and included 16 (53%) comparisons from  10 (63%) studies, and enrolled 464 participants with 24,223 paired measurements.

### 2019-09-18 zhf_manuscript/zhf_manuscript.tex
prisma right size
dataframe ma output

@@
 
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
+
 \begin{document}
@@
 
-    \titlerunning{Short form of title (if too long for head)}
+    \titlerunning{Accuracy of zero-heat-flux temperature monitoring}
 
-\author{  Aaron Conway \and  Âuthóř 2 \and  }
+\author{  Aaron Conway \and  }
 
-    \authorrunning{ Conway, }
+    \authorrunning{ Conway }
 
@@
      \email{\href{mailto:aaron.conway@utoronto.ca}{\nolinkurl{aaron.conway@utoronto.ca}}}  %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-    \and
-        Âuthóř 2 \at
-     Department of ZZZ, University of WWW \\
-     \email{\href{mailto:djf@wef}{\nolinkurl{djf@wef}}}  %  \\
 %             \emph{Present address:} of F. Author  %  if needed
@@
 
-Zero-heat-flux (ZHF) thermometry is an alternative non-invasive method
-that allows for continuous monitoring of core temperature. Originally
-developed in the 1970s, ZHF technology was recently implemented in the
-3M SpotOn (3M, St Paul, MN), a single-use, disposable sensor \((ref)\).
-In practice, the ZHF sensor, such as the 3M SpotOn, is placed on the
-lateral surface of the forehead and initially warmed to equilibrate the
-temperature of the skin surface to the underlaying core
-tissues\((ref)\). Equipped with a thermal insulator, the ZHF sensor
-eliminates heat loss to the environment to allow for changes in core
-temperature to be directly reflected by a change in skin surface
-temperature \((ref)\).
+Zero-heat-flux thermometry is an alternative non-invasive method that
+allows for continuous monitoring of core temperature. Originally
+developed in the 1970s, zero-heat-flux technology was recently
+implemented in the 3M SpotOn (3M, St Paul, MN), a single-use, disposable
+sensor \((ref)\). In practice, the zero-heat-flux sensor, such as the 3M
+SpotOn, is placed on the lateral surface of the forehead and initially
+warmed to equilibrate the temperature of the skin surface to the
+underlaying core tissues\((ref)\). Equipped with a thermal insulator,
+the zero-heat-flux sensor eliminates heat loss to the environment to
+allow for changes in core temperature to be directly reflected by a
+change in skin surface temperature \((ref)\).
 
-The agreement between ZHF and established core temperature devices has
-been investigated in several studies conducted within the clinical
-setting, each with varied results. Appraisal of these studies and
+The agreement between zero-heat-flux thermometers and core as well as
+other peripheral thermometers has been investigated in several studies
+conducted within clinical settings. Appraisal of these studies and
 synthesis of the results would aid clinicians in deciding the
-appropriate circumstances in which ZHF may be used.
-
-We aimed to determine if ZHF has clinically acceptable accuracy and
-precision relative to established core temperature measurement devices.
-Accuracy is defined as the average difference between temperature
-measurements from the ZHF and comparator device and precisions as the
-variance (typically reported as the SD) in the differences.
+appropriate circumstances in which zero-heat-flux thermometers may be
+used. We aimed to determine if zero-heat-flux thermometers have
+clinically acceptable accuracy and precision relative to established
+core and peripheral temperature measurement devices. Accuracy is defined
+as the average difference between temperature measurements from the
+zero-heat-flux and comparator device and precision as the variance
+(standard deviation) in the differences.
 
@@
 A systematic review was conducted in accordance with a predetermined
-protocol (PROSPERO trial registration number:
-\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#).
+protocol. The protocol was submitted to PROSPERO for registration but
+due to delays in processing we had started data extraction by the time
+it was reviewed. Therefore, the protocol did not meet the requirements
+for registration. A copy of the submitted protocol can be accessed
+\href{insert\%20link}{here}. The primary comparison for this review was
+temperature measured from a zero-heat-flux thermometer versus a
+temperature measured from a core site, which we defined as arterial,
+esophaeal, bladder and rectal sites. Secondary comparisons were made
+between zero-heat-flux thermometers and temperatures taken at peripheral
+sites.
+
+\hypertarget{inclusion-criteria}{%
+\subsection{Inclusion criteria}\label{inclusion-criteria}}
+
+Observational studies that reported temperature measurements from a
+zero-heat-flux thermometer and comparator thermometer were included.
+Studies involving a case control design were excluded due to potential
+for overestimation of the intervention performance. Studies were
+excluded if conducted on non-human subjects or outside of a clinical
+healthcare setting. No publication date restrictions were
+applied.Published conference abstracts were included if there was enough
+information reported to appraise the quality of the study. There were no
+language restrictions applied during the search.
 
@@
 Published studies were found by searching Medline and EMBASE from
-January 2000 to July 2019, \textgreater{}as well as the reference lists
-of articles identified to be relevant to the review. This search
-strategy is an efficient approach for systematic reviews of diagnostic
-test accuracy studies (Preston et al. 2015). Unpublished and ongoing
-studies were located by searching the International Clinical Trials
-Platform.
-
-Published conference abstracts were included if there was enough
-information reported to appraise the quality of the study. There were no
-language restrictions applied during the search. \textgreater{}The
-Cochrane-recommended search strategy combining terms for the `target
-condition' and `index test' was used (Mann and Gilbody 2012).
-
-The search strategies used for each data base can be located in
-\href{}{file 1}.
-
-The selection of studies was undertaken by two independent reviewers.
-Studies were included if reported measures from a ZHF and comparator
-device coincided. Studies involving a case control design were excluded
-due to potential for overestimation of the intervention performance.
-Studies were excluded if conducted on non-human subjects or outside of a
-clinical healthcare setting. Studies were excluded if conducted earlier
-than the year 2000 as prior studies evaluated outdated technology that
-is no longer relevant to current clinical practice.
+January 2000 to July 2019. The Cochrane-recommended search strategy
+combining terms for the `target condition' and `index test' was used
+(Mann and Gilbody 2012). This search strategy is an efficient approach
+for systematic reviews of diagnostic test accuracy studies.(Preston et
+al. 2015) We also conducted forward citation searching, by using Google
+Scholar to search the citations of the first article published on the
+accuracy of zero-heat-flux thermometers. The search strategies used for
+each data base can be located in \href{}{file 1}. Selection of studies
+was undertaken independently by two reviewers using
+\href{https://www.covidence.org}{Covidence}.
 
@@
 studied and analyses for each outcome), population characteristics
-(inclusion and exclusion criteria) and ZHF characteristics (placement of
-sensor, timing and methods of measurements). The outcomes that were
-extracted included the mean bias (eg, accuracy) and variance (eg, SD,
-precision) in temperature measurement between the ZHF sensor and
-comparator device. \textgreater{}Information was extracted about how
-repeated measurements were handled: (1) analysed each pair of data
-separately; (2) treated each pair of data as independent; or (3) used
-either analysis of variance or a random effects model as a way to
+(inclusion and exclusion criteria) and temperature measurement
+characteristics (placement of sensor, timing and methods of
+measurements). The outcomes that were extracted included the mean bias
+(eg, accuracy) and variance (eg, SD, precision) in temperature
+measurement between the zero-heat-flux and comparator thermometers. We
+also extracted information about how repeated measurements were handled.
+In particular we assessed whether studies: (1) analysed each pair of
+data separately; (2) treated each pair of data as independent; or (3)
+used either analysis of variance or a random effects model as a way to
 control for the dependent nature of the repeated measures data (Myles
@@
 
-Using the revised Quality Assessment of Diagnostic Accuracy Studies
-(QUADAS-2), each reviewer independently assessed the risk of bias for
-the included studies (Whiting et al. 2011). Using guiding questions,
-reviewers rated the risk of bias for patient selection, conduct of the
-ZHF measurements, conduct of the comparator device measurements, and
-timing and flow (eg, timing of ZHF and established core temperature
-measurements, dropouts) as ``high'', ``low'' or ``unclear''. We worked
-to minimize the risk of publication bias by conducting a comprehensive
+Two reviewers independently assessed the risk of bias for the included
+studies using the revised Quality Assessment of Diagnostic Accuracy
+Studies (QUADAS-2) (Whiting et al. 2011). Reviewers rated the risk of
+bias for patient selection, conduct of the zero-heat-flux measurements,
+conduct of the comparator thermometer measurements, and timing and flow
+(eg, timing of ZHF and established core temperature measurements,
+dropouts) as ``high'', ``low'' or ``unclear'' risk of bias. We worked to
+minimize the risk of publication bias by conducting a comprehensive
 search of multiple databases as well as an international clinical trial
-registry (Glasziou et al. 2001). \textgreater{}Statistical analyses to
-detect reporting bias were not conducted due to lack of validated
-methods (Begg 2005). Although some meta-analyses of method comparison
-studies have used tests for detecting funnel plot asymmetry (Niven et
-al. 2015), simulations have revealed that such tests will result in
-publication bias being incorrectly identified too often (Deeks,
-Macaskill, and Irwig 2005).
+registry (Glasziou et al. 2001). Statistical approaches for detection of
+reporting bias were not conducted due to lack of validated methods (Begg
+2005). ASimulations have revealed that tests for detecting funnel plot
+asymmetry will result in publication bias being incorrectly identified
+too often (Deeks, Macaskill, and Irwig 2005).
 
@@
 limits of agreement between temperature measurements from the ZHF and
-established comparator devices. \textgreater{}The framework for
-meta-analysis of Bland-Altman method comparison studies based on limits
-of agreement (LoA) approach was used (Tipton and Shuster 2017).
-
-This method was selected because it parallels the approach used in
-primary Bland-Altman studies, whereby an estimate is generated for the
-pooled LoAs in the population (not just in the samples studied). The
-`population LoA' is more broad than the LoA commonly reported in the
-meta-analyses of Bland-Altman studies (Tipton and Shuster 2017). In
-these instances, \textgreater{}the pooled LoAs are calculated using
-\(\delta\pm2\sqrt{\sigma2+\tau2}\), where \(\delta\) is the average bias
-across studies, \(\sigma2\) is the average within-study variation in
-differences and \(\tau2\) is the variation in bias across studies.
+established comparator thermometers. A framework for meta-analysis of
+Bland-Altman method comparison studies developed by Tipton and Shuster
+(2017) based on limits of agreement approach was used. This method was
+selected because it parallels the approach used in primary Bland-Altman
+studies, whereby an estimate is generated for the pooled LoAs in the
+population (not just in the samples studied). The `population LoA' is
+more broad than the LoA commonly reported in the meta-analyses of
+Bland-Altman studies (Tipton and Shuster 2017). Pooled limits of
+agreement were calculated using \(\delta\pm2\sqrt{\sigma2+\tau2}\),
+where \(\delta\) is the average bias across studies, \(\sigma2\) is the
+average within-study variation in differences and \(\tau2\) is the
+variation in bias across studies.
 
@@
 least-squares model (similar to a random-effects approach), with the
-associated SEs estimated using robust variance estimation (RVE). RVE was
-used alternatively to model-based SEs as several studies included in the
-systematic review used repeated-measures designs without accommodating
-for the correlation between measurements (Hedges, Tipton, and Johnson
-2010; Tanner-Smith, Tipton, and Polanin 2016; Tipton 2015). We used the
-\textgreater{}method-of-moments estimator from ref 16 for the \(\tau2\)
-parameter.
+associated standard errors estimated using robust variance estimation.
+Robust variance estimation was used alternatively to model-based
+standard errors as some studies included in the systematic review used
+repeated-measures designs without accommodating for the correlation
+between measurements (Hedges, Tipton, and Johnson 2010; Tanner-Smith,
+Tipton, and Polanin 2016; Tipton 2015). We used the method-of-moments
+estimator from DerSimonian and Laird (1986) for the \(\tau2\) parameter.
 
-In accordance with ref 12, (1) measures of uncertainty were included
-\textgreater{}when interpreting the LoA estimates by calculating the
-outer \(95\%\) CIs for pooled LoA;
-
-and (2) repeated measurements were adjusted if improperly adjusted for
-in \textgreater{}individual studies (by using weights proportional to
-the number of participants, not the total number of measurements).
-
-The formulas for the above calculations from ref 12 can be found in
-\href{}{file 1}. The R statistical program was used to conduct all
-analyses (Team 2017). All data and R code (provided in ref 12) used in
-the meta-analyses can be located \href{https://doi.org}{here}.
+Measures of uncertainty were included in our meta-analyses by
+calculating the outer \(95\%\) confidence intervals for pooled limits of
+agreement. We also accounted for repeated measurements if they were not
+properly adjusted for in individual studies. This was achieved by using
+weights proportional to the number of participants, not the total number
+of measurements. The R statistical program was used to conduct all
+analyses (Team 2017). All data and R code used in the meta-analyses can
+be located \href{}{here}.
 
 Prior to conducting the meta-analyses, the results from each study were
-converted into a standard format, with bias meaning \(comparator-ZHF\)
-measured in \(^\circ C\). In several studies, results were reported for
-multiple groups of participants, therefore in the meta-analysis each of
-these groups was treated as a separate `comparison'. Other studies
-reported multiple sets of results, whereby analyses were conducted
-between ZHF and various comparator devices used on the same participant.
-These instances were also treated as a separate `comparison' if the
-comparator devices were apart of separate meta-analyses groups. One
-study reported intraoperative, postoperative and overall results for the
-same participants. Only the paired measurements from the overall results
-were included in the main and low risk bias analyses, leaving paired
+converted into a standard format, with bias meaning
+\(comparator thermometer-ZHF thermometer\) measured in \(^\circ C\). In
+several studies, results were reported for multiple groups of
+participants, therefore in the meta-analysis each of these groups was
+treated as a separate `comparison'. Other studies reported multiple sets
+of results, whereby analyses were conducted between ZHF and various
+comparator devices used on the same participant. These instances were
+also treated as a separate `comparison' if the comparator devices were
+apart of separate meta-analyses groups. One study reported
+intraoperative, postoperative and overall results for the same
+participants. Only the paired measurements from the overall results were
+included in the main and low risk bias analyses, leaving paired
 measurements exclusively from the intraoperative and postoperative
-timepoints to be included in respective meta-analyses subgroups. The
-conventionally cited clinically acceptable agreement between ZHF and
+timepoints to be included in respective meta-analyses subgroups.
+
+The conventionally cited clinically acceptable agreement between ZHF and
 comparator devices is 0.5 \(^\circ C\)
-\((ref - most of the studies site this range from Eshragi...)\).
-\textgreater{}It was deemed that outer confidence bounds for 95\% LoA
-between ECT and ZHF (termed as `population limits of agreement') outside
-of these bounds would
+\((ref - most of the studies site this range from Eshragi...)\). It was
+deemed that outer confidence bounds for 95\% LoA between zero-heat-flux
+and core temperature measurements (termed as `population limits of
+agreement') outside of these bounds wouldbe clinically unacceptable.
 
-be clinically unacceptable. Sensitivity analysis for the primary
-meta-analysis was performed based on risk of bias, whereby `unclear risk
-of bias' was treated as `high risk' and `high risk of bias' studies were
-excluded from analyses. As clinicians would be interested in the
-accuracy of ZHF relative to the thermometer devices they use, and within
-the clinical setting in which they use it we conducted subgroup analyses
-according to the comparator device used (eg, core, peripheral,
-nasopharangeal) and clinical setting (eg, intraoperative, intensuve care
-unit).
+A sensitivity analysis for the primary comparison (ZHF versus
+temperature measurement at core site) was performed based on risk of
+bias, whereby `unclear risk of bias' was treated as `high risk' and
+`high risk of bias' studies were excluded from analyses. As clinicians
+would be interested in the accuracy of ZHF relative to the thermometer
+devices they use, and within the clinical setting in which they use it,
+we conducted subgroup analyses according to the comparator device used
+(either core, sublingual or nasopharangeal) and clinical setting (either
+intraoperative or intensive care unit).
 
@@
 
-Sixteen studies were eligible for inclusion in this systematic review
-(Figure 1).
+Fifteen studies were included in this systematic review (Figure 1). Two
+studies reported only in abstract form were not included and assigned as
+`studies awaiting classification' because there was insufficient
+information provided.
 
-\includegraphics[width=53.08in]{figure_one}
+\begin{figure}
+
+{\centering \includegraphics[width=4.86in]{zhf_manuscript_files/figure-latex/fig-1-1}
+
+}
+
+\caption{PRISMA Flow Diagram}\label{fig:fig-1}
+\end{figure}
 
@@
 
-Using these studies, we conducted 6 different meta-analyses. The first
-group compared ZHF to core (eg, arterial, bladder, esophageal, rectal)
-temperature measurements and included 22 (73\%) comparisons from 14 (\%)
-studies, and enrolled 607 participants with 179,821 paired measurements.
-The second group compared ZHF to core temperature measurements in low
-risk bias studies studies that scored a low risk of bias in all
-categories) and included 10 (\%) comparisons from 5 (\%) studies, and
-enrolled 273 participants with 104,294 paired measurements. The third
-group compared ZHF to core temperature measurements in ICU patients and
-included 7 (23\%) comparisons from 5 (31\%) studies, and enrolled 246
-participants with 155,598 paired measurements. The fourth group compared
-ZHF to core temperature measurement in intraoperative patients and
-included 16 (53\%) comparisons from 10 (63\%) studies, and enrolled 464
-participants with 24,223 paired measurements. The fifth group compared
-ZHF to nasopharyngeal temperature measurements and included 4 (13\%)
-comparisons from 4 (25\%) studies, and enrolled 297 participants with
-109,819 paired measurements. The sixth group compared ZHF to sublingual
-temperature measurement and included 2 (7\%) comparisons from 2 (13\%)
-studies, and enrolled 107 participants with 22731 paired measurements.
-The studies included in this systematic review evaluated a ZHF
-temperature monitoring system manufactured by 3M. Previously known as
-the SpotOn Temperature Monitoring System, the 3M ZHF device is now
-referred to as the Bair Hugger Temperature Monitoring System. All
-comparisons reported adherence to the ZHF device manufacturer
-instructions and placed the sensor on the forehead of the participants.
-High risk of bias was associated with patient selection for 13 (43\%)
-comparisons from 9 (56\%) studies, conduct of ZHF and comparator
-measurements in 10(33\%) comparisons from 8 (50\%) studies and 12 (40\%)
-comparisons 9 (30\%) studies, respectively (mostly due to ZHF
-measurements being taken with knowledge of the comparator measurements
-and vice versa) and participant flow for 13 (43\%) studies. In 19 (50\%)
-comparisons from 8 (50\%) studies, the authors had declared a conflict
-of interest or receipt of funding or equipment from the manufacturer of
-the ZHF device under evaluation.
+The primary comparison of zero-heat-flux versus core temperature
+measurements (eg, arterial, bladder, esophageal or rectal) consisted of
+19 comparisons from 13 individual studies. In total, data from 576
+participants with 179821 paired measurements were included in this
+comparison (two studies did not report the total number of measurements
+included in their analysis). The sensitivity analysis for the primary
+comparison with only studies that were judged as low risk of bias across
+all domains included 10 comparisons from 5 studies that enrolled 273
+participants with 104294 paired measurements (two studies did not report
+the total number of measurements included in their analysis). The third
+group compared zero-heat-flux to core temperature measurements in ICU
+patients and included 7 (23\%) comparisons from 5 (31\%) studies, and
+enrolled 246 participants with 155,598 paired measurements. The fourth
+group compared ZHF to core temperature measurement in intraoperative
+patients and included 16 (53\%) comparisons from 10 (63\%) studies, and
+enrolled 464 participants with 24,223 paired measurements. The fifth
+group compared ZHF to nasopharyngeal temperature measurements and
+included 4 (13\%) comparisons from 4 (25\%) studies, and enrolled 297
+participants with 109,819 paired measurements. The sixth group compared
+ZHF to sublingual temperature measurement and included 2 (7\%)
+comparisons from 2 (13\%) studies, and enrolled 107 participants with
+22731 paired measurements. The studies included in this systematic
+review evaluated a ZHF temperature monitoring system manufactured by 3M.
+Previously known as the SpotOn Temperature Monitoring System, the 3M ZHF
+device is now referred to as the Bair Hugger Temperature Monitoring
+System. All comparisons reported adherence to the ZHF device
+manufacturer instructions and placed the sensor on the forehead of the
+participants. High risk of bias was associated with patient selection
+for 13 (43\%) comparisons from 9 (56\%) studies, conduct of ZHF and
+comparator measurements in 10(33\%) comparisons from 8 (50\%) studies
+and 12 (40\%) comparisons 9 (30\%) studies, respectively (mostly due to
+ZHF measurements being taken with knowledge of the comparator
+measurements and vice versa) and participant flow for 13 (43\%) studies.
+In 19 (50\%) comparisons from 8 (50\%) studies, the authors had declared
+a conflict of interest or receipt of funding or equipment from the
+manufacturer of the ZHF device under evaluation.
 
@@
 \emph{Journal of Clinical Epidemiology} 58 (9). Elsevier: 882--93.
+
+\leavevmode\hypertarget{ref-dersimonian1986meta}{}%
+DerSimonian, Rebecca, and Nan Laird. 1986. ``Meta-Analysis in Clinical
+Trials.'' \emph{Controlled Clinical Trials} 7 (3). Elsevier: 177--88.
 
@@
 Measure Agreement with Repeated Measures.'' Oxford University Press.
-
-\leavevmode\hypertarget{ref-niven2015accuracy}{}%
-Niven, Daniel J, Jonathan E Gaudet, Kevin B Laupland, Kelly J Mrklas,
-Derek J Roberts, and Henry Thomas Stelfox. 2015. ``Accuracy of
-Peripheral Thermometers for Estimating Temperature: A Systematic Review
-and Meta-Analysis.'' \emph{Annals of Internal Medicine} 163 (10).
-American College of Physicians: 768--77.
 

### 2019-09-18 app.R

@@ -129,8 +129,8 @@ ui <- dashboardPage(skin ="red",
                               "Sublingual")), br(), 
       h4(htmlOutput("select_format")), # "select display format"
       # menu item tabs for plot and data table
-      menuItem("Plot", tabName="Plot", icon=icon("chart-area")),
-      menuItem("Data Table", tabName="DT", icon=icon("table"))
+      menuItem("Results", tabName="Plot", icon=icon("chart-area")),
+      menuItem("Data", tabName="DT", icon=icon("table"))
       
 
     ) 

### 2019-09-18 zhf_manuscript/prisma_nomnoml.R

@@ -14,9 +14,10 @@ nomnoml::nomnoml("#import: my-common-styles.nomnoml
   [94 studies screened against title and abstract]->[23 studies assessed for full-text eligibility]
   [94 studies screened against title and abstract]-->[<blob> 71 studies excluded]
 
-[23 studies assessed for full-text eligibility] -> [16 studies included]
+[23 studies assessed for full-text eligibility] -> [15 studies included]
 
  [23 studies assessed for full-text eligibility] --> [<blob> 6 studies excluded | 4 wrong intervention
                                                       1 wrong comparator
                                                       1 wrong study design]
- [23 studies assessed for full-text eligibility] --> [<blob> 1 study awaiting classification]", png = here::here("zhf_manuscript", "figure_one.png"))
+ [23 studies assessed for full-text eligibility] --> [<blob> 2 studies awaiting classification]", 
+                 png = here::here("figure_one.png"))

### 2019-09-21 zhf_manuscript/zhf_manuscript.Rmd
ggplot based prisma works good

@@
 
-```{r fig-1, fig.align="center", fig.cap="PRISMA Flow Diagram", echo=FALSE}
-img <- magick::image_read("figure_one.png")
-img %>% magick::image_scale("350")
+```{r fig-1, fig.align="center",fig.cap="PRISMA Flow Diagram", echo=FALSE}
+prsm <- PRISMAstatement::flow_exclusions(
+  incl_counts = c(129, 94, 23, 15),
+  total_label = "References imported for screening",
+  incl_labels = c("Studies screened", "Full-text assessed for eligibility", "Included"),
+  excl_labels = c("Duplicates removed", "Excluded", "Full-text excluded"),
+               width = 200, height = 200)
+tiff("figure-one.tiff", width=7.5, height=7, units='in', res=300, compression = 'lzw')
+prsm
+PRISMAstatement:::prisma_pdf(prsm)
 ```

### 2019-09-21 PRISMAstatement.R

@@ -1,0 +1,6 @@
+# can't get right dpi
+PRISMAstatement::flow_exclusions(
+  incl_counts = c(129, 94, 23, 15),
+  total_label = "References imported for screening",
+  incl_labels = c("Studies screened", "Full-text assessed for eligibility", "Included"),
+  excl_labels = c("Duplicates removed", "Excluded", "Full-text excluded"))

### 2019-09-21 zhf_manuscript/prisma.R

@@ -1,0 +1,220 @@
+  library(ggplot2)
+  library(tibble)
+  library(tidyverse)
+  library(ggfittext)
+  
+  line_size <- 0.50
+  box_type <- "round"
+  box_lines <- 0.5
+  box_colour <- "white"
+  box_fill <- alpha("#14c4ff", 0.3)
+  text_colour <- "#ff4f14"
+  arrow_colour <- "#ff4f14"
+  
+  
+  retrieved <- 129
+  duplicates <- 35
+  screened <- retrieved-duplicates
+  full_text <- 21
+  screen_excluded <- screened-full_text
+  included <- 15
+  full_text_excluded <- full_text-included
+  wrong_intervention <- 4
+  wrong_comparator <- 2
+  wrong_design <- 1
+  awaiting_classification <- 2
+  
+
+# Main flow y coordinates  
+  import_y_max <- 100
+  import_y_min <- 90
+  screen_y_max <- 80
+  screen_y_min <- 70
+  full_y_max <- 60
+  full_y_min <- 50
+  included_y_max <- 40
+  included_y_min <- 30
+  
+# Scondary flow y coordinates  
+  duplicates_y_max <- 90
+  duplicates_y_min <- 80
+  
+  full_excluded_y_min <- 25
+  full_excluded_y_max <- 45
+  
+  screen_excluded_y_min <- 65
+  screen_excluded_y_max <- 75
+  
+  awaiting_classification_y_min <- 50
+  awaiting_classification_y_max <- 60
+  
+# x coordinates  
+  main_x_min <- 20
+  main_x_max <- 70
+  
+  second_x_min <- 75
+  second_x_max <- 95
+  
+  arrow_x <- 45
+  
+  ###Plot space set-up####
+  data <- tibble(x= 23:100, y = 23:100)
+  
+  p <- data %>% 
+    ggplot(aes(x, y)) +
+    theme_linedraw() +
+  
+  
+  
+  ########## Main box flow ###########
+  
+  # import box
+
+  annotation_custom(grob = grid::roundrectGrob(gp = grid::gpar(col = box_colour, fill = box_fill)),
+    xmin = main_x_min, xmax=main_x_max, ymin=import_y_min, ymax=import_y_max)+
+    geom_fit_text(xmin = main_x_min, xmax=main_x_max, ymin=import_y_min, ymax=100,
+                  label= glue::glue(retrieved, ' references identified'), 
+                  reflow = TRUE, colour = text_colour) +
+
[…]

### 2019-09-23 zhf_manuscript/zhf_manuscript.Rmd
new author

@@
   email: aaron.conway@utoronto.ca
+- name: Navpreet Kamboj
+  address: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
+  email: navpreet.kamboj@mail.utoronto.ca
 

### 2019-09-25 PRISMAstatement.R
tidied up folders

@@ -1,6 +1,0 @@
-# can't get right dpi
-PRISMAstatement::flow_exclusions(
-  incl_counts = c(129, 94, 23, 15),
-  total_label = "References imported for screening",
-  incl_labels = c("Studies screened", "Full-text assessed for eligibility", "Included"),
-  excl_labels = c("Duplicates removed", "Excluded", "Full-text excluded"))

### 2019-09-25 app.R

@@ -1,534 +1,0 @@
-
-library(shiny)
-library(shinydashboard)
-library(shinydashboardPlus)
-library(tidyverse)
-library(ggplot2)
-library(DT)
-
-# Manuscript screenshot resolution ----
-# resolution to be set to 600 DP for springer articles
-# screenshot image and open in preview, then go to tools > adjust size... 
-# 1. enter new desired resolution 
-# 2. check box for 'resample image' to ensure new image is created with additional pixels
-# note that this will new image retains the same dimensions as original picture but has extra pixels
-
-
-# Load data ----
-
-data <- readxl::read_xlsx("zhf_extracted.xlsx")
-sum_findings <- readxl::read_xlsx("sum_findings.xlsx")
-
-# Functions for calculating the Bland-Altman meta-analysis ----
-
-meta <-  function(Te,V_T){
-  m <- length(Te)
-  wt_FE=1/V_T
-  T_FE <- sum(Te*wt_FE)/sum(wt_FE)
-  Q <- sum(wt_FE*(Te - T_FE)^2)
-  S1 <- sum(wt_FE)
-  S2 <- sum(wt_FE^2)
-  o2 <- (Q - (m - 1))/(S1 - S2/S1)
-  wt_RE <- 1/(V_T + o2)
-  T_RE <- sum(Te*wt_RE)/sum(wt_RE)
-  V_T_RE_mod <- 1/sum(wt_RE)
-  V_T_RE_rve <- (m/(m-1))*sum(wt_RE^2*(Te - T_RE)^2)/(sum(wt_RE))^2
-  c(m,T_RE,o2,V_T_RE_mod, V_T_RE_rve)
-}
-loa_maker <- function(bias,V_bias,logs2,V_logs2) {
-  bias_row=meta(bias, V_bias)
-  logs2_row=meta(logs2, V_logs2)
-  bias_mean <- bias_row[2]
-  sd2_est <- exp(logs2_row[2])
-  tau_est <- bias_row[3]
-  LOA_L <- bias_mean - 2*sqrt(sd2_est + tau_est)
-  LOA_U <- bias_mean + 2*sqrt(sd2_est + tau_est)
-  m <- bias_row[1]
-  tcrit <- qt(1-.05/2,m-1)
[…]

### 2019-09-25 oldapp.R

@@ -1,301 +1,0 @@
-library(shiny)
-library(tidyverse)
-library(ggplot2)
-library(DT)
-
-
-
-# Load data ----
-
-data <- readxl::read_xlsx("zhf_extracted.xlsx")
-
-# Functions for calculating the Bland-Altman meta-analysis ----
-
-meta <-  function(Te,V_T){
-  m <- length(Te)
-  wt_FE=1/V_T
-  T_FE <- sum(Te*wt_FE)/sum(wt_FE)
-  Q <- sum(wt_FE*(Te - T_FE)^2)
-  S1 <- sum(wt_FE)
-  S2 <- sum(wt_FE^2)
-  o2 <- (Q - (m - 1))/(S1 - S2/S1)
-  wt_RE <- 1/(V_T + o2)
-  T_RE <- sum(Te*wt_RE)/sum(wt_RE)
-  V_T_RE_mod <- 1/sum(wt_RE)
-  V_T_RE_rve <- (m/(m-1))*sum(wt_RE^2*(Te - T_RE)^2)/(sum(wt_RE))^2
-  c(m,T_RE,o2,V_T_RE_mod, V_T_RE_rve)
-}
-loa_maker <- function(bias,V_bias,logs2,V_logs2) {
-  bias_row=meta(bias, V_bias)
-  logs2_row=meta(logs2, V_logs2)
-  bias_mean <- bias_row[2]
-  sd2_est <- exp(logs2_row[2])
-  tau_est <- bias_row[3]
-  LOA_L <- bias_mean - 2*sqrt(sd2_est + tau_est)
-  LOA_U <- bias_mean + 2*sqrt(sd2_est + tau_est)
-  m <- bias_row[1]
-  tcrit <- qt(1-.05/2,m-1)
-  B1 <- sd2_est^2/(sd2_est + tau_est)
-  B2 <- tau_est^2/(sd2_est + tau_est)
-  wt <- 1/V_bias
-  S1 <- sum(wt)
-  S2 <- sum(wt^2)
-  S3 <- sum(wt^3)
-  A0 <- 2*(m-1)/(S1-S2/S1)^2
-  A1 <- 4/(S1 - S2/S1)
-  A2 <- 2*(S2-2*S3/S1+S2^2/S1^2)/(S1-S2/S1)^2
-  V_logT2 <- A0/tau_est^2 + A1/tau_est + A2
-  V_logT2 <- 2/sum((V_bias + tau_est)^(-2))
[…]

### 2019-09-25 zhf_manuscript/prisma.R

@@ -1,220 +1,0 @@
-  library(ggplot2)
-  library(tibble)
-  library(tidyverse)
-  library(ggfittext)
-  
-  line_size <- 0.50
-  box_type <- "round"
-  box_lines <- 0.5
-  box_colour <- "white"
-  box_fill <- alpha("#14c4ff", 0.3)
-  text_colour <- "#ff4f14"
-  arrow_colour <- "#ff4f14"
-  
-  
-  retrieved <- 129
-  duplicates <- 35
-  screened <- retrieved-duplicates
-  full_text <- 21
-  screen_excluded <- screened-full_text
-  included <- 15
-  full_text_excluded <- full_text-included
-  wrong_intervention <- 4
-  wrong_comparator <- 2
-  wrong_design <- 1
-  awaiting_classification <- 2
-  
-
-# Main flow y coordinates  
-  import_y_max <- 100
-  import_y_min <- 90
-  screen_y_max <- 80
-  screen_y_min <- 70
-  full_y_max <- 60
-  full_y_min <- 50
-  included_y_max <- 40
-  included_y_min <- 30
-  
-# Scondary flow y coordinates  
-  duplicates_y_max <- 90
-  duplicates_y_min <- 80
-  
-  full_excluded_y_min <- 25
-  full_excluded_y_max <- 45
-  
-  screen_excluded_y_min <- 65
-  screen_excluded_y_max <- 75
-  
-  awaiting_classification_y_min <- 50
-  awaiting_classification_y_max <- 60
-  
-# x coordinates  
-  main_x_min <- 20
-  main_x_max <- 70
-  
-  second_x_min <- 75
-  second_x_max <- 95
-  
-  arrow_x <- 45
-  
-  ###Plot space set-up####
-  data <- tibble(x= 23:100, y = 23:100)
-  
-  p <- data %>% 
-    ggplot(aes(x, y)) +
-    theme_linedraw() +
-  
-  
-  
-  ########## Main box flow ###########
-  
-  # import box
-
-  annotation_custom(grob = grid::roundrectGrob(gp = grid::gpar(col = box_colour, fill = box_fill)),
-    xmin = main_x_min, xmax=main_x_max, ymin=import_y_min, ymax=import_y_max)+
-    geom_fit_text(xmin = main_x_min, xmax=main_x_max, ymin=import_y_min, ymax=100,
-                  label= glue::glue(retrieved, ' references identified'), 
-                  reflow = TRUE, colour = text_colour) +
-
[…]

### 2019-09-25 zhf_manuscript/prisma_nomnoml.R

@@ -1,23 +1,0 @@
-nomnoml::nomnoml("#import: my-common-styles.nomnoml
-#stroke: black
-#.blob: fill=#DBDBDB visual=italic
-#direction: down
-#edges: rounded
-#arrowSize: 0.6
-#bendSize: 0.3
-#fillArrows: true
-
-  [129 references imported for screening]->[94 studies screened against title and abstract]
-
-  [129 references imported for screening]-->[<blob> 35 duplicates removed]
-
-  [94 studies screened against title and abstract]->[23 studies assessed for full-text eligibility]
-  [94 studies screened against title and abstract]-->[<blob> 71 studies excluded]
-
-[23 studies assessed for full-text eligibility] -> [15 studies included]
-
- [23 studies assessed for full-text eligibility] --> [<blob> 6 studies excluded | 4 wrong intervention
-                                                      1 wrong comparator
-                                                      1 wrong study design]
- [23 studies assessed for full-text eligibility] --> [<blob> 2 studies awaiting classification]", 
-                 png = here::here("figure_one.png"))

### 2019-09-25 manuscript/manuscript.Rmd
tidied up folders

--- 2019-09-18 zhf_manuscript/zhf_manuscript.Rmd
@@
 
-#PACS: 
-#- PAC1
-#- superPAC
-
-MSC:
-- MSC code 1
-- MSC code 2
-
 abstract: |
@@
 output: rticles::springer_article
-
 ---
@@
 library(qwraps2)
-```
-# Introduction
-
-Core temperature monitoring is an important intervention within perioperative and intensive care settings.
-Thermoregulatory dysfunction is commonly associated with the induction of anesthesia and can lead to adverse outcomes including cardiac dysrhythmias, altered hemostasis and increased risk of surgical site infection [@frank1997perioperative; @kurz1996perioperative; @michelson1994reversible; @rohrer1992effect].
-The pulmonary artery catheter is the reference standard for continuous core temperature monitoring$(ref - trouble finding a statement regarding this in the literature)$, however, the invasive nature of this method renders an increased risk of bloodstream infections and damage to surrounding tissue[@hadian2006evidence].
-Although clinically accurate relative to pulmonary artery temperature measurements, surrogate measures of core temperature at esophageal, rectal, and bladder locations remain mildly invasive interventions$(ref)$.
-
-Zero-heat-flux thermometry is an alternative non-invasive method that allows for continuous monitoring of core temperature.
-Originally developed in the 1970s, zero-heat-flux technology was recently implemented in the 3M SpotOn (3M, St Paul, MN), a single-use, disposable sensor $(ref)$.
-In practice, the zero-heat-flux sensor, such as the 3M SpotOn, is placed on the lateral surface of the forehead and initially warmed to equilibrate the temperature of the skin surface to the underlaying core tissues$(ref)$.
-Equipped with a thermal insulator, the zero-heat-flux sensor eliminates heat loss to the environment to allow for changes in core temperature to be directly reflected by a change in skin surface temperature $(ref)$.
-
-The agreement between zero-heat-flux thermometers and core as well as other peripheral thermometers has been investigated in several studies conducted within clinical settings.
-Appraisal of these studies and synthesis of the results would aid clinicians in deciding the appropriate circumstances in which zero-heat-flux thermometers may be used.
-We aimed to determine if zero-heat-flux thermometers have clinically acceptable accuracy and precision relative to established core and peripheral temperature measurement devices.
-Accuracy is defined as the average difference between temperature measurements from the zero-heat-flux and comparator device and precision as the variance (standard deviation) in the differences.
-
-# Methods
-
-A systematic review was conducted in accordance with a predetermined protocol.
-The protocol was submitted to PROSPERO for registration but due to delays in processing we had started data extraction by the time it was reviewed.
-Therefore, the protocol did not meet the requirements for registration.
-A copy of the submitted protocol can be accessed [here](insert link).
-The primary comparison for this review was temperature measured from a zero-heat-flux thermometer versus a temperature measured from a core site, which we defined as arterial, esophaeal, bladder and rectal sites.
-Secondary comparisons were made between zero-heat-flux thermometers and temperatures taken at peripheral sites.
-
-## Inclusion criteria
-
-Observational studies that reported temperature measurements from a zero-heat-flux thermometer and comparator thermometer were included.
-Studies involving a case control design were excluded due to potential for overestimation of the intervention performance.
-Studies were excluded if conducted on non-human subjects or outside of a clinical healthcare setting.
-No publication date restrictions were applied.Published conference abstracts were included if there was enough information reported to appraise the quality of the study.
-There were no language restrictions applied during the search.
-
-## Data sources and searches
-
-Published studies were found by searching Medline and EMBASE from January 2000 to July 2019.
-The Cochrane-recommended search strategy combining terms for the ‘target condition’ and ‘index test’ was used [@mann2012should].
-This search strategy is an efficient approach for systematic reviews of diagnostic test accuracy studies.[@preston2015improving] We also conducted forward citation searching, by using Google Scholar to search the citations of the first article published on the accuracy of zero-heat-flux thermometers.
-The search strategies used for each data base can be located in [file 1]().
-Selection of studies was undertaken independently by two reviewers using [Covidence](https://www.covidence.org).
-
-## Data extraction and quality assessment
-
-Information was extracted regarding study characteristics (author, year of publication, country, design, sample size, clinical setting, numbers studied and analyses for each outcome), population characteristics (inclusion and exclusion criteria) and temperature measurement characteristics (placement of sensor, timing and methods of measurements).
-The outcomes that were extracted included the mean bias (eg, accuracy) and variance (eg, SD, precision) in temperature measurement between the zero-heat-flux and comparator thermometers.
-We also extracted information about how repeated measurements were handled.
-In particular we assessed whether studies: (1) analysed each pair of data separately; (2) treated each pair of data as independent; or (3) used either analysis of variance or a random effects model as a way to control for the dependent nature of the repeated measures data [@myles2007using].
-
-Two reviewers independently assessed the risk of bias for the included studies using the revised Quality Assessment of Diagnostic Accuracy Studies (QUADAS-2) [@whiting2011quadas].
-Reviewers rated the risk of bias for patient selection, conduct of the zero-heat-flux measurements, conduct of the comparator thermometer measurements, and timing and flow (eg, timing of ZHF and established core temperature measurements, dropouts) as “high”, “low” or “unclear” risk of bias.
-We worked to minimize the risk of publication bias by conducting a comprehensive search of multiple databases as well as an international clinical trial registry [@glasziou2001systematic].
-Statistical approaches for detection of reporting bias were not conducted due to lack of validated methods [@begg2005systematic].
-ASimulations have revealed that tests for detecting funnel plot asymmetry will result in publication bias being incorrectly identified too often [@deeks2005performance].
-
-In order to rate the quality of evidence, we applied the Grading Quality of Evidence and Strength of Recommendation methodology [@schunemann2008grading].
-Evidence was downgraded in accordance with study limitations, inconsistency and imprecision.
-There were no circumstances in which evidence was downgraded for indirectness as this systematic review only included relevant studies.
-Although the possibility of publication bias was not excluded, this bias was not formally assessed as it was not considered sufficient enough to reason downgrading the quality of evidence.
-
-## Data synthesis and analysis
-
-The objective for the meta-analysis was to estimate the population limits of agreement between temperature measurements from the ZHF and established comparator thermometers.
-A framework for meta-analysis of Bland-Altman method comparison studies developed by @tipton2017framework based on limits of agreement approach was used.
-This method was selected because it parallels the approach used in primary Bland-Altman studies, whereby an estimate is generated for the pooled LoAs in the population (not just in the samples studied).
-The ‘population LoA’ is more broad than the LoA commonly reported in the meta-analyses of Bland-Altman studies [@tipton2017framework].
-Pooled limits of agreement were calculated using $\delta\pm2\sqrt{\sigma2+\tau2}$, where $\delta$ is the average bias across studies, $\sigma2$ is the average within-study variation in differences and $\tau2$ is the variation in bias across studies.
-
-Estimations of $\delta$ and $\sigma2$ were made using a weighted least-squares model (similar to a random-effects approach), with the associated standard errors estimated using robust variance estimation.
-Robust variance estimation was used alternatively to model-based standard errors as some studies included in the systematic review used repeated-measures designs without accommodating for the correlation between measurements [@hedges2010robust; @tanner2016handling; @tipton2015small].
-We used the method-of-moments estimator from @dersimonian1986meta for the $\tau2$ parameter.
-
-Measures of uncertainty were included in our meta-analyses by calculating the outer $95\%$ confidence intervals for pooled limits of agreement.
-We also accounted for repeated measurements if they were not properly adjusted for in individual studies.
-This was achieved by using weights proportional to the number of participants, not the total number of measurements.
-The R statistical program was used to conduct all analyses [@team2017r].
-All data and R code used in the meta-analyses can be located [here]().
-
-Prior to conducting the meta-analyses, the results from each study were converted into a standard format, with bias meaning $comparator thermometer-ZHF thermometer$ measured in $^\circ C$.
-In several studies, results were reported for multiple groups of participants, therefore in the meta-analysis each of these groups was treated as a separate 'comparison'.
-Other studies reported multiple sets of results, whereby analyses were conducted between ZHF and various comparator devices used on the same participant.
-These instances were also treated as a separate 'comparison' if the comparator devices were apart of separate meta-analyses groups.
-One study reported intraoperative, postoperative and overall results for the same participants.
-Only the paired measurements from the overall results were included in the main and low risk bias analyses, leaving paired measurements exclusively from the intraoperative and postoperative timepoints to be included in respective meta-analyses subgroups.
-
-The conventionally cited clinically acceptable agreement between ZHF and comparator devices is 0.5 $^\circ C$ $(ref - most of the studies site this range from Eshragi...)$.
-It was deemed that outer confidence bounds for 95% LoA between zero-heat-flux and core temperature measurements (termed as ‘population limits of agreement’) outside of these bounds wouldbe clinically unacceptable.
-
-A sensitivity analysis for the primary comparison (ZHF versus temperature measurement at core site) was performed based on risk of bias, whereby ‘unclear risk of bias’ was treated as ‘high risk’ and ‘high risk of bias’ studies were excluded from analyses.
-As clinicians would be interested in the accuracy of ZHF relative to the thermometer devices they use, and within the clinical setting in which they use it, we conducted subgroup analyses according to the comparator device used (either core, sublingual or nasopharangeal) and clinical setting (either intraoperative or intensive care unit).
-
-# Results
-
-Fifteen studies were included in this systematic review (Figure 1).
-Two studies reported only in abstract form were not included and assigned as 'studies awaiting classification' because there was insufficient information provided.
-
-```{r fig-1, fig.align="center", fig.cap="PRISMA Flow Diagram", echo=FALSE}
-img <- magick::image_read("figure_one.png")
-img %>% magick::image_scale("350")
+library(knitr)
 ```
@@
   mutate(Participants = sum(group$n_count, na.rm=T)) %>% 
-  mutate(Measurements = sum(group$N, na.rm = T)) %>% 
+  mutate(Measurements = format(sum(group$N, na.rm = T), big.mark=",", scientific = FALSE)) %>% 
   mutate(Studies = length(unique(group$Study))) %>% 
@@
 
->The characteristics of each study are in online supplementary [file 1](link to file 1).
+# Introduction
 
+Core temperature monitoring is an important intervention within perioperative and intensive care settings.
+Thermoregulatory dysfunction is commonly associated with the induction of anesthesia and can lead to adverse outcomes including cardiac dysrhythmias, altered hemostasis and increased risk of surgical site infection [@frank1997perioperative; @kurz1996perioperative; @michelson1994reversible; @rohrer1992effect].
+The pulmonary artery catheter is the reference standard for continuous core temperature monitoring$(ref - trouble finding a statement regarding this in the literature)$, however, the invasive nature of this method renders an increased risk of bloodstream infections and damage to surrounding tissue[@hadian2006evidence].
+Although clinically accurate relative to pulmonary artery temperature measurements, surrogate measures of core temperature at esophageal, rectal, and bladder locations remain mildly invasive interventions$(ref)$.
+
+Zero-heat-flux thermometry is an alternative non-invasive method that allows for continuous monitoring of core temperature.
+Originally developed in the 1970s, zero-heat-flux technology was recently implemented in the 3M SpotOn (3M, St Paul, MN), a single-use, disposable sensor $(ref)$.
+In practice, the zero-heat-flux sensor, such as the 3M SpotOn, is placed on the lateral surface of the forehead and initially warmed to equilibrate the temperature of the skin surface to the underlaying core tissues$(ref)$.
+Equipped with a thermal insulator, the zero-heat-flux sensor eliminates heat loss to the environment to allow for changes in core temperature to be directly reflected by a change in skin surface temperature $(ref)$.
+
+The agreement between zero-heat-flux thermometers and core as well as other peripheral thermometers has been investigated in several studies conducted within clinical settings.
+Appraisal of these studies and synthesis of the results would aid clinicians in deciding the appropriate circumstances in which zero-heat-flux thermometers may be used.
+We aimed to determine if zero-heat-flux thermometers have clinically acceptable accuracy and precision relative to established core and peripheral temperature measurement devices.
+Accuracy is defined as the average difference between temperature measurements from the zero-heat-flux and comparator device and precision as the variance (standard deviation) in the differences.
+
+# Methods
+
+A systematic review was conducted in accordance with a predetermined protocol.
+The protocol was submitted to PROSPERO for registration but due to delays in processing we had started data extraction by the time it was reviewed.
+Therefore, the protocol did not meet the requirements for registration.
+A copy of the submitted protocol can be accessed [here](insert link).
+The primary comparison for this review was temperature measured from a zero-heat-flux thermometer versus a temperature measured from a core site, which we defined as arterial, esophaeal, bladder and rectal sites.
+Secondary comparisons were made between zero-heat-flux thermometers and temperatures taken at peripheral sites.
+
+## Inclusion criteria
+
+Observational studies that reported temperature measurements from a zero-heat-flux thermometer and comparator thermometer were included.
+Studies involving a case control design were excluded due to potential for overestimation of the intervention performance.
+Studies were excluded if conducted on non-human subjects or outside of a clinical healthcare setting.
+No publication date restrictions were applied.Published conference abstracts were included if there was enough information reported to appraise the quality of the study.
+There were no language restrictions applied during the search.
+
+## Data sources and searches
+
+Published studies were found by searching Medline and EMBASE from January 2000 to July 2019.
+The Cochrane-recommended search strategy combining terms for the ‘target condition’ and ‘index test’ was used [@mann2012should].
+This search strategy is an efficient approach for systematic reviews of diagnostic test accuracy studies.[@preston2015improving] We also conducted forward citation searching, by using Google Scholar to search the citations of the first article published on the accuracy of zero-heat-flux thermometers.
+The search strategies used for each data base can be located in [file 1]().
+Selection of studies was undertaken independently by two reviewers using [Covidence](https://www.covidence.org).
+
+## Data extraction and quality assessment
+
+Information was extracted regarding study characteristics (author, year of publication, country, design, sample size, clinical setting, numbers studied and analyses for each outcome), population characteristics (inclusion and exclusion criteria) and temperature measurement characteristics (placement of sensor, timing and methods of measurements).
+The outcomes that were extracted included the mean bias (eg, accuracy) and variance (eg, SD, precision) in temperature measurement between the zero-heat-flux and comparator thermometers.
+We also extracted information about how repeated measurements were handled.
+In particular we assessed whether studies: (1) analysed each pair of data separately; (2) treated each pair of data as independent; or (3) used either analysis of variance or a random effects model as a way to control for the dependent nature of the repeated measures data [@myles2007using].
+
+Two reviewers independently assessed the risk of bias for the included studies using the revised Quality Assessment of Diagnostic Accuracy Studies (QUADAS-2) [@whiting2011quadas].
+Reviewers rated the risk of bias for patient selection, conduct of the zero-heat-flux measurements, conduct of the comparator thermometer measurements, and timing and flow (eg, timing of ZHF and established core temperature measurements, dropouts) as “high”, “low” or “unclear” risk of bias.
+We worked to minimize the risk of publication bias by conducting a comprehensive search of multiple databases as well as an international clinical trial registry [@glasziou2001systematic].
+Statistical approaches for detection of reporting bias were not conducted due to lack of validated methods [@begg2005systematic].
+ASimulations have revealed that tests for detecting funnel plot asymmetry will result in publication bias being incorrectly identified too often [@deeks2005performance].
+
+In order to rate the quality of evidence, we applied the Grading Quality of Evidence and Strength of Recommendation methodology [@schunemann2008grading].
+Evidence was downgraded in accordance with study limitations, inconsistency and imprecision.
+There were no circumstances in which evidence was downgraded for indirectness as this systematic review only included relevant studies.
+Although the possibility of publication bias was not excluded, this bias was not formally assessed as it was not considered sufficient enough to reason downgrading the quality of evidence.
+
+## Data synthesis and analysis
+
+The objective for the meta-analysis was to estimate the population limits of agreement between temperature measurements from the ZHF and established comparator thermometers.
+A framework for meta-analysis of Bland-Altman method comparison studies developed by @tipton2017framework based on limits of agreement approach was used.
+This method was selected because it parallels the approach used in primary Bland-Altman studies, whereby an estimate is generated for the pooled LoAs in the population (not just in the samples studied).
+The ‘population LoA’ is more broad than the LoA commonly reported in the meta-analyses of Bland-Altman studies [@tipton2017framework].
+Pooled limits of agreement were calculated using $\delta\pm2\sqrt{\sigma2+\tau2}$, where $\delta$ is the average bias across studies, $\sigma2$ is the average within-study variation in differences and $\tau2$ is the variation in bias across studies.
+
+Estimations of $\delta$ and $\sigma2$ were made using a weighted least-squares model (similar to a random-effects approach), with the associated standard errors estimated using robust variance estimation.
+Robust variance estimation was used alternatively to model-based standard errors as some studies included in the systematic review used repeated-measures designs without accommodating for the correlation between measurements [@hedges2010robust; @tanner2016handling; @tipton2015small].
+We used the method-of-moments estimator from @dersimonian1986meta for the $\tau2$ parameter.
+
+Measures of uncertainty were included in our meta-analyses by calculating the outer $95\%$ confidence intervals for pooled limits of agreement.
+We also accounted for repeated measurements if they were not properly adjusted for in individual studies.
+This was achieved by using weights proportional to the number of participants, not the total number of measurements.
+The R statistical program was used to conduct all analyses [@team2017r].
+All data and R code used in the meta-analyses can be located [here]().
+
+Prior to conducting the meta-analyses, the results from each study were converted into a standard format, with bias meaning $comparator thermometer-ZHF thermometer$ measured in $^\circ C$.
+In several studies, results were reported for multiple groups of participants, therefore in the meta-analysis each of these groups was treated as a separate 'comparison'.
+Other studies reported multiple sets of results, whereby analyses were conducted between ZHF and various comparator devices used on the same participant.
+These instances were also treated as a separate 'comparison' if the comparator devices were apart of separate meta-analyses groups.
+One study reported intraoperative, postoperative and overall results for the same participants.
+Only the paired measurements from the overall results were included in the main and low risk bias analyses, leaving paired measurements exclusively from the intraoperative and postoperative timepoints to be included in respective meta-analyses subgroups.
+
+The conventionally cited clinically acceptable agreement between ZHF and comparator devices is 0.5 $^\circ C$ $(ref - most of the studies site this range from Eshragi...)$.
+It was deemed that outer confidence bounds for 95% LoA between zero-heat-flux and core temperature measurements (termed as ‘population limits of agreement’) outside of these bounds wouldbe clinically unacceptable.
+
+A sensitivity analysis for the primary comparison (ZHF versus temperature measurement at core site) was performed based on risk of bias, whereby ‘unclear risk of bias’ was treated as ‘high risk’ and ‘high risk of bias’ studies were excluded from analyses.
+As clinicians would be interested in the accuracy of ZHF relative to the thermometer devices they use, and within the clinical setting in which they use it, we conducted subgroup analyses according to the comparator device used (either core, sublingual or nasopharangeal) and clinical setting (either intraoperative or intensive care unit).
+
+# Results
+
+## Study selection and description
+
+Fifteen studies were included (Figure 1).
+Two studies reported only in abstract form were not included and assigned as 'studies awaiting classification' because there was insufficient information provided.
+
+```{r fig-1, fig.align="center", fig.cap="PRISMA Flow Diagram", echo=FALSE, fig.width=5.5, fig.path=""}
+library(ggplot2)
+  library(tibble)
+  library(tidyverse)
+  library(ggfittext)
+
+  line_size <- 0.50
+  box_type <- "round"
+  box_lines <- 0.5
+  box_colour <- "#ff4f14"
+  box_fill <- "white"
+  text_colour <- "#ff4f14"
+  arrow_colour <- "#ff4f14"
+
+  retrieved <- 129
+  duplicates <- 35
+  screened <- retrieved-duplicates
+  full_text <- 21
+  screen_excluded <- screened-full_text
+  included <- 15
+  full_text_excluded <- full_text-included
+  wrong_intervention <- 4
+  wrong_comparator <- 2
+  wrong_design <- 1
+  awaiting_classification <- 2
+
+# Main flow y coordinates  
+  import_y_max <- 100
+  import_y_min <- 90
+  screen_y_max <- 80
+  screen_y_min <- 70
+  full_y_max <- 60
+  full_y_min <- 50
+  included_y_max <- 40
+  included_y_min <- 30
+
+# Scondary flow y coordinates  
+  duplicates_y_max <- 90
+  duplicates_y_min <- 80
+
+  full_excluded_y_min <- 25
+  full_excluded_y_max <- 45
+
+  screen_excluded_y_min <- 65
+  screen_excluded_y_max <- 75
+
+  awaiting_classification_y_min <- 50
+  awaiting_classification_y_max <- 60
+
+# x coordinates  
+  main_x_min <- 20
+  main_x_max <- 70
+
+  second_x_min <- 75
+  second_x_max <- 95
+
+  arrow_x <- 45
+
+  ###Plot space set-up####
+  data <- tibble(x= 23:100, y = 23:100)
+   data %>% 
+    ggplot(aes(x, y)) +
+    theme_linedraw() +
+
+  ########## Main box flow ###########
+
+  # import box
+
+  annotation_custom(grob = grid::roundrectGrob(gp = grid::gpar(col = box_colour, fill = box_fill)),
+    xmin = main_x_min, xmax=main_x_max, ymin=import_y_min, ymax=import_y_max)+
+    geom_fit_text(xmin = main_x_min, xmax=main_x_max, ymin=import_y_min, ymax=100,
+                  label= glue::glue(retrieved, ' references identified'), 
+                  reflow = TRUE, colour = text_colour) +
+
+# screen box
+  annotation_custom(grob = grid::roundrectGrob(gp = 
+                    grid::gpar(col = box_colour, fill = box_fill)),
+                    xmin = main_x_min, xmax=main_x_max, ymin=screen_y_min, 
+                    ymax=screen_y_max) +
+  geom_fit_text(xmin = main_x_min, xmax=main_x_max, ymin=screen_y_min, ymax=screen_y_max,
+           label= glue::glue(screened, ' titles and abstracts screened'), 
+           reflow = TRUE, colour = text_colour) +
+
+# full text box
+  annotation_custom(grob = grid::roundrectGrob(gp = 
+          grid::gpar(col = box_colour, fill = box_fill)),
+          xmin = main_x_min, xmax=main_x_max, ymin=full_y_min, ymax=full_y_max) +
+  geom_fit_text( xmin = main_x_min, xmax=main_x_max, ymin=full_y_min, ymax=full_y_max,
+                 label= glue::glue(full_text, ' full-text articles assessed'), 
+                  reflow = TRUE, colour = text_colour) +
+
+# included box 
+  annotation_custom(grob = grid::roundrectGrob(gp = 
+               grid::gpar(col = box_colour, fill = box_fill)),
+               xmin = main_x_min, xmax=main_x_max, 
+                    ymin=included_y_min, ymax=included_y_max) +
+  geom_fit_text(xmin = main_x_min, xmax=main_x_max, 
+                ymin=included_y_min, ymax=included_y_max,
+                label= glue::glue(included, ' studies included'), 
+                 reflow = TRUE, colour = text_colour) +
+
+######### Secondary flow boxes ############
+
+  annotation_custom(grob = grid::roundrectGrob(gp = 
+        grid::gpar(col = box_colour, fill = box_fill)),
+        xmin = second_x_min, xmax=second_x_max, 
+                    ymin=duplicates_y_min, ymax=duplicates_y_max) +
+  geom_fit_text(xmin = second_x_min, xmax=second_x_max, 
+                ymin=duplicates_y_min, ymax=duplicates_y_max,
+                label= glue::glue(duplicates, ' duplicates removed'),
+                 reflow = TRUE, colour = text_colour) +
+
+# excluded box 
+ annotation_custom(grob = 
+                              grid::roundrectGrob(gp = 
+                              grid::gpar(col = box_colour, fill = box_fill)),
+                            xmin = second_x_min, xmax=second_x_max, 
+                    ymin=screen_excluded_y_min, ymax=screen_excluded_y_max) +
+  geom_fit_text(xmin = second_x_min, xmax=second_x_max, 
+                ymin=screen_excluded_y_min, ymax=screen_excluded_y_max,
+                label= glue::glue(screen_excluded, ' studies excluded'),
+                 reflow = TRUE, colour = text_colour) +
+
+# awaiting classifications box 
+    annotation_custom(grob = 
+                        grid::roundrectGrob(gp = 
+                                              grid::gpar(col = box_colour, fill = box_fill)),
+                      xmin = second_x_min, xmax=second_x_max, 
+                      ymin=awaiting_classification_y_min, ymax=awaiting_classification_y_max) +
+    geom_fit_text(xmin = second_x_min, xmax=second_x_max, 
+                  ymin=awaiting_classification_y_min, ymax=awaiting_classification_y_max,
+                  label= glue::glue(awaiting_classification, ' studies awaiting classification'),
+                  reflow = TRUE, colour = text_colour) +
+
+# full text excluded box 
+annotation_custom(grob = 
+                             grid::roundrectGrob(gp = 
+                            grid::gpar(col = box_colour, fill = box_fill)),
+                           xmin = second_x_min, xmax=second_x_max, 
+                   ymin=full_excluded_y_min, ymax=full_excluded_y_max) +
+ geom_fit_text(xmin = second_x_min, xmax=second_x_max,
+                ymin=full_excluded_y_max-7, ymax=full_excluded_y_max,
+                label= glue::glue(full_text_excluded, ' studies excluded'),
+                 reflow = TRUE, colour = text_colour) +
+ geom_fit_text(xmin = second_x_min, xmax=second_x_max,
+                ymin=full_excluded_y_max-17, ymax=full_excluded_y_max-7,
+                label= glue::glue(wrong_intervention, ' wrong intervention','\n',
+                                  wrong_intervention, ' wrong comparator','\n',
+                                  wrong_intervention, ' wrong design'),
+                 colour = text_colour, grow = TRUE) +
+
+####### Main flow arrows#######
+
+  # Import - screen
+ geom_segment(
+  x=arrow_x, xend = arrow_x, y = import_y_min, yend = screen_y_max+0.25, 
+  size = line_size,  colour = arrow_colour,
+  arrow = arrow(length = unit(2, "mm"), type= "closed")) +
+
+# Screen - full text
+  geom_segment(
+    x=arrow_x, xend=arrow_x, y=screen_y_min, yend=full_y_max+0.25, 
+    size = line_size,  colour = arrow_colour,
+    arrow = arrow(length = unit(2, "mm"), type= "closed")) +
+
+# Full text - included
+
+  geom_segment(
+    x=arrow_x, xend=arrow_x, y=full_y_min, yend=included_y_max+0.25, 
+    size = line_size,  colour = arrow_colour,
+    arrow = arrow(length = unit(2, "mm"), type= "closed")) +
+
+####Secondary flow arrows########
+
+# Import - duplicates
+
+  geom_curve(
+    x = arrow_x, xend = second_x_min, 
+    y = duplicates_y_max,  yend = duplicates_y_max-5, linetype = "dashed",
+    curvature = 0.1, colour = arrow_colour) +
+
+# Screen - excluded
+
+  geom_curve(
+    x = arrow_x, xend = second_x_min, 
+    y = screen_y_min,  yend = screen_excluded_y_max-5, linetype = "dashed",
+    curvature = 0.1, colour = arrow_colour) +
+
+# Screen - awaiting
+
+    geom_curve(
+      x = arrow_x, xend = second_x_min, 
+      y = screen_y_min,  yend = awaiting_classification_y_max-5, linetype = "dashed",
+      curvature = -0.2, colour = arrow_colour) +
+
+  # Full text - excluded
+
+  geom_curve(
+    x = arrow_x, xend = second_x_min, 
+    y = full_y_min, yend = full_excluded_y_max-10, linetype = "dashed",
+    curvature = -0.2, colour = arrow_colour) +
+
+ theme_void() +
+  coord_cartesian(ylim = c(23,100))
+```
+
+The characteristics of included studies can be viewed [here](link to shiny app).
 The primary comparison of zero-heat-flux versus core temperature measurements (eg, arterial, bladder, esophageal or rectal) consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies.
 In total, data from `r primary$Participants` participants with `r format(primary$Measurements, scientfic=F)` paired measurements were included in this comparison (two studies did not report the total number of measurements included in their analysis).
-The sensitivity analysis for the primary comparison with only studies that were judged as low risk of bias across all domains included `r low_risk$Comparisons` comparisons from `r low_risk$Studies` studies that enrolled `r low_risk$Participants` participants with `r format(low_risk$Measurements, scientific=F)` paired measurements (two studies did not report the total number of measurements included in their analysis).
-The third group compared zero-heat-flux to core temperature measurements in ICU patients and included 7 (23%) comparisons from 5 (31%) studies, and enrolled 246 participants with 155,598 paired measurements.
-The fourth group compared ZHF to core temperature measurement in intraoperative patients and included 16 (53%) comparisons from  10 (63%) studies, and enrolled 464 participants with 24,223 paired measurements.
-The fifth group compared ZHF to nasopharyngeal temperature measurements and included 4 (13%) comparisons from  4 (25%) studies, and enrolled 297 participants with 109,819 paired measurements.
-The sixth group compared ZHF to sublingual temperature measurement and included 2 (7%) comparisons from  2 (13%) studies, and enrolled 107 participants with 22731 paired measurements.
-The studies included in this systematic review evaluated a ZHF temperature monitoring system manufactured by 3M.
-Previously known as the SpotOn Temperature Monitoring System, the 3M ZHF device is now referred to as the Bair Hugger Temperature Monitoring System.
-All comparisons reported adherence to the ZHF device manufacturer instructions and placed the sensor on the forehead of the participants.
+The sensitivity analysis for the primary comparison with only studies that were judged as low risk of bias across all domains included `r low_risk$Comparisons` comparisons from `r low_risk$Studies` studies that enrolled `r low_risk$Participants` participants with `r low_risk$Measurements` paired measurements (two studies did not report the total number of measurements included in their analysis).
+There were `r ICU$Studies` studies that compared zero-heat-flux to core temperature measurements in ICU patients, comprising `r ICU$Comparisons` comparisons with `r ICU$Measurements` measurements from `r ICU$Participants` participants.
+Another `r OT$Studies` studies were included that compared zero-heat-flux to core temperature measurements in patients undergoing surgery, comprising `r OT$Comparisons` comparisons with `r OT$Measurements` measurements from `r OT$Participants` participants.
+Nasopharyngeal thermometers were used as the comparator devices in `r NPA$Studies` studies, with `r NPA$Measurements` paired measurements from `r NPA$Measurements` participants.
+Sublingual thermometers were used as the comparator devices in `r SL$Studies` studies that reported `r SL$Measurements` paired measurements from `r SL$Participants` participants.
+
+All studies included in this systematic review evaluated the zero-heat-flux temperature monitoring system manufactured by 3M.
+Previously known as the SpotOn Temperature Monitoring System, the 3M ZHF device is now referred to commercially as the Bair Hugger Temperature Monitoring System.
+All comparisons reported adherence to the zero-heat-flux device manufacturer instructions and placed the sensor on the forehead of the participants.
+One included study also reported results for a comparison where the zero-heat-flux thermometer was placed on the forehead.
+We did not included this comparison in our meta-analysis.
+
 High risk of bias was associated with patient selection for 13 (43%) comparisons from 9 (56%) studies, conduct of ZHF and comparator measurements in 10(33%) comparisons from 8 (50%) studies and 12 (40%) comparisons 9 (30%) studies, respectively (mostly due to ZHF measurements being taken with knowledge of the comparator measurements and vice versa) and participant flow for 13 (43%) studies.
 In 19 (50%) comparisons from 8 (50%) studies, the authors had declared a conflict of interest or receipt of funding or equipment from the manufacturer of the ZHF device under evaluation.
-
-## Study selection and description
 

### 2019-09-25 manuscript/manuscript.tex
tidied up folders

--- 2019-09-18 zhf_manuscript/zhf_manuscript.tex
@@
 
-\author{  Aaron Conway \and  }
+\author{  Aaron Conway \and  Navpreet Kamboj \and  }
 
@@
      \email{\href{mailto:aaron.conway@utoronto.ca}{\nolinkurl{aaron.conway@utoronto.ca}}}  %  \\
+%             \emph{Present address:} of F. Author  %  if needed
+    \and
+        Navpreet Kamboj \at
+     Lawrence S. Bloomberg Faculty of Nursing, University of Toronto \\
+     \email{\href{mailto:navpreet.kamboj@mail.utoronto.ca}{\nolinkurl{navpreet.kamboj@mail.utoronto.ca}}}  %  \\
 %             \emph{Present address:} of F. Author  %  if needed
@@
 
-Fifteen studies were included in this systematic review (Figure 1). Two
-studies reported only in abstract form were not included and assigned as
-`studies awaiting classification' because there was insufficient
-information provided.
+\hypertarget{study-selection-and-description}{%
+\subsection{Study selection and
+description}\label{study-selection-and-description}}
+
+Fifteen studies were included (Figure 1). Two studies reported only in
+abstract form were not included and assigned as `studies awaiting
+classification' because there was insufficient information provided.
 
@@
 
-{\centering \includegraphics[width=4.86in]{zhf_manuscript_files/figure-latex/fig-1-1}
+{\centering \includegraphics{fig-1-1}
 
@@
 
-\begin{quote}
-The characteristics of each study are in online supplementary
-\href{link\%20to\%20file\%201}{file 1}.
-\end{quote}
+The characteristics of included studies can be viewed
+\href{link\%20to\%20shiny\%20app}{here}. The primary comparison of
+zero-heat-flux versus core temperature measurements (eg, arterial,
+bladder, esophageal or rectal) consisted of 19 comparisons from 13
+individual studies. In total, data from 576 participants with 179,821
+paired measurements were included in this comparison (two studies did
+not report the total number of measurements included in their analysis).
+The sensitivity analysis for the primary comparison with only studies
+that were judged as low risk of bias across all domains included 10
+comparisons from 5 studies that enrolled 273 participants with 104,294
+paired measurements (two studies did not report the total number of
+measurements included in their analysis). There were 5 studies that
+compared zero-heat-flux to core temperature measurements in ICU
+patients, comprising 7 comparisons with 155,598 measurements from 246
+participants. Another 9 studies were included that compared
+zero-heat-flux to core temperature measurements in patients undergoing
+surgery, comprising 13 comparisons with 24,223 measurements from 433
+participants. Nasopharyngeal thermometers were used as the comparator
+devices in 4 studies, with 109,819 paired measurements from 109,819
+participants. Sublingual thermometers were used as the comparator
+devices in 2 studies that reported 22,731 paired measurements from 107
+participants.
 
-The primary comparison of zero-heat-flux versus core temperature
-measurements (eg, arterial, bladder, esophageal or rectal) consisted of
-19 comparisons from 13 individual studies. In total, data from 576
-participants with 179821 paired measurements were included in this
-comparison (two studies did not report the total number of measurements
-included in their analysis). The sensitivity analysis for the primary
-comparison with only studies that were judged as low risk of bias across
-all domains included 10 comparisons from 5 studies that enrolled 273
-participants with 104294 paired measurements (two studies did not report
-the total number of measurements included in their analysis). The third
-group compared zero-heat-flux to core temperature measurements in ICU
-patients and included 7 (23\%) comparisons from 5 (31\%) studies, and
-enrolled 246 participants with 155,598 paired measurements. The fourth
-group compared ZHF to core temperature measurement in intraoperative
-patients and included 16 (53\%) comparisons from 10 (63\%) studies, and
-enrolled 464 participants with 24,223 paired measurements. The fifth
-group compared ZHF to nasopharyngeal temperature measurements and
-included 4 (13\%) comparisons from 4 (25\%) studies, and enrolled 297
-participants with 109,819 paired measurements. The sixth group compared
-ZHF to sublingual temperature measurement and included 2 (7\%)
-comparisons from 2 (13\%) studies, and enrolled 107 participants with
-22731 paired measurements. The studies included in this systematic
-review evaluated a ZHF temperature monitoring system manufactured by 3M.
+All studies included in this systematic review evaluated the
+zero-heat-flux temperature monitoring system manufactured by 3M.
 Previously known as the SpotOn Temperature Monitoring System, the 3M ZHF
-device is now referred to as the Bair Hugger Temperature Monitoring
-System. All comparisons reported adherence to the ZHF device
-manufacturer instructions and placed the sensor on the forehead of the
-participants. High risk of bias was associated with patient selection
-for 13 (43\%) comparisons from 9 (56\%) studies, conduct of ZHF and
-comparator measurements in 10(33\%) comparisons from 8 (50\%) studies
-and 12 (40\%) comparisons 9 (30\%) studies, respectively (mostly due to
-ZHF measurements being taken with knowledge of the comparator
-measurements and vice versa) and participant flow for 13 (43\%) studies.
-In 19 (50\%) comparisons from 8 (50\%) studies, the authors had declared
-a conflict of interest or receipt of funding or equipment from the
-manufacturer of the ZHF device under evaluation.
+device is now referred to commercially as the Bair Hugger Temperature
+Monitoring System. All comparisons reported adherence to the
+zero-heat-flux device manufacturer instructions and placed the sensor on
+the forehead of the participants. One included study also reported
+results for a comparison where the zero-heat-flux thermometer was placed
+on the forehead. We did not included this comparison in our
+meta-analysis.
 
-\hypertarget{study-selection-and-description}{%
-\subsection{Study selection and
-description}\label{study-selection-and-description}}
+High risk of bias was associated with patient selection for 13 (43\%)
+comparisons from 9 (56\%) studies, conduct of ZHF and comparator
+measurements in 10(33\%) comparisons from 8 (50\%) studies and 12 (40\%)
+comparisons 9 (30\%) studies, respectively (mostly due to ZHF
+measurements being taken with knowledge of the comparator measurements
+and vice versa) and participant flow for 13 (43\%) studies. In 19 (50\%)
+comparisons from 8 (50\%) studies, the authors had declared a conflict
+of interest or receipt of funding or equipment from the manufacturer of
+the ZHF device under evaluation.
 

### 2019-09-25 app/app.R

@@ -1,0 +1,534 @@
+
+library(shiny)
+library(shinydashboard)
+library(shinydashboardPlus)
+library(tidyverse)
+library(ggplot2)
+library(DT)
+
+# Manuscript screenshot resolution ----
+# resolution to be set to 600 DP for springer articles
+# screenshot image and open in preview, then go to tools > adjust size... 
+# 1. enter new desired resolution 
+# 2. check box for 'resample image' to ensure new image is created with additional pixels
+# note that this will new image retains the same dimensions as original picture but has extra pixels
+
+
+# Load data ----
+
+data <- readxl::read_xlsx(here::here("data", "zhf_extracted.xlsx"))
+sum_findings <- readxl::read_xlsx(here::here("data", "sum_findings.xlsx"))
+
+# Functions for calculating the Bland-Altman meta-analysis ----
+
+meta <-  function(Te,V_T){
+  m <- length(Te)
+  wt_FE=1/V_T
+  T_FE <- sum(Te*wt_FE)/sum(wt_FE)
+  Q <- sum(wt_FE*(Te - T_FE)^2)
+  S1 <- sum(wt_FE)
+  S2 <- sum(wt_FE^2)
+  o2 <- (Q - (m - 1))/(S1 - S2/S1)
+  wt_RE <- 1/(V_T + o2)
+  T_RE <- sum(Te*wt_RE)/sum(wt_RE)
+  V_T_RE_mod <- 1/sum(wt_RE)
+  V_T_RE_rve <- (m/(m-1))*sum(wt_RE^2*(Te - T_RE)^2)/(sum(wt_RE))^2
+  c(m,T_RE,o2,V_T_RE_mod, V_T_RE_rve)
+}
+loa_maker <- function(bias,V_bias,logs2,V_logs2) {
+  bias_row=meta(bias, V_bias)
+  logs2_row=meta(logs2, V_logs2)
+  bias_mean <- bias_row[2]
+  sd2_est <- exp(logs2_row[2])
+  tau_est <- bias_row[3]
+  LOA_L <- bias_mean - 2*sqrt(sd2_est + tau_est)
+  LOA_U <- bias_mean + 2*sqrt(sd2_est + tau_est)
+  m <- bias_row[1]
[…]

### 2019-09-25 manuscript/prisma.R

@@ -1,0 +1,214 @@
+  library(ggplot2)
+  library(tibble)
+  library(tidyverse)
+  library(ggfittext)
+  
+  line_size <- 0.50
+  box_type <- "round"
+  box_lines <- 0.5
+  box_colour <- "white"
+  box_fill <- alpha("#14c4ff", 0.3)
+  text_colour <- "#ff4f14"
+  arrow_colour <- "#ff4f14"
+  
+  
+  retrieved <- 129
+  duplicates <- 35
+  screened <- retrieved-duplicates
+  full_text <- 21
+  screen_excluded <- screened-full_text
+  included <- 15
+  full_text_excluded <- full_text-included
+  wrong_intervention <- 4
+  wrong_comparator <- 2
+  wrong_design <- 1
+  awaiting_classification <- 2
+  
+
+# Main flow y coordinates  
+  import_y_max <- 100
+  import_y_min <- 90
+  screen_y_max <- 80
+  screen_y_min <- 70
+  full_y_max <- 60
+  full_y_min <- 50
+  included_y_max <- 40
+  included_y_min <- 30
+  
+# Scondary flow y coordinates  
+  duplicates_y_max <- 90
+  duplicates_y_min <- 80
+  
+  full_excluded_y_min <- 25
+  full_excluded_y_max <- 45
+  
+  screen_excluded_y_min <- 65
+  screen_excluded_y_max <- 75
+  
+  awaiting_classification_y_min <- 50
+  awaiting_classification_y_max <- 60
+  
+# x coordinates  
+  main_x_min <- 20
+  main_x_max <- 70
+  
+  second_x_min <- 75
+  second_x_max <- 95
+  
+  arrow_x <- 45
+  
+  ###Plot space set-up####
+  data <- tibble(x= 23:100, y = 23:100)
+  
+  p <- data %>% 
+    ggplot(aes(x, y)) +
+    theme_linedraw() +
+  
+  
+  
+  ########## Main box flow ###########
+  
+  # import box
+
+  annotation_custom(grob = grid::roundrectGrob(gp = grid::gpar(col = box_colour, fill = box_fill)),
+    xmin = main_x_min, xmax=main_x_max, ymin=import_y_min, ymax=import_y_max)+
+    geom_fit_text(xmin = main_x_min, xmax=main_x_max, ymin=import_y_min, ymax=100,
+                  label= glue::glue(retrieved, ' references identified'), 
+                  reflow = TRUE, colour = text_colour) +
+
[…]

### 2019-09-25 app/app.R
file path corrected

@@ -16,8 +16,8 @@ library(DT)
 
 # Load data ----
 
-data <- readxl::read_xlsx(here::here("data", "zhf_extracted.xlsx"))
-sum_findings <- readxl::read_xlsx(here::here("data", "sum_findings.xlsx"))
+data <- readxl::read_xlsx(here::here("app", "data", "zhf_extracted.xlsx"))
+sum_findings <- readxl::read_xlsx(here::here("app", "data", "sum_findings.xlsx"))
 
 # Functions for calculating the Bland-Altman meta-analysis ----
 

### 2019-09-26 app/xml.R
extract from covidence spreadhseet using xml

@@ -1,0 +1,19 @@
+library(xml2)
+library(tidyverse)
+
+testxml <- xml2::read_xml(here::here("app", "data", "study-characteristics.xml"))
+
+#Study names
+study <- xml_find_all(testxml, ".//ss:Worksheet")
+study <- xml_attr(study, "Name")
+
+#Inclusion criteria
+rows <- xml_find_all(testxml, ".//ss:Row")
+inclusions <- xml_find_all(rows, "//ss:Row[@ss:Index='17']")
+inclusions <- xml_text(inclusions)
+inclusions <- stringr::str_remove(inclusions, "Inclusion criteria")
+# Dataframe
+datadrame <- tibble::tibble(study, inclusions)
+
+#Resource
+#https://stackoverflow.com/questions/42799674/r-and-xml2-how-to-read-text-that-is-not-in-children-nodes-and-read-information

### 2019-09-26 app/xml.R
filepath fixed

@@ -1,7 +1,7 @@
 library(xml2)
 library(tidyverse)
 
-testxml <- xml2::read_xml(here::here("app", "data", "study-characteristics.xml"))
+testxml <- xml2::read_xml(here::here("app", "data", "study-characteristics", "study-characteristics.xml"))
 
 #Study names
 study <- xml_find_all(testxml, ".//ss:Worksheet")
@@ -13,7 +13,7 @@ inclusions <- xml_find_all(rows, "//ss:Row[@ss:Index='17']")
 inclusions <- xml_text(inclusions)
 inclusions <- stringr::str_remove(inclusions, "Inclusion criteria")
 # Dataframe
-datadrame <- tibble::tibble(study, inclusions)
+dataframe <- tibble::tibble(study, inclusions)
 
 #Resource
 #https://stackoverflow.com/questions/42799674/r-and-xml2-how-to-read-text-that-is-not-in-children-nodes-and-read-information

### 2019-09-26 manuscript/manuscript.Rmd
results added - more work on figure needed

@@
 CI_U_rve <- LOA_U + tcrit*sqrt(V_LOA_rve)
-data.frame(m, bias_mean,sqrt(sd2_est), tau_est, LOA_L, LOA_U, CI_L_mod, CI_U_mod, CI_L_rve, CI_U_rve)
+data.frame(m, bias_mean, sd2_est, tau_est, LOA_L, LOA_U, CI_L_mod, CI_U_mod, CI_L_rve, CI_U_rve)
 }
@@
 ```{r load-data, include=FALSE}
-library(tidyverse)
-data <- readxl::read_xlsx(here::here("data","zhf_extracted.xlsx"))
+data <- readxl::read_xlsx(here::here("data", "zhf_extracted.xlsx"))
 ```
@@
   mutate(Studies = length(unique(group$Study))) %>% 
-  select(Studies, m, Participants, Measurements, bias_mean, tau_est, LOA_L, LOA_U, CI_L_rve, CI_U_rve) %>% 
-  rename("Comparisons" = m, "Mean bias" = bias_mean, "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, "Upper bound for 95% limits of agreement" = LOA_U, "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve)
+  select(Studies, m, Participants, Measurements, bias_mean, sd2_est, tau_est, LOA_L, LOA_U, CI_L_rve, CI_U_rve) %>% 
+  rename("Comparisons" = m)
 out
+
+# Better names for columns
+# , "Mean bias" = bias_mean, "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, "Upper bound for 95% limits of agreement" = LOA_U, "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve
 }
@@
 Thermoregulatory dysfunction is commonly associated with the induction of anesthesia and can lead to adverse outcomes including cardiac dysrhythmias, altered hemostasis and increased risk of surgical site infection [@frank1997perioperative; @kurz1996perioperative; @michelson1994reversible; @rohrer1992effect].
-The pulmonary artery catheter is the reference standard for continuous core temperature monitoring$(ref - trouble finding a statement regarding this in the literature)$, however, the invasive nature of this method renders an increased risk of bloodstream infections and damage to surrounding tissue[@hadian2006evidence].
-Although clinically accurate relative to pulmonary artery temperature measurements, surrogate measures of core temperature at esophageal, rectal, and bladder locations remain mildly invasive interventions$(ref)$.
+The pulmonary artery catheter is the reference standard for continuous core temperature monitoring, however, the invasive nature of this method renders an increased risk of bloodstream infections and damage to surrounding tissue[@hadian2006evidence].
+Although clinically accurate relative to pulmonary artery temperature measurements, surrogate measures of core temperature at esophageal, rectal, and bladder locations remain mildly invasive interventions.
 
 Zero-heat-flux thermometry is an alternative non-invasive method that allows for continuous monitoring of core temperature.
-Originally developed in the 1970s, zero-heat-flux technology was recently implemented in the 3M SpotOn (3M, St Paul, MN), a single-use, disposable sensor $(ref)$.
-In practice, the zero-heat-flux sensor, such as the 3M SpotOn, is placed on the lateral surface of the forehead and initially warmed to equilibrate the temperature of the skin surface to the underlaying core tissues$(ref)$.
-Equipped with a thermal insulator, the zero-heat-flux sensor eliminates heat loss to the environment to allow for changes in core temperature to be directly reflected by a change in skin surface temperature $(ref)$.
+Originally developed in the 1970s, zero-heat-flux technology was recently implemented in the 3M SpotOn temperature monitoring system (3M, St Paul, MN), as a single-use, disposable sensor.
+In practice, the zero-heat-flux sensor, such as the 3M SpotOn, is placed on the lateral surface of the forehead and isinitially warmed to equilibrate the temperature of the skin surface to the underlaying core tissues.
+Equipped with a thermal insulator, the zero-heat-flux sensor eliminates heat loss to the environment to allow for changes in core temperature to be directly reflected by a change in skin surface temperature [@eshraghi2014].
 
-The agreement between zero-heat-flux thermometers and core as well as other peripheral thermometers has been investigated in several studies conducted within clinical settings.
+The agreement between zero-heat-flux thermometers and core as well as other peripheral thermometers has been investigated in multiple studies over the last five years.
 Appraisal of these studies and synthesis of the results would aid clinicians in deciding the appropriate circumstances in which zero-heat-flux thermometers may be used.
@@
 Therefore, the protocol did not meet the requirements for registration.
-A copy of the submitted protocol can be accessed [here](insert link).
-The primary comparison for this review was temperature measured from a zero-heat-flux thermometer versus a temperature measured from a core site, which we defined as arterial, esophaeal, bladder and rectal sites.
+A copy of the submitted protocol can be accessed [here](https://github.com/awconway/zhf-review).
+The primary comparison for this review was temperature measured from a zero-heat-flux thermometer versus temperature measured from a core site, which we defined as temperature measured at either an arterial, esophaeal, bladder or rectal site.
 Secondary comparisons were made between zero-heat-flux thermometers and temperatures taken at peripheral sites.
@@
 This search strategy is an efficient approach for systematic reviews of diagnostic test accuracy studies.[@preston2015improving] We also conducted forward citation searching, by using Google Scholar to search the citations of the first article published on the accuracy of zero-heat-flux thermometers.
-The search strategies used for each data base can be located in [file 1]().
+The search strategies used for each data base can be located [here](shiny app).
 Selection of studies was undertaken independently by two reviewers using [Covidence](https://www.covidence.org).
@@
 
-## Agreement between ZHF and core temperature measurements
+## Primary comparison: zero-heat-flux thermometer versus core thermometers
+
+The pooled estimate for the mean bias between zero-heat-flux and core temperature measurements was `r primary$bias_mean`$^\circ C$.
+However, the variation in differences between studies was large, as displayed by the density plot in Figure 2.
+Consequently, the population limits of agreement, which take into consideration the between-study heterogeneity and sampling error, were wide, spanning from `r primary$CI_L_rve`$^\circ C$ to `r primary$CI_U_rve`$^\circ C$ (`r primary$Measurements` measurements; `r primary$Participants` participants; `r primary$Studies` studies).
+The quality of evidence for the primary comparison was downgraded to low quality due to concerns about study limitations and inconsistency.
+Population limits of agreement for the sensitivity analysis restricted to studies rated as having low risk of bias across all the domains of the QADAS-2 were similar to the primary analysis (`r low_risk$Measurements` measurements; `r low_risk$Participants` participants; `r low_risk$Studies` stsudies).
+The mean bias was again `r low_risk$bias_mean`$^\circ C$ with population agreements spanning from `r low_risk$CI_L_rve`$^\circ C$ to `r low_risk$CI_U_rve`$^\circ C$.
+
+```{r fig-2, fig.align="center", fig.cap="Comparisons between core and zero-heat-flux thermometers within and across studies.
+Blue curves are distributions of the differences between measurements from zero-heat-flux (ZHF) sensors and core temperature measurements in individual studies.
+The red curve is the distribution of the pooled estimate.", echo=FALSE, fig.width=5.1, fig.path=""}
+
+    bias=data_core$bias
+    s2_unb = data_core$s2
+    pooled_bias = primary$bias_mean
+    pooled_sd = primary$sd2_est
+    pooled_tau2 = primary$tau_est
+    pooled_sd = sqrt(pooled_sd^2 + pooled_tau2)
+
+    LOA_l = primary$LOA_L
+    LOA_u = primary$LOA_U
+    LOA_l_CI = primary$CI_L_rve
+    LOA_u_CI = primary$CI_U_rve
+
+g <- ggplot(data.frame(x=seq(-20,20,length=200)), aes(x=x)) + 
+      stat_function(fun=dnorm, args = list(bias[1], sd=sqrt(s2_unb[1])), colour = "cornflowerblue", size=0.6, alpha = 0.5)
+
+    for (i in 2:length(bias)){
+      g <- g + stat_function(fun=dnorm, args = list(bias[i], sd=sqrt(s2_unb[i])), color = "cornflowerblue", size = 0.6, alpha = 0.5)
+    }
+
+    g <- g + stat_function(fun=dnorm, args = list(pooled_bias, pooled_sd), colour ="lightcoral", alpha = 0.05) + 
+      stat_function(fun=dnorm, args = list(pooled_bias, pooled_sd), colour = NA, geom="area", fill="lightcoral", alpha = 0.6) + 
+      scale_x_continuous(limits = c(-3.5,3.5)) + labs(x = expression('Difference between core and ZHF temperature measurements in'*~degree*C*''))+
+      scale_y_continuous(name = "Density \n", limits = c(0,2.5)) +  
+      #labs(title = "\nOuter confidence intervals for pooled limits of agreement\n\n  Pooled limits of agreement")+
+      theme(plot.title = element_text(hjust = 0.5, margin = margin(t=10, b=-32), size=10),
+            axis.text=element_text(hjust = 0.5, size=10),                                                                        
+            axis.title=element_text(hjust = 0.5, size=10),
+            axis.line=element_line(colour="black", size=0.2),
+            panel.background = element_blank(),
+            axis.ticks = element_blank(), 
+            plot.caption = element_text(hjust = 0)) #+ 
+      #CI lines that extend to arrow tips
+      # geom_segment(aes(x=LOA_u, y=0, xend=LOA_u, yend=2.25), size = 0.3, linetype="dashed")+ 
+      # geom_segment(aes(x=LOA_l, y=0, xend=LOA_l, yend=2.25), size = 0.3, linetype="dashed")+
+      # geom_segment(aes(x=LOA_u_CI, y=0, xend=LOA_u_CI, yend=2.48), size = 0.3)+
+      # geom_segment(aes(x=LOA_l_CI, y=0, xend=LOA_l_CI, yend=2.48), size = 0.3)#+
+      # 
+      # geom_segment(aes(x=0, y=2.48, xend=LOA_u_CI, yend=2.48), size = 0.4, arrow = arrow(length = unit(0.03, "npc")))+ #R arrow high
+      # geom_segment(aes(x=0, y=2.48, xend=LOA_l_CI, yend=2.48), size = 0.4, arrow = arrow(length = unit(0.03, "npc")))+ #L arrow high
+      # geom_segment(aes(x=0, y=2.25, xend=LOA_u, yend=2.25), size = 0.4,  arrow = arrow(length = unit(0.03, "npc")))+ #R arrow low
+      # geom_segment(aes(x=0, y=2.25, xend=LOA_l, yend=2.25), size = 0.4,  arrow = arrow(length = unit(0.03, "npc"))) #L arrow low
+g
+```
+
+We conducted two subgroup analyses for the primary comparison according to the clinical setting in which the study was conducted.
+In the subset of studies conducted in the ICU, the mean bias was `r ICU$bias_mean` $^\circ C$ with population limits of agreement between `r ICU$CI_L_rve` $^\circ C$ and `r ICU$CI_U_rve` $^\circ C$.
+Whereas in the subset of studies that evaluated the use of zero-heat-flux thermometers during surgery found a mean bias of `r OT$bias_mean` $^\circ C$ with population limits of agreement from `r OT$CI_L_rve` $^\circ C$ to `r OT$CI_U_rve` $^\circ C$.
+The quality of evidence for these subgroup analyses was similarly rated as low quality due to concerns about study limitations and inconsistency.
+
+## Secondary comparisons: zero-heat-flux thermometer versus peripheral thermometers
+
+Zero-heat-flux thermometers were compared with sublingual thermometers and nasopharyngeal thermometers in the studies included in this review.
+The mean bias between zero-heat-flux and sublingual temperature measurements in meta-analysis of results from `r SL$Studies` studies was `r SL$bias_mean` $^\circ C$.
+Due to the limited number of studies and measurements, population limits of agreement were extremely wide, spanning from `r SL$CI_L_rve` $^\circ C$ to `r SL$CI_U_rve` $^\circ C$.
+The quality of evidence for this comparison was rated as very low quality due to serious concerns about imprecision.
+
+The mean bias between zero-heat-flux and nasopharyngeal temperature measurements in meta-analysis of results from `r NPA$Studies` studies was `r NPA$bias_mean` $^\circ C$.
+Population limits of agreement were `r NPA$CI_L_rve` $^\circ C$ to `r NPA$CI_U_rve` $^\circ C$.
+We downgraded the quality of evidence to low, again due to concerns about inconsistency and study limitations.
 
 # Discussion
+
+Results from this systematic review have important implications for practice.
+Clinicians should consider the potential that a temperature measurement from a zero-heat-flux thermometer could be as much as one $^\circ C$ higher or lower than the true core temperature.
+This is similar to results from previous meta-analyses that compared other peripheral thermometers with core temperature measurements.
+However, these previous meta-analyses used statistical approaches that did not incorporate the magnitude of heteroogeneity in results between studies or sampling error.
+As such, it is possible that the zero-heat-flux thermometer is still more precise than these other peripheral thermometers.
+
+Whether or not teh zero-heat-flux thermometer is sufficiently accurate to be used in place of nasopharyngeal thermometers is unclear.
 

### 2019-09-26 manuscript/manuscript.tex
results added - more work on figure needed

@@
 
-    \subclass{
-                    MSC code 1 \and
-                    MSC code 2 \and
-            }
-
 \end{abstract}
@@
 1992). The pulmonary artery catheter is the reference standard for
-continuous core temperature
-monitoring\((ref - trouble finding a statement regarding this in the literature)\),
-however, the invasive nature of this method renders an increased risk of
-bloodstream infections and damage to surrounding tissue(Hadian and
-Pinsky 2006). Although clinically accurate relative to pulmonary artery
-temperature measurements, surrogate measures of core temperature at
-esophageal, rectal, and bladder locations remain mildly invasive
-interventions\((ref)\).
+continuous core temperature monitoring, however, the invasive nature of
+this method renders an increased risk of bloodstream infections and
+damage to surrounding tissue(Hadian and Pinsky 2006). Although
+clinically accurate relative to pulmonary artery temperature
+measurements, surrogate measures of core temperature at esophageal,
+rectal, and bladder locations remain mildly invasive interventions.
 
@@
 developed in the 1970s, zero-heat-flux technology was recently
-implemented in the 3M SpotOn (3M, St Paul, MN), a single-use, disposable
-sensor \((ref)\). In practice, the zero-heat-flux sensor, such as the 3M
-SpotOn, is placed on the lateral surface of the forehead and initially
-warmed to equilibrate the temperature of the skin surface to the
-underlaying core tissues\((ref)\). Equipped with a thermal insulator,
-the zero-heat-flux sensor eliminates heat loss to the environment to
-allow for changes in core temperature to be directly reflected by a
-change in skin surface temperature \((ref)\).
+implemented in the 3M SpotOn temperature monitoring system (3M, St Paul,
+MN), as a single-use, disposable sensor. In practice, the zero-heat-flux
+sensor, such as the 3M SpotOn, is placed on the lateral surface of the
+forehead and isinitially warmed to equilibrate the temperature of the
+skin surface to the underlaying core tissues. Equipped with a thermal
+insulator, the zero-heat-flux sensor eliminates heat loss to the
+environment to allow for changes in core temperature to be directly
+reflected by a change in skin surface temperature (Eshraghi et al.
+2014).
 
 The agreement between zero-heat-flux thermometers and core as well as
-other peripheral thermometers has been investigated in several studies
-conducted within clinical settings. Appraisal of these studies and
-synthesis of the results would aid clinicians in deciding the
-appropriate circumstances in which zero-heat-flux thermometers may be
-used. We aimed to determine if zero-heat-flux thermometers have
-clinically acceptable accuracy and precision relative to established
-core and peripheral temperature measurement devices. Accuracy is defined
-as the average difference between temperature measurements from the
-zero-heat-flux and comparator device and precision as the variance
-(standard deviation) in the differences.
+other peripheral thermometers has been investigated in multiple studies
+over the last five years. Appraisal of these studies and synthesis of
+the results would aid clinicians in deciding the appropriate
+circumstances in which zero-heat-flux thermometers may be used. We aimed
+to determine if zero-heat-flux thermometers have clinically acceptable
+accuracy and precision relative to established core and peripheral
+temperature measurement devices. Accuracy is defined as the average
+difference between temperature measurements from the zero-heat-flux and
+comparator device and precision as the variance (standard deviation) in
+the differences.
 
@@
 for registration. A copy of the submitted protocol can be accessed
-\href{insert\%20link}{here}. The primary comparison for this review was
-temperature measured from a zero-heat-flux thermometer versus a
-temperature measured from a core site, which we defined as arterial,
-esophaeal, bladder and rectal sites. Secondary comparisons were made
+\href{https://github.com/awconway/zhf-review}{here}. The primary
+comparison for this review was temperature measured from a
+zero-heat-flux thermometer versus temperature measured from a core site,
+which we defined as temperature measured at either an arterial,
+esophaeal, bladder or rectal site. Secondary comparisons were made
 between zero-heat-flux thermometers and temperatures taken at peripheral
@@
 accuracy of zero-heat-flux thermometers. The search strategies used for
-each data base can be located in \href{}{file 1}. Selection of studies
-was undertaken independently by two reviewers using
+each data base can be located \href{shiny\%20app}{here}. Selection of
+studies was undertaken independently by two reviewers using
 \href{https://www.covidence.org}{Covidence}.
@@
 
-\hypertarget{agreement-between-zhf-and-core-temperature-measurements}{%
-\subsection{Agreement between ZHF and core temperature
-measurements}\label{agreement-between-zhf-and-core-temperature-measurements}}
+\hypertarget{primary-comparison-zero-heat-flux-thermometer-versus-core-thermometers}{%
+\subsection{Primary comparison: zero-heat-flux thermometer versus core
+thermometers}\label{primary-comparison-zero-heat-flux-thermometer-versus-core-thermometers}}
+
+The pooled estimate for the mean bias between zero-heat-flux and core
+temperature measurements was 0\(^\circ C\). However, the variation in
+differences between studies was large, as displayed by the density plot
+in Figure 2. Consequently, the population limits of agreement, which
+take into consideration the between-study heterogeneity and sampling
+error, were wide, spanning from -1\(^\circ C\) to 1.1\(^\circ C\)
+(179,821 measurements; 576 participants; 13 studies). The quality of
+evidence for the primary comparison was downgraded to low quality due to
+concerns about study limitations and inconsistency. Population limits of
+agreement for the sensitivity analysis restricted to studies rated as
+having low risk of bias across all the domains of the QADAS-2 were
+similar to the primary analysis (104,294 measurements; 273 participants;
+5 stsudies). The mean bias was again 0\(^\circ C\) with population
+agreements spanning from -1\(^\circ C\) to 1.1\(^\circ C\).
+
+\begin{figure}
+
+{\centering \includegraphics{fig-2-1}
+
+}
+
+\caption{Comparisons between core and zero-heat-flux thermometers within and across studies.
+Blue curves are distributions of the differences between measurements from zero-heat-flux (ZHF) sensors and core temperature measurements in individual studies.
+The red curve is the distribution of the pooled estimate.}\label{fig:fig-2}
+\end{figure}
+
+We conducted two subgroup analyses for the primary comparison according
+to the clinical setting in which the study was conducted. In the subset
+of studies conducted in the ICU, the mean bias was 0 \(^\circ C\) with
+population limits of agreement between -1.5 \(^\circ C\) and 1.4
+\(^\circ C\). Whereas in the subset of studies that evaluated the use of
+zero-heat-flux thermometers during surgery found a mean bias of 0
+\(^\circ C\) with population limits of agreement from -1.1 \(^\circ C\)
+to 1.1 \(^\circ C\). The quality of evidence for these subgroup analyses
+was similarly rated as low quality due to concerns about study
+limitations and inconsistency.
+
+\hypertarget{secondary-comparisons-zero-heat-flux-thermometer-versus-peripheral-thermometers}{%
+\subsection{Secondary comparisons: zero-heat-flux thermometer versus
+peripheral
+thermometers}\label{secondary-comparisons-zero-heat-flux-thermometer-versus-peripheral-thermometers}}
+
+Zero-heat-flux thermometers were compared with sublingual thermometers
+and nasopharyngeal thermometers in the studies included in this review.
+The mean bias between zero-heat-flux and sublingual temperature
+measurements in meta-analysis of results from 2 studies was -0.2
+\(^\circ C\). Due to the limited number of studies and measurements,
+population limits of agreement were extremely wide, spanning from -13.3
+\(^\circ C\) to 12.8 \(^\circ C\). The quality of evidence for this
+comparison was rated as very low quality due to serious concerns about
+imprecision.
+
+The mean bias between zero-heat-flux and nasopharyngeal temperature
+measurements in meta-analysis of results from 4 studies was 0
+\(^\circ C\). Population limits of agreement were -1 \(^\circ C\) to 1
+\(^\circ C\). We downgraded the quality of evidence to low, again due to
+concerns about inconsistency and study limitations.
 
@@
 \section{Discussion}\label{discussion}}
+
+Results from this systematic review have important implications for
+practice. Clinicians should consider the potential that a temperature
+measurement from a zero-heat-flux thermometer could be as much as one
+\(^\circ C\) higher or lower than the true core temperature. This is
+similar to results from previous meta-analyses that compared other
+peripheral thermometers with core temperature measurements. However,
+these previous meta-analyses used statistical approaches that did not
+incorporate the magnitude of heteroogeneity in results between studies
+or sampling error. As such, it is possible that the zero-heat-flux
+thermometer is still more precise than these other peripheral
+thermometers.
+
+Whether or not teh zero-heat-flux thermometer is sufficiently accurate
+to be used in place of nasopharyngeal thermometers is unclear.
 
@@
 Trials.'' \emph{Controlled Clinical Trials} 7 (3). Elsevier: 177--88.
+
+\leavevmode\hypertarget{ref-eshraghi2014}{}%
+Eshraghi, Yashar, Vivian Nasr, Ivan Parra-Sanchez, Albert Van Duren,
+Mark Botham, Thomas Santoscoy, and Daniel I Sessler. 2014. ``An
+Evaluation of a Zero-Heat-Flux Cutaneous Thermometer in Cardiac Surgical
+Patients.'' \emph{Anesthesia \& Analgesia} 119 (3). LWW: 543--49.
 

### 2019-10-01 app/xml.R
dataframe

@@ -2,18 +2,41 @@ library(xml2)
 library(tidyverse)
 
 testxml <- xml2::read_xml(here::here("app", "data", "study-characteristics", "study-characteristics.xml"))
+rows <- xml_find_all(testxml, ".//ss:Row")
 
 #Study names
 study <- xml_find_all(testxml, ".//ss:Worksheet")
 study <- xml_attr(study, "Name")
 
-#Inclusion criteria
-rows <- xml_find_all(testxml, ".//ss:Row")
-inclusions <- xml_find_all(rows, "//ss:Row[@ss:Index='17']")
-inclusions <- xml_text(inclusions)
-inclusions <- stringr::str_remove(inclusions, "Inclusion criteria")
+index_number <- 3
+xml_extract <- function(index_number, source_name){
+  if(missing(source_name)) {
+    new_column <- xml_find_all(rows, glue::glue("//ss:Row[@ss:Index='{index_number}']"))
+    xml_text(new_column)
+  } else {
+  new_column <- xml_find_all(rows, glue::glue("//ss:Row[@ss:Index='{index_number}']"))
+  new_column <- xml_text(new_column)
+  stringr::str_remove(new_column, source_name)
+ }
+ }
+
+sponsorship <- xml_extract(3, "Sponsorship source")
+country <- xml_extract(4, "Country")
+setting <- xml_extract(5, "Setting")
+design <- xml_extract(13, "Design")
+inclusions <- xml_extract(17, "Inclusion criteria")
+exclusions <- xml_extract(18, "Exclusion criteria")
+temp_range <- xml_extract(25, "Temperature range (Celsius)")
+groups <- xml_extract(21)
+age <- xml_extract(22)
+female <- xml_extract(23)
+male <- xml_extract(24)
+
 # Dataframe
-dataframe <- tibble::tibble(study, inclusions)
+dataframe <- tibble::tibble(study, country, setting, design,
+                            inclusions, exclusions, sponsorship)
+
+glimpse(dataframe)
 
 #Resource
 #https://stackoverflow.com/questions/42799674/r-and-xml2-how-to-read-text-that-is-not-in-children-nodes-and-read-information

### 2019-10-01 app/app.R
data frame meta

@@ -1,9 +1,7 @@
-
 library(shiny)
 library(shinydashboard)
 library(shinydashboardPlus)
 library(tidyverse)
-library(ggplot2)
 library(DT)
 
 # Manuscript screenshot resolution ----
@@ -16,7 +14,7 @@ library(DT)
 
 # Load data ----
 
-data <- readxl::read_xlsx(here::here("app", "data", "zhf_extracted.xlsx"))
+data <- readxl::read_xlsx(here::here("app", "data", "zhf_extracted.xlsx"), n_max = 27)
 sum_findings <- readxl::read_xlsx(here::here("app", "data", "sum_findings.xlsx"))
 
 # Functions for calculating the Bland-Altman meta-analysis ----
@@ -62,18 +60,19 @@ loa_maker <- function(bias,V_bias,logs2,V_logs2) {
   CI_U_mod <- LOA_U + tcrit*sqrt(V_LOA_mod)
   CI_L_rve <- LOA_L - tcrit*sqrt(V_LOA_rve)
   CI_U_rve <- LOA_U + tcrit*sqrt(V_LOA_rve)
-  c(m, bias_mean,sqrt(sd2_est), tau_est, LOA_L, LOA_U, CI_L_mod, CI_U_mod, CI_L_rve, CI_U_rve)}
+  data.frame(m, bias_mean, sd2_est, tau_est, LOA_L, LOA_U, CI_L_mod, CI_U_mod, CI_L_rve, CI_U_rve)
+}
 
 #Primary meta-analysis (all included studies)
 data <- data %>%
   mutate(c = N/n)
 
 #variance
-data <-  if (data$corrected == "Yes"){
-  mutate(data, s2 = ((upper - bias)/1.96)^2)
-} else {
-  mutate(data, s2 = ((upper - bias)/1.96)^2)*((N-1)/(N-c))
-}
+data <- data %>% 
+  mutate(s2 = case_when(corrected == "Yes"  ~ ((upper - bias)/1.96)^2,
+                        corrected == "No" ~  ((upper - bias)/1.96)^2*(N-1)/(N-c)
+  )
+  )
 
 data <- data %>% 
   mutate(V_bias = s2/n)
@@ -97,7 +96,7 @@ data_core <- data %>% #eshragi overall
 data_core_lowrisk <- data_core %>% #eshragi overall
   filter(RoB_selection == "low" & RoB_spoton == "low" & RoB_comparator == "low" & RoB_flow =="low")
 
-data_core_op <- data%>% #eshragi intraop
[…]

### 2019-10-01 manuscript/manuscript.Rmd
minor

@@
 library(kableExtra)
-library(purrr)
-library(ggplot2)
-library(dplyr)
 library(qwraps2)
@@
 ```{r load-data, include=FALSE}
-data <- readxl::read_xlsx(here::here("data", "zhf_extracted.xlsx"))
+data <- readxl::read_xlsx(here::here("app", "data", "zhf_extracted.xlsx"))
 ```
@@
 data <- data %>%
-
   mutate(c = N/n)
@@
 
-data <-  if (data$corrected == "Yes"){
-
-  mutate(data, s2 = ((upper - bias)/1.96)^2)
-
-  } else {
-
-    mutate(data, s2 = ((upper - bias)/1.96)^2)*((N-1)/(N-c))
-
-    }
+data <- data %>% 
+  mutate(s2 = case_when(corrected == "Yes"  ~ ((upper - bias)/1.96)^2,
+         corrected == "No" ~  ((upper - bias)/1.96)^2*(N-1)/(N-c)
+                        )
+        )
 
@@
 
-data_core_op <- data%>% #eshragi intraop
+data_core_op <- data %>% #eshragi intraop
     filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
@@
 out <- loa_maker(group$bias,group$V_bias, group$logs2, group$V_logs2)
-out <- round(out, digits=1)
+out <- round(out, digits=2)
 out <- out %>% 
@@
       stat_function(fun=dnorm, args = list(pooled_bias, pooled_sd), colour = NA, geom="area", fill="lightcoral", alpha = 0.6) + 
-      scale_x_continuous(limits = c(-3.5,3.5)) + labs(x = expression('Difference between core and ZHF temperature measurements in'*~degree*C*''))+
+      scale_x_continuous(limits = c(-3.5,3.5), breaks = c(-2, -1, 0, 1, 2)) + labs(x = expression('Difference between core and ZHF temperature measurements in'*~degree*C*''))+
       scale_y_continuous(name = "Density \n", limits = c(0,2.5)) +  
@@
 
+We did not include studies that used the Temple Touch Pro.
+This is a thermometer similar to the zero-heat-flux device in that it is placed cutaneously, but the underlying technology is different.
+There have been x studies that evaluated the Temple Touch Pro device with promising results.
+
 ## Limitations

### 2019-10-01 manuscript/manuscript.tex
minor

@@
 %% load any required packages here
-
-\usepackage{booktabs}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{wrapfig}
-\usepackage{float}
-\usepackage{colortbl}
-\usepackage{pdflscape}
-\usepackage{tabu}
-\usepackage{threeparttable}
-\usepackage{threeparttablex}
-\usepackage[normalem]{ulem}
-\usepackage{makecell}
-\usepackage{xcolor}
 
@@
 \(^\circ C\). Due to the limited number of studies and measurements,
-population limits of agreement were extremely wide, spanning from -13.3
-\(^\circ C\) to 12.8 \(^\circ C\). The quality of evidence for this
+population limits of agreement were extremely wide, spanning from -17.9
+\(^\circ C\) to 17.5 \(^\circ C\). The quality of evidence for this
 comparison was rated as very low quality due to serious concerns about
@@
 to be used in place of nasopharyngeal thermometers is unclear.
+
+We did not include studies that used the Temple Touch Pro. This is a
+thermometer similar to the zero-heat-flux device in that it is placed
+cutaneously, but the underlying technology is different. There have been
+x studies that evaluated the Temple Touch Pro device with promising
+results.
 

### 2019-10-01 app/app.R
fixed issue with op

@@ -104,6 +104,9 @@ data_core_icu <- data %>% #eshragi postop
   filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
   filter(clinical_setting=="ICU" | clinical_setting=="Postoperative")
 
+data_conflict <- data_core %>% 
+  filter(`Funding/equipment/conflict with ZHF company` == "Yes")
+
 #clean up comparison column, change to full word
 data$comparison <- sub("NPA", "Nasopharyngeal", data$comparison) 
 data$comparison <- sub("PA", "Pulmonary artery", data$comparison) 
@@ -113,14 +116,12 @@ data$comparison <- sub("Eso", "Esophageal", data$comparison)
 
 format_results <- function(group){
   out <- loa_maker(group$bias,group$V_bias, group$logs2, group$V_logs2)
-  out <- round(out, digits=3)
   out <- out %>% 
     mutate(Participants = sum(group$n_count, na.rm=T)) %>% 
     mutate(Measurements = format(sum(group$N, na.rm = T), big.mark=",", scientific = FALSE)) %>% 
     mutate(Studies = length(unique(group$Study))) %>% 
     select(Studies, m, Participants, Measurements, bias_mean, sd2_est, tau_est, LOA_L, LOA_U, CI_L_rve, CI_U_rve) %>% 
     rename("Comparisons" = m)
-  out
 }
 
 
@@ -143,8 +144,8 @@ ui <- dashboardPage(
                    h4("Select a subset of studies to display in results:"), 
                    choices= c("Core",
                               "Core (low risk studies)",
-                              "Core (ICU only)",
-                              "Core (Intraoperative only)",
+                              "Core (ICU studies)",
+                              "Core (Intra-operative studies)",
                               "Nasopharyngeal",
                               "Sublingual",
                               "No conflicts of interest"))
@@ -422,8 +423,8 @@ server <- shinyUI(function(input, output) {
       switch(input$dataset,
              "Core" = data_core,
              "Core (low risk studies)" = data_core_lowrisk,
-             "Core (ICU only)" = data_core_icu,
-             "Core (intraoperative only)" = data_core_op,
+             "Core (ICU studies)" = data_core_icu,
+             "Core (Intra-operative studies)" = data_core_op,
              "Nasopharyngeal" = data_NPA,
              "Sublingual" = data_SL,
[…]

### 2019-10-03 RoB-figures.R
code to produce rob figures

@@ -1,0 +1,19 @@
+library(robvis)
+library(readxl)
+library(tidyverse)
+
+frame <- read_excel(here::here("manuscript", "data", "zhf_extracted.xlsx"))
+
+RoB <- frame %>% 
+  select(Study, RoB_selection, RoB_spoton, RoB_comparator, RoB_flow) %>% 
+  mutate(RoB_overall = if_else(RoB_selection == "low" &
+                                 RoB_spoton == "low" &
+                                 RoB_comparator == "low" &
+                                 RoB_flow == "low", "low", "high"))
+
+RoB[RoB == "unclear"] <- "some concerns"
+
+rob_summary(data = RoB, tool = "QUADAS-2", weighted = FALSE)
+rob_traffic_light(data = RoB, tool = "QUADAS-2")
+
+pr_push()

### 2019-10-03 app/app.R
deleted comments

@@ -1,15 +1,10 @@
 library(shiny)
+library(shinyLP)
 library(shinydashboard)
 library(shinydashboardPlus)
 library(tidyverse)
 library(DT)
 
-# Manuscript screenshot resolution ----
-# resolution to be set to 600 DP for springer articles
-# screenshot image and open in preview, then go to tools > adjust size... 
-# 1. enter new desired resolution 
-# 2. check box for 'resample image' to ensure new image is created with additional pixels
-# note that this will new image retains the same dimensions as original picture but has extra pixels
 
 
 # Load data ----

### 2019-10-16 manuscript/manuscript.Rmd
plot code simplified

@@
 ---
-title: "Accuracy and precision of zero-heat-flux temperature monitoring: a systematic review and meta- analysis"
+title: "Accuracy and precision of zero-heat-flux temperature monitoring: a systematic review and meta-analysis"
 titlerunning: Accuracy of zero-heat-flux temperature monitoring
@@
 m <- length(Te)
-wt_FE=1/V_T
+wt_FE <- 1/V_T
 T_FE <- sum(Te*wt_FE)/sum(wt_FE)
@@
 ```{r fig-1, fig.align="center", fig.cap="PRISMA Flow Diagram", echo=FALSE, fig.width=5.5, fig.path=""}
-library(ggplot2)
-  library(tibble)
-  library(tidyverse)
-  library(ggfittext)
-
-  line_size <- 0.50
-  box_type <- "round"
-  box_lines <- 0.5
-  box_colour <- "#ff4f14"
-  box_fill <- "white"
-  text_colour <- "#ff4f14"
-  arrow_colour <- "#ff4f14"
-
-  retrieved <- 129
-  duplicates <- 35
-  screened <- retrieved-duplicates
-  full_text <- 21
-  screen_excluded <- screened-full_text
-  included <- 15
-  full_text_excluded <- full_text-included
-  wrong_intervention <- 4
-  wrong_comparator <- 2
-  wrong_design <- 1
-  awaiting_classification <- 2
-
-# Main flow y coordinates  
-  import_y_max <- 100
-  import_y_min <- 90
-  screen_y_max <- 80
-  screen_y_min <- 70
-  full_y_max <- 60
-  full_y_min <- 50
-  included_y_max <- 40
-  included_y_min <- 30
-
-# Scondary flow y coordinates  
-  duplicates_y_max <- 90
-  duplicates_y_min <- 80
-
-  full_excluded_y_min <- 25
-  full_excluded_y_max <- 45
-
-  screen_excluded_y_min <- 65
-  screen_excluded_y_max <- 75
-
-  awaiting_classification_y_min <- 50
-  awaiting_classification_y_max <- 60
-
-# x coordinates  
-  main_x_min <- 20
-  main_x_max <- 70
-
-  second_x_min <- 75
-  second_x_max <- 95
-
-  arrow_x <- 45
-
-  ###Plot space set-up####
-  data <- tibble(x= 23:100, y = 23:100)
-   data %>% 
-    ggplot(aes(x, y)) +
-    theme_linedraw() +
-
-  ########## Main box flow ###########
-
-  # import box
-
-  annotation_custom(grob = grid::roundrectGrob(gp = grid::gpar(col = box_colour, fill = box_fill)),
-    xmin = main_x_min, xmax=main_x_max, ymin=import_y_min, ymax=import_y_max)+
-    geom_fit_text(xmin = main_x_min, xmax=main_x_max, ymin=import_y_min, ymax=100,
-                  label= glue::glue(retrieved, ' references identified'), 
-                  reflow = TRUE, colour = text_colour) +
-
-# screen box
-  annotation_custom(grob = grid::roundrectGrob(gp = 
-                    grid::gpar(col = box_colour, fill = box_fill)),
-                    xmin = main_x_min, xmax=main_x_max, ymin=screen_y_min, 
-                    ymax=screen_y_max) +
-  geom_fit_text(xmin = main_x_min, xmax=main_x_max, ymin=screen_y_min, ymax=screen_y_max,
-           label= glue::glue(screened, ' titles and abstracts screened'), 
-           reflow = TRUE, colour = text_colour) +
-
-# full text box
-  annotation_custom(grob = grid::roundrectGrob(gp = 
-          grid::gpar(col = box_colour, fill = box_fill)),
-          xmin = main_x_min, xmax=main_x_max, ymin=full_y_min, ymax=full_y_max) +
-  geom_fit_text( xmin = main_x_min, xmax=main_x_max, ymin=full_y_min, ymax=full_y_max,
-                 label= glue::glue(full_text, ' full-text articles assessed'), 
-                  reflow = TRUE, colour = text_colour) +
-
-# included box 
-  annotation_custom(grob = grid::roundrectGrob(gp = 
-               grid::gpar(col = box_colour, fill = box_fill)),
-               xmin = main_x_min, xmax=main_x_max, 
-                    ymin=included_y_min, ymax=included_y_max) +
-  geom_fit_text(xmin = main_x_min, xmax=main_x_max, 
-                ymin=included_y_min, ymax=included_y_max,
-                label= glue::glue(included, ' studies included'), 
-                 reflow = TRUE, colour = text_colour) +
-
-######### Secondary flow boxes ############
-
-  annotation_custom(grob = grid::roundrectGrob(gp = 
-        grid::gpar(col = box_colour, fill = box_fill)),
-        xmin = second_x_min, xmax=second_x_max, 
-                    ymin=duplicates_y_min, ymax=duplicates_y_max) +
-  geom_fit_text(xmin = second_x_min, xmax=second_x_max, 
-                ymin=duplicates_y_min, ymax=duplicates_y_max,
-                label= glue::glue(duplicates, ' duplicates removed'),
-                 reflow = TRUE, colour = text_colour) +
-
-# excluded box 
- annotation_custom(grob = 
-                              grid::roundrectGrob(gp = 
-                              grid::gpar(col = box_colour, fill = box_fill)),
-                            xmin = second_x_min, xmax=second_x_max, 
-                    ymin=screen_excluded_y_min, ymax=screen_excluded_y_max) +
-  geom_fit_text(xmin = second_x_min, xmax=second_x_max, 
-                ymin=screen_excluded_y_min, ymax=screen_excluded_y_max,
-                label= glue::glue(screen_excluded, ' studies excluded'),
-                 reflow = TRUE, colour = text_colour) +
-
-# awaiting classifications box 
-    annotation_custom(grob = 
-                        grid::roundrectGrob(gp = 
-                                              grid::gpar(col = box_colour, fill = box_fill)),
-                      xmin = second_x_min, xmax=second_x_max, 
-                      ymin=awaiting_classification_y_min, ymax=awaiting_classification_y_max) +
-    geom_fit_text(xmin = second_x_min, xmax=second_x_max, 
-                  ymin=awaiting_classification_y_min, ymax=awaiting_classification_y_max,
-                  label= glue::glue(awaiting_classification, ' studies awaiting classification'),
-                  reflow = TRUE, colour = text_colour) +
-
-# full text excluded box 
-annotation_custom(grob = 
-                             grid::roundrectGrob(gp = 
-                            grid::gpar(col = box_colour, fill = box_fill)),
-                           xmin = second_x_min, xmax=second_x_max, 
-                   ymin=full_excluded_y_min, ymax=full_excluded_y_max) +
- geom_fit_text(xmin = second_x_min, xmax=second_x_max,
-                ymin=full_excluded_y_max-7, ymax=full_excluded_y_max,
-                label= glue::glue(full_text_excluded, ' studies excluded'),
-                 reflow = TRUE, colour = text_colour) +
- geom_fit_text(xmin = second_x_min, xmax=second_x_max,
-                ymin=full_excluded_y_max-17, ymax=full_excluded_y_max-7,
-                label= glue::glue(wrong_intervention, ' wrong intervention','\n',
-                                  wrong_intervention, ' wrong comparator','\n',
-                                  wrong_intervention, ' wrong design'),
-                 colour = text_colour, grow = TRUE) +
-
-####### Main flow arrows#######
-
-  # Import - screen
- geom_segment(
-  x=arrow_x, xend = arrow_x, y = import_y_min, yend = screen_y_max+0.25, 
-  size = line_size,  colour = arrow_colour,
-  arrow = arrow(length = unit(2, "mm"), type= "closed")) +
-
-# Screen - full text
-  geom_segment(
-    x=arrow_x, xend=arrow_x, y=screen_y_min, yend=full_y_max+0.25, 
-    size = line_size,  colour = arrow_colour,
-    arrow = arrow(length = unit(2, "mm"), type= "closed")) +
-
-# Full text - included
-
-  geom_segment(
-    x=arrow_x, xend=arrow_x, y=full_y_min, yend=included_y_max+0.25, 
-    size = line_size,  colour = arrow_colour,
-    arrow = arrow(length = unit(2, "mm"), type= "closed")) +
-
-####Secondary flow arrows########
-
-# Import - duplicates
-
-  geom_curve(
-    x = arrow_x, xend = second_x_min, 
-    y = duplicates_y_max,  yend = duplicates_y_max-5, linetype = "dashed",
-    curvature = 0.1, colour = arrow_colour) +
-
-# Screen - excluded
-
-  geom_curve(
-    x = arrow_x, xend = second_x_min, 
-    y = screen_y_min,  yend = screen_excluded_y_max-5, linetype = "dashed",
-    curvature = 0.1, colour = arrow_colour) +
-
-# Screen - awaiting
-
-    geom_curve(
-      x = arrow_x, xend = second_x_min, 
-      y = screen_y_min,  yend = awaiting_classification_y_max-5, linetype = "dashed",
-      curvature = -0.2, colour = arrow_colour) +
-
-  # Full text - excluded
-
-  geom_curve(
-    x = arrow_x, xend = second_x_min, 
-    y = full_y_min, yend = full_excluded_y_max-10, linetype = "dashed",
-    curvature = -0.2, colour = arrow_colour) +
-
- theme_void() +
-  coord_cartesian(ylim = c(23,100))
+# https://github.com/awconway/ggprisma
+ggprisma::ggprisma(retrieved = 129, included = 15, duplicates = 35, full_text = 21, wrong_intervention = 4, wrong_comparator = 2, wrong_design = 1, awaiting_classification = 2)
 ```

### 2019-10-17 app/app.R
added prisma diagram tab

@@ -130,10 +130,11 @@ ui <- dashboardPage(
       # menu item tabs
       menuItem("Home", tabName="landing_page", icon=icon("home")),
       menuItem("Search strategy", tabName="search", icon=icon("search")),
+      menuItem("PRISMA flow diagram", tabName = "prisma", icon = icon("project-diagram")),
       menuItem("Results", tabName="Plot", icon=icon("chart-area")),
       menuItem("Data used in meta-analysis", tabName="DT", icon=icon("table")),
       menuItem("Extracted data", tabName="frame", icon=icon("file-excel")), 
-      menuItem("Risk-of-bias", tabName = "Rob", icon = icon("exclamation-circle")),
+      menuItem("Risk-of-bias", tabName = "rob", icon = icon("exclamation-circle")),
       
       br(), 
       
@@ -191,16 +192,21 @@ ui <- dashboardPage(
   
 
     tabItems(
-      tabItem(tabName="Rob",
+      tabItem(tabName = "rob",
               fluidRow(
                 tabBox(width = 12,
                        tabPanel(p("Risk of bias across studies"),
-                                plotOutput("Rob_summary")
+                                plotOutput("rob_summary")
                        ),
                        tabPanel(p("Risk of bias in individual studies"),
-                                plotOutput("Rob_traffic_light")
+                                plotOutput("rob_traffic_light")
                        )
                 )
+              )
+      ),
+      tabItem(tabName = "prisma",
+              fluidRow(width  = 12,
+                       plotOutput("prisma_diagram")
               )
       ),
       tabItem(tabName="Plot",
@@ -419,7 +425,7 @@ ui <- dashboardPage(
 
 server <- shinyUI(function(input, output) {
   
-  output$Rob_summary <- renderPlot({
+  output$rob_summary <- renderPlot({
     frame <- read_excel(here::here("manuscript", "data", "zhf_extracted.xlsx"))
     
     RoB <- frame %>% 
@@ -434,7 +440,7 @@ server <- shinyUI(function(input, output) {
     rob_summary(data = RoB, tool = "QUADAS-2", weighted = FALSE)
   })
   
-  output$Rob_traffic_light <- renderPlot({
+  output$rob_traffic_light <- renderPlot({
     frame <- read_excel(here::here("manuscript", "data", "zhf_extracted.xlsx"))
     
     RoB <- frame %>% 
[…]

### 2019-10-25 forest-plot.R
more work on plot to do

@@ -1,0 +1,101 @@
+library(ggimage)
+data_core$image <- sample("user.png",
+                          size=19, replace = TRUE)
+data_core$ruler <- sample("ruler.png",
+                          size=19, replace = TRUE)
+
+
+study <- data_core %>% 
+  mutate(id = row_number()) %>% 
+  ggplot()+
+  geom_text(aes(x=id, y=0, label=Study, hjust="left"))+
+  theme_void()+
+  coord_flip()
+
+
+results <- data_core %>% 
+  mutate(id = row_number()) %>% 
+  ggplot()+
+  geom_point(aes(x=id, y=bias), colour = "#6D9EC1")+
+  geom_linerange(aes(x=id, ymin=lower, ymax=upper), colour = "#6D9EC1", size=1)+
+  coord_flip()+ 
+  theme_void()+
+  theme(
+    panel.background = element_rect(fill = "#BFD5E3", colour = "white",
+                                    size = 2, linetype = "solid"),
+    panel.grid.major = element_line(size = 0.5, linetype = 'solid',
+                                    colour = "white"), 
+    panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
+                                    colour = "white")
+        )+
+  scale_x_continuous(breaks = NULL)
+
+
+
+participants <- data_core %>% 
+  mutate(id = row_number()) %>% 
+  ggplot()+
+    geom_linerange(aes(x=id, ymin=0, ymax=n), colour = "#930093", size=2)+
+  geom_label(aes(x=id, y=n, label = n), colour="#930093")+
+  theme_void()+
+  coord_flip()+
+  theme_void()+
+  theme(
+    panel.background = element_rect(fill = "white", colour = "white",
+                                    linetype = "solid"),
+    panel.grid.major = element_line(size = 0.1, linetype = 'solid',
+                                    colour = "#ffceff")
+  )+
+  scale_x_continuous(breaks = NULL)+
+  geom_image(aes(x=id, y=-5, image=image), hjust="left")
+
+comparison <- data_core %>% 
+  mutate(id = row_number()) %>% 
+  ggplot()+
+  geom_text(aes(x=id, y=0, label = comparison), hjust="left")+
+  theme_void()+
+  coord_flip()
+
+# ruler <- data_core %>% 
+#   mutate(id = row_number()) %>% 
+#   ggplot()+
[…]

### 2019-10-28 forest-plot.R
responsive text using ggfittext

@@ -1,23 +1,37 @@
-library(ggimage)
-data_core$image <- sample("user.png",
-                          size=19, replace = TRUE)
-data_core$ruler <- sample("ruler.png",
-                          size=19, replace = TRUE)
+# library(ggimage)
+# data_core$image <- sample("user.png",
+#                           size=19, replace = TRUE)
+# data_core$ruler <- sample("ruler.png",
+#                           size=19, replace = TRUE)
 
+
+library(ggfittext)
+
+year <- data_core %>%
+  separate(Study, c("Study", "Year"), sep = ", ")  %>% 
+  mutate(Study = as.factor(Study)) %>% 
+  ggplot()+
+  geom_fit_text(aes(x=Study, y=0, label=Year, hjust="left"), place = "left", reflow=TRUE, grow = FALSE,
+                 position = position_dodge(width = 0.99), show.legend=FALSE)+
+  theme_void()+
+  coord_flip()
 
 study <- data_core %>% 
-  mutate(id = row_number()) %>% 
+  separate(Study, c("Study", "Year"), sep = ", ")  %>% 
+  mutate(id = row_number()) %>%  
+  mutate(Study = as.factor(Study)) %>% 
   ggplot()+
-  geom_text(aes(x=id, y=0, label=Study, hjust="left"))+
+  geom_fit_text(aes(x=Study, y=0, label=Study, hjust="left"), place = "left", reflow=TRUE, grow = FALSE,
+                position = position_dodge(width = 0.99), show.legend=FALSE)+
   theme_void()+
   coord_flip()
 
 
 results <- data_core %>% 
-  mutate(id = row_number()) %>% 
-  ggplot()+
-  geom_point(aes(x=id, y=bias), colour = "#6D9EC1")+
-  geom_linerange(aes(x=id, ymin=lower, ymax=upper), colour = "#6D9EC1", size=1)+
+  mutate(id = row_number()) %>%
+  ggplot(aes(x=Study, y=bias))+
+  geom_point(aes(x=Study, y=bias, colour=group), position = position_dodge(width = 0.99), show.legend=FALSE)+
+  geom_linerange(aes(x=Study, ymin=lower, ymax=upper, colour=group), size=1, position = position_dodge(width = 0.99), show.legend=FALSE)+
   coord_flip()+ 
   theme_void()+
   theme(
@@ -28,15 +42,18 @@ results <- data_core %>%
     panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
[…]

### 2019-11-05 app/app.R
rows in spreadsheet and no conflict corrected

@@ -10,7 +10,7 @@ library(readxl)
 
 # Load data ----
 
-data <- readxl::read_xlsx(here::here("app", "data", "zhf_extracted.xlsx"), n_max = 27)
+data <- readxl::read_xlsx(here::here("app", "data", "zhf_extracted.xlsx"))
 sum_findings <- readxl::read_xlsx(here::here("app", "data", "sum_findings.xlsx"))
 
 # Functions for calculating the Bland-Altman meta-analysis ----
@@ -101,7 +101,7 @@ data_core_icu <- data %>% #eshragi postop
   filter(clinical_setting=="ICU" | clinical_setting=="Postoperative")
 
 data_conflict <- data_core %>% 
-  filter(`Funding/equipment/conflict with ZHF company` == "Yes")
+  filter(`Funding/equipment/conflict with ZHF company` == "No")
 
 #clean up comparison column, change to full word
 data$comparison <- sub("NPA", "Nasopharyngeal", data$comparison) 

### 2019-11-05 manuscript/manuscript.Rmd
more work on plot to do
additional study added

@@
 ```{r load-data, include=FALSE}
-data <- readxl::read_xlsx(here::here("app", "data", "zhf_extracted.xlsx"))
+data <- readxl::read_xlsx(here::here("data", "zhf_extracted.xlsx"))
 ```
@@
 
-data_core <- data %>% #eshragi overall
+#eshragi overall
+data_core <- data %>% 
   filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
@@
 data_conflict <- data_core %>% 
-  filter(`Funding/equipment/conflict with ZHF company` == "Yes")
+  filter(`Funding/equipment/conflict with ZHF company` == "No")
 
@@
 # https://github.com/awconway/ggprisma
-ggprisma::ggprisma(retrieved = 129, included = 15, duplicates = 35, full_text = 21, wrong_intervention = 4, wrong_comparator = 2, wrong_design = 1, awaiting_classification = 2)
+ggprisma::ggprisma(retrieved = 130, included = 16, duplicates = 35, full_text = 22, wrong_intervention = 4, wrong_comparator = 2, wrong_design = 1, awaiting_classification = 2)
 ```

### 2019-11-05 manuscript/manuscript.Rmd
source meta-analysis function from github

@@
 library(knitr)
-```
-
-```{r meta-function, echo=FALSE}
-meta <-  function(Te,V_T){
-m <- length(Te)
-wt_FE <- 1/V_T
-T_FE <- sum(Te*wt_FE)/sum(wt_FE)
-Q <- sum(wt_FE*(Te - T_FE)^2)
-S1 <- sum(wt_FE)
-S2 <- sum(wt_FE^2)
-o2 <- (Q - (m - 1))/(S1 - S2/S1)
-wt_RE <- 1/(V_T + o2)
-T_RE <- sum(Te*wt_RE)/sum(wt_RE)
-V_T_RE_mod <- 1/sum(wt_RE)
-V_T_RE_rve <- (m/(m-1))*sum(wt_RE^2*(Te - T_RE)^2)/(sum(wt_RE))^2
-c(m,T_RE,o2,V_T_RE_mod, V_T_RE_rve)
-}
-loa_maker <- function(bias,V_bias,logs2,V_logs2) {
-bias_row=meta(bias, V_bias)
-logs2_row=meta(logs2, V_logs2)
-bias_mean <- bias_row[2]
-sd2_est <- exp(logs2_row[2])
-tau_est <- bias_row[3]
-LOA_L <- bias_mean - 2*sqrt(sd2_est + tau_est)
-LOA_U <- bias_mean + 2*sqrt(sd2_est + tau_est)
-m <- bias_row[1]
-tcrit <- qt(1-.05/2,m-1)
-B1 <- sd2_est^2/(sd2_est + tau_est)
-B2 <- tau_est^2/(sd2_est + tau_est)
-wt <- 1/V_bias
-S1 <- sum(wt)
-S2 <- sum(wt^2)
-S3 <- sum(wt^3)
-A0 <- 2*(m-1)/(S1-S2/S1)^2
-A1 <- 4/(S1 - S2/S1)
-A2 <- 2*(S2-2*S3/S1+S2^2/S1^2)/(S1-S2/S1)^2
-V_logT2 <- A0/tau_est^2 + A1/tau_est + A2
-V_logT2 <- 2/sum((V_bias + tau_est)^(-2))
-V_LOA_mod <- bias_row[4] + B1*logs2_row[4] + B2*V_logT2
-V_LOA_rve <- bias_row[5] + B1*logs2_row[5] + B2*V_logT2
-CI_L_mod <- LOA_L - tcrit*sqrt(V_LOA_mod)
-CI_U_mod <- LOA_U + tcrit*sqrt(V_LOA_mod)
-CI_L_rve <- LOA_L - tcrit*sqrt(V_LOA_rve)
-CI_U_rve <- LOA_U + tcrit*sqrt(V_LOA_rve)
-data.frame(m, bias_mean, sd2_est, tau_est, LOA_L, LOA_U, CI_L_mod, CI_U_mod, CI_L_rve, CI_U_rve)
-}
+library(bama)
 ```
@@
 format_results <- function(group){
-out <- loa_maker(group$bias,group$V_bias, group$logs2, group$V_logs2)
+out <- bama::loa_maker(group$bias,group$V_bias, group$logs2, group$V_logs2)
 out <- round(out, digits=2)

### 2019-11-05 app/app.R
app is working

@@ -6,60 +6,15 @@ library(tidyverse)
 library(DT)
 library(robvis)
 library(readxl)
-
+library(bama) #awconway/bama
+library(ggprisma)
 
 # Load data ----
 
 data <- readxl::read_xlsx(here::here("app", "data", "zhf_extracted.xlsx"))
 sum_findings <- readxl::read_xlsx(here::here("app", "data", "sum_findings.xlsx"))
 
-# Functions for calculating the Bland-Altman meta-analysis ----
-
-meta <-  function(Te,V_T){
-  m <- length(Te)
-  wt_FE=1/V_T
-  T_FE <- sum(Te*wt_FE)/sum(wt_FE)
-  Q <- sum(wt_FE*(Te - T_FE)^2)
-  S1 <- sum(wt_FE)
-  S2 <- sum(wt_FE^2)
-  o2 <- (Q - (m - 1))/(S1 - S2/S1)
-  wt_RE <- 1/(V_T + o2)
-  T_RE <- sum(Te*wt_RE)/sum(wt_RE)
-  V_T_RE_mod <- 1/sum(wt_RE)
-  V_T_RE_rve <- (m/(m-1))*sum(wt_RE^2*(Te - T_RE)^2)/(sum(wt_RE))^2
-  c(m,T_RE,o2,V_T_RE_mod, V_T_RE_rve)
-}
-loa_maker <- function(bias,V_bias,logs2,V_logs2) {
-  bias_row=meta(bias, V_bias)
-  logs2_row=meta(logs2, V_logs2)
-  bias_mean <- bias_row[2]
-  sd2_est <- exp(logs2_row[2])
-  tau_est <- bias_row[3]
-  LOA_L <- bias_mean - 2*sqrt(sd2_est + tau_est)
-  LOA_U <- bias_mean + 2*sqrt(sd2_est + tau_est)
-  m <- bias_row[1]
-  tcrit <- qt(1-.05/2,m-1)
-  B1 <- sd2_est^2/(sd2_est + tau_est)
-  B2 <- tau_est^2/(sd2_est + tau_est)
-  wt <- 1/V_bias
-  S1 <- sum(wt)
-  S2 <- sum(wt^2)
-  S3 <- sum(wt^3)
-  A0 <- 2*(m-1)/(S1-S2/S1)^2
-  A1 <- 4/(S1 - S2/S1)
-  A2 <- 2*(S2-2*S3/S1+S2^2/S1^2)/(S1-S2/S1)^2
[…]

### 2019-11-05 app/app.R
deleted "app" from read_xlsx filepaths

@@ -11,8 +11,8 @@ library(ggprisma)
 
 # Load data ----
 
-data <- readxl::read_xlsx(here::here("app", "data", "zhf_extracted.xlsx"))
-sum_findings <- readxl::read_xlsx(here::here("app", "data", "sum_findings.xlsx"))
+data <- readxl::read_xlsx(here::here("data", "zhf_extracted.xlsx"))
+sum_findings <- readxl::read_xlsx(here::here( "data", "sum_findings.xlsx"))
 
 # create additional columns for meta-analysis
 data <- data %>%
@@ -387,7 +387,7 @@ ui <- dashboardPage(
 server <- shinyUI(function(input, output) {
   
   output$Rob_summary <- renderPlot({
-    frame <- read_excel(here::here("app", "data", "zhf_extracted.xlsx"))
+    frame <- read_excel(here::here("data", "zhf_extracted.xlsx"))
     
     RoB <- frame %>% 
       select(Study, RoB_selection, RoB_spoton, RoB_comparator, RoB_flow) %>% 
@@ -402,7 +402,7 @@ server <- shinyUI(function(input, output) {
   })
   
   output$Rob_traffic_light <- renderPlot({
-    frame <- read_excel(here::here("app", "data", "zhf_extracted.xlsx"))
+    frame <- read_excel(here::here("data", "zhf_extracted.xlsx"))
     
     RoB <- frame %>% 
       select(Study, RoB_selection, RoB_spoton, RoB_comparator, RoB_flow) %>% 

### 2019-11-06 app/app.R
fixed figure caption and reordered tabs

@@ -89,10 +89,10 @@ ui <- dashboardPage(
       menuItem("Home", tabName="landing_page", icon=icon("home")),
       menuItem("Search strategy", tabName="search", icon=icon("search")),
       menuItem("Study selection", tabName="selection", icon=icon("hand-pointer")),
+      menuItem("Risk of bias", tabName = "Rob", icon = icon("exclamation-circle")),
       menuItem("Meta-analysis results", tabName="Plot", icon=icon("chart-area")),
       menuItem("Data used in meta-analysis", tabName="DT", icon=icon("table")),
       menuItem("Extracted data", tabName="frame", icon=icon("file-excel")), 
-      menuItem("Risk of bias", tabName = "Rob", icon = icon("exclamation-circle")),
       
       br(), 
       
@@ -183,7 +183,7 @@ ui <- dashboardPage(
             br(),
             br(),
             br(),
-                   h2("This plot shows comparisons between core and zero-heat-flux thermometers within and across studies.") ,
+                   h2("This plot shows comparisons between comparator and zero-heat-flux thermometers within and across studies.") ,
                    h4("Blue curves are distributions of the differences in individual studies. The red curve is the distribution of the pooled estimate."),  # caption = caption under the plot
             
             

### 2019-11-07 app/app.R
added loading screen

@@ -8,7 +8,7 @@ library(robvis)
 library(readxl)
 library(bama) #awconway/bama
 library(ggprisma)
-
+library(waiter)
 # Load data ----
 
 data <- readxl::read_xlsx(here::here("data", "zhf_extracted.xlsx"))
@@ -108,7 +108,9 @@ ui <- dashboardPage(
       
     ) 
   ),
-  dashboardBody(
+  dashboardBody(  
+    use_waiter(include_js = FALSE),
+
     tags$head(tags$style(HTML(
     # increase padding on "select display format" in side bar  
     '#select_format {
@@ -381,10 +383,12 @@ ui <- dashboardPage(
 </div>
 ')
               ))
-  )) #end dashboardBody
+  )  ,  show_waiter_on_load(spin_folding_cube()) 
+) #end dashboardBody
 ) #end dashboardPage
 
 server <- shinyUI(function(input, output) {
+  Sys.sleep(3) # do something that takes time
   
   output$Rob_summary <- renderPlot({
     frame <- read_excel(here::here("data", "zhf_extracted.xlsx"))
@@ -671,6 +675,7 @@ output$dt_selected_subset <- renderUI({HTML(paste("Comparison between", tolower(
 #                                          estimates of limits of agreement (LoA) between", tolower(input$dataset), "and ZHF thermometry (ie. population LoA)."))
 # #}) # end of output$caption
 
+hide_waiter()
 
 }) # end of server
 

### 2019-11-26 app/app.R
changed to show images instead of reactive content

@@ -2,83 +2,83 @@ library(shiny)
 library(shinyLP)
 library(shinydashboard)
 library(shinydashboardPlus)
-library(tidyverse)
-library(DT)
-library(robvis)
-library(readxl)
-library(bama) #awconway/bama
-library(ggprisma)
+# library(tidyverse)
+# library(DT)
+# library(robvis)
+# library(readxl)
+# library(bama) #awconway/bama
+# library(ggprisma)
 library(waiter)
 # Load data ----
+# 
+# data <- readxl::read_xlsx(here::here("app", "data", "zhf_extracted.xlsx"))
+# sum_findings <- readxl::read_xlsx(here::here("app", "data", "sum_findings.xlsx"))
+# 
+# # create additional columns for meta-analysis
+# data <- data %>%
+#   mutate(c = N/n)
+# 
+# #variance
+# data <- data %>% 
+#   mutate(s2 = case_when(corrected == "Yes"  ~ ((upper - bias)/1.96)^2,
+#                         corrected == "No" ~  ((upper - bias)/1.96)^2*(N-1)/(N-c)
+#   )
+#   )
+# 
+# data <- data %>% 
+#   mutate(V_bias = s2/n)
+# 
+# data <- data %>% 
+#   mutate(logs2 = log(s2)+1/(n-1))
+# 
+# data <- data %>% 
+#   mutate(V_logs2 = 2/(n-1))
+# 
+# # Create subgroups
+# 
+# data_NPA <- data %>% 
+#   filter(comparison == "NPA")
+# 
+# data_SL <- data %>% 
+#   filter(comparison == "Sublingual")
+# 
+# data_core <- data %>% #eshragi overall
+#   filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
+#   filter(comments != "Intraoperative, off cardiopulmonary bypass" & comments != "Postoperative")
+# 
+# data_core_lowrisk <- data_core %>% #eshragi overall
+#   filter(RoB_selection == "low" & RoB_spoton == "low" & RoB_comparator == "low" & RoB_flow =="low")
+# 
+# data_core_op <- data %>% #eshragi intraop
+#   filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
[…]

### 2019-11-26 app/app.R
additional gofers

@@ -184,6 +184,12 @@ ui <- dashboardPage(
                        ),
                        tabPanel(p("ZHF vs nasopharyngeal"),
                                 img(src="gofer_NPA.png", height="100%", width="100%")
+                       ),
+                       tabPanel(p("ZHF vs sublingual"),
+                                img(src="gofer_SL.png", height="100%", width="100%")
+                       ),
+                       tabPanel(p("Studies without industry funding - ZHF vs core"),
+                                  img(src="gofer_no_conflict.png", height="100%", width="100%")
                        )
                 )
               )

### 2019-11-26 manuscript/manuscript.Rmd
manuscript in distill format

@@
 ---
-title: "Accuracy and precision of zero-heat-flux temperature monitoring: a systematic review and meta-analysis"
-titlerunning: Accuracy of zero-heat-flux temperature monitoring
-authorrunning: Conway
-thanks: | 
-    Grants or other notes about the article that should go on the front 
-    page should be placed here. General acknowledgments should be placed at the
-    end of the article.
-
-authors: 
+title: "Accuracy and precision of zero-heat-flux temperature monitoring"
+description: A systematic review and meta-analysis
+author: 
 - name: Aaron Conway
@@
   email: aaron.conway@utoronto.ca
+  url: https://www.aaronconway.info
+- name: Megan Bittner
+  address: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
+- name: Dan Phan
+  address: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
 - name: Navpreet Kamboj
@@
   email: navpreet.kamboj@mail.utoronto.ca
-
-keywords:
-- key
-- dictionary
-- word
-
-abstract: |
-  The text of your abstract.  150 -- 250 words.
-
+- name: Kristina Chang
+  address: Toronto General Hospital, UHN
+- name: Peter Collins
+  address: Toronto General Hospital, UHN
+- name: Matteo Parotto
+  address: Toronto General Hospital, UHN
+date: "`r Sys.Date()`"
 bibliography: bibliography.bib
-output: rticles::springer_article
+output: distill::distill_article
 ---
@@
 library(tidyverse)
-library(kableExtra)
-library(qwraps2)
 library(knitr)
-library(bama)
+library(bama) # https://github.com/awconway/bama
+library(ggprisma) # https://github.com/awconway/ggprisma
+library(gt)
 ```
@@
 ```{r load-data, include=FALSE}
-data <- readxl::read_xlsx(here::here("data", "zhf_extracted.xlsx"))
+data <- readxl::read_xlsx(here::here("manuscript", "data", "zhf_extracted.xlsx"))
 ```
@@
 
-# Introduction
+<div class="l-page-outset">
+<blockquote>
+### Abstract
+
+**Background**
+
+Zero-heat-flux thermometers are non-invasive devices that can be used to continuously monitor temperature.
+These devices are increasingly being used in clinical practice to substitute for invasive core temperature measurement during surgery and in critical care settings.
+The aim of this review was to determine the accuracy and precision of zero-heat-flux temperture measurements.
+
+**Methods**
+
+Medline and EMBASE were searched for studies that reported on a measurement of core or peripheral temperature that coincided with a measurement from the zero-heat-flux device.
+Study selection and quality assessment (using the QUADAS-2) was performed independently.
+The GRADE approach was used to summarize the strength of the body of evidence.
+Pooled estimates of the mean bias and limits of agreement with outer 95% confidence intervals (termed population limits of agreement) were calculated.
+
+**Results**
+
+Sixteen studies were included.
+The primary comparison of zero-heat-flux versus core temperature measurements consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies.
+Data from `r primary$Participants` participants with `r format(primary$Measurements, scientfic=F)` paired measurements were included.
+The pooled estimate for the mean bias was `r primary$bias_mean`°C.
+Population limits of agreement, which take into consideration the between-study heterogeneity and sampling error, were wide, spanning from `r primary$CI_L_rve`°C to `r primary$CI_U_rve`°C.
+The GRADE evidence quality rating was downgraded to moderate due to concerns about study limitations.
+Population limits of agreement for the sensitivity analysis restricted to studies rated as having low risk of bias across all the domains of the QADAS-2 were similar to the primary analysis.
+
+**Conclusion**
+
+The range of uncertainty in the accuracy of the zero-heat-flux thermometer should be taken into account when using measurements from this device to inform clinical decision-making.
+Clinicians should therefore consider the potential that a temperature measurement from a zero-heat-flux thermometer could be as much as 1°C higher or lower than core temperature.
+Use of this device may not be appropriate in situations where a difference in temperature of less than 1°C is important to detect.
+
+</blockquote>
+</div>
+
+## Introduction
 
@@
 
-# Methods
+## Methods
 
@@
 
-## Inclusion criteria
+### Inclusion criteria
 
@@
 
-## Data sources and searches
+### Data sources and searches
 
@@
 This search strategy is an efficient approach for systematic reviews of diagnostic test accuracy studies.[@preston2015improving] We also conducted forward citation searching, by using Google Scholar to search the citations of the first article published on the accuracy of zero-heat-flux thermometers.
-The search strategies used for each data base can be located [here](shiny app).
+The search strategies used for each data base can be located [here](https://aconway.dev/zhf app).
 Selection of studies was undertaken independently by two reviewers using [Covidence](https://www.covidence.org).
 
-## Data extraction and quality assessment
+### Data extraction and quality assessment
 
@@
 
-## Data synthesis and analysis
+### Data synthesis and analysis
 
@@
 
-Measures of uncertainty were included in our meta-analyses by calculating the outer $95\%$ confidence intervals for pooled limits of agreement.
+Measures of uncertainty were included in our meta-analyses by calculating the outer 95% confidence intervals for pooled limits of agreement.
 We also accounted for repeated measurements if they were not properly adjusted for in individual studies.
@@
 The R statistical program was used to conduct all analyses [@team2017r].
-All data and R code used in the meta-analyses can be located [here]().
+All data and R code used in the meta-analyses can be located [here](https://github.com/awconway/zhf-review).
 
-Prior to conducting the meta-analyses, the results from each study were converted into a standard format, with bias meaning $comparator thermometer-ZHF thermometer$ measured in $^\circ C$.
+Prior to conducting the meta-analyses, the results from each study were converted into a standard format, with bias meaning comparator thermometer minus ZHF thermometer measured in °C.
 In several studies, results were reported for multiple groups of participants, therefore in the meta-analysis each of these groups was treated as a separate 'comparison'.
@@
 
-The conventionally cited clinically acceptable agreement between ZHF and comparator devices is 0.5 $^\circ C$ $(ref - most of the studies site this range from Eshragi...)$.
+The conventionally cited clinically acceptable agreement between ZHF and comparator devices is 0.5 °C [@eshraghi2014].
 It was deemed that outer confidence bounds for 95% LoA between zero-heat-flux and core temperature measurements (termed as ‘population limits of agreement’) outside of these bounds wouldbe clinically unacceptable.
@@
 A sensitivity analysis for the primary comparison (ZHF versus temperature measurement at core site) was performed based on risk of bias, whereby ‘unclear risk of bias’ was treated as ‘high risk’ and ‘high risk of bias’ studies were excluded from analyses.
-As clinicians would be interested in the accuracy of ZHF relative to the thermometer devices they use, and within the clinical setting in which they use it, we conducted subgroup analyses according to the comparator device used (either core, sublingual or nasopharangeal) and clinical setting (either intraoperative or intensive care unit).
+We also conducted a sensitivity analysis for the primary comparison (ZHF versus temperature measurement at core site) excluding studies that received funding from industry.
+As clinicians would be interested in the accuracy of ZHF relative within the clinical setting in which they use it, we conducted subgroup analyses for the primary comparison according to clinical setting of the study (either intraoperative or intensive care unit).
 
-# Results
+## Results
 
-## Study selection and description
+### Study selection and description
 
-Fifteen studies were included (Figure 1).
+Sixteen studies were included (Figure \@ref(fig:fig-1)).
 Two studies reported only in abstract form were not included and assigned as 'studies awaiting classification' because there was insufficient information provided.
@@
 
-The characteristics of included studies can be viewed [here](link to shiny app).
+The characteristics of included studies can be viewed [here](https://aconway.dev/zhf).
 The primary comparison of zero-heat-flux versus core temperature measurements (eg, arterial, bladder, esophageal or rectal) consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies.
@@
 
-## Primary comparison: zero-heat-flux thermometer versus core thermometers
+### Primary comparison: zero-heat-flux thermometer versus core thermometers
 
-The pooled estimate for the mean bias between zero-heat-flux and core temperature measurements was `r primary$bias_mean`$^\circ C$.
-However, the variation in differences between studies was large, as displayed by the density plot in Figure 2.
-Consequently, the population limits of agreement, which take into consideration the between-study heterogeneity and sampling error, were wide, spanning from `r primary$CI_L_rve`$^\circ C$ to `r primary$CI_U_rve`$^\circ C$ (`r primary$Measurements` measurements; `r primary$Participants` participants; `r primary$Studies` studies).
+A graphical overview of the findings for the primary analysis is presented in Figure \@ref(fig:fig-2).
+The pooled estimate for the mean bias between zero-heat-flux and core temperature measurements was `r primary$bias_mean`°C.
+The population limits of agreement, which take into consideration the between-study heterogeneity and sampling error, were wide, spanning from `r primary$CI_L_rve`°C to `r primary$CI_U_rve`°C (`r primary$Measurements` measurements; `r primary$Participants` participants; `r primary$Studies` studies).
 The quality of evidence for the primary comparison was downgraded to low quality due to concerns about study limitations and inconsistency.
 Population limits of agreement for the sensitivity analysis restricted to studies rated as having low risk of bias across all the domains of the QADAS-2 were similar to the primary analysis (`r low_risk$Measurements` measurements; `r low_risk$Participants` participants; `r low_risk$Studies` stsudies).
-The mean bias was again `r low_risk$bias_mean`$^\circ C$ with population agreements spanning from `r low_risk$CI_L_rve`$^\circ C$ to `r low_risk$CI_U_rve`$^\circ C$.
+The mean bias was again `r low_risk$bias_mean`°C with population limits of agreement spanning from `r low_risk$CI_L_rve`°C to `r low_risk$CI_U_rve`°C.
+A further sensitivity analysis excluding studies that received industry funding revealed population limits of agreement that were considerably wider than the primary analysis (`r conflict$CI_L_rve`°C to `r conflict$CI_U_rve`°C).
+The GRADE rating for this sensitivity was downgraded to low quality though, due to concerns about study limitations, inconsistency and imprecision.
 
-```{r fig-2, fig.align="center", fig.cap="Comparisons between core and zero-heat-flux thermometers within and across studies.
-Blue curves are distributions of the differences between measurements from zero-heat-flux (ZHF) sensors and core temperature measurements in individual studies.
-The red curve is the distribution of the pooled estimate.", echo=FALSE, fig.width=5.1, fig.path=""}
+<div class="l-screen-inset">
 
-    bias=data_core$bias
-    s2_unb = data_core$s2
-    pooled_bias = primary$bias_mean
-    pooled_sd = primary$sd2_est
-    pooled_tau2 = primary$tau_est
-    pooled_sd = sqrt(pooled_sd^2 + pooled_tau2)
-
-    LOA_l = primary$LOA_L
-    LOA_u = primary$LOA_U
-    LOA_l_CI = primary$CI_L_rve
-    LOA_u_CI = primary$CI_U_rve
-
-g <- ggplot(data.frame(x=seq(-20,20,length=200)), aes(x=x)) + 
-      stat_function(fun=dnorm, args = list(bias[1], sd=sqrt(s2_unb[1])), colour = "cornflowerblue", size=0.6, alpha = 0.5)
-
-    for (i in 2:length(bias)){
-      g <- g + stat_function(fun=dnorm, args = list(bias[i], sd=sqrt(s2_unb[i])), color = "cornflowerblue", size = 0.6, alpha = 0.5)
-    }
-
-    g <- g + stat_function(fun=dnorm, args = list(pooled_bias, pooled_sd), colour ="lightcoral", alpha = 0.05) + 
-      stat_function(fun=dnorm, args = list(pooled_bias, pooled_sd), colour = NA, geom="area", fill="lightcoral", alpha = 0.6) + 
-      scale_x_continuous(limits = c(-3.5,3.5), breaks = c(-2, -1, 0, 1, 2)) + labs(x = expression('Difference between core and ZHF temperature measurements in'*~degree*C*''))+
-      scale_y_continuous(name = "Density \n", limits = c(0,2.5)) +  
-      #labs(title = "\nOuter confidence intervals for pooled limits of agreement\n\n  Pooled limits of agreement")+
-      theme(plot.title = element_text(hjust = 0.5, margin = margin(t=10, b=-32), size=10),
-            axis.text=element_text(hjust = 0.5, size=10),                                                                        
-            axis.title=element_text(hjust = 0.5, size=10),
-            axis.line=element_line(colour="black", size=0.2),
-            panel.background = element_blank(),
-            axis.ticks = element_blank(), 
-            plot.caption = element_text(hjust = 0)) #+ 
-      #CI lines that extend to arrow tips
-      # geom_segment(aes(x=LOA_u, y=0, xend=LOA_u, yend=2.25), size = 0.3, linetype="dashed")+ 
-      # geom_segment(aes(x=LOA_l, y=0, xend=LOA_l, yend=2.25), size = 0.3, linetype="dashed")+
-      # geom_segment(aes(x=LOA_u_CI, y=0, xend=LOA_u_CI, yend=2.48), size = 0.3)+
-      # geom_segment(aes(x=LOA_l_CI, y=0, xend=LOA_l_CI, yend=2.48), size = 0.3)#+
-      # 
-      # geom_segment(aes(x=0, y=2.48, xend=LOA_u_CI, yend=2.48), size = 0.4, arrow = arrow(length = unit(0.03, "npc")))+ #R arrow high
-      # geom_segment(aes(x=0, y=2.48, xend=LOA_l_CI, yend=2.48), size = 0.4, arrow = arrow(length = unit(0.03, "npc")))+ #L arrow high
-      # geom_segment(aes(x=0, y=2.25, xend=LOA_u, yend=2.25), size = 0.4,  arrow = arrow(length = unit(0.03, "npc")))+ #R arrow low
-      # geom_segment(aes(x=0, y=2.25, xend=LOA_l, yend=2.25), size = 0.4,  arrow = arrow(length = unit(0.03, "npc"))) #L arrow low
-g
+```{r fig-2, fig.align="center", fig.cap="Graphical overview of findings for the primary analysis", echo=FALSE, fig.path=""}
+include_graphics("gofer_core.png")
 ```
 
+</div>
+
+Table 1 presents results of the primary, sensitivity and all subgroup analyses for the primary comparison as well as secondary comparisons.
 We conducted two subgroup analyses for the primary comparison according to the clinical setting in which the study was conducted.
-In the subset of studies conducted in the ICU, the mean bias was `r ICU$bias_mean` $^\circ C$ with population limits of agreement between `r ICU$CI_L_rve` $^\circ C$ and `r ICU$CI_U_rve` $^\circ C$.
-Whereas in the subset of studies that evaluated the use of zero-heat-flux thermometers during surgery found a mean bias of `r OT$bias_mean` $^\circ C$ with population limits of agreement from `r OT$CI_L_rve` $^\circ C$ to `r OT$CI_U_rve` $^\circ C$.
-The quality of evidence for these subgroup analyses was similarly rated as low quality due to concerns about study limitations and inconsistency.
+In the subset of studies conducted in the ICU, the mean bias was `r ICU$bias_mean`°C with population limits of agreement between `r ICU$CI_L_rve`°C and `r ICU$CI_U_rve` °C.
+The GRADE rating for quality of evidence was downgraded to very low quality due to study limitations, inconsistency and imprecision.
+In the subset of studies that evaluated the use of zero-heat-flux thermometers during surgery found a mean bias of `r OT$bias_mean`°C with population limits of agreement from `r OT$CI_L_rve`°C to `r OT$CI_U_rve` °C.
+The quality of evidence rated as moderate quality due to concerns about study limitations.
 
-## Secondary comparisons: zero-heat-flux thermometer versus peripheral thermometers
+<div class="l-page-outset">
+
+```{r table-1}
+ma <- list(primary, low_risk, ICU, OT,  NPA,SL, conflict)
+names(ma) <- c("Primary", "Low risk studies", "Intensive Care Unit", 
+               "Surgery", "Nasopharyngeal", "Sublingual",
+               "Studies not funded by industry")
+df <- bind_rows(ma, .id="Comparison")
+df %>% 
+  rename("Mean bias" = bias_mean, "Variance" = sd2_est, "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, "Upper bound for 95% limits of agreement" = LOA_U, "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve) %>%
+    gt() %>% 
+  tab_header(
+    title = "Table 1. Results of meta-analyses"  )  %>% 
+  tab_spanner(
+    label = "Population limits of agreement",
+    columns = vars(
+      `Outer confidence interval for lower 95% limits of agreement`, `Outer confidence interval for upper 95% limits of agreement`)
+  )
+```
+</div>
+
+### Secondary comparisons: zero-heat-flux thermometer versus peripheral thermometers
 
 Zero-heat-flux thermometers were compared with sublingual thermometers and nasopharyngeal thermometers in the studies included in this review.
-The mean bias between zero-heat-flux and sublingual temperature measurements in meta-analysis of results from `r SL$Studies` studies was `r SL$bias_mean` $^\circ C$.
-Due to the limited number of studies and measurements, population limits of agreement were extremely wide, spanning from `r SL$CI_L_rve` $^\circ C$ to `r SL$CI_U_rve` $^\circ C$.
+The mean bias between zero-heat-flux and sublingual temperature measurements in meta-analysis of results from `r SL$Studies` studies was `r SL$bias_mean`°C.
+Due to the limited number of studies and measurements, population limits of agreement were extremely wide, spanning from `r SL$CI_L_rve`°C to `r SL$CI_U_rve`°C.
 The quality of evidence for this comparison was rated as very low quality due to serious concerns about imprecision.
 
-The mean bias between zero-heat-flux and nasopharyngeal temperature measurements in meta-analysis of results from `r NPA$Studies` studies was `r NPA$bias_mean` $^\circ C$.
-Population limits of agreement were `r NPA$CI_L_rve` $^\circ C$ to `r NPA$CI_U_rve` $^\circ C$.
-We downgraded the quality of evidence to low, again due to concerns about inconsistency and study limitations.
+The mean bias between zero-heat-flux and nasopharyngeal temperature measurements in meta-analysis of results from `r NPA$Studies` studies was `r NPA$bias_mean` °C.
+Population limits of agreement were `r NPA$CI_L_rve`°C to `r NPA$CI_U_rve`°C.
+We downgraded the quality of evidence to low, again due to concerns about imprecision and study limitations.
 
-# Discussion
+## Discussion
 
 Results from this systematic review have important implications for practice.
-Clinicians should consider the potential that a temperature measurement from a zero-heat-flux thermometer could be as much as one $^\circ C$ higher or lower than the true core temperature.
-This is similar to results from previous meta-analyses that compared other peripheral thermometers with core temperature measurements.
-However, these previous meta-analyses used statistical approaches that did not incorporate the magnitude of heteroogeneity in results between studies or sampling error.
-As such, it is possible that the zero-heat-flux thermometer is still more precise than these other peripheral thermometers.
+Clinicians should consider the potential that a temperature measurement from a zero-heat-flux thermometer could be as much as one degree Celcius higher or lower than core temperature.
+It was reassuting that results of our sensitivity analysis restricted to studies judged to be at low risk of bias using the QADAS-2 tool were similar.
+As such, it is vital for clinicians considering using this device to first determine if differences in temperature smaller than this magnitude would be important for the given clinical situation.
+If so, then it may not be appropriate to substitute the zero-heat-flux device in place of a core thermometer.
 
-Whether or not teh zero-heat-flux thermometer is sufficiently accurate to be used in place of nasopharyngeal thermometers is unclear.
+Our estimates of the accuracy of zero-heat-flux thermometers are similar to results from a previous meta-analysis that compared other peripheral thermometers, such as sublingual and temporal artery devices, with core temperature measurements [@niven2015accuracy].
+However, this previous meta-analysis used a statistical approach that did not incorporate the magnitude of heteroogeneity in results between studies or sampling error.
+As such, it is possible that the zero-heat-flux thermometer may still more precise than other peripheral thermometers.
 
-We did not include studies that used the Temple Touch Pro.
-This is a thermometer similar to the zero-heat-flux device in that it is placed cutaneously, but the underlying technology is different.
-There have been x studies that evaluated the Temple Touch Pro device with promising results.
+Subgroup analyses revealed insights to direct future research.
+There were fewer participants included in the subgroup of studies conducted in the Intensive Care Unit compared to those conducted during surgery.
+As a result, population limits of agreement for the Intensive Care Unit subgroup were broad.
+Additional studies are required to increase confidence in the accuracy of zero-heat-flux device in this setting, where continuous temperature monitoring is often required.
 
-## Limitations
+Although comparisons with core temperture are the most important to evaluate, we included studies that compared zero heat flux and peripheral temperature monitoring devices in our review because clinicians may be interested to determine if this new technology is sufficiently accurate to replace other ways non-invasive monitor temperature.
+Also, there may be situations where it is not practical to expose research participants to the potential additional risk of invasive core temperature monitoring for the purposes of evaluating the new temperature monitoring device when it is standard practice for only peripheral temperature monitoring to be used.
+Whether or not the zero-heat-flux thermometer is sufficiently accurate to be used in place of nasopharyngeal thermometers is unclear.
+Population limits of agreement calculated from four studies were broad, spanning from one degree less than zero heat flux temperature to one degree higher.
+Further studies are therefore required.
 
-# Conclusion
+It should be noted that we did not include studies that used the Temple Touch Pro because it is not strictly a zero-heat-flux device.
+This is a new thermometer that is similar to the zero-heat-flux device in that it is placed cutaneously, but the underlying technology is different.
+Far fewer studies have  evaluated the Temple Touch Pro compared to the zero-heat-flux device [@evron2017evaluation; @sastre2019evaluation].
 
-# References
+Many studies in this review analysed a large number of measurements of temperature with relatively small sample sizes.
+Importantly, the approach we used for our meta-analysis takes this into account.
+By using robust variance estimation, weights for pooling estimates in the meta-analyis become proportional to the number of patients not the total number of measurements.[@tipton2017framework]
+
+The accuracy of zero heat flux temperature monitoring has been evaluated in various intra-operative contexts as well as in the intensive care unit setting.
+Our subgroup analyses did not indicate that the accuracy of this temperature monitoring device was any more effective in a particular setting.
+Only one study included in our systematic review included pediatric patients.
+Additional studies to evaluate the accuracy of this device in children may be warranted to increase confidence.
+
+### Limitations
+
+We did not extract data on adverse events due to zero-heat-flux temperature monitoring.
+The possibility of publication bias cannot be ruled out, although the evidence suggests this may not be as serious of a problem for studies that are not randomized controlled trials [@begg2005systematic].
+Our focus for the meta-analysis was on calculating population limits of agreement, which incorporate the variation in bias between studies into the estimates.
+For this reason, we did not use meta-regression or tests for interaction between subgroups as a way to investigate sources of heterogeneity.
+It is important to note that this review did not assess the clinical utility of temperature monitoring using the zero-heat-flux device.
+The evidence from this review should be considered in the context of other information about the reliability and ease of use of this device.
+
+## Conclusion
+
+Substantial differences between core and zero-heat-flux temperature measurements were identified in this meta-analysis.
+Clinicians should consider the range of uncertainty in the accuracy of the zero-heat-flux thermometer when using this device to inform their decision-making.
+As such, there may be circumstances where use of this device would not be appropriate because a difference in temperature of 1°C is important to detect for the given clinical situation.

### 2019-11-26 manuscript/manuscript.Rmd
sent to co-authors

@@
 - name: Aaron Conway
-  address: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
+  affiliation: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
   email: aaron.conway@utoronto.ca
@@
 - name: Megan Bittner
-  address: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
+  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
 - name: Dan Phan
-  address: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
+  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
 - name: Navpreet Kamboj
-  address: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
+  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
   email: navpreet.kamboj@mail.utoronto.ca
 - name: Kristina Chang
-  address: Toronto General Hospital, UHN
+  affiliation: Toronto General Hospital, UHN
 - name: Peter Collins
-  address: Toronto General Hospital, UHN
+  affiliation: Toronto General Hospital, UHN
 - name: Matteo Parotto
-  address: Toronto General Hospital, UHN
+  affiliation: Toronto General Hospital, UHN
 date: "`r Sys.Date()`"
@@
 output: distill::distill_article
+repository_url: https://github.com/awconway/zhf-review
+twitter:
+  creator: "@aw_conway"
 ---
@@
 These devices are increasingly being used in clinical practice to substitute for invasive core temperature measurement during surgery and in critical care settings.
-The aim of this review was to determine the accuracy and precision of zero-heat-flux temperture measurements.
+The aim of this review was to determine the accuracy and precision of zero-heat-flux temperature measurements.
 
@@
 
-Core temperature monitoring is an important intervention within perioperative and intensive care settings.
-Thermoregulatory dysfunction is commonly associated with the induction of anesthesia and can lead to adverse outcomes including cardiac dysrhythmias, altered hemostasis and increased risk of surgical site infection [@frank1997perioperative; @kurz1996perioperative; @michelson1994reversible; @rohrer1992effect].
-The pulmonary artery catheter is the reference standard for continuous core temperature monitoring, however, the invasive nature of this method renders an increased risk of bloodstream infections and damage to surrounding tissue[@hadian2006evidence].
-Although clinically accurate relative to pulmonary artery temperature measurements, surrogate measures of core temperature at esophageal, rectal, and bladder locations remain mildly invasive interventions.
+Continuous core temperature monitoring is commonly used within perioperative and intensive care settings.
+Thermoregulatory dysfunction is commonly associated with the induction of anesthesia and can lead to adverse outcomes including cardiac arrhythmia, altered hemostasis and increased risk of surgical site infection.[@frank1997perioperative; @kurz1996perioperative; @michelson1994reversible; @rohrer1992effect] The pulmonary artery catheter is the reference standard for continuous core temperature monitoring, however, the invasive nature of this method renders an increased risk of bloodstream infections and damage to surrounding tissue.[@hadian2006evidence] Although clinically accurate relative to pulmonary artery temperature measurements, surrogate measures of core temperature at esophageal, rectal, and bladder locations remain mildly invasive interventions.
 
@@
 Originally developed in the 1970s, zero-heat-flux technology was recently implemented in the 3M SpotOn temperature monitoring system (3M, St Paul, MN), as a single-use, disposable sensor.
-In practice, the zero-heat-flux sensor, such as the 3M SpotOn, is placed on the lateral surface of the forehead and isinitially warmed to equilibrate the temperature of the skin surface to the underlaying core tissues.
-Equipped with a thermal insulator, the zero-heat-flux sensor eliminates heat loss to the environment to allow for changes in core temperature to be directly reflected by a change in skin surface temperature [@eshraghi2014].
+In practice, the zero-heat-flux sensor, such as the 3M SpotOn, is placed on the lateral surface of the forehead and is initially warmed to equilibrate the temperature of the skin surface to the underlying core tissues.
+Equipped with a thermal insulator, the zero-heat-flux sensor eliminates heat loss to the environment to allow for changes in core temperature to be directly reflected by a change in skin surface temperature.[@eshraghi2014]
 
@@
 A copy of the submitted protocol can be accessed [here](https://github.com/awconway/zhf-review).
-The primary comparison for this review was temperature measured from a zero-heat-flux thermometer versus temperature measured from a core site, which we defined as temperature measured at either an arterial, esophaeal, bladder or rectal site.
+The primary comparison for this review was temperature measured from a zero-heat-flux thermometer versus temperature measured from a core site, which we defined as temperature measured at either an arterial, esophageal, bladder or rectal site.
 Secondary comparisons were made between zero-heat-flux thermometers and temperatures taken at peripheral sites.
@@
 Published studies were found by searching Medline and EMBASE from January 2000 to July 2019.
-The Cochrane-recommended search strategy combining terms for the ‘target condition’ and ‘index test’ was used [@mann2012should].
-This search strategy is an efficient approach for systematic reviews of diagnostic test accuracy studies.[@preston2015improving] We also conducted forward citation searching, by using Google Scholar to search the citations of the first article published on the accuracy of zero-heat-flux thermometers.
+The Cochrane-recommended search strategy combining terms for the ‘target condition’ and ‘index test’ was used.[@mann2012should] This search strategy is an efficient approach for systematic reviews of diagnostic test accuracy studies.[@preston2015improving] We also conducted forward citation searching, by using Google Scholar to search the citations of the first article published on the accuracy of zero-heat-flux thermometers.
 The search strategies used for each data base can be located [here](https://aconway.dev/zhf app).
@@
 We also extracted information about how repeated measurements were handled.
-In particular we assessed whether studies: (1) analysed each pair of data separately; (2) treated each pair of data as independent; or (3) used either analysis of variance or a random effects model as a way to control for the dependent nature of the repeated measures data [@myles2007using].
+In particular we assessed whether studies: (1) analysed each pair of data separately; (2) treated each pair of data as independent; or (3) used either analysis of variance or a random effects model as a way to control for the dependent nature of the repeated measures data.[@myles2007using]
 
-Two reviewers independently assessed the risk of bias for the included studies using the revised Quality Assessment of Diagnostic Accuracy Studies (QUADAS-2) [@whiting2011quadas].
-Reviewers rated the risk of bias for patient selection, conduct of the zero-heat-flux measurements, conduct of the comparator thermometer measurements, and timing and flow (eg, timing of ZHF and established core temperature measurements, dropouts) as “high”, “low” or “unclear” risk of bias.
-We worked to minimize the risk of publication bias by conducting a comprehensive search of multiple databases as well as an international clinical trial registry [@glasziou2001systematic].
-Statistical approaches for detection of reporting bias were not conducted due to lack of validated methods [@begg2005systematic].
-ASimulations have revealed that tests for detecting funnel plot asymmetry will result in publication bias being incorrectly identified too often [@deeks2005performance].
+Two reviewers independently assessed the risk of bias for the included studies using the revised Quality Assessment of Diagnostic Accuracy Studies (QUADAS-2).[@whiting2011quadas] Reviewers rated the risk of bias for patient selection, conduct of the zero-heat-flux measurements, conduct of the comparator thermometer measurements, and timing and flow (eg, timing of ZHF and established core temperature measurements, dropouts) as “high”, “low” or “unclear” risk of bias.
+We worked to minimize the risk of publication bias by conducting a comprehensive search of multiple databases as well as an international clinical trial registry.[@glasziou2001systematic] Statistical approaches for detection of reporting bias were not conducted due to lack of validated methods.[@begg2005systematic] Simulations have revealed that tests for detecting funnel plot asymmetry will result in publication bias being incorrectly identified too often.[@deeks2005performance]
 
-In order to rate the quality of evidence, we applied the Grading Quality of Evidence and Strength of Recommendation methodology [@schunemann2008grading].
-Evidence was downgraded in accordance with study limitations, inconsistency and imprecision.
+In order to rate the quality of evidence, we applied the Grading Quality of Evidence and Strength of Recommendation methodology.[@schunemann2008grading] Evidence was downgraded in accordance with study limitations, inconsistency and imprecision.
 There were no circumstances in which evidence was downgraded for indirectness as this systematic review only included relevant studies.
@@
 A framework for meta-analysis of Bland-Altman method comparison studies developed by @tipton2017framework based on limits of agreement approach was used.
-This method was selected because it parallels the approach used in primary Bland-Altman studies, whereby an estimate is generated for the pooled LoAs in the population (not just in the samples studied).
-The ‘population LoA’ is more broad than the LoA commonly reported in the meta-analyses of Bland-Altman studies [@tipton2017framework].
-Pooled limits of agreement were calculated using $\delta\pm2\sqrt{\sigma2+\tau2}$, where $\delta$ is the average bias across studies, $\sigma2$ is the average within-study variation in differences and $\tau2$ is the variation in bias across studies.
+This method was selected because it parallels the approach used in primary Bland-Altman studies, whereby an estimate is generated for the pooled limits of agreement in the population (not just in the samples studied).
+The ‘population limits of agreement’ is more broad than the limits of agreement commonly reported in the meta-analyses of Bland-Altman studies.[@tipton2017framework] Pooled limits of agreement were calculated using $\delta\pm2\sqrt{\sigma2+\tau2}$, where $\delta$ is the average bias across studies, $\sigma2$ is the average within-study variation in differences and $\tau2$ is the variation in bias across studies.
 
 Estimations of $\delta$ and $\sigma2$ were made using a weighted least-squares model (similar to a random-effects approach), with the associated standard errors estimated using robust variance estimation.
-Robust variance estimation was used alternatively to model-based standard errors as some studies included in the systematic review used repeated-measures designs without accommodating for the correlation between measurements [@hedges2010robust; @tanner2016handling; @tipton2015small].
-We used the method-of-moments estimator from @dersimonian1986meta for the $\tau2$ parameter.
+Robust variance estimation was used alternatively to model-based standard errors as some studies included in the systematic review used repeated-measures designs without accommodating for the correlation between measurements[@hedges2010robust; @tanner2016handling; @tipton2015small] We used the method-of-moments estimator from @dersimonian1986meta for the $\tau2$ parameter.
 
@@
 This was achieved by using weights proportional to the number of participants, not the total number of measurements.
-The R statistical program was used to conduct all analyses [@team2017r].
-All data and R code used in the meta-analyses can be located [here](https://github.com/awconway/zhf-review).
+The R statistical program was used to conduct all analyses[@team2017r] All data and R code used in the meta-analyses can be located [here](https://github.com/awconway/zhf-review).
 
@@
 
-The conventionally cited clinically acceptable agreement between ZHF and comparator devices is 0.5 °C [@eshraghi2014].
-It was deemed that outer confidence bounds for 95% LoA between zero-heat-flux and core temperature measurements (termed as ‘population limits of agreement’) outside of these bounds wouldbe clinically unacceptable.
+The conventionally cited clinically acceptable agreement between ZHF and comparator devices is 0.5 °C.[@eshraghi2014] It was deemed that outer confidence bounds for 95% limits of agreement between zero-heat-flux and core temperature measurements (termed as ‘population limits of agreement’) outside of these bounds would be clinically unacceptable.
 
@@
 The quality of evidence for the primary comparison was downgraded to low quality due to concerns about study limitations and inconsistency.
-Population limits of agreement for the sensitivity analysis restricted to studies rated as having low risk of bias across all the domains of the QADAS-2 were similar to the primary analysis (`r low_risk$Measurements` measurements; `r low_risk$Participants` participants; `r low_risk$Studies` stsudies).
+Population limits of agreement for the sensitivity analysis restricted to studies rated as having low risk of bias across all the domains of the QADAS-2 were similar to the primary analysis (`r low_risk$Measurements` measurements; `r low_risk$Participants` participants; `r low_risk$Studies` studies).
 The mean bias was again `r low_risk$bias_mean`°C with population limits of agreement spanning from `r low_risk$CI_L_rve`°C to `r low_risk$CI_U_rve`°C.
@@
 
-<div class="l-screen-inset">
-
-```{r fig-2, fig.align="center", fig.cap="Graphical overview of findings for the primary analysis", echo=FALSE, fig.path=""}
+```{r fig-2, preview=TRUE, layout="l-screen-inset", fig.align="center", fig.cap="Graphical overview of findings for the primary analysis", echo=FALSE, fig.path=""}
 include_graphics("gofer_core.png")
 ```
-
-</div>
 
@@
 
-<div class="l-page-outset">
-
-```{r table-1}
+```{r table-1, layout="l-page-outset"}
 ma <- list(primary, low_risk, ICU, OT,  NPA,SL, conflict)
@@
 ```
-</div>
 
@@
 Results from this systematic review have important implications for practice.
-Clinicians should consider the potential that a temperature measurement from a zero-heat-flux thermometer could be as much as one degree Celcius higher or lower than core temperature.
-It was reassuting that results of our sensitivity analysis restricted to studies judged to be at low risk of bias using the QADAS-2 tool were similar.
+Clinicians should consider the potential that a temperature measurement from a zero-heat-flux thermometer could be as much as one degree Celsius higher or lower than core temperature.
+It was reassuring that results of our sensitivity analysis restricted to studies judged to be at low risk of bias using the QADAS-2 tool were similar.
 As such, it is vital for clinicians considering using this device to first determine if differences in temperature smaller than this magnitude would be important for the given clinical situation.
@@
 
-Our estimates of the accuracy of zero-heat-flux thermometers are similar to results from a previous meta-analysis that compared other peripheral thermometers, such as sublingual and temporal artery devices, with core temperature measurements [@niven2015accuracy].
-However, this previous meta-analysis used a statistical approach that did not incorporate the magnitude of heteroogeneity in results between studies or sampling error.
+Our estimates of the accuracy of zero-heat-flux thermometers are similar to results from a previous meta-analysis that compared other peripheral thermometers, such as sublingual and temporal artery devices, with core temperature measurements.[@niven2015accuracy] However, this previous meta-analysis used a statistical approach that did not incorporate the magnitude of heterogeneity in results between studies or sampling error.
 As such, it is possible that the zero-heat-flux thermometer may still more precise than other peripheral thermometers.
@@
 
-Although comparisons with core temperture are the most important to evaluate, we included studies that compared zero heat flux and peripheral temperature monitoring devices in our review because clinicians may be interested to determine if this new technology is sufficiently accurate to replace other ways non-invasive monitor temperature.
+Although comparisons with core temperature are the most important to evaluate, we included studies that compared zero-heat-flux and peripheral temperature monitoring devices in our review because clinicians may be interested to determine if this new technology is sufficiently accurate to replace other ways non-invasive monitor temperature.
 Also, there may be situations where it is not practical to expose research participants to the potential additional risk of invasive core temperature monitoring for the purposes of evaluating the new temperature monitoring device when it is standard practice for only peripheral temperature monitoring to be used.
 Whether or not the zero-heat-flux thermometer is sufficiently accurate to be used in place of nasopharyngeal thermometers is unclear.
-Population limits of agreement calculated from four studies were broad, spanning from one degree less than zero heat flux temperature to one degree higher.
+Population limits of agreement calculated from four studies were broad, spanning from one degree less than zero-heat-flux temperature to one degree higher.
 Further studies are therefore required.
@@
 This is a new thermometer that is similar to the zero-heat-flux device in that it is placed cutaneously, but the underlying technology is different.
-Far fewer studies have  evaluated the Temple Touch Pro compared to the zero-heat-flux device [@evron2017evaluation; @sastre2019evaluation].
+Far fewer studies have  evaluated the Temple Touch Pro compared to the zero-heat-flux device.[@evron2017evaluation; @sastre2019evaluation]
 
@@
 Importantly, the approach we used for our meta-analysis takes this into account.
-By using robust variance estimation, weights for pooling estimates in the meta-analyis become proportional to the number of patients not the total number of measurements.[@tipton2017framework]
+By using robust variance estimation, weights for pooling estimates in the meta-analysis become proportional to the number of patients not the total number of measurements.[@tipton2017framework]
 
-The accuracy of zero heat flux temperature monitoring has been evaluated in various intra-operative contexts as well as in the intensive care unit setting.
+The accuracy of zero-heat-flux temperature monitoring has been evaluated in various intraoperative-operative contexts as well as in the intensive care unit setting.
 Our subgroup analyses did not indicate that the accuracy of this temperature monitoring device was any more effective in a particular setting.
@@
 We did not extract data on adverse events due to zero-heat-flux temperature monitoring.
-The possibility of publication bias cannot be ruled out, although the evidence suggests this may not be as serious of a problem for studies that are not randomized controlled trials [@begg2005systematic].
-Our focus for the meta-analysis was on calculating population limits of agreement, which incorporate the variation in bias between studies into the estimates.
+The possibility of publication bias cannot be ruled out, although the evidence suggests this may not be as serious of a problem for studies that are not randomized controlled trials.[@begg2005systematic] Our focus for the meta-analysis was on calculating population limits of agreement, which incorporate the variation in bias between studies into the estimates.
 For this reason, we did not use meta-regression or tests for interaction between subgroups as a way to investigate sources of heterogeneity.
@@
 As such, there may be circumstances where use of this device would not be appropriate because a difference in temperature of 1°C is important to detect for the given clinical situation.
+
+<script src="https://hypothes.is/embed.js" async></script>

### 2019-11-27 app/app.R
put reactive data table back in

@@ -2,8 +2,8 @@ library(shiny)
 library(shinyLP)
 library(shinydashboard)
 library(shinydashboardPlus)
-# library(tidyverse)
-# library(DT)
+library(tidyverse)
+library(DT)
 # library(robvis)
 # library(readxl)
 # library(bama) #awconway/bama
@@ -11,61 +11,61 @@ library(shinydashboardPlus)
 library(waiter)
 # Load data ----
 # 
-# data <- readxl::read_xlsx(here::here("app", "data", "zhf_extracted.xlsx"))
-# sum_findings <- readxl::read_xlsx(here::here("app", "data", "sum_findings.xlsx"))
-# 
-# # create additional columns for meta-analysis
-# data <- data %>%
-#   mutate(c = N/n)
-# 
-# #variance
-# data <- data %>% 
-#   mutate(s2 = case_when(corrected == "Yes"  ~ ((upper - bias)/1.96)^2,
-#                         corrected == "No" ~  ((upper - bias)/1.96)^2*(N-1)/(N-c)
-#   )
-#   )
-# 
-# data <- data %>% 
-#   mutate(V_bias = s2/n)
-# 
-# data <- data %>% 
-#   mutate(logs2 = log(s2)+1/(n-1))
-# 
-# data <- data %>% 
-#   mutate(V_logs2 = 2/(n-1))
-# 
-# # Create subgroups
-# 
-# data_NPA <- data %>% 
-#   filter(comparison == "NPA")
-# 
-# data_SL <- data %>% 
-#   filter(comparison == "Sublingual")
-# 
-# data_core <- data %>% #eshragi overall
-#   filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
-#   filter(comments != "Intraoperative, off cardiopulmonary bypass" & comments != "Postoperative")
-# 
-# data_core_lowrisk <- data_core %>% #eshragi overall
-#   filter(RoB_selection == "low" & RoB_spoton == "low" & RoB_comparator == "low" & RoB_flow =="low")
-# 
-# data_core_op <- data %>% #eshragi intraop
-#   filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
-#   filter (clinical_setting=="Intraoperative")
-# 
-# data_core_icu <- data %>% #eshragi postop
[…]

### 2019-11-27 app/app.R
renderPlot for RoB figures and fied columns for data

@@ -4,15 +4,15 @@ library(shinydashboard)
 library(shinydashboardPlus)
 library(tidyverse)
 library(DT)
-# library(robvis)
-# library(readxl)
+library(robvis)
+library(readxl)
 # library(bama) #awconway/bama
 # library(ggprisma)
 library(waiter)
 # Load data ----
 # 
 data <- readxl::read_xlsx(here::here("data", "zhf_extracted.xlsx"))
-sum_findings <- readxl::read_xlsx(here::here("data", "sum_findings.xlsx"))
+# sum_findings <- readxl::read_xlsx(here::here("data", "sum_findings.xlsx"))
 
 # create additional columns for meta-analysis
 data <- data %>%
@@ -66,17 +66,17 @@ data$comparison <- sub("PA", "Pulmonary artery", data$comparison)
 data$comparison <- sub("Iliac", "Iliac artery", data$comparison)
 data$comparison <- sub("Ax", "Axillary artery", data$comparison)
 data$comparison <- sub("Eso", "Esophageal", data$comparison)
-# 
-# # Clean up results
-# format_results <- function(group){
-#   out <- bama::loa_maker(group$bias,group$V_bias, group$logs2, group$V_logs2)
-#   out <- out %>% 
-#     mutate(Participants = sum(group$n_count, na.rm=T)) %>% 
-#     mutate(Measurements = format(sum(group$N, na.rm = T), big.mark=",", scientific = FALSE)) %>% 
-#     mutate(Studies = length(unique(group$Study))) %>% 
-#     select(Studies, m, Participants, Measurements, bias_mean, sd2_est, tau_est, LOA_L, LOA_U, CI_L_rve, CI_U_rve) %>% 
-#     rename("Comparisons" = m)
-# }
+
+# Clean up results
+format_results <- function(group){
+  out <- bama::loa_maker(group$bias,group$V_bias, group$logs2, group$V_logs2)
+  out <- out %>%
+    mutate(Participants = sum(group$n_count, na.rm=T)) %>%
+    mutate(Measurements = format(sum(group$N, na.rm = T), big.mark=",", scientific = FALSE)) %>%
+    mutate(Studies = length(unique(group$Study))) %>%
+    select(Studies, m, Participants, Measurements, bias_mean, sd2_est, tau_est, LOA_L, LOA_U, CI_L_rve, CI_U_rve) %>%
+    rename("Comparisons" = m)
+}
 
 ######UI#########
 ui <- dashboardPage(
[…]

### 2019-11-27 manuscript/manuscript.Rmd
added beth and edits from KC

@@
   affiliation: Toronto General Hospital, UHN
+- name: Elizabeth Tipton
+  affiliation: Dapartment of Statistics, Northwestern University
 - name: Matteo Parotto
@@
 Studies were excluded if conducted on non-human subjects or outside of a clinical healthcare setting.
-No publication date restrictions were applied.Published conference abstracts were included if there was enough information reported to appraise the quality of the study.
+No publication date restrictions were applied.
+Published conference abstracts were included if there was enough information reported to appraise the quality of the study.
 There were no language restrictions applied during the search.
@@
 
-Published studies were found by searching Medline and EMBASE from January 2000 to July 2019.
+Published studies were found by searching Medline and EMBASE to July 2019.
 The Cochrane-recommended search strategy combining terms for the ‘target condition’ and ‘index test’ was used.[@mann2012should] This search strategy is an efficient approach for systematic reviews of diagnostic test accuracy studies.[@preston2015improving] We also conducted forward citation searching, by using Google Scholar to search the citations of the first article published on the accuracy of zero-heat-flux thermometers.
@@
 
-Two reviewers independently assessed the risk of bias for the included studies using the revised Quality Assessment of Diagnostic Accuracy Studies (QUADAS-2).[@whiting2011quadas] Reviewers rated the risk of bias for patient selection, conduct of the zero-heat-flux measurements, conduct of the comparator thermometer measurements, and timing and flow (eg, timing of ZHF and established core temperature measurements, dropouts) as “high”, “low” or “unclear” risk of bias.
+Two reviewers independently assessed the risk of bias for the included studies using the revised Quality Assessment of Diagnostic Accuracy Studies (QUADAS-2).[@whiting2011quadas] Reviewers rated the risk of bias for patient selection, conduct of the zero-heat-flux measurements, conduct of the comparator thermometer measurements, and timing and flow (eg, timing of zero-heat-flux and established core temperature measurements, dropouts) as “high”, “low” or “unclear” risk of bias.
 We worked to minimize the risk of publication bias by conducting a comprehensive search of multiple databases as well as an international clinical trial registry.[@glasziou2001systematic] Statistical approaches for detection of reporting bias were not conducted due to lack of validated methods.[@begg2005systematic] Simulations have revealed that tests for detecting funnel plot asymmetry will result in publication bias being incorrectly identified too often.[@deeks2005performance]
@@
 
-The objective for the meta-analysis was to estimate the population limits of agreement between temperature measurements from the ZHF and established comparator thermometers.
-A framework for meta-analysis of Bland-Altman method comparison studies developed by @tipton2017framework based on limits of agreement approach was used.
-This method was selected because it parallels the approach used in primary Bland-Altman studies, whereby an estimate is generated for the pooled limits of agreement in the population (not just in the samples studied).
+The objective for the meta-analysis was to estimate the population limits of agreement between temperature measurements from the zero-heat-flux and established comparator thermometers.
+A framework for meta-analysis of Bland-Altman method comparison studies based on limits of agreement approach was used.[@tipton2017framework]  This method was selected because it parallels the approach used in primary Bland-Altman studies, whereby an estimate is generated for the pooled limits of agreement in the population (not just in the samples studied).
 The ‘population limits of agreement’ is more broad than the limits of agreement commonly reported in the meta-analyses of Bland-Altman studies.[@tipton2017framework] Pooled limits of agreement were calculated using $\delta\pm2\sqrt{\sigma2+\tau2}$, where $\delta$ is the average bias across studies, $\sigma2$ is the average within-study variation in differences and $\tau2$ is the variation in bias across studies.
@@
 Estimations of $\delta$ and $\sigma2$ were made using a weighted least-squares model (similar to a random-effects approach), with the associated standard errors estimated using robust variance estimation.
-Robust variance estimation was used alternatively to model-based standard errors as some studies included in the systematic review used repeated-measures designs without accommodating for the correlation between measurements[@hedges2010robust; @tanner2016handling; @tipton2015small] We used the method-of-moments estimator from @dersimonian1986meta for the $\tau2$ parameter.
+Robust variance estimation was used alternatively to model-based standard errors as some studies included in the systematic review used repeated-measures designs without accommodating for the correlation between measurements.[@hedges2010robust; @tanner2016handling; @tipton2015small] We used the method-of-moments estimator from DerSimonian & Laird @dersimonian1986meta for the $\tau2$ parameter.
 
@@
 This was achieved by using weights proportional to the number of participants, not the total number of measurements.
-The R statistical program was used to conduct all analyses[@team2017r] All data and R code used in the meta-analyses can be located [here](https://github.com/awconway/zhf-review).
+The R statistical program was used to conduct all analyses[@team2017r] All data and R code used in the meta-analyses can be located [here](https://github.com/awconway/zero-heat-flux-review).
 
-Prior to conducting the meta-analyses, the results from each study were converted into a standard format, with bias meaning comparator thermometer minus ZHF thermometer measured in °C.
+Prior to conducting the meta-analyses, the results from each study were converted into a standard format, with bias meaning comparator thermometer minus zero-heat-flux thermometer measured in °C.
 In several studies, results were reported for multiple groups of participants, therefore in the meta-analysis each of these groups was treated as a separate 'comparison'.
-Other studies reported multiple sets of results, whereby analyses were conducted between ZHF and various comparator devices used on the same participant.
-These instances were also treated as a separate 'comparison' if the comparator devices were apart of separate meta-analyses groups.
+Other studies reported multiple sets of results, whereby analyses were conducted between zero-heat-flux and various comparator devices used on the same participant.
+These instances were also treated as a separate 'comparison' if the comparator devices were a part of separate meta-analysis groups.
 One study reported intraoperative, postoperative and overall results for the same participants.
@@
 
-The conventionally cited clinically acceptable agreement between ZHF and comparator devices is 0.5 °C.[@eshraghi2014] It was deemed that outer confidence bounds for 95% limits of agreement between zero-heat-flux and core temperature measurements (termed as ‘population limits of agreement’) outside of these bounds would be clinically unacceptable.
+The conventionally cited clinically acceptable agreement between zero-heat-flux and comparator devices is 0.5 °C.[@eshraghi2014] It was deemed that outer confidence bounds for 95% limits of agreement between zero-heat-flux and core temperature measurements (termed as ‘population limits of agreement’) outside of these bounds would be clinically unacceptable.
 
-A sensitivity analysis for the primary comparison (ZHF versus temperature measurement at core site) was performed based on risk of bias, whereby ‘unclear risk of bias’ was treated as ‘high risk’ and ‘high risk of bias’ studies were excluded from analyses.
-We also conducted a sensitivity analysis for the primary comparison (ZHF versus temperature measurement at core site) excluding studies that received funding from industry.
-As clinicians would be interested in the accuracy of ZHF relative within the clinical setting in which they use it, we conducted subgroup analyses for the primary comparison according to clinical setting of the study (either intraoperative or intensive care unit).
+A sensitivity analysis for the primary comparison (zero-heat-flux versus temperature measurement at core site) was performed based on risk of bias, whereby ‘unclear risk of bias’ was treated as ‘high risk’ and ‘high risk of bias’ studies were excluded from analyses.
+We also conducted a sensitivity analysis for the primary comparison (zero-heat-flux versus temperature measurement at core site) excluding studies that received funding from industry.
+As clinicians would be interested in the accuracy of zero-heat-flux relative within the clinical setting in which they use it, we conducted subgroup analyses for the primary comparison according to clinical setting of the study (either intraoperative or intensive care unit).
 
@@
 All studies included in this systematic review evaluated the zero-heat-flux temperature monitoring system manufactured by 3M.
-Previously known as the SpotOn Temperature Monitoring System, the 3M ZHF device is now referred to commercially as the Bair Hugger Temperature Monitoring System.
+Previously known as the SpotOn Temperature Monitoring System, the 3M zero-heat-flux device is now referred to commercially as the Bair Hugger Temperature Monitoring System.
 All comparisons reported adherence to the zero-heat-flux device manufacturer instructions and placed the sensor on the forehead of the participants.
-One included study also reported results for a comparison where the zero-heat-flux thermometer was placed on the forehead.
-We did not included this comparison in our meta-analysis.
+One included study also reported results for comparisons where the zero-heat-flux thermometer was not placed on the forehead.
+We did not include these comparisons in our meta-analysis.
 
-High risk of bias was associated with patient selection for 13 (43%) comparisons from 9 (56%) studies, conduct of ZHF and comparator measurements in 10(33%) comparisons from 8 (50%) studies and 12 (40%) comparisons 9 (30%) studies, respectively (mostly due to ZHF measurements being taken with knowledge of the comparator measurements and vice versa) and participant flow for 13 (43%) studies.
-In 19 (50%) comparisons from 8 (50%) studies, the authors had declared a conflict of interest or receipt of funding or equipment from the manufacturer of the ZHF device under evaluation.
+High risk of bias was associated with patient selection for 13 (43%) comparisons from 9 (56%) studies, conduct of zero-heat-flux and comparator measurements in 10 (33%) comparisons from 8 (50%) studies and 12 (40%) comparisons 9 (30%) studies, respectively (mostly due to zero-heat-flux measurements being taken with knowledge of the comparator measurements and vice versa) and participant flow for 13 (43%) studies.
+In 19 (50%) comparisons from 8 (50%) studies, the authors had declared a conflict of interest or receipt of funding or equipment from the manufacturer of the zero-heat-flux device under evaluation.
 
@@
 
-Although comparisons with core temperature are the most important to evaluate, we included studies that compared zero-heat-flux and peripheral temperature monitoring devices in our review because clinicians may be interested to determine if this new technology is sufficiently accurate to replace other ways non-invasive monitor temperature.
+Although comparisons with core temperature are the most important to evaluate, we included studies that compared zero-heat-flux and peripheral temperature monitoring devices in our review because clinicians may be interested to determine if this new technology is sufficiently accurate to replace other ways to non-invasively monitor temperature.
 Also, there may be situations where it is not practical to expose research participants to the potential additional risk of invasive core temperature monitoring for the purposes of evaluating the new temperature monitoring device when it is standard practice for only peripheral temperature monitoring to be used.
@@
 Importantly, the approach we used for our meta-analysis takes this into account.
-By using robust variance estimation, weights for pooling estimates in the meta-analysis become proportional to the number of patients not the total number of measurements.[@tipton2017framework]
+By using robust variance estimation, weights for pooling estimates in the meta-analysis become proportional to the number of patients, not the total number of measurements.[@tipton2017framework]
 

### 2019-11-28 manuscript/manuscript.Rmd
column header removed for comparison

@@
 df %>% 
-  rename("Mean bias" = bias_mean, "Variance" = sd2_est, "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, "Upper bound for 95% limits of agreement" = LOA_U, "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve) %>%
+  rename(" " = Comparison, "Mean bias" = bias_mean, "Variance" = sd2_est, "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, "Upper bound for 95% limits of agreement" = LOA_U, "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve) %>%
     gt() %>% 

### 2019-11-28 manuscript/manuscript.Rmd
fixed megan's edits

@@
 The GRADE evidence quality rating was downgraded to moderate due to concerns about study limitations.
-Population limits of agreement for the sensitivity analysis restricted to studies rated as having low risk of bias across all the domains of the QADAS-2 were similar to the primary analysis.
+Population limits of agreement for the sensitivity analysis restricted to studies rated as having low risk of bias across all the domains of the QUADAS-2 were similar to the primary analysis.
 
@@
 
-Two reviewers independently assessed the risk of bias for the included studies using the revised Quality Assessment of Diagnostic Accuracy Studies (QUADAS-2).[@whiting2011quadas] Reviewers rated the risk of bias for patient selection, conduct of the zero-heat-flux measurements, conduct of the comparator thermometer measurements, and timing and flow (eg, timing of zero-heat-flux and established core temperature measurements, dropouts) as “high”, “low” or “unclear” risk of bias.
+Two reviewers independently assessed the risk of bias for the included studies using the revised Quality Assessment of Diagnostic Accuracy Studies (QUADAS-2).[@whiting2011quadas] Reviewers rated the risk of bias for patient selection, conduct of the zero-heat-flux measurements, conduct of the comparator thermometer measurements, and timing and flow (eg, timing of zero-heat-flux and established core temperature measurements, dropouts) as 'high', 'low' or 'unclear' risk of bias.
 We worked to minimize the risk of publication bias by conducting a comprehensive search of multiple databases as well as an international clinical trial registry.[@glasziou2001systematic] Statistical approaches for detection of reporting bias were not conducted due to lack of validated methods.[@begg2005systematic] Simulations have revealed that tests for detecting funnel plot asymmetry will result in publication bias being incorrectly identified too often.[@deeks2005performance]
@@
 This was achieved by using weights proportional to the number of participants, not the total number of measurements.
-The R statistical program was used to conduct all analyses[@team2017r] All data and R code used in the meta-analyses can be located [here](https://github.com/awconway/zero-heat-flux-review).
+The R statistical program was used to conduct all analyses.[@team2017r] All data and R code used in the meta-analyses can be located [here](https://github.com/awconway/zero-heat-flux-review).
 
-Prior to conducting the meta-analyses, the results from each study were converted into a standard format, with bias meaning comparator thermometer minus zero-heat-flux thermometer measured in °C.
+Prior to conducting the meta-analyses, the results from each study were converted into a standard format, with bias meaning comparator thermometer minus zero-heat-flux thermometer measured in degrees Celsius (°C).
 In several studies, results were reported for multiple groups of participants, therefore in the meta-analysis each of these groups was treated as a separate 'comparison'.
@@
 
-The conventionally cited clinically acceptable agreement between zero-heat-flux and comparator devices is 0.5 °C.[@eshraghi2014] It was deemed that outer confidence bounds for 95% limits of agreement between zero-heat-flux and core temperature measurements (termed as ‘population limits of agreement’) outside of these bounds would be clinically unacceptable.
+The conventionally cited clinically acceptable agreement between zero-heat-flux and comparator devices is 0.5°C.[@eshraghi2014] It was deemed that outer confidence bounds for 95% limits of agreement between zero-heat-flux and core temperature measurements (termed as ‘population limits of agreement’) outside of these bounds would be clinically unacceptable.
 
@@
 The quality of evidence for the primary comparison was downgraded to low quality due to concerns about study limitations and inconsistency.
-Population limits of agreement for the sensitivity analysis restricted to studies rated as having low risk of bias across all the domains of the QADAS-2 were similar to the primary analysis (`r low_risk$Measurements` measurements; `r low_risk$Participants` participants; `r low_risk$Studies` studies).
+Population limits of agreement for the sensitivity analysis restricted to studies rated as having low risk of bias across all the domains of the QUADAS-2 were similar to the primary analysis (`r low_risk$Measurements` measurements; `r low_risk$Participants` participants; `r low_risk$Studies` studies).
 The mean bias was again `r low_risk$bias_mean`°C with population limits of agreement spanning from `r low_risk$CI_L_rve`°C to `r low_risk$CI_U_rve`°C.
@@
 The GRADE rating for quality of evidence was downgraded to very low quality due to study limitations, inconsistency and imprecision.
-In the subset of studies that evaluated the use of zero-heat-flux thermometers during surgery found a mean bias of `r OT$bias_mean`°C with population limits of agreement from `r OT$CI_L_rve`°C to `r OT$CI_U_rve` °C.
-The quality of evidence rated as moderate quality due to concerns about study limitations.
+In the subset of studies that evaluated the use of zero-heat-flux thermometers during surgery found a mean bias of `r OT$bias_mean`°C with population limits of agreement from `r OT$CI_L_rve`°C to `r OT$CI_U_rve`°C.
+The quality of evidence was rated as moderate quality due to concerns about study limitations.
 
@@
 
-The mean bias between zero-heat-flux and nasopharyngeal temperature measurements in meta-analysis of results from `r NPA$Studies` studies was `r NPA$bias_mean` °C.
+The mean bias between zero-heat-flux and nasopharyngeal temperature measurements in meta-analysis of results from `r NPA$Studies` studies was `r NPA$bias_mean`°C.
 Population limits of agreement were `r NPA$CI_L_rve`°C to `r NPA$CI_U_rve`°C.
@@
 Results from this systematic review have important implications for practice.
-Clinicians should consider the potential that a temperature measurement from a zero-heat-flux thermometer could be as much as one degree Celsius higher or lower than core temperature.
-It was reassuring that results of our sensitivity analysis restricted to studies judged to be at low risk of bias using the QADAS-2 tool were similar.
+Clinicians should consider the potential that a temperature measurement from a zero-heat-flux thermometer could be as much as 1°C higher or lower than core temperature.
+It was reassuring that results of our sensitivity analysis restricted to studies judged to be at low risk of bias using the QUADAS-2 tool were similar.
 As such, it is vital for clinicians considering using this device to first determine if differences in temperature smaller than this magnitude would be important for the given clinical situation.
@@
 Our estimates of the accuracy of zero-heat-flux thermometers are similar to results from a previous meta-analysis that compared other peripheral thermometers, such as sublingual and temporal artery devices, with core temperature measurements.[@niven2015accuracy] However, this previous meta-analysis used a statistical approach that did not incorporate the magnitude of heterogeneity in results between studies or sampling error.
-As such, it is possible that the zero-heat-flux thermometer may still more precise than other peripheral thermometers.
+As such, it is possible that the zero-heat-flux thermometer may still be more precise than other peripheral thermometers.
 
@@
 Although comparisons with core temperature are the most important to evaluate, we included studies that compared zero-heat-flux and peripheral temperature monitoring devices in our review because clinicians may be interested to determine if this new technology is sufficiently accurate to replace other ways to non-invasively monitor temperature.
-Also, there may be situations where it is not practical to expose research participants to the potential additional risk of invasive core temperature monitoring for the purposes of evaluating the new temperature monitoring device when it is standard practice for only peripheral temperature monitoring to be used.
+Also, there may be situations where it is standard practice for only peripheral temperature monitoring to be used.
+In these circumstances, it is not practical to expose research participants to the potential risks of invasive core temperature monitoring for the purpose of evaluating the new temperature monitoring device.
 Whether or not the zero-heat-flux thermometer is sufficiently accurate to be used in place of nasopharyngeal thermometers is unclear.
-Population limits of agreement calculated from four studies were broad, spanning from one degree less than zero-heat-flux temperature to one degree higher.
+Population limits of agreement calculated from four studies were broad, spanning from 1°C less than zero-heat-flux temperature to one degree higher.
 Further studies are therefore required.
@@
 
-The accuracy of zero-heat-flux temperature monitoring has been evaluated in various intraoperative-operative contexts as well as in the intensive care unit setting.
+The accuracy of zero-heat-flux temperature monitoring has been evaluated in various intraoperative contexts as well as in the intensive care unit setting.
 Our subgroup analyses did not indicate that the accuracy of this temperature monitoring device was any more effective in a particular setting.

### 2019-11-29 app/app.R
try gofer to render core plot

@@ -9,10 +9,15 @@ library(readxl)
 # library(bama) #awconway/bama
 # library(ggprisma)
 library(waiter)
+library(gofer)#awconway/gofer
 # Load data ----
 # 
-data <- readxl::read_xlsx(here::here("data", "zhf_extracted.xlsx"))
-# sum_findings <- readxl::read_xlsx(here::here("data", "sum_findings.xlsx"))
+load(here::here("app", "data", "data_core_age.rda"))
+load(here::here("app", "data", "data_core.rda"))
+load(here::here("app", "data", "ma_core.rda"))
+
+data <- readxl::read_xlsx(here::here("app", "data", "zhf_extracted.xlsx"))
+# sum_findings <- readxl::read_xlsx(here::here("app", "data", "sum_findings.xlsx"))
 
 # create additional columns for meta-analysis
 data <- data %>%
@@ -163,7 +168,7 @@ ui <- dashboardPage(
               fluidRow(
                 tabBox(width = 12, 
                               tabPanel(p("Primary comparison - ZHF vs core"),
-                                       img(src="gofer.png", height="100%", width="100%")
+                                       plotOutput("gofer_core")
                               ),
                               tabPanel(p("Low risk - ZHF vs core"),
                                        img(src="gofer_low_risk.png", height="100%", width="100%")
@@ -438,7 +443,7 @@ server <- shinyUI(function(input, output) {
   Sys.sleep(3) # do something that takes time
   
   output$Rob_summary <- renderPlot({
-    frame <- read_excel(here::here("data", "zhf_extracted.xlsx"))
+    frame <- read_excel(here::here("app", "data", "zhf_extracted.xlsx"))
 
     RoB <- frame %>%
       select(Study, RoB_selection, RoB_spoton, RoB_comparator, RoB_flow) %>%
@@ -453,7 +458,7 @@ server <- shinyUI(function(input, output) {
   })
 
   output$Rob_traffic_light <- renderPlot({
-    frame <- read_excel(here::here("data", "zhf_extracted.xlsx"))
+    frame <- read_excel(here::here("app", "data", "zhf_extracted.xlsx"))
 
     RoB <- frame %>%
       select(Study, RoB_selection, RoB_spoton, RoB_comparator, RoB_flow) %>%
@@ -721,7 +726,15 @@ server <- shinyUI(function(input, output) {
[…]

### 2019-11-29 app/app.R
just grid.draw in renderPlot

@@ -16,6 +16,10 @@ load(here::here("app", "data", "data_core_age.rda"))
 load(here::here("app", "data", "data_core.rda"))
 load(here::here("app", "data", "ma_core.rda"))
 
+gofer_core <- gofer::gofer(data_core, ma_effect = ma_core$effect_estimate,
+                      ma_lower = ma_core$lower_limit, ma_upper = ma_core$upper_limit,
+                      grade_rating="Moderate", data_age = data_core_age, dodge_width = 0.85)
+
 data <- readxl::read_xlsx(here::here("app", "data", "zhf_extracted.xlsx"))
 # sum_findings <- readxl::read_xlsx(here::here("app", "data", "sum_findings.xlsx"))
 
@@ -167,8 +171,9 @@ ui <- dashboardPage(
       tabItem(tabName = "gofer",
               fluidRow(
                 tabBox(width = 12, 
-                              tabPanel(p("Primary comparison - ZHF vs core"),
-                                       plotOutput("gofer_core")
+                              tabPanel(
+                                       p("Primary comparison - ZHF vs core"),
+                                       plotOutput(outputId = "gofer_core", height="1200px")
                               ),
                               tabPanel(p("Low risk - ZHF vs core"),
                                        img(src="gofer_low_risk.png", height="100%", width="100%")
@@ -727,10 +732,8 @@ server <- shinyUI(function(input, output) {
 #                                          estimates of limits of agreement (LoA) between", tolower(input$dataset), "and ZHF thermometry (ie. population LoA)."))
 # #}) # end of output$caption
   output$gofer_core <- renderPlot({
-    gofer <- gofer::gofer(data_core, ma_effect = ma_core$effect_estimate,
-                 ma_lower = ma_core$lower_limit, ma_upper = ma_core$upper_limit,
-                 grade_rating="Moderate", data_age = data_core_age, dodge_width = 0.85)
-    grid::grid.draw(gofer)
+
+    grid::grid.draw(gofer_core)
   }
     
   )

### 2019-11-29 app/app.R
added pdf(NULL) to allow it to run on server

@@ -12,16 +12,16 @@ library(waiter)
 library(gofer)#awconway/gofer
 # Load data ----
 # 
-load(here::here("app", "data", "data_core_age.rda"))
-load(here::here("app", "data", "data_core.rda"))
-load(here::here("app", "data", "ma_core.rda"))
-
+load(here::here("data", "data_core_age.rda"))
+load(here::here("data", "data_core.rda"))
+load(here::here("data", "ma_core.rda"))
+pdf(NULL)
 gofer_core <- gofer::gofer(data_core, ma_effect = ma_core$effect_estimate,
                       ma_lower = ma_core$lower_limit, ma_upper = ma_core$upper_limit,
                       grade_rating="Moderate", data_age = data_core_age, dodge_width = 0.85)
 
-data <- readxl::read_xlsx(here::here("app", "data", "zhf_extracted.xlsx"))
-# sum_findings <- readxl::read_xlsx(here::here("app", "data", "sum_findings.xlsx"))
+data <- readxl::read_xlsx(here::here("data", "zhf_extracted.xlsx"))
+# sum_findings <- readxl::read_xlsx(here::here("data", "sum_findings.xlsx"))
 
 # create additional columns for meta-analysis
 data <- data %>%
@@ -448,7 +448,7 @@ server <- shinyUI(function(input, output) {
   Sys.sleep(3) # do something that takes time
   
   output$Rob_summary <- renderPlot({
-    frame <- read_excel(here::here("app", "data", "zhf_extracted.xlsx"))
+    frame <- read_excel(here::here("data", "zhf_extracted.xlsx"))
 
     RoB <- frame %>%
       select(Study, RoB_selection, RoB_spoton, RoB_comparator, RoB_flow) %>%
@@ -463,7 +463,7 @@ server <- shinyUI(function(input, output) {
   })
 
   output$Rob_traffic_light <- renderPlot({
-    frame <- read_excel(here::here("app", "data", "zhf_extracted.xlsx"))
+    frame <- read_excel(here::here("data", "zhf_extracted.xlsx"))
 
     RoB <- frame %>%
       select(Study, RoB_selection, RoB_spoton, RoB_comparator, RoB_flow) %>%
@@ -732,7 +732,7 @@ server <- shinyUI(function(input, output) {
 #                                          estimates of limits of agreement (LoA) between", tolower(input$dataset), "and ZHF thermometry (ie. population LoA)."))
 # #}) # end of output$caption
[…]

### 2019-11-29 app/app.R
reactive gofer not yet working

@@ -6,19 +6,12 @@ library(tidyverse)
 library(DT)
 library(robvis)
 library(readxl)
-# library(bama) #awconway/bama
+library(bama) #awconway/bama
 # library(ggprisma)
 library(waiter)
 library(gofer)#awconway/gofer
 # Load data ----
 # 
-load(here::here("data", "data_core_age.rda"))
-load(here::here("data", "data_core.rda"))
-load(here::here("data", "ma_core.rda"))
-pdf(NULL)
-gofer_core <- gofer::gofer(data_core, ma_effect = ma_core$effect_estimate,
-                      ma_lower = ma_core$lower_limit, ma_upper = ma_core$upper_limit,
-                      grade_rating="Moderate", data_age = data_core_age, dodge_width = 0.85)
 
 data <- readxl::read_xlsx(here::here("data", "zhf_extracted.xlsx"))
 # sum_findings <- readxl::read_xlsx(here::here("data", "sum_findings.xlsx"))
@@ -76,6 +69,7 @@ data$comparison <- sub("Iliac", "Iliac artery", data$comparison)
 data$comparison <- sub("Ax", "Axillary artery", data$comparison)
 data$comparison <- sub("Eso", "Esophageal", data$comparison)
 
+
 # Clean up results
 format_results <- function(group){
   out <- bama::loa_maker(group$bias,group$V_bias, group$logs2, group$V_logs2)
@@ -86,6 +80,59 @@ format_results <- function(group){
     select(Studies, m, Participants, Measurements, bias_mean, sd2_est, tau_est, LOA_L, LOA_U, CI_L_rve, CI_U_rve) %>%
     rename("Comparisons" = m)
 }
+
+
+ma_low_risk <- format_results(data_core_lowrisk) %>% rename("lower_limit" = CI_L_rve, 
+                                                             "effect_estimate" = bias_mean, 
+                                                             "upper_limit" = CI_U_rve)
+
+ma_NPA <- format_results(data_NPA) %>% rename("lower_limit" = CI_L_rve, 
+                                                             "effect_estimate" = bias_mean, 
+                                                             "upper_limit" = CI_U_rve)
+
+ma_SL <- format_results(data_SL) %>% rename("lower_limit" = CI_L_rve, 
+                                                   "effect_estimate" = bias_mean, 
+                                                   "upper_limit" = CI_U_rve)
+
+ma_conflict <- format_results(data_conflict) %>% rename("lower_limit" = CI_L_rve, 
[…]

### 2019-11-29 app/app.R
reactive gofer attempt - taking a long time

@@ -37,28 +37,28 @@ data <- data %>%
   mutate(V_logs2 = 2/(n-1))
 
 # Create subgroups
-
-data_NPA <- data %>%
-  filter(comparison == "NPA")
-
-data_SL <- data %>%
-  filter(comparison == "Sublingual")
-
-data_core <- data %>% #eshragi overall
-  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
-  filter(comments != "Intraoperative, off cardiopulmonary bypass" & comments != "Postoperative")
-
-data_core_lowrisk <- data_core %>% #eshragi overall
+# use data from gofer package
+# data_NPA <- data %>%
+#   filter(comparison == "NPA")
+# 
+# data_SL <- data %>%
+#   filter(comparison == "Sublingual")
+# 
+# data_core <- data %>% #eshragi overall
+#   filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
+#   filter(comments != "Intraoperative, off cardiopulmonary bypass" & comments != "Postoperative")
+# 
+data_core_low_risk <- data_core %>% #eshragi overall
   filter(RoB_selection == "low" & RoB_spoton == "low" & RoB_comparator == "low" & RoB_flow =="low")
-
-data_core_op <- data %>% #eshragi intraop
-  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
-  filter (clinical_setting=="Intraoperative")
-
-data_core_icu <- data %>% #eshragi postop
-  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
-  filter(clinical_setting=="ICU" | clinical_setting=="Postoperative")
-
+# 
+# data_core_op <- data %>% #eshragi intraop
+#   filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
+#   filter (clinical_setting=="Intraoperative")
+# 
+# data_core_icu <- data %>% #eshragi postop
[…]

### 2019-11-29 app/app.R
back to just core that is created on load

@@ -6,12 +6,19 @@ library(tidyverse)
 library(DT)
 library(robvis)
 library(readxl)
-library(bama) #awconway/bama
+# library(bama) #awconway/bama
 # library(ggprisma)
 library(waiter)
 library(gofer)#awconway/gofer
 # Load data ----
 # 
+load(here::here("data", "data_core_age.rda"))
+load(here::here("data", "data_core.rda"))
+load(here::here("data", "ma_core.rda"))
+pdf(NULL)
+gofer_core <- gofer::gofer(data_core, ma_effect = ma_core$effect_estimate,
+                           ma_lower = ma_core$lower_limit, ma_upper = ma_core$upper_limit,
+                           grade_rating="Moderate", data_age = data_core_age, dodge_width = 0.85)
 
 data <- readxl::read_xlsx(here::here("data", "zhf_extracted.xlsx"))
 # sum_findings <- readxl::read_xlsx(here::here("data", "sum_findings.xlsx"))
@@ -37,28 +44,28 @@ data <- data %>%
   mutate(V_logs2 = 2/(n-1))
 
 # Create subgroups
-# use data from gofer package
-# data_NPA <- data %>%
-#   filter(comparison == "NPA")
-# 
-# data_SL <- data %>%
-#   filter(comparison == "Sublingual")
-# 
-# data_core <- data %>% #eshragi overall
-#   filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
-#   filter(comments != "Intraoperative, off cardiopulmonary bypass" & comments != "Postoperative")
-# 
-data_core_low_risk <- data_core %>% #eshragi overall
+
+data_NPA <- data %>%
+  filter(comparison == "NPA")
+
+data_SL <- data %>%
+  filter(comparison == "Sublingual")
+
+data_core <- data %>% #eshragi overall
+  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
+  filter(comments != "Intraoperative, off cardiopulmonary bypass" & comments != "Postoperative")
+
+data_core_lowrisk <- data_core %>% #eshragi overall
   filter(RoB_selection == "low" & RoB_spoton == "low" & RoB_comparator == "low" & RoB_flow =="low")
-# 
[…]

### 2019-12-02 app/app.R
data for rob

@@ -204,9 +204,9 @@ server <- shinyUI(function(input, output) {
   Sys.sleep(3) # do something that takes time
   
   output$Rob_summary <- renderPlot({
-    frame <- read_excel(here::here("app", "data", "zhf_extracted.xlsx"))
     
-    RoB <- frame %>%
+    
+    RoB <- data_core %>%
       select(Study, RoB_selection, RoB_spoton, RoB_comparator, RoB_flow) %>%
       mutate(RoB_overall = if_else(RoB_selection == "low" &
                                      RoB_spoton == "low" &
@@ -219,9 +219,9 @@ server <- shinyUI(function(input, output) {
   })
   
   output$Rob_traffic_light <- renderPlot({
-    frame <- read_excel(here::here("app", "data", "zhf_extracted.xlsx"))
     
-    RoB <- frame %>%
+    
+    RoB <- data_core %>%
       select(Study, RoB_selection, RoB_spoton, RoB_comparator, RoB_flow) %>%
       mutate(RoB_overall = if_else(RoB_selection == "low" &
                                      RoB_spoton == "low" &

### 2019-12-02 app/app.R
waitress for gofer plot

@@ -44,7 +44,7 @@ ui <- dashboardPage(
     ) 
   ),
   dashboardBody(  
-    use_waiter(include_js = FALSE),
+    
     
     tabItems(
       tabItem(tabName="Rob",
@@ -61,9 +61,9 @@ ui <- dashboardPage(
       ),
       
       tabItem(tabName = "gofer",
-              fillPage(      tags$style(type = "text/css", "#gofer {height: calc(100vh - 80px) !important;}"),
-
-                              plotOutput("gofer", height="100%")
+              fillPage(    tags$style(type = "text/css", "#gofer {height: calc(100vh - 80px) !important;}"),
+                           use_waitress(color = "#7F7FFF"),
+                           plotOutput("gofer", height="100%")
                               )
               
       ),
@@ -196,7 +196,6 @@ ui <- dashboardPage(
 ')
               ))
     )  
-    ,  show_waiter_on_load(spin_folding_cube())
   ) #end dashboardBody
 ) #end dashboardPage
 
@@ -306,8 +305,19 @@ server <- shinyUI(function(input, output) {
     )
   })
   
+  waitress <- Waitress$new(theme = "overlay-percent") # call the waitress  observeEvent(input$load, {
+  observeEvent(input$gofer, {
+    waitress$
+      start()$
+      auto(percent = 5, ms = 150) # increase by 5 percent every 150 milliseconds
+    Sys.sleep(3.5)
+    waitress$hide()
+  })
+  
   output$gofer <- renderPlot({
-
+    waitress$start()
+    
+    
     plot <- gofer::gofer(gofer_input()[[1]], ma_effect = gofer_input()[[2]]$effect_estimate,
                                    ma_lower = gofer_input()[[2]]$lower_limit, ma_upper = gofer_input()[[2]]$upper_limit,
                                    grade_rating=gofer_input()[[4]], data_age = gofer_input()[[3]], 
@@ -315,6 +325,8 @@ server <- shinyUI(function(input, output) {
         
     
     grid::grid.draw(plot)
+    
+    waitress$hide() # hide when done
      
                                   }) # renderPlot
   
@@ -324,8 +336,9 @@ output$ggprisma <- renderPlot({
                      wrong_design = 1, awaiting_classification = 2)
 })  
   
-  hide_waiter()
-  
+
+
+
 }) # end of server
 
 shinyApp(ui, server)

### 2019-12-02 app/app.R
waitress in navbar

@@ -62,7 +62,7 @@ ui <- dashboardPage(
       
       tabItem(tabName = "gofer",
               fillPage(    tags$style(type = "text/css", "#gofer {height: calc(100vh - 80px) !important;}"),
-                           use_waitress(color = "#7F7FFF"),
+                           use_waitress(),
                            plotOutput("gofer", height="100%")
                               )
               
@@ -304,19 +304,19 @@ server <- shinyUI(function(input, output) {
            
     )
   })
-  
-  waitress <- Waitress$new(theme = "overlay-percent") # call the waitress  observeEvent(input$load, {
-  observeEvent(input$gofer, {
-    waitress$
-      start()$
-      auto(percent = 5, ms = 150) # increase by 5 percent every 150 milliseconds
-    Sys.sleep(3.5)
-    waitress$hide()
-  })
+  waitress <- call_waitress("nav", theme = "overlay-percent") # call the waitress
   
   output$gofer <- renderPlot({
     waitress$start()
     
+    
+    dat <- vector()
+    
+    for(i in 1:10){
+      waitress$increase(10) # increase by 10%
+      Sys.sleep(.3)
+      dat <- c(dat, sample(1:100, 1))
+    }
     
     plot <- gofer::gofer(gofer_input()[[1]], ma_effect = gofer_input()[[2]]$effect_estimate,
                                    ma_lower = gofer_input()[[2]]$lower_limit, ma_upper = gofer_input()[[2]]$upper_limit,

### 2019-12-03 manuscript/manuscript.Rmd
cleaned folders and added loa_maker source files

@@
 library(knitr)
-library(bama) # https://github.com/awconway/bama
 library(ggprisma) # https://github.com/awconway/ggprisma
 library(gt)
+source("loa_maker.R")
+source("meta.R")
 ```
@@
 format_results <- function(group){
-out <- bama::loa_maker(group$bias,group$V_bias, group$logs2, group$V_logs2)
+out <- loa_maker(group$bias,group$V_bias, group$logs2, group$V_logs2)
 out <- round(out, digits=2)
@@
 Sixteen studies were included.
-The primary comparison of zero-heat-flux versus core temperature measurements consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies.
+The primary meta-analysis of zero-heat-flux versus core temperature measurements consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies.
 Data from `r primary$Participants` participants with `r format(primary$Measurements, scientfic=F)` paired measurements were included.

### 2019-12-03 RoB-figures.R

@@ -1,19 +1,0 @@
-library(robvis)
-library(readxl)
-library(tidyverse)
-
-frame <- read_excel(here::here("manuscript", "data", "zhf_extracted.xlsx"))
-
-RoB <- frame %>% 
-  select(Study, RoB_selection, RoB_spoton, RoB_comparator, RoB_flow) %>% 
-  mutate(RoB_overall = if_else(RoB_selection == "low" &
-                                 RoB_spoton == "low" &
-                                 RoB_comparator == "low" &
-                                 RoB_flow == "low", "low", "high"))
-
-RoB[RoB == "unclear"] <- "some concerns"
-
-rob_summary(data = RoB, tool = "QUADAS-2", weighted = FALSE)
-rob_traffic_light(data = RoB, tool = "QUADAS-2")
-
-pr_push()

### 2019-12-03 app/app.R

@@ -5,7 +5,6 @@ library(shinydashboardPlus)
 library(tidyverse)
 library(DT)
 library(robvis)
-library(bama) #awconway/bama
 library(ggprisma) #awconway/ggprisma
 library(waiter)
 library(gofer)#awconway/gofer

### 2019-12-03 app/xml.R

@@ -1,42 +1,0 @@
-library(xml2)
-library(tidyverse)
-
-testxml <- xml2::read_xml(here::here("app", "data", "study-characteristics", "study-characteristics.xml"))
-rows <- xml_find_all(testxml, ".//ss:Row")
-
-#Study names
-study <- xml_find_all(testxml, ".//ss:Worksheet")
-study <- xml_attr(study, "Name")
-
-index_number <- 3
-xml_extract <- function(index_number, source_name){
-  if(missing(source_name)) {
-    new_column <- xml_find_all(rows, glue::glue("//ss:Row[@ss:Index='{index_number}']"))
-    xml_text(new_column)
-  } else {
-  new_column <- xml_find_all(rows, glue::glue("//ss:Row[@ss:Index='{index_number}']"))
-  new_column <- xml_text(new_column)
-  stringr::str_remove(new_column, source_name)
- }
- }
-
-sponsorship <- xml_extract(3, "Sponsorship source")
-country <- xml_extract(4, "Country")
-setting <- xml_extract(5, "Setting")
-design <- xml_extract(13, "Design")
-inclusions <- xml_extract(17, "Inclusion criteria")
-exclusions <- xml_extract(18, "Exclusion criteria")
-temp_range <- xml_extract(25, "Temperature range (Celsius)")
-groups <- xml_extract(21)
-age <- xml_extract(22)
-female <- xml_extract(23)
-male <- xml_extract(24)
-
-# Dataframe
-dataframe <- tibble::tibble(study, country, setting, design,
-                            inclusions, exclusions, sponsorship)
-
-glimpse(dataframe)
-
-#Resource
-#https://stackoverflow.com/questions/42799674/r-and-xml2-how-to-read-text-that-is-not-in-children-nodes-and-read-information

### 2019-12-03 gofer/gofer.R

@@ -1,802 +1,0 @@
-library(tidyverse)
-library(ggfittext)
-library(gridExtra)
-library(grid)
-library(gtable)
-library(naniar)
-library(ggimage)
-
-data <- readxl::read_xlsx("~/zhf-review/manuscript/data/zhf_extracted.xlsx")
-
-
-# Study characteristics data
-demographics <- readxl::read_xlsx("~/zhf-review/gofer/study-characteristics.xlsx")
-
-
-data <- data %>%
-  mutate(c = N/n)
-
-#variance
-
-data <- data %>% 
-  mutate(s2 = case_when(corrected == "Yes"  ~ ((upper - bias)/1.96)^2,
-                        corrected == "No" ~  ((upper - bias)/1.96)^2*(N-1)/(N-c)
-  )
-  )
-
-data <- data %>% 
-  mutate(V_bias = s2/n)
-
-data <- data %>% 
-  mutate(logs2 = log(s2)+1/(n-1))
-
-data <- data %>% 
-  mutate(V_logs2 = 2/(n-1))
-
-# meta-analyses categories
-
-data_NPA <- data %>% 
-  filter(comparison == "NPA")
-
-data_SL <- data %>% 
-  filter(comparison == "Sublingual")
-
-#eshragi overall
-data_core <- data %>% 
-  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
-  filter(comments != "Intraoperative, off cardiopulmonary bypass" & comments != "Postoperative")
-
-data_core_op <- data %>% #eshragi intraop
-  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
-  filter (clinical_setting=="Intraoperative")
-
-data_core_icu <- data %>% #eshragi postop
-  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
-  filter(clinical_setting=="ICU" | clinical_setting=="Postoperative")
-
-# ROB 
-
-data_core_lowrisk <- data_core %>% #eshragi overall
-  filter(RoB_selection == "low" & RoB_spoton == "low" & RoB_comparator == "low" & RoB_flow =="low")
-
-# conflict of interests
-
[…]

### 2019-12-03 gofer/gofer_function.R

@@ -1,83 +1,0 @@
-library(tidyverse)
-library(ggfittext)
-library(gridExtra)
-library(grid)
-library(gtable)
-library(naniar)
-library(ggimage)
-data <- readxl::read_xlsx("~/zhf-review/gofer/data.xlsx")
-
-data <- data %>%
-  mutate(c = N/n)
-
-#variance
-
-data <- data %>% 
-  mutate(s2 = case_when(corrected == "Yes"  ~ ((upper - bias)/1.96)^2,
-                        corrected == "No" ~  ((upper - bias)/1.96)^2*(N-1)/(N-c)
-  )
-  )
-
-data <- data %>% 
-  mutate(V_bias = s2/n)
-
-data <- data %>% 
-  mutate(logs2 = log(s2)+1/(n-1))
-
-data <- data %>% 
-  mutate(V_logs2 = 2/(n-1))
-
-# meta-analyses categories
-
-data_NPA <- data %>% 
-  filter(comparison == "NPA")
-
-data_SL <- data %>% 
-  filter(comparison == "Sublingual")
-
-#eshragi overall
-data_core <- data %>% 
-  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
-  filter(comments != "Intraoperative, off cardiopulmonary bypass" & comments != "Postoperative")
-
-data_core_op <- data %>% #eshragi intraop
-  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
-  filter (clinical_setting=="Intraoperative")
-
-data_core_icu <- data %>% #eshragi postop
-  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
-  filter(clinical_setting=="ICU" | clinical_setting=="Postoperative")
-
-# ROB 
-
-data_core_lowrisk <- data_core %>% #eshragi overall
-  filter(RoB_selection == "low" & RoB_spoton == "low" & RoB_comparator == "low" & RoB_flow =="low")
-
-# conflict of interests
-
-data_conflict <- data_core %>% 
-  filter(`Funding/equipment/conflict with ZHF company` == "No")
-
-format_results <- function(group){
[…]

### 2019-12-03 manuscript/prisma.R

@@ -1,214 +1,0 @@
-  library(ggplot2)
-  library(tibble)
-  library(tidyverse)
-  library(ggfittext)
-  
-  line_size <- 0.50
-  box_type <- "round"
-  box_lines <- 0.5
-  box_colour <- "white"
-  box_fill <- alpha("#14c4ff", 0.3)
-  text_colour <- "#ff4f14"
-  arrow_colour <- "#ff4f14"
-  
-  
-  retrieved <- 129
-  duplicates <- 35
-  screened <- retrieved-duplicates
-  full_text <- 21
-  screen_excluded <- screened-full_text
-  included <- 15
-  full_text_excluded <- full_text-included
-  wrong_intervention <- 4
-  wrong_comparator <- 2
-  wrong_design <- 1
-  awaiting_classification <- 2
-  
-
-# Main flow y coordinates  
-  import_y_max <- 100
-  import_y_min <- 90
-  screen_y_max <- 80
-  screen_y_min <- 70
-  full_y_max <- 60
-  full_y_min <- 50
-  included_y_max <- 40
-  included_y_min <- 30
-  
-# Scondary flow y coordinates  
-  duplicates_y_max <- 90
-  duplicates_y_min <- 80
-  
-  full_excluded_y_min <- 25
-  full_excluded_y_max <- 45
-  
-  screen_excluded_y_min <- 65
-  screen_excluded_y_max <- 75
-  
-  awaiting_classification_y_min <- 50
-  awaiting_classification_y_max <- 60
-  
-# x coordinates  
-  main_x_min <- 20
-  main_x_max <- 70
-  
-  second_x_min <- 75
-  second_x_max <- 95
-  
-  arrow_x <- 45
-  
-  ###Plot space set-up####
-  data <- tibble(x= 23:100, y = 23:100)
-  
-  p <- data %>% 
-    ggplot(aes(x, y)) +
-    theme_linedraw() +
-  
-  
-  
-  ########## Main box flow ###########
-  
-  # import box
-
-  annotation_custom(grob = grid::roundrectGrob(gp = grid::gpar(col = box_colour, fill = box_fill)),
-    xmin = main_x_min, xmax=main_x_max, ymin=import_y_min, ymax=import_y_max)+
-    geom_fit_text(xmin = main_x_min, xmax=main_x_max, ymin=import_y_min, ymax=100,
-                  label= glue::glue(retrieved, ' references identified'), 
-                  reflow = TRUE, colour = text_colour) +
-
[…]

### 2019-12-03 app/app.R
added ggimage because required for binder to open app

@@ -8,6 +8,7 @@ library(robvis)
 library(ggprisma) #awconway/ggprisma
 library(waiter)
 library(gofer)#awconway/gofer
+library(ggimage)
 
 ######UI#########
 ui <- dashboardPage(
@@ -183,6 +184,8 @@ ui <- dashboardPage(
 <p>Kristina Chang  (Toronto General Hospital, UHN)
   
 <p>Peter Collins  (Toronto General Hospital, UHN)
+
+<p>Elizabeth Tipton (Dapartment of Statistics, Northwestern University)
   
 <p>Matteo Parotto  (Toronto General Hospital, UHN)
 

### 2019-12-03 manuscript/figures/fig-one.R
code to produce figure 1 and table 1 for manuscript

@@ -1,0 +1,6 @@
+fig <- ggprisma::ggprisma(retrieved = 130, included = 16, duplicates = 35, 
+                   full_text = 22, wrong_intervention = 4, 
+                   wrong_comparator = 2, wrong_design = 1, 
+                   awaiting_classification = 2)
+
+ggsave("fig-one.pdf", device = "pdf")

### 2019-12-03 manuscript/figures/table-1.R

@@ -1,0 +1,16 @@
+gt <- df %>% 
+  rename(" " = Comparison, "Mean bias" = bias_mean, "Variance" = sd2_est, 
+         "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, 
+         "Upper bound for 95% limits of agreement" = LOA_U, 
+         "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, 
+         "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve) %>% 
+  gt() %>%
+  tab_header(
+    title = "Table 1. Results of meta-analyses"  )  %>%
+  tab_spanner(
+    label = "Population limits of agreement",
+    columns = vars(
+      `Outer confidence interval for lower 95% limits of agreement`, `Outer confidence interval for upper 95% limits of agreement`)
+  )
+
+gtsave(data = gt, filename = "table_gt.pdf", vwidth = 600)

### 2019-12-03 manuscript/manuscript.Rmd
hyperlink fixed

@@
 A systematic review was conducted in accordance with a predetermined protocol.
-The protocol was submitted to PROSPERO for registration but due to delays in processing we had started data extraction by the time it was reviewed.
-Therefore, the protocol did not meet the requirements for registration.
-A copy of the submitted protocol can be accessed [here](https://github.com/awconway/zhf-review).
 The primary comparison for this review was temperature measured from a zero-heat-flux thermometer versus temperature measured from a core site, which we defined as temperature measured at either an arterial, esophageal, bladder or rectal site.
@@
 The Cochrane-recommended search strategy combining terms for the ‘target condition’ and ‘index test’ was used.[@mann2012should] This search strategy is an efficient approach for systematic reviews of diagnostic test accuracy studies.[@preston2015improving] We also conducted forward citation searching, by using Google Scholar to search the citations of the first article published on the accuracy of zero-heat-flux thermometers.
-The search strategies used for each data base can be located [here](https://aconway.dev/zhf app).
+The search strategies used for each data base can be located [here](https://aconway.dev/zhf).
 Selection of studies was undertaken independently by two reviewers using [Covidence](https://www.covidence.org).
@@
 
-```{r table-1, layout="l-page-outset"}
+```{r table-1, layout="l-page-outset", echo=FALSE}
+library(kableExtra)
   ma <- list(primary, low_risk, ICU, OT,  NPA,SL, conflict)

### 2019-12-03 manuscript/manuscript.Rmd
params to show text for word output

@@
 ---
-title: "Accuracy and precision of zero-heat-flux temperature monitoring"
-description: A systematic review and meta-analysis
+title: "Accuracy and precision of zero-heat-flux temperature monitoring: A systematic review and meta-analysis"
 author:
@@
 - name: Elizabeth Tipton
-  affiliation: Dapartment of Statistics, Northwestern University
+  affiliation: Department of Statistics, Northwestern University
 - name: Matteo Parotto
   affiliation: Toronto General Hospital, UHN
-date: "`r Sys.Date()`"
-bibliography: bibliography.bib
-output: distill::distill_article
+# date: "`r Sys.Date()`"
 repository_url: https://github.com/awconway/zhf-review
@@
   creator: "@aw_conway"
+bibliography: bibliography.bib
+csl: anesthesiology.csl
+output: word_document
+# output: distill::distill_article
+params:
+  distill: FALSE
+  word: TRUE
 ---
+
+```{r global_options, include=FALSE}
+knitr::opts_chunk$set(include=FALSE,
+                      echo=FALSE, warning=FALSE, message=FALSE)
+```
+
+```{r conditional_title_page, results='asis', include=params$word}
+cat("
+## Author information
+
+<p>Aaron Conway PhD^1,2,3^
+<p>Megan Bittner BSc^2^
+<p>Dan Phan BSc^2^
+<p>Navpreet Kamboj BScN^2^
+<p>Kristina Chang MScN^4^
+<p>Peter Collins MStatistics^4^
+<p>Elizabeth Tipton PhD^5^
+<p>Matteo Parotto MD^4^
+
+<p>^1^ Peter Munk Cardiac Centre, University Health Network
+<p>^2^Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
+<p>^3^School of Nursing, Queensland University of Technology (QUT)
+<p>^4^Toronto General Hospital, UHN
+<p>^5^Department of Statistics, Northwestern University
+
+## Corresponding author
+
+Dr Aaron Conway BN (Hons) PhD
+RBC Chair in Cardiovascular Nursing Research | Peter Munk Cardiac Centre | Toronto General Hospital | University Health Network
+Clinician Investigator | Toronto General Hospital Research Institute | University Health Network
+Assistant Professor | Lawrence S. Bloomberg Faculty of Nursing | University of Toronto
+
+585 University Ave, 4NU - 476
+Toronto, ON  M5G 2N2
+
+e. aaron.conway@utoronto.ca  | t. (416) 946-7112
+
+## Declarations
+
+Clinical trial number: Not applicable
+
+Prior presentations: Not applicable
+
+Abstract word count: 300 words
+
+Total word count: 3075 words
+
+Introduction word count: 303 words
+
+Discussion word count: 781 words
+
+Number of figures: 2
+
+Number of tables: 1
+
+Abbreviated title: Accuracy of zero-heat-flux thermometers
+
+Summary statement: Clinicians should consider the potential that a temperature measurement from a zero-heat-flux thermometer could be as much as 1°C higher or lower than core temperature.
+
+Funding statement: Support was provided solely from institutional and/or departmental sources.
+
+Conflicts of interest: The authors declare no competing interests.
+
+")
+```
 
@@
 Zero-heat-flux thermometers are non-invasive devices that can be used to continuously monitor temperature.
-These devices are increasingly being used in clinical practice to substitute for invasive core temperature measurement during surgery and in critical care settings.
+These devices are increasingly being used to substitute for invasive core temperature measurement during surgery and in critical care.
 The aim of this review was to determine the accuracy and precision of zero-heat-flux temperature measurements.
@@
 Medline and EMBASE were searched for studies that reported on a measurement of core or peripheral temperature that coincided with a measurement from the zero-heat-flux device.
-Study selection and quality assessment (using the QUADAS-2) was performed independently.
-The GRADE approach was used to summarize the strength of the body of evidence.
-Pooled estimates of the mean bias and limits of agreement with outer 95% confidence intervals (termed population limits of agreement) were calculated.
+Study selection and quality assessment (using QUADAS-2) was performed independently.
+The GRADE approach was used to summarize the strength of the evidence.
+Pooled estimates of the mean bias and limits of agreement with outer 95% confidence intervals (population limits of agreement) were calculated.
 
@@
 Sixteen studies were included.
-The primary meta-analysis of zero-heat-flux versus core temperature measurements consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies.
+The primary meta-analysis of zero-heat-flux versus core temperature consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies.
 Data from `r primary$Participants` participants with `r format(primary$Measurements, scientfic=F)` paired measurements were included.
@@
 
-The range of uncertainty in the accuracy of the zero-heat-flux thermometer should be taken into account when using measurements from this device to inform clinical decision-making.
+The range of uncertainty in the accuracy of the zero-heat-flux thermometer should be taken into account when using this device to inform clinical decision-making.
 Clinicians should therefore consider the potential that a temperature measurement from a zero-heat-flux thermometer could be as much as 1°C higher or lower than core temperature.
@@
 The Cochrane-recommended search strategy combining terms for the ‘target condition’ and ‘index test’ was used.[@mann2012should] This search strategy is an efficient approach for systematic reviews of diagnostic test accuracy studies.[@preston2015improving] We also conducted forward citation searching, by using Google Scholar to search the citations of the first article published on the accuracy of zero-heat-flux thermometers.
-The search strategies used for each data base can be located [here](https://aconway.dev/zhf).
+The search strategies used for each data base can be located at this [link](https://aconway.dev/zhf).
 Selection of studies was undertaken independently by two reviewers using [Covidence](https://www.covidence.org).
@@
 This was achieved by using weights proportional to the number of participants, not the total number of measurements.
-The R statistical program was used to conduct all analyses.[@team2017r] All data and R code used in the meta-analyses can be located [here](https://github.com/awconway/zero-heat-flux-review).
+The R statistical program was used to conduct all analyses.[@team2017r] All data and R code used in the meta-analyses can be located at this [link](https://github.com/awconway/zhf-review).
 
@@
 
-```{r fig-1, fig.align="center", fig.cap="PRISMA Flow Diagram", echo=FALSE, fig.width=5.5, fig.path=""}
+```{r fig-1, fig.align="center", fig.cap="PRISMA Flow Diagram", echo=FALSE, fig.width=5.5, fig.path="", include=params$distill}
 # https://github.com/awconway/ggprisma
@@
 
-The characteristics of included studies can be viewed [here](https://aconway.dev/zhf).
+The characteristics of included studies can be viewed at this [link](https://aconway.dev/zhf).
 The primary comparison of zero-heat-flux versus core temperature measurements (eg, arterial, bladder, esophageal or rectal) consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies.
@@
 
-```{r fig-2, preview=TRUE, layout="l-screen-inset", fig.align="center", fig.cap="Graphical overview of findings for the primary analysis", echo=FALSE, fig.path=""}
+```{r fig-2, preview=TRUE, layout="l-screen-inset", fig.align="center", fig.cap="Graphical overview of findings for the primary analysis", echo=FALSE, fig.path="", include=params$distill}
 include_graphics("gofer_core.png")
@@
 
-```{r table-1, layout="l-page-outset", echo=FALSE}
+```{r table-1, layout="l-page-outset", include=params$distill}
 library(kableExtra)
@@
 <script src="https://hypothes.is/embed.js" async></script>
+
+```{r  conditional_references, include=params$word, results='asis'}
+cat("# References")
+```
+<div id="refs"></div>
+
+```{r  conditional_figure_legend, include=params$word, results='asis'}
+cat("# Figure legend
+
+Figure 1: PRISMA Flow Diagram
+
+Figure 2: Graphical overview of findings for the primary analysis")
+```

### 2019-12-04 app/app.R
scrollable datatable

@@ -8,7 +8,6 @@ library(robvis)
 library(ggprisma) #awconway/ggprisma
 library(waiter)
 library(gofer)#awconway/gofer
-library(ggimage)
 
 ######UI#########
 ui <- dashboardPage(
@@ -78,7 +77,7 @@ ui <- dashboardPage(
       ),
       
       tabItem(tabName="DT",
-              column(12,
+              fillPage(      tags$style(type = "text/css", "#ggprisma {height: calc(100vh - 80px) !important;}"),
                      DT::dataTableOutput("dt"))),
       tabItem(tabName="search",
               fluidRow(
@@ -283,7 +282,7 @@ server <- shinyUI(function(input, output) {
         )
       )
     ))
-    DT::datatable(datasetInput[,c(1,4:19)], container = sketch, extensions = "Buttons", options = list(dom = "Bt", scrollX=T, buttons = c('copy', 'csv', 'excel'), sort = FALSE, paging=F, scrollY=T,
+    DT::datatable(datasetInput[,c(1,4:19)], container = sketch, extensions = "Buttons", options = list(dom = "Bt", scrollX=T, buttons = c('copy', 'csv', 'excel'), sort = FALSE, paging=F, sScrollY = '75vh', 
                                                                                                        #use 'title' previously noted in column header as tooltip
                                                                                                        initComplete = JS("function(settings, json){",
                                                                                                                          "$('th').tooltip({container: 'body'});

### 2019-12-04 manuscript/manuscript.Rmd
removed tidyverse call for specific packages

@@
 ```{r echo=FALSE, include=FALSE}
-library(tidyverse)
-library(knitr)
-library(ggprisma) # https://github.com/awconway/ggprisma
-library(gt)
+library(magrittr)
 source("loa_maker.R")
@@
 data <- data %>%
-  mutate(c = N/n)
+  dplyr::mutate(c = N/n)
 
@@
 data <- data %>% 
-  mutate(s2 = case_when(corrected == "Yes"  ~ ((upper - bias)/1.96)^2,
+  dplyr::mutate(s2 = dplyr::case_when(corrected == "Yes"  ~ ((upper - bias)/1.96)^2,
          corrected == "No" ~  ((upper - bias)/1.96)^2*(N-1)/(N-c)
@@
 data <- data %>% 
-  mutate(V_bias = s2/n)
+  dplyr::mutate(V_bias = s2/n)
 
 data <- data %>% 
-  mutate(logs2 = log(s2)+1/(n-1))
+  dplyr::mutate(logs2 = log(s2)+1/(n-1))
 
 data <- data %>% 
-  mutate(V_logs2 = 2/(n-1))
+  dplyr::mutate(V_logs2 = 2/(n-1))
 ```
@@
 data_NPA <- data %>% 
-  filter(comparison == "NPA")
+  dplyr::filter(comparison == "NPA")
 
 data_SL <- data %>% 
-  filter(comparison == "Sublingual")
+  dplyr::filter(comparison == "Sublingual")
 
@@
 data_core <- data %>% 
-  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
-  filter(comments != "Intraoperative, off cardiopulmonary bypass" & comments != "Postoperative")
+  dplyr::filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
+  dplyr::filter(comments != "Intraoperative, off cardiopulmonary bypass" & comments != "Postoperative")
 
 data_core_op <- data %>% #eshragi intraop
-    filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
-  filter (clinical_setting=="Intraoperative")
+    dplyr::filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
+  dplyr::filter (clinical_setting=="Intraoperative")
 
 data_core_icu <- data %>% #eshragi postop
-      filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
-  filter(clinical_setting=="ICU" | clinical_setting=="Postoperative")
+      dplyr::filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
+  dplyr::filter(clinical_setting=="ICU" | clinical_setting=="Postoperative")
 
@@
 data_core_lowrisk <- data_core %>% #eshragi overall
-  filter(RoB_selection == "low" & RoB_spoton == "low" & RoB_comparator == "low" & RoB_flow =="low")
+  dplyr::filter(RoB_selection == "low" & RoB_spoton == "low" & RoB_comparator == "low" & RoB_flow =="low")
 
@@
 data_conflict <- data_core %>% 
-  filter(`Funding/equipment/conflict with ZHF company` == "No")
+  dplyr::filter(`Funding/equipment/conflict with ZHF company` == "No")
 
@@
 out <- out %>% 
-  mutate(Participants = sum(group$n_count, na.rm=T)) %>% 
-  mutate(Measurements = format(sum(group$N, na.rm = T), big.mark=",", scientific = FALSE)) %>% 
-  mutate(Studies = length(unique(group$Study))) %>% 
-  select(Studies, m, Participants, Measurements, bias_mean, sd2_est, tau_est, LOA_L, LOA_U, CI_L_rve, CI_U_rve) %>% 
-  rename("Comparisons" = m)
+  dplyr::mutate(Participants = sum(group$n_count, na.rm=T)) %>% 
+  dplyr::mutate(Measurements = format(sum(group$N, na.rm = T), big.mark=",", scientific = FALSE)) %>% 
+  dplyr::mutate(Studies = length(unique(group$Study))) %>% 
+  dplyr::select(Studies, m, Participants, Measurements, bias_mean, sd2_est, tau_est, LOA_L, LOA_U, CI_L_rve, CI_U_rve) %>% 
+  dplyr::rename("Comparisons" = m)
 out
@@
 ```{r fig-2, preview=TRUE, layout="l-screen-inset", fig.align="center", fig.cap="Graphical overview of findings for the primary analysis", echo=FALSE, fig.path="", include=params$distill}
-include_graphics("gofer_core.png")
+knitr::include_graphics("gofer_core.png")
 ```
@@
 ```{r table-1, layout="l-page-outset", include=params$distill}
-library(kableExtra)
   ma <- list(primary, low_risk, ICU, OT,  NPA,SL, conflict)
@@
                "Studies not funded by industry")
-df <- bind_rows(ma, .id="Comparison")
+df <- dplyr::bind_rows(ma, .id="Comparison")
 df %>% 
-  rename(" " = Comparison, "Mean bias" = bias_mean, "Variance" = sd2_est, "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, "Upper bound for 95% limits of agreement" = LOA_U, "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve) %>%
-    gt() %>%
-  tab_header(
+  dplyr::rename(" " = Comparison, "Mean bias" = bias_mean, "Variance" = sd2_est, "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, "Upper bound for 95% limits of agreement" = LOA_U, "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve) %>%
+    gt::gt() %>%
+  gt::tab_header(
     title = "Table 1. Results of meta-analyses"  )  %>%
-  tab_spanner(
+  gt::tab_spanner(
     label = "Population limits of agreement",
-    columns = vars(
+    columns = gt::vars(
       `Outer confidence interval for lower 95% limits of agreement`, `Outer confidence interval for upper 95% limits of agreement`)

### 2019-12-04 app/app.R

@@ -2,8 +2,9 @@ library(shiny)
 library(shinyLP)
 library(shinydashboard)
 library(shinydashboardPlus)
-library(tidyverse)
 library(DT)
+library(magrittr)
+library(dplyr)
 library(robvis)
 library(ggprisma) #awconway/ggprisma
 library(waiter)
@@ -207,8 +208,8 @@ server <- shinyUI(function(input, output) {
     
     
     RoB <- data_core %>%
-      select(Study, RoB_selection, RoB_spoton, RoB_comparator, RoB_flow) %>%
-      mutate(RoB_overall = if_else(RoB_selection == "low" &
+      dplyr::select(Study, RoB_selection, RoB_spoton, RoB_comparator, RoB_flow) %>%
+      dplyr::mutate(RoB_overall = dplyr::if_else(RoB_selection == "low" &
                                      RoB_spoton == "low" &
                                      RoB_comparator == "low" &
                                      RoB_flow == "low", "low", "high"))
@@ -222,8 +223,8 @@ server <- shinyUI(function(input, output) {
     
     
     RoB <- data_core %>%
-      select(Study, RoB_selection, RoB_spoton, RoB_comparator, RoB_flow) %>%
-      mutate(RoB_overall = if_else(RoB_selection == "low" &
+      dplyr::select(Study, RoB_selection, RoB_spoton, RoB_comparator, RoB_flow) %>%
+      dplyr::mutate(RoB_overall = dplyr::if_else(RoB_selection == "low" &
                                      RoB_spoton == "low" &
                                      RoB_comparator == "low" &
                                      RoB_flow == "low", "low", "high"))

### 2019-12-05 manuscript/manuscript.Rmd
word doc formatted to template

@@
 ---
-title: "Accuracy and precision of zero-heat-flux temperature monitoring: A systematic review and meta-analysis"
+title: "Accuracy and precision of zero-heat-flux temperature monitoring"
+subtitle: A systematic review and meta-analysis
+description: "A systematic review and meta-analysis"
+# author:
+# - name: Aaron Conway
+#   affiliation: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
+#   email: aaron.conway@utoronto.ca
+#   url: https://www.aaronconway.info
+# - name: Megan Bittner
+#   affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
+# - name: Dan Phan
+#   affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
+# - name: Navpreet Kamboj
+#   affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
+#   email: navpreet.kamboj@mail.utoronto.ca
+# - name: Kristina Chang
+#   affiliation: Toronto General Hospital, UHN
+# - name: Peter Collins
+#   affiliation: Toronto General Hospital, UHN
+# - name: Elizabeth Tipton
+#   affiliation: Department of Statistics, Northwestern University
+# - name: Matteo Parotto
+#   affiliation: Toronto General Hospital, UHN
+# date: "`r Sys.Date()`"
+# repository_url: https://github.com/awconway/zhf-review
+# twitter:
+#   creator: "@aw_conway"
+bibliography: Extras/bibliography.bib
+csl: Extras/anesthesiology.csl
 author:
-- name: Aaron Conway
-  affiliation: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
+  - Aaron Conway PhD:
       email: aaron.conway@utoronto.ca
-  url: https://www.aaronconway.info
-- name: Megan Bittner
-  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
-- name: Dan Phan
-  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
-- name: Navpreet Kamboj
-  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
-  email: navpreet.kamboj@mail.utoronto.ca
-- name: Kristina Chang
-  affiliation: Toronto General Hospital, UHN
-- name: Peter Collins
-  affiliation: Toronto General Hospital, UHN
-- name: Elizabeth Tipton
-  affiliation: Department of Statistics, Northwestern University
-- name: Matteo Parotto
-  affiliation: Toronto General Hospital, UHN
-# date: "`r Sys.Date()`"
-repository_url: https://github.com/awconway/zhf-review
-twitter:
-  creator: "@aw_conway"
-bibliography: bibliography.bib
-csl: anesthesiology.csl
-output: word_document
-# output: distill::distill_article
+      institute: [PMCC, LBFON, QUT]
+      correspondence: true
+  - Megan Bittner BSc:
+      institute: [LBFON]
+      correspondence: false
+  - Dan Phan BSc:
+      institute: [LBFON]
+      correspondence: false
+  - Kristina Chang MScN:
+      institute: [TGH]
+      correspondence: false
+  - Elizabeth Tipton PhD:
+      institute: [NW]
+      correspondence: false
+  - Matteo Parotto MD:
+      institute: [TGH]
+      correspondence: false
+institute:
+  - PMCC: Peter Munk Cardiac Centre, University Health Network
+  - LBFON: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
+  - QUT: School of Nursing, Queensland University of Technology (QUT)
+  - TGH: Toronto General Hospital, UHN
+  - NW: Department of Statistics, Northwestern University
+output:
+  bookdown::word_document2:
+    reference_docx: Extras/manuscript_template.docx
+    pandoc_args:
+      - --csl=Extras/anesthesiology.csl
+      - --lua-filter=Extras/scholarly-metadata.lua
+      - --lua-filter=Extras/author-info-blocks.lua
+#output: distill::distill_article
 params:
@@
                       echo=FALSE, warning=FALSE, message=FALSE)
+library(dplyr)
+library(ggprisma) # https://github.com/awconway/ggprisma
+library(gt)
+library(knitr)
+library(magrittr)
+source("R/loa_maker.R")
+source("R/meta.R")
 ```
@@
 cat("
-## Author information
-
-<p>Aaron Conway PhD^1,2,3^
-<p>Megan Bittner BSc^2^
-<p>Dan Phan BSc^2^
-<p>Navpreet Kamboj BScN^2^
-<p>Kristina Chang MScN^4^
-<p>Peter Collins MStatistics^4^
-<p>Elizabeth Tipton PhD^5^
-<p>Matteo Parotto MD^4^
-
-<p>^1^ Peter Munk Cardiac Centre, University Health Network
-<p>^2^Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
-<p>^3^School of Nursing, Queensland University of Technology (QUT)
-<p>^4^Toronto General Hospital, UHN
-<p>^5^Department of Statistics, Northwestern University
-
-## Corresponding author
-
-Dr Aaron Conway BN (Hons) PhD
-RBC Chair in Cardiovascular Nursing Research | Peter Munk Cardiac Centre | Toronto General Hospital | University Health Network
-Clinician Investigator | Toronto General Hospital Research Institute | University Health Network
-Assistant Professor | Lawrence S. Bloomberg Faculty of Nursing | University of Toronto
-
-585 University Ave, 4NU - 476
-Toronto, ON  M5G 2N2
-
-e. aaron.conway@utoronto.ca  | t. (416) 946-7112
-
 ## Declarations
@@
 
+##### Page break
+
 ")
 ```
-
-```{r echo=FALSE, include=FALSE}
-library(magrittr)
-source("loa_maker.R")
-source("meta.R")
-```
-
 ```{r load-data, include=FALSE}
@@
 
-Zero-heat-flux thermometers are non-invasive devices that can be used to continuously monitor temperature.
+Zero-heat-flux thermometers provide clinicians with the ability to continuously and non-invasively monitor body temperature.
 These devices are increasingly being used to substitute for invasive core temperature measurement during surgery and in critical care.
@@
 </div>
-
+```{r conditional_page_break, results='asis', include=params$word}
+cat("
+##### Page break
+")
+```
 ## Introduction
@@
 
-Sixteen studies were included (Figure \@ref(fig:fig-1)).
+Sixteen studies were included (Figure 1).
 Two studies reported only in abstract form were not included and assigned as 'studies awaiting classification' because there was insufficient information provided.
 
-```{r fig-1, fig.align="center", fig.cap="PRISMA Flow Diagram", echo=FALSE, fig.width=5.5, fig.path="", include=params$distill}
+```{r fig-1, fig.align="center", fig.cap="PRISMA Flow Diagram", echo=FALSE, fig.width=5.5, fig.path="figures/", include=params$distill, eval=params$distill}
 # https://github.com/awconway/ggprisma
@@
 
-A graphical overview of the findings for the primary analysis is presented in Figure \@ref(fig:fig-2).
+A graphical overview of the findings for the primary analysis is presented in Figure 2.
 The pooled estimate for the mean bias between zero-heat-flux and core temperature measurements was `r primary$bias_mean`°C.
@@
 ```{r fig-2, preview=TRUE, layout="l-screen-inset", fig.align="center", fig.cap="Graphical overview of findings for the primary analysis", echo=FALSE, fig.path="", include=params$distill}
-knitr::include_graphics("gofer_core.png")
+knitr::include_graphics("figures/gofer_core.png")
 ```
@@
 
-<script src="https://hypothes.is/embed.js" async></script>
+```{r  conditional_references, include=params$word, results='asis'}
+cat("##### Page break
 
-```{r  conditional_references, include=params$word, results='asis'}
-cat("# References")
+# References")
 ```
@@
 ```{r  conditional_figure_legend, include=params$word, results='asis'}
-cat("# Figure legend
+cat("##### Page break
+
+# Figure legend
 

### 2019-12-05 manuscript/manuscript.Rmd
kableExtra for table because gt was slow to install on binder

@@
 description: "A systematic review and meta-analysis"
-# author:
-# - name: Aaron Conway
-#   affiliation: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
-#   email: aaron.conway@utoronto.ca
-#   url: https://www.aaronconway.info
-# - name: Megan Bittner
-#   affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
-# - name: Dan Phan
-#   affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
-# - name: Navpreet Kamboj
-#   affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
-#   email: navpreet.kamboj@mail.utoronto.ca
-# - name: Kristina Chang
-#   affiliation: Toronto General Hospital, UHN
-# - name: Peter Collins
-#   affiliation: Toronto General Hospital, UHN
-# - name: Elizabeth Tipton
-#   affiliation: Department of Statistics, Northwestern University
-# - name: Matteo Parotto
-#   affiliation: Toronto General Hospital, UHN
-# date: "`r Sys.Date()`"
-# repository_url: https://github.com/awconway/zhf-review
-# twitter:
-#   creator: "@aw_conway"
+author:
+- name: Aaron Conway
+  affiliation: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
+  email: aaron.conway@utoronto.ca
+  url: https://www.aaronconway.info
+- name: Megan Bittner
+  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
+- name: Dan Phan
+  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
+- name: Navpreet Kamboj
+  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
+  email: navpreet.kamboj@mail.utoronto.ca
+- name: Kristina Chang
+  affiliation: Toronto General Hospital, UHN
+- name: Peter Collins
+  affiliation: Toronto General Hospital, UHN
+- name: Elizabeth Tipton
+  affiliation: Department of Statistics, Northwestern University
+- name: Matteo Parotto
+  affiliation: Toronto General Hospital, UHN
+date: "`r Sys.Date()`"
+repository_url: https://github.com/awconway/zhf-review
+twitter:
+  creator: "@aw_conway"
 bibliography: Extras/bibliography.bib
 csl: Extras/anesthesiology.csl
-author:
-  - Aaron Conway PhD:
-      email: aaron.conway@utoronto.ca
-      institute: [PMCC, LBFON, QUT]
-      correspondence: true
-  - Megan Bittner BSc:
-      institute: [LBFON]
-      correspondence: false
-  - Dan Phan BSc:
-      institute: [LBFON]
-      correspondence: false
-  - Kristina Chang MScN:
-      institute: [TGH]
-      correspondence: false
-  - Elizabeth Tipton PhD:
-      institute: [NW]
-      correspondence: false
-  - Matteo Parotto MD:
-      institute: [TGH]
-      correspondence: false
-institute:
-  - PMCC: Peter Munk Cardiac Centre, University Health Network
-  - LBFON: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
-  - QUT: School of Nursing, Queensland University of Technology (QUT)
-  - TGH: Toronto General Hospital, UHN
-  - NW: Department of Statistics, Northwestern University
-output:
-  bookdown::word_document2:
-    reference_docx: Extras/manuscript_template.docx
-    pandoc_args:
-      - --csl=Extras/anesthesiology.csl
-      - --lua-filter=Extras/scholarly-metadata.lua
-      - --lua-filter=Extras/author-info-blocks.lua
-#output: distill::distill_article
+# author:
+#   - Aaron Conway PhD:
+#       email: aaron.conway@utoronto.ca
+#       institute: [PMCC, LBFON, QUT]
+#       correspondence: true
+#   - Megan Bittner BSc:
+#       institute: [LBFON]
+#       correspondence: false
+#   - Dan Phan BSc:
+#       institute: [LBFON]
+#       correspondence: false
+#   - Kristina Chang MScN:
+#       institute: [TGH]
+#       correspondence: false
+#   - Elizabeth Tipton PhD:
+#       institute: [NW]
+#       correspondence: false
+#   - Matteo Parotto MD:
+#       institute: [TGH]
+#       correspondence: false
+# institute:
+#   - PMCC: Peter Munk Cardiac Centre, University Health Network
+#   - LBFON: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
+#   - QUT: School of Nursing, Queensland University of Technology (QUT)
+#   - TGH: Toronto General Hospital, UHN
+#   - NW: Department of Statistics, Northwestern University
+# output:
+#   bookdown::word_document2:
+#     reference_docx: Extras/manuscript_template.docx
+#     pandoc_args:
+#       - --csl=Extras/anesthesiology.csl
+#       - --lua-filter=Extras/scholarly-metadata.lua
+#       - --lua-filter=Extras/author-info-blocks.lua
+output: distill::distill_article
 params:
-  distill: FALSE
-  word: TRUE
+  distill: TRUE
+  word: FALSE
 ---
@@
 library(ggprisma) # https://github.com/awconway/ggprisma
-library(gt)
+library(kableExtra)
 library(knitr)
@@
   dplyr::rename(" " = Comparison, "Mean bias" = bias_mean, "Variance" = sd2_est, "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, "Upper bound for 95% limits of agreement" = LOA_U, "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve) %>%
-    gt::gt() %>%
-  gt::tab_header(
-    title = "Table 1. Results of meta-analyses"  )  %>%
-  gt::tab_spanner(
-    label = "Population limits of agreement",
-    columns = gt::vars(
-      `Outer confidence interval for lower 95% limits of agreement`, `Outer confidence interval for upper 95% limits of agreement`)
-  )
+  kableExtra::kable() %>% 
+   kableExtra::add_header_above(c(" ","","","","","","","","","", "Population limits of agreement" = 2)) %>% 
+  kableExtra::add_header_above(c("Table 1. Results of meta-analyses" = 12))
 ```

### 2019-12-05 manuscript/manuscript.Rmd
author updated html

@@
 - name: Kristina Chang
-  affiliation: Toronto General Hospital, UHN
-- name: Peter Collins
   affiliation: Toronto General Hospital, UHN

### 2019-12-05 manuscript/manuscript.Rmd
anesthesiology submission

@@
   creator: "@aw_conway"
+output: distill::distill_article
 bibliography: Extras/bibliography.bib
@@
 #   - Kristina Chang MScN:
-#       institute: [TGH]
+#       institute: [PMCC]
 #       correspondence: false
@@
 #       correspondence: false
-#   - Matteo Parotto MD:
-#       institute: [TGH]
+#   - Matteo Parotto MD, PhD:
+#       institute: [TGH, UoT]
 #       correspondence: false
@@
 #   - QUT: School of Nursing, Queensland University of Technology (QUT)
-#   - TGH: Toronto General Hospital, UHN
 #   - NW: Department of Statistics, Northwestern University
+#   - TGH: Department of Anesthesia and Pain Management, Toronto General Hospital, UHN
+#   - UoT: Department of Anesthesia and Interdepartmental Division of Critical Care Medicine, University of Toronto
 # output:
@@
 #       - --lua-filter=Extras/author-info-blocks.lua
-output: distill::distill_article
 params:
@@
   word: FALSE
+always_allow_html: true
 ---
@@
 Funding statement: Support was provided solely from institutional and/or departmental sources.
+MP is supported by an Early Investigator Merit Award from the Department of Anesthesia, University of Toronto and Toronto General Hospital
 
@@
 
-```{r fig-1, fig.align="center", fig.cap="PRISMA Flow Diagram", echo=FALSE, fig.width=5.5, fig.path="figures/", include=params$distill, eval=params$distill}
+```{r fig-1,  fig.cap="PRISMA Flow Diagram", echo=FALSE, fig.width=5.5, fig.path="figures/", include=params$distill, eval=params$distill}
 # https://github.com/awconway/ggprisma
@@
 
-Results from this systematic review have important implications for practice.
-Clinicians should consider the potential that a temperature measurement from a zero-heat-flux thermometer could be as much as 1°C higher or lower than core temperature.
+This systematic review showed that a temperature measurement from a zero-heat-flux thermometer could be as much as 1°C higher or lower than core temperature.
+These results may have important implications for practice that clinicians should consider.
 It was reassuring that results of our sensitivity analysis restricted to studies judged to be at low risk of bias using the QUADAS-2 tool were similar.
-As such, it is vital for clinicians considering using this device to first determine if differences in temperature smaller than this magnitude would be important for the given clinical situation.
+As such, it is vital for healthcare professionals considering using this device to first determine if differences in temperature smaller than this magnitude would be important for the given clinical situation.
 If so, then it may not be appropriate to substitute the zero-heat-flux device in place of a core thermometer.

### 2019-12-06 manuscript/manuscript.Rmd
extra formatting as per anesthesiology

@@
 description: "A systematic review and meta-analysis"
-author:
-- name: Aaron Conway
-  affiliation: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
-  email: aaron.conway@utoronto.ca
-  url: https://www.aaronconway.info
-- name: Megan Bittner
-  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
-- name: Dan Phan
-  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
-- name: Navpreet Kamboj
-  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
-  email: navpreet.kamboj@mail.utoronto.ca
-- name: Kristina Chang
-  affiliation: Toronto General Hospital, UHN
-- name: Elizabeth Tipton
-  affiliation: Department of Statistics, Northwestern University
-- name: Matteo Parotto
-  affiliation: Toronto General Hospital, UHN
-date: "`r Sys.Date()`"
-repository_url: https://github.com/awconway/zhf-review
-twitter:
-  creator: "@aw_conway"
-output: distill::distill_article
+# author:
+# - name: Aaron Conway
+#   affiliation: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
+#   email: aaron.conway@utoronto.ca
+#   url: https://www.aaronconway.info
+# - name: Megan Bittner
+#   affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
+# - name: Dan Phan
+#   affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
+# - name: Navpreet Kamboj
+#   affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
+#   email: navpreet.kamboj@mail.utoronto.ca
+# - name: Kristina Chang
+#   affiliation: Toronto General Hospital, UHN
+# - name: Elizabeth Tipton
+#   affiliation: Department of Statistics, Northwestern University
+# - name: Matteo Parotto
+#   affiliation: Toronto General Hospital, UHN
+# date: "`r Sys.Date()`"
+# repository_url: https://github.com/awconway/zhf-review
+# twitter:
+#   creator: "@aw_conway"
+# output: distill::distill_article
 bibliography: Extras/bibliography.bib
 csl: Extras/anesthesiology.csl
-# author:
-#   - Aaron Conway PhD:
-#       email: aaron.conway@utoronto.ca
-#       institute: [PMCC, LBFON, QUT]
-#       correspondence: true
-#   - Megan Bittner BSc:
-#       institute: [LBFON]
-#       correspondence: false
-#   - Dan Phan BSc:
-#       institute: [LBFON]
-#       correspondence: false
-#   - Kristina Chang MScN:
-#       institute: [PMCC]
-#       correspondence: false
-#   - Elizabeth Tipton PhD:
-#       institute: [NW]
-#       correspondence: false
-#   - Matteo Parotto MD, PhD:
-#       institute: [TGH, UoT]
-#       correspondence: false
-# institute:
-#   - PMCC: Peter Munk Cardiac Centre, University Health Network
-#   - LBFON: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
-#   - QUT: School of Nursing, Queensland University of Technology (QUT)
-#   - NW: Department of Statistics, Northwestern University
-#   - TGH: Department of Anesthesia and Pain Management, Toronto General Hospital, UHN
-#   - UoT: Department of Anesthesia and Interdepartmental Division of Critical Care Medicine, University of Toronto
-# output:
-#   bookdown::word_document2:
-#     reference_docx: Extras/manuscript_template.docx
-#     pandoc_args:
-#       - --csl=Extras/anesthesiology.csl
-#       - --lua-filter=Extras/scholarly-metadata.lua
-#       - --lua-filter=Extras/author-info-blocks.lua
+author:
+  - Aaron Conway PhD:
+      email: aaron.conway@utoronto.ca
+      phone: +1 416 946 7112
+      address: 585 University Ave, 4NU - 476 | Toronto, ON  M5G 2N2
+      institute: [PMCC, LBFON, QUT]
+      correspondence: true
+  - Megan Bittner BSc:
+      institute: [LBFON]
+      correspondence: false
+  - Dan Phan BSc:
+      institute: [LBFON]
+      correspondence: false
+  - Kristina Chang MScN:
+      institute: [PMCC]
+      correspondence: false
+  - Navpreet Kamboj BScN:
+      institute: [LBFON]
+      correspondence: false
+  - Elizabeth Tipton PhD:
+      institute: [NW]
+      correspondence: false
+  - Matteo Parotto MD, PhD:
+      institute: [TGH, UoT]
+      correspondence: false
+institute:
+  - PMCC: Peter Munk Cardiac Centre, University Health Network, Toronto, Canada
+  - LBFON: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto, Toronto, Canada
+  - QUT: School of Nursing, Queensland University of Technology (QUT), Brisbane, Australia
+  - NW: Department of Statistics, Northwestern University, Evanston, IL, United States
+  - TGH: Department of Anesthesia and Pain Management, Toronto General Hospital, UHN, Toronto, Canada
+  - UoT: Department of Anesthesia and Interdepartmental Division of Critical Care Medicine, University of Toronto, Toronto, Canada
+output:
+  bookdown::word_document2:
+    reference_docx: Extras/manuscript_template.docx
+    pandoc_args:
+      - --lua-filter=Extras/scholarly-metadata.lua
+      - --lua-filter=Extras/author-info-blocks.lua
+      - --lua-filter=Extras/pagebreak.lua
+always_allow_html: true
 params:
-  distill: TRUE
-  word: FALSE
-always_allow_html: true
+  distill: FALSE
+  word: TRUE
 ---
@@
 ```
+\pagebreak
 
@@
 
-##### Page break
-
 ")
 ```
+
 ```{r load-data, include=FALSE}
@@
 </div>
-```{r conditional_page_break, results='asis', include=params$word}
-cat("
-##### Page break
-")
-```
+
+\pagebreak
+
 ## Introduction
@@
 
+\pagebreak
+
 ```{r  conditional_references, include=params$word, results='asis'}
-cat("##### Page break
+cat("
 
@@
 
+\pagebreak
 ```{r  conditional_figure_legend, include=params$word, results='asis'}
-cat("##### Page break
+cat("
 

### 2019-12-06 manuscript/figures/fig-two.R
updated fig-two years

@@ -1,0 +1,6 @@
+library(gofer)
+gofer <- gofer::gofer(data = data_core, ma_effect = ma_core$effect_estimate,
+                      ma_lower =  ma_core$lower_limit, ma_upper = ma_core$upper_limit, 
+                      data_age = data_core_age, grade_rating = "Moderate")
+ggplot2::ggsave(gofer, device = "tiff", filename = "fig-two.tiff",
+                height=14, width=20, units = "in")

### 2019-12-06 manuscript/manuscript.Rmd
resubmitted to anesthesiology with format corrections

--- 2019-12-05 manuscript/manuscript.Rmd
@@
 #       email: aaron.conway@utoronto.ca
+#       phone: +1 416 946 7112
+#       address: 585 University Ave, 4NU - 476 | Toronto, ON  M5G 2N2
 #       institute: [PMCC, LBFON, QUT]
@@
 #       correspondence: false
+#   - Navpreet Kamboj BScN:
+#       institute: [LBFON]
+#       correspondence: false
 #   - Elizabeth Tipton PhD:
@@
 # institute:
-#   - PMCC: Peter Munk Cardiac Centre, University Health Network
-#   - LBFON: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
-#   - QUT: School of Nursing, Queensland University of Technology (QUT)
-#   - NW: Department of Statistics, Northwestern University
-#   - TGH: Department of Anesthesia and Pain Management, Toronto General Hospital, UHN
-#   - UoT: Department of Anesthesia and Interdepartmental Division of Critical Care Medicine, University of Toronto
+#   - PMCC: Peter Munk Cardiac Centre, University Health Network, Toronto, Canada
+#   - LBFON: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto, Toronto, Canada
+#   - QUT: School of Nursing, Queensland University of Technology (QUT), Brisbane, Australia
+#   - NW: Department of Statistics, Northwestern University, Evanston, IL, United States
+#   - TGH: Department of Anesthesia and Pain Management, Toronto General Hospital, UHN, Toronto, Canada
+#   - UoT: Department of Anesthesia and Interdepartmental Division of Critical Care Medicine, University of Toronto, Toronto, Canada
 # output:
@@
 #     pandoc_args:
-#       - --csl=Extras/anesthesiology.csl
 #       - --lua-filter=Extras/scholarly-metadata.lua
 #       - --lua-filter=Extras/author-info-blocks.lua
+#       - --lua-filter=Extras/pagebreak.lua
+# always_allow_html: true
 params:
@@
   word: FALSE
-always_allow_html: true
 ---

### 2019-12-06 app/app.R
waiter works better

@@ -306,31 +306,29 @@ server <- shinyUI(function(input, output) {
            
     )
   })
-  waitress <- call_waitress("nav", theme = "overlay-percent") # call the waitress
   
   output$gofer <- renderPlot({
-    waitress$start()
+    
+    waitress <- Waitress$new(dom="#gofer", theme = "overlay-percent") # call the waitress
     
     
-    dat <- vector()
+    waitress$
+      start()$
+      auto(percent = 5, ms = 320) # increase by 5 percent every 150 milliseconds
     
-    for(i in 1:10){
-      waitress$increase(10) # increase by 10%
-      Sys.sleep(.3)
-      dat <- c(dat, sample(1:100, 1))
-    }
     
     plot <- gofer::gofer(gofer_input()[[1]], ma_effect = gofer_input()[[2]]$effect_estimate,
-                                   ma_lower = gofer_input()[[2]]$lower_limit, ma_upper = gofer_input()[[2]]$upper_limit,
-                                   grade_rating=gofer_input()[[4]], data_age = gofer_input()[[3]], 
-                                   dodge_width = 0.85)
-        
+                         ma_lower = gofer_input()[[2]]$lower_limit, ma_upper = gofer_input()[[2]]$upper_limit,
+                         grade_rating=gofer_input()[[4]], data_age = gofer_input()[[3]], 
+                         dodge_width = 0.85)
     
     grid::grid.draw(plot)
     
-    waitress$hide() # hide when done
-     
-                                  }) # renderPlot
+    
+    waitress$hide()
+    
+    
+  }) # renderPlot
   
 output$ggprisma <- renderPlot({
   ggprisma::ggprisma(retrieved = 130, included = 16, duplicates = 35, 

### 2019-12-06 app/app.R
authors updated in app

@@ -183,8 +183,6 @@ ui <- dashboardPage(
   
 <p>Kristina Chang  (Toronto General Hospital, UHN)
   
-<p>Peter Collins  (Toronto General Hospital, UHN)
-
 <p>Elizabeth Tipton (Dapartment of Statistics, Northwestern University)
   
 <p>Matteo Parotto  (Toronto General Hospital, UHN)
@@ -314,7 +312,7 @@ server <- shinyUI(function(input, output) {
     
     waitress$
       start()$
-      auto(percent = 5, ms = 320) # increase by 5 percent every 150 milliseconds
+      auto(percent = 5, ms = 350) # increase by 5 percent every 150 milliseconds
     
     
     plot <- gofer::gofer(gofer_input()[[1]], ma_effect = gofer_input()[[2]]$effect_estimate,

### 2019-12-06 app/app.R
update authors

@@ -183,6 +183,8 @@ ui <- dashboardPage(
   
 <p>Kristina Chang  (Toronto General Hospital, UHN)
   
+<p>Peter Collins  (Toronto General Hospital, UHN)
+
 <p>Elizabeth Tipton (Dapartment of Statistics, Northwestern University)
   
 <p>Matteo Parotto  (Toronto General Hospital, UHN)
@@ -312,7 +314,7 @@ server <- shinyUI(function(input, output) {
     
     waitress$
       start()$
-      auto(percent = 5, ms = 350) # increase by 5 percent every 150 milliseconds
+      auto(percent = 5, ms = 320) # increase by 5 percent every 150 milliseconds
     
     
     plot <- gofer::gofer(gofer_input()[[1]], ma_effect = gofer_input()[[2]]$effect_estimate,

### 2019-12-06 manuscript/manuscript.Rmd
fixed reference for r core team

@@
 This was achieved by using weights proportional to the number of participants, not the total number of measurements.
-The R statistical program was used to conduct all analyses.[@team2017r] All data and R code used in the meta-analyses can be located at this [link](https://github.com/awconway/zhf-review).
+The R statistical program was used to conduct all analyses.[@R2018] All data and R code used in the meta-analyses can be located at this [link](https://github.com/awconway/zhf-review).
 

### 2019-12-09 manuscript/manuscript.Rmd
additional formatting requested anesthesiology

--- 2019-12-06 manuscript/manuscript.Rmd
@@
       phone: +1 416 946 7112
-      address: 585 University Ave, 4NU - 476 | Toronto, ON  M5G 2N2
+      address: 585 University Ave | Toronto, ON  M5G 2N2
       institute: [PMCC, LBFON, QUT]
@@
       - --lua-filter=Extras/author-info-blocks.lua
-      - --lua-filter=Extras/pagebreak.lua
 always_allow_html: true

### 2019-12-09 manuscript/manuscript.Rmd
html default

--- 2019-12-06 manuscript/manuscript.Rmd
@@
 #       phone: +1 416 946 7112
-#       address: 585 University Ave, 4NU - 476 | Toronto, ON  M5G 2N2
+#       address: 585 University Ave | Toronto, ON  M5G 2N2
 #       institute: [PMCC, LBFON, QUT]
@@
 #       - --lua-filter=Extras/author-info-blocks.lua
-#       - --lua-filter=Extras/pagebreak.lua
 # always_allow_html: true

### 2019-12-11 app/app.R
measurement scale for gofer added

@@ -318,7 +318,8 @@ server <- shinyUI(function(input, output) {
     plot <- gofer::gofer(gofer_input()[[1]], ma_effect = gofer_input()[[2]]$effect_estimate,
                          ma_lower = gofer_input()[[2]]$lower_limit, ma_upper = gofer_input()[[2]]$upper_limit,
                          grade_rating=gofer_input()[[4]], data_age = gofer_input()[[3]], 
-                         dodge_width = 0.85)
+                         dodge_width = 0.85,
+                         measurements_logscale =TRUE)
     
     grid::grid.draw(plot)
     

### 2020-01-06 manuscript/manuscript.Rmd
submission to a&a

@@
 ```
+
 \pagebreak
@@
 
-Summary statement: Clinicians should consider the potential that a temperature measurement from a zero-heat-flux thermometer could be as much as 1°C higher or lower than core temperature.
-
 Funding statement: Support was provided solely from institutional and/or departmental sources.
@@
 ```
+
+\pagebreak
 
@@
 Use of this device may not be appropriate in situations where a difference in temperature of less than 1°C is important to detect.
+
+### Key points
+
+**Question:** How accurate are temperature measurements from zero-heat-flux temperature monitors?
+
+**Findings:** Population limits of agreement, which take into consideration the between-study heterogeneity and sampling error, were wide, spanning from `r primary$CI_L_rve`°C to `r primary$CI_U_rve`°C.
+
+**Meaning:** Zero-heat-flux temperature monitoring would not be appropriate if a difference in temperature of 1°C is important to detect for the given clinical situation.
 

### 2020-03-18 flexdashboard/index.Rmd
flex

---
title: ""
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---
```{r setup}
library(shiny)
library(shinyLP)
library(shinydashboard)
library(shinydashboardPlus)
library(DT)
library(magrittr)
library(dplyr)
library(robvis)
library(ggprisma) #awconway/ggprisma
library(waiter)
library(gofer)#awconway/gofer
library(forcats)
```

Home 
=======================================================================

###

```{r}
div(class = "jumbotron", style="background:transparent !important", 
                           h1("Accuracy of zero-heat-flux temperature monitoring"), p("A systematic review and meta-analysis"),
                           p(a(class = "btn btn-primary btn-lg button", id='tabBut', "Click here to access the full review")))

```

```{r}
HTML('<div class="row">
  <div class="col-sm-12">
    <div class="col-sm-12">
      <div class="box box-solid bg-black-gradient collapsed-box">
        <div class="box-header">
          <i class="fa fa-info"></i>
          <h3 class="box-title">Information</h3>
          <div class="pull-right box-tools">
            <button class="btn bg-black btn-sm" data-widget="collapse" type="button">
              <i class="fa fa-plus"></i>
            </button>
          </div>
        </div>
        <div class="box-body border-radius-none" id="pLoA" collapsed="TRUE" solidHeader="TRUE">
          <div style="width:100%; height:auto;" class="datatables html-widget html-widget-output">          
          </div>
        </div>
        <div class="box-footer text-black">
                  <p>This webpage contains supplementary information for the systematic review. In the results and data pages, users can select a subset of studies to view. We also provide source documents for the data that were extracted from the study.</p>
        </div>
      </div>
    </div>
  </div>
</div>
')
```

```{r}
HTML('<div class="row">
  <div class="col-sm-12">
    <div class="col-sm-12">
      <div class="box box-solid bg-black-gradient collapsed-box">
        <div class="box-header">
          <i class="fa fa-users"></i>
          <h3 class="box-title">Authors</h3>
          <div class="pull-right box-tools">
            <button class="btn bg-black btn-sm" data-widget="collapse" type="button">
              <i class="fa fa-plus"></i>
            </button>
          </div>
        </div>
        <div class="box-body border-radius-none" id="pLoA" collapsed="TRUE" solidHeader="TRUE">
          <div style="width:100%; height:auto;" class="datatables html-widget html-widget-output">          
          </div>
        </div>
        <div class="box-footer text-black">

 <p><a href="https://www.aaronconway.info"> Aaron Conway </a> (Peter Munk Cardiac Centre, UHN &amp; Lawrence S. Bloomberg Faculty of Nursing, University of Toronto)</p>

<p>Megan Bittner  (Lawrence S. Bloomberg Faculty of Nursing, University of Toronto)

<p>Dan Phan  (Lawrence S. Bloomberg Faculty of Nursing, University of Toronto)

<p>Navpreet Kamboj  (Lawrence S. Bloomberg Faculty of Nursing, University of Toronto)

<p>Kristina Chang  (Toronto General Hospital, UHN)

<p>Elizabeth Tipton (Dapartment of Statistics, Northwestern University)

<p>Matteo Parotto  (Toronto General Hospital, UHN)

        </div>
      </div>
    </div>
  </div>
</div>
')
```

Search Strategy
=======================================================================

###

```{r}
fluidRow(
                boxPlus(
                  title = "Medline Search Strategy",
                  closable = FALSE,
                  status = "black",
                  solidHeader = FALSE,
                  collapsible = TRUE,
                  p("1.	zero-heat flux"),
                  p("2.	zero-flux"),
                  p("3.	1 OR 2"),
                  p("4.	(SpotON) OR (Temple Touch Pro)"),
                  p("5.	3 OR 4"),
                  p("6.	Accuracy OR precision OR reliability OR validity OR validation OR standard deviation"),
                  p("7.	Bias OR mean difference OR limit of agreement OR Bland Altman"),
                  p("8.	6 OR 7"),
                  p("9.	(exp “diagnostic errors” / OR exp “sensitivity and specificity” / OR (accura* OR reliability* OR target* OR utilt* OR discriminat* OR differentiat*)
10.	8 OR 9"),
                  p("11.	5 AND 10")
                ),
                boxPlus(
                  title = "Embase Search Strategy",
                  closable = FALSE,
                  status = "black",
                  solidHeader = FALSE,
                  collapsible = TRUE,
                  p("1.	zero-heat flux"),
                  p("2.	zero-flux"),
                  p("3.	1 OR 2"),
                  p("4.	(SpotON) OR (Temple Touch Pro)"),
                  p("5.	3 OR 4"),
                  p("6.	Accuracy OR precision OR reliability OR validity OR validation OR standard deviation"),
                  p("7.	Bias OR mean difference OR limit of agreement OR Bland Altman"),
                  p("8.	6 OR 7"),
                  p("9.	('diagnostic accuracy'/de OR 'diagnostic test accuracy study'/de OR 'diagnostic error'/exp OR 'diagnostic value'/de OR 'sensitivity and specificity'/de OR 'predictive value'/de OR (accura* OR reliabilit* OR target* OR utilit* OR discriminat* OR differentiat*)"),
                  p("11.	5 AND 10")
                )
)
```

Study selection
==========================

```{r}
  ggprisma::ggprisma(retrieved = 130, included = 16, duplicates = 35, 
                     full_text = 22, wrong_intervention = 4, wrong_comparator = 2,
                     wrong_design = 1, awaiting_classification = 2)
```

Risk of bias
==========================

### Across studies

```{r}
    RoB <- data_core %>%
      dplyr::select(Study, RoB_selection, RoB_spoton, RoB_comparator, RoB_flow) %>%
      dplyr::mutate(RoB_overall = dplyr::if_else(RoB_selection == "low" &
                                     RoB_spoton == "low" &
                                     RoB_comparator == "low" &
                                     RoB_flow == "low", "low", "high"))

    RoB[RoB == "unclear"] <- "some concerns"

    rob_summary(data = RoB, tool = "QUADAS-2", weighted = FALSE)
```

### Within studies

```{r}
RoB <- data_core %>%
      dplyr::select(Study, RoB_selection, RoB_spoton, RoB_comparator, RoB_flow) %>%
      dplyr::mutate(RoB_overall = dplyr::if_else(RoB_selection == "low" &
                                     RoB_spoton == "low" &
                                     RoB_comparator == "low" &
                                     RoB_flow == "low", "low", "high"))

    RoB[RoB == "unclear"] <- "some concerns"

    rob_traffic_light(data = RoB, tool = "QUADAS-2")
```

Graphical overview of findings
==================

Column {.tabset}

### Core

```{r}
gofer::gofer(data_core, ma_effect = ma_core$effect_estimate,
                         ma_lower = ma_core$lower_limit, ma_upper = ma_core$upper_limit,
                         grade_rating="Moderate", data_age = data_core_age, 
                         dodge_width = 0.85,
                         measurements_logscale =TRUE)

```

Source data
=================

```{r}
shinyLP::iframe(url_link = "https://docs.google.com/spreadsheets/d/e/2PACX-1vSR9-h4cb4ONj7d5Yw9ksyEysVngocRSrMQ6vVjny-6f-d_0CZlhe3HhNG-zaQSJ6rWpBLCb5mVYcYK/pubhtml?widget=true&amp;headers=false", 
                    height="100%", width="100%")
```

### 2020-03-18 manuscript/manuscript.Rmd
table 1 updated

--- 2019-12-09 manuscript/manuscript.Rmd
@@
 subtitle: A systematic review and meta-analysis
-description: "A systematic review and meta-analysis"
+# description: "A systematic review and meta-analysis"
 # author:
@@
 bibliography: Extras/bibliography.bib
-csl: Extras/anesthesiology.csl
+csl: Extras/anesthesia-and-analgesia.csl
 author:
@@
 
+Author contributions: 
+AC: Study design, analysis, wrote manuscript; MB: Study design, data extraction, risk of bias assessment, data analysis, contributed to writing manuscript; DP: Study design, data extraction, risk of bias assessment, revised the manuscript for important intellectual content; NK: Study design, revised the manuscript for important intellectual content; KC: Study design, revised the manuscript for important intellectual content; ET: Study design, data analysis, revised the manuscript for important intellectual content; MP: Study design, revised the manuscript for important intellectual content.
+
+**Glossary of terms:**
+
+GRADE = Grading of Recommendations, Assessment, Development and Evaluations
+
+QUADAS-2 = Revised Quality Assessment of Diagnostic Accuracy Studies tool
+
+LoA = Limits of Agreement
+
+CI = Confidence intervals
+
+SD^2^ = Variance
+
+&tau;^2^ = Tau-squared
+
 ")
 ```
+
+\pagebreak
 
@@
 ```{r meta-analysis-prep, include=FALSE}
+
 data <- data %>%
@@
   dplyr::filter(comments != "Intraoperative, off cardiopulmonary bypass" & comments != "Postoperative")
+
+data_PA <- data_core %>% 
+   dplyr::filter(comparison=="PA")
 
@@
 Medline and EMBASE were searched for studies that reported on a measurement of core or peripheral temperature that coincided with a measurement from the zero-heat-flux device.
-Study selection and quality assessment (using QUADAS-2) was performed independently.
-The GRADE approach was used to summarize the strength of the evidence.
+Study selection and quality assessment was performed independently using the Revised Quality Assessment of Diagnostic Accuracy Studies tool (QUADAS-2).
+The Grading of Recommendations, Assessment, Development and Evaluations (GRADE) approach was used to summarize the strength of the evidence.
 Pooled estimates of the mean bias and limits of agreement with outer 95% confidence intervals (population limits of agreement) were calculated.
@@
 
+\pagebreak
+
 ## Methods
@@
 
-Published studies were found by searching Medline and EMBASE to July 2019.
-The Cochrane-recommended search strategy combining terms for the ‘target condition’ and ‘index test’ was used.[@mann2012should] This search strategy is an efficient approach for systematic reviews of diagnostic test accuracy studies.[@preston2015improving] We also conducted forward citation searching, by using Google Scholar to search the citations of the first article published on the accuracy of zero-heat-flux thermometers.
-The search strategies used for each data base can be located at this [link](https://aconway.dev/zhf).
-Selection of studies was undertaken independently by two reviewers using [Covidence](https://www.covidence.org).
+Published studies were found by searching Medline and EMBASE to January 2020.
+The Cochrane-recommended search strategy combining terms for the ‘target condition’ and ‘index test’ was used.[@mann2012should] This search strategy is an efficient approach for systematic reviews of diagnostic test accuracy studies.[@preston2015improving] We also conducted forward citation searching, by using Google Scholar to search the citations of the first article published on the accuracy of zero-heat-flux thermometers.[@eshraghi2014] The search strategies used for each database are available on a [webpage](https://aconway.dev/zhf) containing supplementary information for the systematic review.
+Selection of studies was undertaken independently by two reviewers.
 
@@
 This was achieved by using weights proportional to the number of participants, not the total number of measurements.
-The R statistical program was used to conduct all analyses.[@R2018] All data and R code used in the meta-analyses can be located at this [link](https://github.com/awconway/zhf-review).
+The R statistical program was used to conduct all analyses.[@R2018] All data and R code used in the meta-analyses is available [here](https://github.com/awconway/zhf-review).
 
@@
 
+\pagebreak
+
 ## Results
@@
 # https://github.com/awconway/ggprisma
-ggprisma::ggprisma(retrieved = 130, included = 16, duplicates = 35, full_text = 22, wrong_intervention = 4, wrong_comparator = 2, wrong_design = 1, awaiting_classification = 2)
+ggprisma::ggprisma(retrieved = 131, included = 18, duplicates = 35, full_text = 23, wrong_intervention = 3, wrong_comparator = 2, wrong_design = 1, awaiting_classification = 2)
 ```
 
-The characteristics of included studies can be viewed at this [link](https://aconway.dev/zhf).
+Detailed characteristics of included studies can be viewed on the [webpage](https://aconway.dev/zhf/) containing supplementary information for the systematic review.
 The primary comparison of zero-heat-flux versus core temperature measurements (eg, arterial, bladder, esophageal or rectal) consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies.
@@
 
-All studies included in this systematic review evaluated the zero-heat-flux temperature monitoring system manufactured by 3M.
+Most studies included in this systematic review evaluated the zero-heat-flux temperature monitoring system manufactured by 3M.
 Previously known as the SpotOn Temperature Monitoring System, the 3M zero-heat-flux device is now referred to commercially as the Bair Hugger Temperature Monitoring System.
-All comparisons reported adherence to the zero-heat-flux device manufacturer instructions and placed the sensor on the forehead of the participants.
+One study evaluated the Tcore^TM^ device.[@sastre2019evaluation] The oldest study included in this review, published in 2000, was an evaluation of the Coretemp device from Terumo.[@Harioka_2000] All comparisons reported adherence to the zero-heat-flux device manufacturer instructions and placed the sensor on the forehead of the participants.
 One included study also reported results for comparisons where the zero-heat-flux thermometer was not placed on the forehead.
@@
 
-A graphical overview of the findings for the primary analysis is presented in Figure 2.
+Table 1 presents results of the primary, sensitivity and all subgroup analyses for the primary comparison as well as secondary comparisons.
 The pooled estimate for the mean bias between zero-heat-flux and core temperature measurements was `r primary$bias_mean`°C.
@@
 A further sensitivity analysis excluding studies that received industry funding revealed population limits of agreement that were considerably wider than the primary analysis (`r conflict$CI_L_rve`°C to `r conflict$CI_U_rve`°C).
-The GRADE rating for this sensitivity was downgraded to low quality though, due to concerns about study limitations, inconsistency and imprecision.
+The evidence rating for this sensitivity analysis was downgraded to low quality though, due to concerns about study limitations, inconsistency and imprecision.
 
-```{r fig-2, preview=TRUE, layout="l-screen-inset", fig.align="center", fig.cap="Graphical overview of findings for the primary analysis", echo=FALSE, fig.path="", include=params$distill}
-knitr::include_graphics("figures/gofer_core.png")
-```
-
-Table 1 presents results of the primary, sensitivity and all subgroup analyses for the primary comparison as well as secondary comparisons.
 We conducted two subgroup analyses for the primary comparison according to the clinical setting in which the study was conducted.
@@
 Zero-heat-flux thermometers were compared with sublingual thermometers and nasopharyngeal thermometers in the studies included in this review.
-The mean bias between zero-heat-flux and sublingual temperature measurements in meta-analysis of results from `r SL$Studies` studies was `r SL$bias_mean`°C.
-Due to the limited number of studies and measurements, population limits of agreement were extremely wide, spanning from `r SL$CI_L_rve`°C to `r SL$CI_U_rve`°C.
-The quality of evidence for this comparison was rated as very low quality due to serious concerns about imprecision.
-
 The mean bias between zero-heat-flux and nasopharyngeal temperature measurements in meta-analysis of results from `r NPA$Studies` studies was `r NPA$bias_mean`°C.
@@
 We downgraded the quality of evidence to low, again due to concerns about imprecision and study limitations.
+The mean bias between zero-heat-flux and sublingual temperature measurements in meta-analysis of results from `r SL$Studies` studies was `r SL$bias_mean`°C.
+Due to the limited number of studies and measurements, population limits of agreement were extremely wide, spanning outside physiologically plausible range for temperature.
+As such, they are not reported.
+The quality of evidence for this comparison was rated as very low quality due to serious concerns about imprecision.
+
+\pagebreak
 
@@
 It should be noted that we did not include studies that used the Temple Touch Pro because it is not strictly a zero-heat-flux device.
-This is a new thermometer that is similar to the zero-heat-flux device in that it is placed cutaneously, but the underlying technology is different.
-Far fewer studies have  evaluated the Temple Touch Pro compared to the zero-heat-flux device.[@evron2017evaluation; @sastre2019evaluation]
+This is a new thermometer that is similar to the zero-heat-flux device in that it is placed cutaneously, but the underlying technology is different.[@evron2017evaluation]
 
@@
 
-Figure 2: Graphical overview of findings for the primary analysis")
+")
 ```

### 2020-03-20 manuscript/manuscript.Rmd
submission to jcmc

@@
 bibliography: Extras/bibliography.bib
-csl: Extras/anesthesia-and-analgesia.csl
+csl: Extras/sp-basic.csl
 author:
@@
 source("R/meta.R")
-```
-
-\pagebreak
-
-```{r conditional_title_page, results='asis', include=params$word}
-cat("
-## Declarations
-
-Clinical trial number: Not applicable
-
-Prior presentations: Not applicable
-
-Abstract word count: 300 words
-
-Total word count: 3075 words
-
-Introduction word count: 303 words
-
-Discussion word count: 781 words
-
-Number of figures: 2
-
-Number of tables: 1
-
-Abbreviated title: Accuracy of zero-heat-flux thermometers
-
-Funding statement: Support was provided solely from institutional and/or departmental sources.
-MP is supported by an Early Investigator Merit Award from the Department of Anesthesia, University of Toronto and Toronto General Hospital
-
-Conflicts of interest: The authors declare no competing interests.
-
-Author contributions: 
-AC: Study design, analysis, wrote manuscript; MB: Study design, data extraction, risk of bias assessment, data analysis, contributed to writing manuscript; DP: Study design, data extraction, risk of bias assessment, revised the manuscript for important intellectual content; NK: Study design, revised the manuscript for important intellectual content; KC: Study design, revised the manuscript for important intellectual content; ET: Study design, data analysis, revised the manuscript for important intellectual content; MP: Study design, revised the manuscript for important intellectual content.
-
-**Glossary of terms:**
-
-GRADE = Grading of Recommendations, Assessment, Development and Evaluations
-
-QUADAS-2 = Revised Quality Assessment of Diagnostic Accuracy Studies tool
-
-LoA = Limits of Agreement
-
-CI = Confidence intervals
-
-SD^2^ = Variance
-
-&tau;^2^ = Tau-squared
-
-")
 ```
@@
 
-**Background**
+**Purpose**
 
@@
 
-Sixteen studies were included.
+Eighteen studies were included.
 The primary meta-analysis of zero-heat-flux versus core temperature consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies.
@@
 
-### Key points
+Clinical trial number: Not applicable
 
-**Question:** How accurate are temperature measurements from zero-heat-flux temperature monitors?
-
-**Findings:** Population limits of agreement, which take into consideration the between-study heterogeneity and sampling error, were wide, spanning from `r primary$CI_L_rve`°C to `r primary$CI_U_rve`°C.
-
-**Meaning:** Zero-heat-flux temperature monitoring would not be appropriate if a difference in temperature of 1°C is important to detect for the given clinical situation.
+Keywords: temperature, measurement, zero-heat-flux, surgery, anesthesia
 
@@
 </div>
+
+\pagebreak
+
+```{r conditional_title_page, results='asis', include=params$word}
+cat("
+## Declarations
+
+Availability of data and material (data transparency): All data used in the meta-analyses is available [here](https://aconway.dev/zhf).
+
+Code availability: All data used in the meta-analyses is available [here](https://github.com/awconway/zhf-review).
+
+Abbreviated title: Accuracy of zero-heat-flux thermometers
+
+Funding statement: Support was provided solely from institutional and/or departmental sources.
+MP is supported by an Early Investigator Merit Award from the Department of Anesthesia, University of Toronto and Toronto General Hospital
+
+Conflicts of interest: The authors declare no competing interests.
+
+Author contributions: 
+AC: Study design, analysis, wrote manuscript; MB: Study design, data extraction, risk of bias assessment, data analysis, contributed to writing manuscript; DP: Study design, data extraction, risk of bias assessment, revised the manuscript for important intellectual content; NK: Study design, revised the manuscript for important intellectual content; KC: Study design, revised the manuscript for important intellectual content; ET: Study design, data analysis, revised the manuscript for important intellectual content; MP: Study design, revised the manuscript for important intellectual content.
+
+**Glossary of terms:**
+
+GRADE = Grading of Recommendations, Assessment, Development and Evaluations
+
+QUADAS-2 = Revised Quality Assessment of Diagnostic Accuracy Studies tool
+
+LoA = Limits of Agreement
+
+CI = Confidence intervals
+
+SD^2^ = Variance
+
+&tau;^2^ = Tau-squared
+
+")
+```
 
@@
 
-Sixteen studies were included (Figure 1).
-Two studies reported only in abstract form were not included and assigned as 'studies awaiting classification' because there was insufficient information provided.
+Eighteen studies were included (Figure 1).
+Two studies reported only in abstract form were not included and assigned as 'studies awaiting classification' because there was insufficient information provided.[@cullen2015measuring; @VendrellJorda2016]
 
@@
 
-Most studies included in this systematic review evaluated the zero-heat-flux temperature monitoring system manufactured by 3M.
-Previously known as the SpotOn Temperature Monitoring System, the 3M zero-heat-flux device is now referred to commercially as the Bair Hugger Temperature Monitoring System.
-One study evaluated the Tcore^TM^ device.[@sastre2019evaluation] The oldest study included in this review, published in 2000, was an evaluation of the Coretemp device from Terumo.[@Harioka_2000] All comparisons reported adherence to the zero-heat-flux device manufacturer instructions and placed the sensor on the forehead of the participants.
+Most studies included in this systematic review evaluated the zero-heat-flux temperature monitoring system manufactured by 3M.[@Boisson_2018; @Carvalho_2019; @Dahyot_Fizelier_2017; @eshraghi2014; @G_mez_Romero_2019; @idei2016; @Iden_2015; @Jack_2019; @Kato_2015; @kollmann2019validation; @M_kinen_2016; @Morettini_2019; @Pesonen_2018; @Schell_Chaple_2018; @Tachibana_2019; @West_2019] Previously known as the SpotOn Temperature Monitoring System, the 3M zero-heat-flux device is now referred to commercially as the Bair Hugger Temperature Monitoring System.
+Two studies evaluated the Tcore^TM^ device.[@sastre2019evaluation; @G_mez_Romero_2019] The oldest study included in this review, published in 2000, was an evaluation of the Coretemp device from Terumo.[@Harioka_2000] All comparisons reported adherence to the zero-heat-flux device manufacturer instructions and placed the sensor on the forehead of the participants.
 One included study also reported results for comparisons where the zero-heat-flux thermometer was not placed on the forehead.
@@
 The pooled estimate for the mean bias between zero-heat-flux and core temperature measurements was `r primary$bias_mean`°C.
-The population limits of agreement, which take into consideration the between-study heterogeneity and sampling error, were wide, spanning from `r primary$CI_L_rve`°C to `r primary$CI_U_rve`°C (`r primary$Measurements` measurements; `r primary$Participants` participants; `r primary$Studies` studies).
+Population limits of agreement, which take into consideration the between-study heterogeneity and sampling error, were wide, spanning from `r primary$CI_L_rve`°C to `r primary$CI_U_rve`°C (`r primary$Measurements` measurements; `r primary$Participants` participants; `r primary$Studies` studies).
+The amount of between-study heterogeneity is displayed graphically in the density plot in Figure 2.
 The quality of evidence for the primary comparison was downgraded to low quality due to concerns about study limitations and inconsistency.
@@
 
+Figure 2: Comparisons between core and zero-heat-flux thermometers within and across studies.
+Blue curves are distributions of the differences between measurements from zero-heat-flux (ZHF) sensors and core temperature measurements in individual studies.
+The red curve is the distribution of the pooled estimate.
+
 ")

### 2020-03-20 manuscript/figures/fig-one.R

@@ -1,6 +1,5 @@
-fig <- ggprisma::ggprisma(retrieved = 130, included = 16, duplicates = 35, 
-                   full_text = 22, wrong_intervention = 4, 
-                   wrong_comparator = 2, wrong_design = 1, 
-                   awaiting_classification = 2)
+fig <- ggprisma::ggprisma(retrieved = 131, included = 18, duplicates = 35, full_text = 23, wrong_intervention = 3, wrong_comparator = 2, wrong_design = 1, awaiting_classification = 2)
 
-ggsave("fig-one.pdf", device = "pdf")
+ggsave(plot = fig, device = "pdf", filename = "manuscript/figures/fig-one.pdf")
+
+ggsave(plot = fig, device = "tiff", filename = "manuscript/figures/fig-one.tiff", width=7.5, height=7, units='in', dpi=600, compression = 'lzw')

### 2020-03-20 manuscript/figures/table-1.R

@@ -14,3 +14,11 @@ gt <- df %>%
   )
 
 gtsave(data = gt, filename = "table_gt.pdf", vwidth = 600)
+
+library(flextable)
+df %>% %>% 
+  rename(" " = Comparison, "Mean bias" = bias_mean, "Variance" = sd2_est, 
+         "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, 
+         "Upper bound for 95% limits of agreement" = LOA_U, 
+         "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, 
+         "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve) %>% flextable()

### 2020-05-06 manuscript/R1/response/response.Rmd
started R1 for jcmc

---
toname: Journal of Clinical Monitoring and Computing
toaddress: Editorial Board
opening: To the editor, 
closing: Regards,
spacing: 1
output: ConwayLetterTemplate::letter
---

Thank you for allowing us to revise our manuscript for further consideration for publication. Please find our responses to the comments from the reviewers below.

# Additional changes

- Title changed to: "Accuracy and precision of zero-heat-flux temperature measurements with the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System: A systematic review and meta-analysis"

# Reviewer 1

## General comments

*Without the previous Figure 2, which has been removed likely because it was a 100MB large image instead of a Table, there is no overview table of the included studies present in this paper and the reader has to visit the authors website to obtain this critical piece of information. I don't find this acceptable for a systematic review, as critical pieces are not contained in the publication and the preservation of the website can't be guaranteed.*

Response:

>We have created a table to describe the study characterstics to be included in the main manuscript (Table 2).

*The website seems to be out of sync with the paper, as references [6, 23-37], [26,38], and [39] are indeed 18 studies, but the figure at "Graphical overview of the findings", which shows 16 studies does not agree with the list of references - West 2019 [37] and Iden 2015 [28] are both missing from the plot. Subsequently I question the total numbers of patients and samples in the remainder of the text.*

Response:

>The 'Graphical overview of findings' figures in the website present the results of each meta-analysis that was undertaken. The primary meta-analysis contains 16 studies because Iden and West were not included in this particular meta-analysis, as they did not report results of a comparison between ZHF and core temperature. They used nasopharyngeal or sublingual. With the new Table 2 to be included in the main manuscript, we have included the study characteristics for these two studies though.

## Specific comments

*Abstract, P2, L16: I am not sure if "invasive" is the best word for a nasopharangeal or oropharangeal temperature probe compared to let's say a pulmonary artery blood temperature? Maybe "more invasive"?*

Response:

>Changed to 'more' invasive.

*Introduction, P6, L36: I believe the system is now referred to as the "3M Bair Hugger Temperature Monitoring System", although still widely referred to as SpotOn?*

Response:

>We have made this distinction more clear in the introduction. It now reads:

>"Originally developed in the 1970s, zero-heat-flux technology was recently implemented in the 3M Bair Hugger Temperature Monitoring System (3M, St Paul, MN), as a single-use, disposable sensor. This device was previously known as the SpotOn Temperature Monitoring System. Another device on the market is the T-core sensor from Dräger."

*Methods, P9, L9: While the shiny-based website is really neat, it might be advisable to have the search strategy included as an Appendix to the manuscript to ensure it will remain available in the figure?*

Response:

>Included the search strategy as an appendix for the main manuscript.

*Methods, P11, L40: Could you at least get a DOI to archive the code/files to provide a stable place to refer to when this Github repository becomes unavailable?*

Response:

>The github repo containing data and code has been added to Zenodo to attain a DOI.

*Methods P11, L53 and P12, L7: These are kind of mixing results and methods; which might be okay here, but you might want to provide the references for these studies?*

Response:

>We have now included the refernces.

*Methods, P12, L54: Did you consider to do subgroup analyses by measurement site? (Or by population age - pediatric vs. adult)*

>We did undertake.......

*Results, P13, L20: Please cite all studies used here. Also I am not convinced that a website link to contain one of the key elements for any systematic review: the overview table, is acceptable instead of converting the figure into a table and including it in the paper.*

Response:

>We have created a table to describe the study characterstics to be included in the main manuscript (Table 2). Citations were added to the text.

*Results, P13, L27: These values don't agree with the website. Figure: Participants 827 vs. text: participants 756; also you missed the West 2019 paper here, so this needs updating.*

Response:

>The numbers of participants reported in the manuscript is correct. The study by Boisson et al. (2018) split the analyses in their study into times during surgery where there were 'rapid' core temperature changes and 'slow' core temperature changes. As such, the total number of participants reported in the website (n=827) counted the number of participants in the Boisson et al. (2018) study twice. We added that explanation to the website under the figure.

*Results, P13, L28: Which 16 studies/8 studies etc?*

Response:

>All studies included in the review have been cited at least once in this introductory paragraph for the results. We believe there is little value in citing each of the studies included in each of the meta-analyses, as this information is better presented in the new Table 2 and in the graphical overview of findings figures in the website.

*Results, P13, L57: The number of subjects can't be the number of measurements, something went wrong here when updating the paper. (You report n=756 in the abstract.)*

Response:

>Thank you for noticing this mistake. The number of participants in this meta-analysis for the nasopharyngeal subgroup was corrected.

*Results, P14, L15: I point this out in my comment in the introduction, why do you clarify it in the results?*

Response:

>Thank you for the suggestion. We moved the explanation to the introduction.

*Results, P14, L35: Can you at least refer to the supplemental material here, if you are not planning to include the bias assessment in the paper?*

Response:

>We have added one of the risk of bias figures to the manuscript (Figure 2) to show risk of bias judgements for each of the included studies.

*Results, P16, L48: So why are you telling us about it if you then don't report it?*

Response:

>

*Discussion, P19, L14: One would assume that the PICU study (Idei) is also in children, not only Carvalho?*

Response:

>Thank you for noticing this mistake - text has been corrected to 'two studies'.

*Discussion, P19, L43: But isn't clinical utility important? Do you want to elaborate here?*

Response:

>

*References: #5 seems incomplete; #7 seems incomplete; #11 is very incomplete, #21 is incomplete; #27 is incomplete*

Response:

>

*Figure 1: Isn't "2 studies awaiting classification" a bit unusual? - You excluded them as they are available only in abstract form, right?*

Response:

>The studies awaiting classification approach is used by Cochrane. In future updates to the review these studies reported in abstract form may be published and full and we could then include them.

# Reviewer 2

*This is a timely and really worthwhile meta-analysis. My main concern is that the level of evidence - moderate at best - is insufficient to draw any definitive conclusions about the utility of the method. It is also worth noting that this method is an 'indirect measurement' as opposed to peripheral thermometers which give an 'indirect estimate' i.e. the temperature they display is not the temperature they read (see the latest NICE CG65 for more detail)*

Response:

>

*I would like to see a figure for the proportion of readings within the acceptable range.*

Response:

>Although some (not all) studies may have reported this outcome, we believe the statistical approach we used to combine results from individual studies is a more robust method to estimate the accuracy of this temperature monitoring device. This is because as it is able to account for potentially unadjusted repeated measures estimates as well as incorporate the degree of inconsistency between results and sampling error into the estimates of the population limits of agreement. In addition, the '% within acceptable limits' outcome is not a very useful outcome for application to practice, as one can never know which measurement was within or not within the limits. With the population limits of agreement approach, we can interpret that each measurement taken from one of these devices may be as much as 1 degree higher or lower than 'core' temperature.

*Most of all, I think the best (and only really acceptable) conclusion from this paper would be to define the exact characteristics of a trial which would determine the accuracy of ZF thermometers with a high level of evidence.  I also think that such a trial would need to be carried out for every device separately because there are small but important differences in the construction of each of them.*

Response:

>

*The introduction should be reviewed and made to read more clearly.  Repetition of the word "commonly' in consecutive sentences for example..*

Response:

>We have removed the repetition of the 'commonly' term.

*The description of the mechanism of action of the ZFT does not clearly explain it to someone who doesn't already understand it.*

Response:

>

*13/57 I'm sure there were 109k measurement but there weren't that number of participants*

Response:

>Thank you for noticing this mistake. We have corrected it to the number of participats.

### 2020-05-06 manuscript/manuscript.Rmd
started R1 for jcmc

@@
 ---
-title: "Accuracy and precision of zero-heat-flux temperature monitoring"
+title: "Accuracy and precision of zero-heat-flux temperature measurements with the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System"
 subtitle: A systematic review and meta-analysis
-# description: "A systematic review and meta-analysis"
-# author:
-# - name: Aaron Conway
-#   affiliation: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
-#   email: aaron.conway@utoronto.ca
-#   url: https://www.aaronconway.info
-# - name: Megan Bittner
-#   affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
-# - name: Dan Phan
-#   affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
-# - name: Navpreet Kamboj
-#   affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
-#   email: navpreet.kamboj@mail.utoronto.ca
-# - name: Kristina Chang
-#   affiliation: Toronto General Hospital, UHN
-# - name: Elizabeth Tipton
-#   affiliation: Department of Statistics, Northwestern University
-# - name: Matteo Parotto
-#   affiliation: Toronto General Hospital, UHN
-# date: "`r Sys.Date()`"
-# repository_url: https://github.com/awconway/zhf-review
-# twitter:
-#   creator: "@aw_conway"
-# output: distill::distill_article
 bibliography: Extras/bibliography.bib
@@
 output:
-  bookdown::word_document2:
+  officedown::rdocx_document:
     reference_docx: Extras/manuscript_template.docx
@@
 always_allow_html: true
-params:
-  distill: FALSE
-  word: TRUE
 ---
@@
 ```{r global_options, include=FALSE}
-knitr::opts_chunk$set(include=FALSE,
+knitr::opts_chunk$set(include=TRUE,
                       echo=FALSE, warning=FALSE, message=FALSE)
@@
 library(magrittr)
-source("R/loa_maker.R")
-source("R/meta.R")
+source(here::here("manuscript", "loa_maker.R"))
+source(here::here("manuscript","meta.R"))
+library(gofer) # https://github.com/awconway/gofer
+library(flextable)
 ```
@@
 
-<div class="l-page-outset">
-<blockquote>
 ### Abstract
@@
 Zero-heat-flux thermometers provide clinicians with the ability to continuously and non-invasively monitor body temperature.
-These devices are increasingly being used to substitute for invasive core temperature measurement during surgery and in critical care.
-The aim of this review was to determine the accuracy and precision of zero-heat-flux temperature measurements.
+These devices are increasingly being used to substitute for more invasive core temperature measurements during surgery and in critical care.
+The aim of this review was to determine the accuracy and precision of zero-heat-flux temperature measurements from the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System.
 
@@
 The range of uncertainty in the accuracy of the zero-heat-flux thermometer should be taken into account when using this device to inform clinical decision-making.
-Clinicians should therefore consider the potential that a temperature measurement from a zero-heat-flux thermometer could be as much as 1°C higher or lower than core temperature.
+Clinicians should therefore consider the potential that a temperature measurement from a 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System could be as much as 1°C higher or lower than core temperature.
 Use of this device may not be appropriate in situations where a difference in temperature of less than 1°C is important to detect.
@@
 
-</blockquote>
-</div>
-
 \pagebreak
 
-```{r conditional_title_page, results='asis', include=params$word}
-cat("
 ## Declarations
 
-Availability of data and material (data transparency): All data used in the meta-analyses is available [here](https://aconway.dev/zhf).
+Availability of data and material (data transparency): All data used in the meta-analyses is available [here](https://zhf-info.netlify.app).
 
@@
 
-")
-```
-
 \pagebreak
@@
 Continuous core temperature monitoring is commonly used within perioperative and intensive care settings.
-Thermoregulatory dysfunction is commonly associated with the induction of anesthesia and can lead to adverse outcomes including cardiac arrhythmia, altered hemostasis and increased risk of surgical site infection.[@frank1997perioperative; @kurz1996perioperative; @michelson1994reversible; @rohrer1992effect] The pulmonary artery catheter is the reference standard for continuous core temperature monitoring, however, the invasive nature of this method renders an increased risk of bloodstream infections and damage to surrounding tissue.[@hadian2006evidence] Although clinically accurate relative to pulmonary artery temperature measurements, surrogate measures of core temperature at esophageal, rectal, and bladder locations remain mildly invasive interventions.
+Thermoregulatory dysfunction is associated with the induction of anesthesia and can lead to adverse outcomes including cardiac arrhythmia, altered hemostasis and increased risk of surgical site infection.[@frank1997perioperative; @kurz1996perioperative; @michelson1994reversible; @rohrer1992effect] The pulmonary artery catheter is the reference standard for continuous core temperature monitoring, however, the invasive nature of this method renders an increased risk of bloodstream infections and damage to surrounding tissue.[@hadian2006evidence] Although clinically accurate relative to pulmonary artery temperature measurements, surrogate measures of core temperature at esophageal, rectal, and bladder locations remain mildly invasive interventions.
 
 Zero-heat-flux thermometry is an alternative non-invasive method that allows for continuous monitoring of core temperature.
-Originally developed in the 1970s, zero-heat-flux technology was recently implemented in the 3M SpotOn temperature monitoring system (3M, St Paul, MN), as a single-use, disposable sensor.
-In practice, the zero-heat-flux sensor, such as the 3M SpotOn, is placed on the lateral surface of the forehead and is initially warmed to equilibrate the temperature of the skin surface to the underlying core tissues.
-Equipped with a thermal insulator, the zero-heat-flux sensor eliminates heat loss to the environment to allow for changes in core temperature to be directly reflected by a change in skin surface temperature.[@eshraghi2014]
+Zero-heat-flux sensors are placed on the lateral surface of the forehead and is initially warmed to equilibrate the temperature of the skin surface to the underlying core tissues.
+Equipped with a thermal insulator, the zero-heat-flux sensor eliminates heat loss to the environment to allow for changes in core temperature to be directly reflected by a change in skin surface temperature.[@eshraghi2014] Originally developed in the 1970s, zero-heat-flux technology was recently implemented in the the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System (3M^TM^, St Paul, MN), as a single-use, disposable sensor.
+This device was previously known as the SpotOn Temperature Monitoring System.
+Another device on the market is the T-core sensor from Dräger.
 
-The agreement between zero-heat-flux thermometers and core as well as other peripheral thermometers has been investigated in multiple studies over the last five years.
-Appraisal of these studies and synthesis of the results would aid clinicians in deciding the appropriate circumstances in which zero-heat-flux thermometers may be used.
-We aimed to determine if zero-heat-flux thermometers have clinically acceptable accuracy and precision relative to established core and peripheral temperature measurement devices.
+The agreement between temperature measurements from zero-heat-flux thermometers and core as well as other peripheral thermometers has been investigated in multiple studies over the last five years.
+The 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System, has been the zero-heat-flux device used in most of these recent studies.
+Appraisal and synthesis of the results would aid clinicians in deciding the appropriate circumstances in which this particular zero-heat-flux thermometer may be used.
+We aimed to determine if 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System has clinically acceptable accuracy and precision relative to established core and peripheral temperature measurement devices.
 Accuracy is defined as the average difference between temperature measurements from the zero-heat-flux and comparator device and precision as the variance (standard deviation) in the differences.
@@
 
-A systematic review was conducted in accordance with a predetermined protocol.
-The primary comparison for this review was temperature measured from a zero-heat-flux thermometer versus temperature measured from a core site, which we defined as temperature measured at either an arterial, esophageal, bladder or rectal site.
-Secondary comparisons were made between zero-heat-flux thermometers and temperatures taken at peripheral sites.
+A systematic review was conducted.
+The primary comparison for this review was zero-heat-flux temperature measured using the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System versus temperature measured from a core site, which we defined as temperature measured at either an arterial, esophageal, bladder or rectal site.
+Secondary comparisons were made between temperatures measured using the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System and temperatures taken at peripheral sites.
 
@@
 
-Observational studies that reported temperature measurements from a zero-heat-flux thermometer and comparator thermometer were included.
+Observational studies that reported temperature measurements from a 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System and comparator thermometer were included.
 Studies involving a case control design were excluded due to potential for overestimation of the intervention performance.
@@
 Published studies were found by searching Medline and EMBASE to January 2020.
-The Cochrane-recommended search strategy combining terms for the ‘target condition’ and ‘index test’ was used.[@mann2012should] This search strategy is an efficient approach for systematic reviews of diagnostic test accuracy studies.[@preston2015improving] We also conducted forward citation searching, by using Google Scholar to search the citations of the first article published on the accuracy of zero-heat-flux thermometers.[@eshraghi2014] The search strategies used for each database are available on a [webpage](https://aconway.dev/zhf) containing supplementary information for the systematic review.
+The Cochrane-recommended search strategy combining terms for the ‘target condition’ and ‘index test’ was used.[@mann2012should] This search strategy is an efficient approach for systematic reviews of diagnostic test accuracy studies.[@preston2015improving] We also conducted forward citation searching, by using Google Scholar to search the citations of the first article published on the accuracy of the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System.[@eshraghi2014] The search strategies used for each database are available in the appendix.
 Selection of studies was undertaken independently by two reviewers.
@@
 
-The objective for the meta-analysis was to estimate the population limits of agreement between temperature measurements from the zero-heat-flux and established comparator thermometers.
+The objective for the meta-analysis was to estimate the population limits of agreement between temperature measurements from the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System and established comparator thermometers.
 A framework for meta-analysis of Bland-Altman method comparison studies based on limits of agreement approach was used.[@tipton2017framework]  This method was selected because it parallels the approach used in primary Bland-Altman studies, whereby an estimate is generated for the pooled limits of agreement in the population (not just in the samples studied).
@@
 
-Prior to conducting the meta-analyses, the results from each study were converted into a standard format, with bias meaning comparator thermometer minus zero-heat-flux thermometer measured in degrees Celsius (°C).
-In several studies, results were reported for multiple groups of participants, therefore in the meta-analysis each of these groups was treated as a separate 'comparison'.
-Other studies reported multiple sets of results, whereby analyses were conducted between zero-heat-flux and various comparator devices used on the same participant.
-These instances were also treated as a separate 'comparison' if the comparator devices were a part of separate meta-analysis groups.
-One study reported intraoperative, postoperative and overall results for the same participants.
+Prior to conducting the meta-analyses, the results from each study were converted into a standard format, with bias meaning comparator thermometer temperature measurement minus the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System measurement in degrees Celsius (°C).
+In several studies, results were reported for multiple groups of participants, therefore in the meta-analysis each of these groups was treated as a separate 'comparison'.[@Boisson_2018; @Dahyot_Fizelier_2017; @Schell_Chaple_2018; @M_kinen_2016] Other studies reported multiple sets of results, whereby analyses were conducted between zero-heat-flux and various comparator devices used on the same participant.
+These instances were also treated as a separate 'comparison' if the comparator devices were a part of separate meta-analysis groups.[@West_2019; @Pesonen_2018; @M_kinen_2016; @Iden_2015] One study reported intraoperative, postoperative and overall results for the same participants[@eshraghi2014].
 Only the paired measurements from the overall results were included in the main and low risk bias analyses, leaving paired measurements exclusively from the intraoperative and postoperative timepoints to be included in respective meta-analyses subgroups.
@@
 
-Eighteen studies were included (Figure 1).
+Sixteen studies were included (Figure 1).
 Two studies reported only in abstract form were not included and assigned as 'studies awaiting classification' because there was insufficient information provided.[@cullen2015measuring; @VendrellJorda2016]
 
-```{r fig-1,  fig.cap="PRISMA Flow Diagram", echo=FALSE, fig.width=5.5, fig.path="figures/", include=params$distill, eval=params$distill}
-# https://github.com/awconway/ggprisma
-ggprisma::ggprisma(retrieved = 131, included = 18, duplicates = 35, full_text = 23, wrong_intervention = 3, wrong_comparator = 2, wrong_design = 1, awaiting_classification = 2)
-```
-
-Detailed characteristics of included studies can be viewed on the [webpage](https://aconway.dev/zhf/) containing supplementary information for the systematic review.
-The primary comparison of zero-heat-flux versus core temperature measurements (eg, arterial, bladder, esophageal or rectal) consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies.
-In total, data from `r primary$Participants` participants with `r format(primary$Measurements, scientfic=F)` paired measurements were included in this comparison (two studies did not report the total number of measurements included in their analysis).
-The sensitivity analysis for the primary comparison with only studies that were judged as low risk of bias across all domains included `r low_risk$Comparisons` comparisons from `r low_risk$Studies` studies that enrolled `r low_risk$Participants` participants with `r low_risk$Measurements` paired measurements (two studies did not report the total number of measurements included in their analysis).
+Detailed characteristics of included studies is displayed in Table 1.
+The primary comparison of the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System versus core temperature measurements (eg, arterial, bladder, esophageal or rectal) consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies.[@Boisson_2018; @Carvalho_2019; @Dahyot_Fizelier_2017; @eshraghi2014; @G_mez_Romero_2019; @idei2016; @Jack_2019; @Kato_2015; @kollmann2019validation; @M_kinen_2016; @Morettini_2019; @Pesonen_2018; @Schell_Chaple_2018; @Tachibana_2019; @G_mez_Romero_2019] In total, data from `r primary$Participants` participants with `r format(primary$Measurements, scientfic=F)` paired measurements were included in this comparison (two studies did not report the total number of measurements included in their analysis).
+The sensitivity analysis for the primary comparison with only studies that were assessed as low risk of bias across all domains included `r low_risk$Comparisons` comparisons from `r low_risk$Studies` studies that enrolled `r low_risk$Participants` participants with `r low_risk$Measurements` paired measurements (two studies did not report the total number of measurements included in their analysis).
 There were `r ICU$Studies` studies that compared zero-heat-flux to core temperature measurements in ICU patients, comprising `r ICU$Comparisons` comparisons with `r ICU$Measurements` measurements from `r ICU$Participants` participants.
 Another `r OT$Studies` studies were included that compared zero-heat-flux to core temperature measurements in patients undergoing surgery, comprising `r OT$Comparisons` comparisons with `r OT$Measurements` measurements from `r OT$Participants` participants.
-Nasopharyngeal thermometers were used as the comparator devices in `r NPA$Studies` studies, with `r NPA$Measurements` paired measurements from `r NPA$Measurements` participants.
+Nasopharyngeal thermometers were used as the comparator devices in `r NPA$Studies` studies, with `r NPA$Measurements` paired measurements from `r NPA$Participants` participants.
 Sublingual thermometers were used as the comparator devices in `r SL$Studies` studies that reported `r SL$Measurements` paired measurements from `r SL$Participants` participants.
+Supplementary information presented in the study [webpage](https://zhf-info.netlify.app) provides comprehensive summaries of the studies included in each of these meta-analyses.
 
-Most studies included in this systematic review evaluated the zero-heat-flux temperature monitoring system manufactured by 3M.[@Boisson_2018; @Carvalho_2019; @Dahyot_Fizelier_2017; @eshraghi2014; @G_mez_Romero_2019; @idei2016; @Iden_2015; @Jack_2019; @Kato_2015; @kollmann2019validation; @M_kinen_2016; @Morettini_2019; @Pesonen_2018; @Schell_Chaple_2018; @Tachibana_2019; @West_2019] Previously known as the SpotOn Temperature Monitoring System, the 3M zero-heat-flux device is now referred to commercially as the Bair Hugger Temperature Monitoring System.
-Two studies evaluated the Tcore^TM^ device.[@sastre2019evaluation; @G_mez_Romero_2019] The oldest study included in this review, published in 2000, was an evaluation of the Coretemp device from Terumo.[@Harioka_2000] All comparisons reported adherence to the zero-heat-flux device manufacturer instructions and placed the sensor on the forehead of the participants.
-One included study also reported results for comparisons where the zero-heat-flux thermometer was not placed on the forehead.
-We did not include these comparisons in our meta-analysis.
+All comparisons reported adherence to the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System manufacturer instructions and placed the sensor on the forehead of the participants.
+One included study also reported results for comparisons where the zero-heat-flux thermometer was not placed on the forehead.[@Tachibana_2019] We did not include these comparisons in our meta-analysis.
 
-High risk of bias was associated with patient selection for 13 (43%) comparisons from 9 (56%) studies, conduct of zero-heat-flux and comparator measurements in 10 (33%) comparisons from 8 (50%) studies and 12 (40%) comparisons 9 (30%) studies, respectively (mostly due to zero-heat-flux measurements being taken with knowledge of the comparator measurements and vice versa) and participant flow for 13 (43%) studies.
+Risk of bias assessments for each study are presented in Figure 2.
+High risk of bias associated with patient selection for 13 (43%) comparisons from 9 (56%) studies, conduct of zero-heat-flux and comparator measurements in 10 (33%) comparisons from 8 (50%) studies and 12 (40%) comparisons 9 (30%) studies, respectively (mostly due to zero-heat-flux measurements being taken with knowledge of the comparator measurements and vice versa) and participant flow for 13 (43%) studies.
 In 19 (50%) comparisons from 8 (50%) studies, the authors had declared a conflict of interest or receipt of funding or equipment from the manufacturer of the zero-heat-flux device under evaluation.
 
-### Primary comparison: zero-heat-flux thermometer versus core thermometers
+### Primary comparison: 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System versus core thermometers
 
 Table 1 presents results of the primary, sensitivity and all subgroup analyses for the primary comparison as well as secondary comparisons.
-The pooled estimate for the mean bias between zero-heat-flux and core temperature measurements was `r primary$bias_mean`°C.
+The pooled estimate for the mean bias between the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System and core temperature measurements was `r primary$bias_mean`°C.
 Population limits of agreement, which take into consideration the between-study heterogeneity and sampling error, were wide, spanning from `r primary$CI_L_rve`°C to `r primary$CI_U_rve`°C (`r primary$Measurements` measurements; `r primary$Participants` participants; `r primary$Studies` studies).
-The amount of between-study heterogeneity is displayed graphically in the density plot in Figure 2.
+The amount of between-study heterogeneity is displayed graphically in the density plot in Figure 3.
 The quality of evidence for the primary comparison was downgraded to low quality due to concerns about study limitations and inconsistency.
@@
 The GRADE rating for quality of evidence was downgraded to very low quality due to study limitations, inconsistency and imprecision.
-In the subset of studies that evaluated the use of zero-heat-flux thermometers during surgery found a mean bias of `r OT$bias_mean`°C with population limits of agreement from `r OT$CI_L_rve`°C to `r OT$CI_U_rve`°C.
+In the subset of studies that evaluated the use of 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System during surgery found a mean bias of `r OT$bias_mean`°C with population limits of agreement from `r OT$CI_L_rve`°C to `r OT$CI_U_rve`°C.
 The quality of evidence was rated as moderate quality due to concerns about study limitations.
 
-```{r table-1, layout="l-page-outset", include=params$distill}
-  ma <- list(primary, low_risk, ICU, OT,  NPA,SL, conflict)
-names(ma) <- c("Primary", "Low risk studies", "Intensive Care Unit", 
-               "Surgery", "Nasopharyngeal", "Sublingual",
-               "Studies not funded by industry")
-df <- dplyr::bind_rows(ma, .id="Comparison")
-df %>% 
-  dplyr::rename(" " = Comparison, "Mean bias" = bias_mean, "Variance" = sd2_est, "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, "Upper bound for 95% limits of agreement" = LOA_U, "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve) %>%
-  kableExtra::kable() %>% 
-   kableExtra::add_header_above(c(" ","","","","","","","","","", "Population limits of agreement" = 2)) %>% 
-  kableExtra::add_header_above(c("Table 1. Results of meta-analyses" = 12))
-```
+### Secondary comparisons: 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System versus peripheral thermometers
 
-### Secondary comparisons: zero-heat-flux thermometer versus peripheral thermometers
-
-Zero-heat-flux thermometers were compared with sublingual thermometers and nasopharyngeal thermometers in the studies included in this review.
-The mean bias between zero-heat-flux and nasopharyngeal temperature measurements in meta-analysis of results from `r NPA$Studies` studies was `r NPA$bias_mean`°C.
+Temperature measurements from the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System  were compared with sublingual and nasopharyngeal temperature measurements in several studies included in this review.
+The mean bias between 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System and nasopharyngeal temperature measurements in meta-analysis of results from `r NPA$Studies` studies was `r NPA$bias_mean`°C.
 Population limits of agreement were `r NPA$CI_L_rve`°C to `r NPA$CI_U_rve`°C.
 We downgraded the quality of evidence to low, again due to concerns about imprecision and study limitations.
-The mean bias between zero-heat-flux and sublingual temperature measurements in meta-analysis of results from `r SL$Studies` studies was `r SL$bias_mean`°C.
+The mean bias between the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System and sublingual temperature measurements in meta-analysis of results from `r SL$Studies` studies was `r SL$bias_mean`°C.
 Due to the limited number of studies and measurements, population limits of agreement were extremely wide, spanning outside physiologically plausible range for temperature.
@@
 
-This systematic review showed that a temperature measurement from a zero-heat-flux thermometer could be as much as 1°C higher or lower than core temperature.
-These results may have important implications for practice that clinicians should consider.
-It was reassuring that results of our sensitivity analysis restricted to studies judged to be at low risk of bias using the QUADAS-2 tool were similar.
+This systematic review showed that a temperature measurement from a 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System device could be as much as 1°C higher or lower than core temperature.
+These results may have important implications for practice.
+It was reassuring that results of our sensitivity analysis restricted to studies assessed to be at low risk of bias using the QUADAS-2 tool were similar.
 As such, it is vital for healthcare professionals considering using this device to first determine if differences in temperature smaller than this magnitude would be important for the given clinical situation.
-If so, then it may not be appropriate to substitute the zero-heat-flux device in place of a core thermometer.
+If so, then it may not be appropriate to substitute the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System in place of a core thermometer.
 
-Our estimates of the accuracy of zero-heat-flux thermometers are similar to results from a previous meta-analysis that compared other peripheral thermometers, such as sublingual and temporal artery devices, with core temperature measurements.[@niven2015accuracy] However, this previous meta-analysis used a statistical approach that did not incorporate the magnitude of heterogeneity in results between studies or sampling error.
+Our estimates of the accuracy of measurements from the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System are similar to results from a previous meta-analysis that compared other peripheral thermometers, such as sublingual and temporal artery devices, with core temperature measurements.[@niven2015accuracy] However, this previous meta-analysis used a statistical approach that did not incorporate the magnitude of heterogeneity in results between studies or sampling error.
 As such, it is possible that the zero-heat-flux thermometer may still be more precise than other peripheral thermometers.
@@
 As a result, population limits of agreement for the Intensive Care Unit subgroup were broad.
-Additional studies are required to increase confidence in the accuracy of zero-heat-flux device in this setting, where continuous temperature monitoring is often required.
+Additional studies are required to increase confidence in the accuracy of 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System device in this setting, where continuous temperature monitoring is often required.
 
-Although comparisons with core temperature are the most important to evaluate, we included studies that compared zero-heat-flux and peripheral temperature monitoring devices in our review because clinicians may be interested to determine if this new technology is sufficiently accurate to replace other ways to non-invasively monitor temperature.
+Although comparisons with core temperature are the most important to evaluate, we included studies that compared 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System and peripheral temperature monitoring devices in our review because clinicians may be interested to determine if this new technology is sufficiently accurate to replace other ways to non-invasively monitor temperature.
 Also, there may be situations where it is standard practice for only peripheral temperature monitoring to be used.
@@
 It should be noted that we did not include studies that used the Temple Touch Pro because it is not strictly a zero-heat-flux device.
-This is a new thermometer that is similar to the zero-heat-flux device in that it is placed cutaneously, but the underlying technology is different.[@evron2017evaluation]
+This is a new thermometer that is similar to the zero-heat-flux device in that it is placed cutaneously, but the underlying technology is different.[@evron2017evaluation] Likewise, studies that evaluated the Drager Tcore device were not included because this review focused specifically on the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System.
 
@@
 
-The accuracy of zero-heat-flux temperature monitoring has been evaluated in various intraoperative contexts as well as in the intensive care unit setting.
+The accuracy of 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System has been evaluated in various intraoperative contexts as well as in the intensive care unit setting.
 Our subgroup analyses did not indicate that the accuracy of this temperature monitoring device was any more effective in a particular setting.
-Only one study included in our systematic review included pediatric patients.
+Only two studies included in our systematic review included pediatric patients.
 Additional studies to evaluate the accuracy of this device in children may be warranted to increase confidence.
@@
 
-We did not extract data on adverse events due to zero-heat-flux temperature monitoring.
+We did not extract data on adverse events due to temperature monitoring with the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System.
 The possibility of publication bias cannot be ruled out, although the evidence suggests this may not be as serious of a problem for studies that are not randomized controlled trials.[@begg2005systematic] Our focus for the meta-analysis was on calculating population limits of agreement, which incorporate the variation in bias between studies into the estimates.
@@
 
-Substantial differences between core and zero-heat-flux temperature measurements were identified in this meta-analysis.
+Substantial differences between temperature measurements from core and the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System were identified in this meta-analysis.
 Clinicians should consider the range of uncertainty in the accuracy of the zero-heat-flux thermometer when using this device to inform their decision-making.
@@
 
-```{r  conditional_references, include=params$word, results='asis'}
-cat("
+# References
 
-# References")
-```
 <div id="refs"></div>
@@
 \pagebreak
-```{r  conditional_figure_legend, include=params$word, results='asis'}
-cat("
 
@@
 
-Figure 1: PRISMA Flow Diagram
+Fig. 1 PRISMA Flow Diagram
 
-Figure 2: Comparisons between core and zero-heat-flux thermometers within and across studies.
-Blue curves are distributions of the differences between measurements from zero-heat-flux (ZHF) sensors and core temperature measurements in individual studies.
-The red curve is the distribution of the pooled estimate.
+Fig. 2 Risk of bias assessments for included studies
 
-")
+Fig. 3 Comparisons between core and zero-heat-flux thermometers within and across studies
+
+\pagebreak
+
+# Appendix
+
+## Medline search strategy
+
+1.	zero-heat-flux
+2.	zero-flux
+3.	1 OR 2
+4.	(SpotON) OR (Temple Touch Pro)
+5.	3 OR 4
+6.	Accuracy OR precision OR reliability OR validity OR validation OR standard deviation
+7.	Bias OR mean difference OR limit of agreement OR Bland Altman
+8.	6 OR 7
+9.	(exp “diagnostic errors” / OR exp “sensitivity and specificity” / OR (accura* OR reliability* OR target* OR utilt* OR discriminat* OR differentiat*)
+10.	8 OR 9
+11.	5 AND 10
+
+## EMBASE search strategy
+
+1.	zero-heat-flux
+2.	zero-flux
+3.	1 OR 2
+4.	(SpotON) OR (Temple Touch Pro)
+5.	3 OR 4
+6.	Accuracy OR precision OR reliability OR validity OR validation OR standard deviation
+7.	Bias OR mean difference OR limit of agreement OR Bland Altman
+8.	6 OR 7
+9.	('diagnostic accuracy'/de OR 'diagnostic test accuracy study'/de OR 'diagnostic error'/exp OR 'diagnostic value'/de OR 'sensitivity and specificity'/de OR 'predictive value'/de OR (accura* OR reliabilit* OR target* OR utilit* OR discriminat* OR differentiat*)
+11.	5 AND 10
+
+\pagebreak
+
+### Table 1: Study Characteristics
+
+```{r }
+data_NPA <- gofer::data_NPA
+data_SL <- gofer::data_SL
+data_core <- gofer::data_core
+data_NPA$comparison <- sub("NPA", "Nasopharyngeal", data_NPA$comparison) 
+data_core$comparison <- sub("PA", "Pulmonary artery", data_core$comparison) 
+data_core$comparison <- sub("Iliac", "Iliac artery", data_core$comparison) 
+data_core$comparison <- sub("Ax", "Axillary artery", data_core$comparison) 
+data_core$comparison <- sub("Eso", "Esophageal", data_core$comparison)
+data_core$patients <- sub("Gynecological Surgery", "Gynecology Surgery", data_core$patients)
+data_core$patients <- sub("Laparosopic Surgery", "Laparoscopy Surgery", data_core$patients)
+
+ft <- data_core %>% 
+    dplyr::bind_rows(data_SL) %>%
+      dplyr::bind_rows(data_NPA) %>%
+    dplyr::arrange(Study) %>% 
+    tidyr::separate(Study, c("Study", "Year"), sep = ", ")  %>% 
+  dplyr::arrange(-as.numeric(Year)) %>% 
+       dplyr::mutate(perc_male = round((male/(female+male))*100, 1)) %>% 
+  dplyr::mutate(N= tidyr::replace_na(N, 0)) %>% 
+    dplyr::mutate(lower_temp= tidyr::replace_na(lower_temp, 0)) %>% 
+  dplyr::mutate(upper_temp= tidyr::replace_na(upper_temp, 0)) %>% 
+    dplyr::mutate(age = ifelse(!is.na(mean_age), 
+                      glue::glue("{mean_age} ({mean_age - lower_mean})"),
+                      glue::glue("{median_age} [{lower_IQR}-{upper_IQR}]"))) %>% 
+    dplyr::mutate(temp_range = glue::glue("{lower_temp}-{upper_temp}")) %>%
+
+     dplyr::select(Year, Study, code, patients, perc_male, age, comparison, n, N, 
+           temp_range) %>%
+      flextable()
+
+ft <- compose( ft, j="perc_male", value = as_paragraph(
+  minibar(value =   perc_male , max=100,
+          barcol = "#8edaff",
+  bg = "#ff8ea2",)
+),
+part = "body")
+
+ft <- compose(ft, i=~code=="US", j = "code",
+  value = as_paragraph(as_image( 
+    src = flagon::flags("US", filetype = "png"),
+    width = .20, height = .15))
+)
+
+ft <- compose(ft, i=~code=="FI", j = "code",
+  value = as_paragraph(as_image( 
+    src = flagon::flags("FI", filetype = "png"),
+    width = .20, height = .15))
+)
+
+ft <- compose(ft, i=~code=="FR", j = "code",
+  value = as_paragraph(as_image( 
+    src = flagon::flags("FR", filetype = "png"),
+    width = .20, height = .15))
+)
+
+ft <- compose(ft, i=~code=="BE", j = "code",
+  value = as_paragraph(as_image( 
+    src = flagon::flags("BE", filetype = "png"), 
+    width = .20, height = .15))
+)
+
+ft <- compose(ft, i=~code=="ES", j = "code",
+  value = as_paragraph(as_image( 
+    src = flagon::flags("ES", filetype = "png"), 
+    width = .20, height = .15))
+)
+
+ft <- compose(ft, i=~code=="BE", j = "code",
+  value = as_paragraph(as_image( 
+    src = flagon::flags("BE", filetype = "png"), 
+    width = .20, height = .15))
+)
+
+ft <- compose(ft, i=~code=="GB", j = "code",
+  value = as_paragraph(as_image( 
+    src = flagon::flags("GB", filetype = "png"), 
+    width = .20, height = .15))
+)
+
+ft <- compose(ft, i=~code=="JP", j = "code",
+  value = as_paragraph(as_image( 
+    src = flagon::flags("JP", filetype = "png"), 
+    width = .20, height = .15))
+)
+
+ft <- compose(ft, i=~code=="IT", j = "code",
+  value = as_paragraph(as_image( 
+    src = flagon::flags("IT", filetype = "png"), 
+    width = .20, height = .15))
+)
+
+ft <- compose(ft, i=~code=="DE", j = "code",
+  value = as_paragraph(as_image( 
+    src = flagon::flags("DE", filetype = "png"), 
+    width = .20, height = .15))
+)
+
+ft <- compose(ft, i=~code=="CA", j = "code",
+  value = as_paragraph(as_image( 
+    src = flagon::flags("CA", filetype = "png"), 
+    width = .20, height = .15))
+)
+
+ft <- compose( ft, j = "n",   value = as_paragraph(as_chunk(format(n)), "    ",
+  minibar(value = n, barcol = "#930093")
+),
+part = "body")
+
+ft <- compose( ft, j = "N",   value = as_paragraph(as_chunk(format(N)), "    ",
+  lollipop(rangecol = "white",positivecol ="#930093", value = log(N), min=0, max=log(max(N)))
+),
+part = "body")
+
+ft <- compose(ft, j = "perc_male",
+  value = as_paragraph(as_image( 
+    src = "figures/sex.png", 
+    width = .20, height = .15)),
+  part="header"
+)
+
+ft <- merge_v(ft, part = "body", j = 1:2)
+
+ft <- merge_at(ft, part = "body", i=~Study=="Boisson", j = "patients")
+ft <- merge_at(ft, part = "body", i=~Study=="Boisson", j = "perc_male")
+ft <- merge_at(ft, part = "body", i=~Study=="Boisson", j = "age")
+ft <- merge_at(ft, part = "body", i=~Study=="Boisson", j = "code")
+ft <- merge_at(ft, part = "body", i=~Study=="Boisson", j = "temp_range")
+
+ft <- merge_at(ft, part = "body", i=~Study=="Schell-Chaple", j = "patients")
+ft <- merge_at(ft, part = "body", i=~Study=="Schell-Chaple", j = "perc_male")
+ft <- merge_at(ft, part = "body", i=~Study=="Schell-Chaple", j = "age")
+ft <- merge_at(ft, part = "body", i=~Study=="Schell-Chaple", j = "code")
+ft <- merge_at(ft, part = "body", i=~Study=="Schell-Chaple", j = "temp_range")
+
+ft <- merge_at(ft, part = "body", i=~Study=="Dahyot-Fizelier", j = "patients")
+ft <- merge_at(ft, part = "body", i=~Study=="Dahyot-Fizelier", j = "perc_male")
+ft <- merge_at(ft, part = "body", i=~Study=="Dahyot-Fizelier", j = "age")
+ft <- merge_at(ft, part = "body", i=~Study=="Dahyot-Fizelier", j = "code")
+ft <- merge_at(ft, part = "body", i=~Study=="Dahyot-Fizelier", j = "temp_range")
+
+ft <- merge_at(ft, part = "body", i=~Study=="West", j = "patients")
+ft <- merge_at(ft, part = "body", i=~Study=="West", j = "perc_male")
+ft <- merge_at(ft, part = "body", i=~Study=="West", j = "age")
+ft <- merge_at(ft, part = "body", i=~Study=="West", j = "code")
+ft <- merge_at(ft, part = "body", i=~Study=="West", j = "temp_range")
+
+ft <- merge_at(ft, part = "body", i=~Study=="Pesonen", j = "patients")
+ft <- merge_at(ft, part = "body", i=~Study=="Pesonen", j = "perc_male")
+ft <- merge_at(ft, part = "body", i=~Study=="Pesonen", j = "age")
+ft <- merge_at(ft, part = "body", i=~Study=="Pesonen", j = "code")
+ft <- merge_at(ft, part = "body", i=~Study=="Pesonen", j = "temp_range")
+ft <- merge_at(ft, part = "body", i=~Study=="Pesonen", j = "n")
+ft <- merge_at(ft, part = "body", i=~Study=="Pesonen", j = "N")
+
+ft <- merge_at(ft, part = "body", i=~Study=="Makinen"& 
+                 patients=="Cardiac Surgery", j = "patients")
+ft <- merge_at(ft, part = "body", i=~Study=="Makinen", j = "perc_male")
+ft <- merge_at(ft, part = "body", i=~Study=="Makinen", j = "age")
+ft <- merge_at(ft, part = "body", i=~Study=="Makinen", j = "code")
+ft <- merge_at(ft, part = "body", i=~Study=="Makinen", j = "temp_range")
+ft <- merge_at(ft, part = "body", i=~Study=="Makinen", j = "N")
+
+ft %>% 
+  fontsize(size = 10) %>% 
+  fix_border_issues() %>% 
+  add_header_row(values = c("Study","Participants", "Temperature measurements"),  colwidths = c(4, 2 , 4)) %>% 
+  align(align = "center", part = "header") %>% 
+  bg(i=1, j=1:4, part="header", bg="#0080ff") %>% 
+  color(i=1, j=1:4, part="header", color="white") %>% 
+  bg(i=1, j=5:6, part="header", bg="#ee721a") %>% 
+  color(i=1, j=5:6, part="header", color="white")  %>% 
+  bg(i=1, j=7:10, part="header", bg="#930093") %>% 
+  color(i=1, j=7:10, part="header", color="white")  %>% 
+  empty_blanks() %>% 
+  set_header_labels(Year ="", Study = "", code = "",
+                    patients = "", age= "Age (years)",
+                    comparison = "", n = "Participants",
+                    N = "Measurements", temp_range = "Range (°C)") %>% 
+  border_remove() %>% 
+   hline(i =~Year=="2019", part = "body", 
+            border = officer::fp_border(color="black", width = 1)) %>%
+
+ hline( i =~Year=="2018", part = "body", 
+            border = officer::fp_border(color="black", width = 1)) %>%
+
+hline(i =~Year=="2017", part = "body", 
+            border = officer::fp_border(color="black", width = 1)) %>%
+
+ hline( i =~Year=="2016", part = "body", 
+            border = officer::fp_border(color="black", width = 1)) %>%
+
+ hline(i =~Year=="2015", part = "body", 
+            border = officer::fp_border(color="black", width = 1)) %>%
+
+hline( i =~Year=="2014", part = "body", 
+            border = officer::fp_border(color="black", width = 1))  %>% 
+  bg(j=~comparison + temp_range + n+N, bg="lightgray") %>% 
+  hline( i =2, part = "header", 
+            border = officer::fp_border(color="black", width = 1)) %>% 
+  hline_bottom(part = "body", 
+            border = officer::fp_border(color="black", width = 1)) %>% 
+  width(j="Year",width = 0.49) %>%
+    width(j="Study",width = 0.79)  %>% 
+   width(j="code",width = 0.39)  %>% 
+    width(j="patients",width = 0.98)  %>% 
+  width(j="perc_male",width = 1.19) %>%
+  width(j="age",width = 0.82) %>%
+  width(j="comparison",width = 1.18) %>%
+  width(j="n",width = 1.75) %>%
+  width(j="N",width = 1.81) %>%
+  width(j="temp_range",width = 0.65)
+
 ```
+
+\pagebreak
+
+### Table 2: Results of meta-analyses
+
+```{r }
+  ma <- list(primary, low_risk, ICU, OT,  NPA,SL, conflict)
+names(ma) <- c("Primary", "Low risk studies", "Intensive Care Unit", 
+               "Surgery", "Nasopharyngeal", "Sublingual",
+               "Studies not funded by industry")
+df <- dplyr::bind_rows(ma, .id="Comparison")
+
+df %>%
+  mutate(CI_U_rve = dplyr::na_if(CI_U_rve, 5109.68)) %>% 
+    mutate(CI_L_rve = dplyr::na_if(CI_L_rve, -5110.03)) %>% 
+  rename(" " = Comparison, "Mean bias" = bias_mean,
+         "Tau-squared" = tau_est, 
+         "Lower 95% LoA" = LOA_L, 
+         "Upper 95% LoA" = LOA_U, 
+         "Outer CI for lower 95% LoA" = CI_L_rve, 
+         "Outer CI for upper 95% LoA" = CI_U_rve) %>% flextable() %>% 
+  compose(j=~sd2_est, part = "header",
+          value = as_paragraph(
+            "SD",
+            as_sup("2")
+          )) %>% 
+  compose(j="Tau-squared", part = "header",
+          value = as_paragraph(
+            "τ",
+            as_sup("2")
+          ))  %>% 
+  footnote(i = 1, j = 6:12,
+               value = as_paragraph(
+                "Units are °C"
+               ),
+               ref_symbols = "a",
+               part = "header") %>% 
+        footnote(i = 1, j = 7,
+               value = as_paragraph(
+                "Variance"
+               ),
+               ref_symbols = "b",
+               part = "header") %>% 
+    footnote(i = 1, j = 8,
+               value = as_paragraph(
+                "Measure of heterogeneity"
+               ),
+               ref_symbols = "c",
+               part = "header") %>% 
+    footnote(i = 1, j = 9:12,
+               value = as_paragraph(
+                "LoA = Limits of Agreement"
+               ),
+               ref_symbols = "d",
+               part = "header") %>% 
+    footnote(i = 1, j = 11:12,
+               value = as_paragraph(
+                "CI = Confidence Intervals"
+               ),
+               ref_symbols = "e",
+               part = "header") %>% 
+    footnote(i =6, j = 11:12,
+               value = as_paragraph(
+                "Population limits of agreement were extremely wide, spanning outside the physiologically plausible range for temperature."
+               ),
+               ref_symbols = "f",
+               part = "body") %>% 
+  add_header_row(values = c("","","","","","","","","","", "Population LoA"),  colwidths = c(rep(1,10, by=1), 2))   %>% 
+  theme_booktabs() %>% 
+  width(j=1,width = 1.19) %>%
+  width(j=2,width = 0.69) %>%
+  width(j=3,width = 1.06) %>%
+  width(j=4,width = 0.94) %>%
+  width(j=5,width = 1.19) %>%
+  width(j=6,width = 0.56) %>%
+  width(j=7,width = 0.56) %>%
+  width(j=8,width = 0.6) %>%
+  width(j=9,width = 0.59) %>%
+  width(j=10,width = 0.75) %>%
+  width(j=11,width = 0.94) %>%
+  width(j=12,width = 0.94) %>% 
+  fontsize(size = 10)
+
+```

### 2020-05-06 app/app.R

@@ -1,343 +1,0 @@
-library(shiny)
-library(shinyLP)
-library(shinydashboard)
-library(shinydashboardPlus)
-library(DT)
-library(magrittr)
-library(dplyr)
-library(robvis)
-library(ggprisma) #awconway/ggprisma
-library(waiter)
-library(gofer)#awconway/gofer
-
-######UI#########
-ui <- dashboardPage(
-  skin ="red",
-  dashboardHeader(title="Options"),
-  dashboardSidebar(
-    sidebarMenu(
-      br(),
-      # menu item tabs
-      menuItem("Home", tabName="landing_page", icon=icon("home")),
-      menuItem("Search strategy", tabName="search", icon=icon("search")),
-      menuItem("Study selection", tabName="selection", icon=icon("hand-pointer")),
-      menuItem("Risk of bias", tabName = "Rob", icon = icon("exclamation-circle")),
-      menuItem("Graphical overview of findings", tabName="gofer", icon=icon("chart-area")), 
-      menuItem("Data used in meta-analysis", tabName="DT", icon=icon("table")), 
-      #menuItem("Meta-analysis results", tabName="Plot", icon=icon("chart-area")),
-      menuItem("All data extracted from source", tabName="frame", icon=icon("file-excel")),
-      
-
-      br(),
-
-      radioButtons(inputId = "dataset",
-                   h4("Select a subset of studies to display:"),
-                   inline = FALSE,
-                   choices= c("Core",
-                              "Core (low risk studies)",
-                              "Core (ICU studies)",
-                              "Core (Intra-operative studies)",
-                              "Nasopharyngeal",
-                              "Sublingual",
-                              "No conflicts of interest"))
-      
-    ) 
-  ),
-  dashboardBody(  
-    
-    
-    tabItems(
-      tabItem(tabName="Rob",
-              fluidRow(
-                tabBox(width = 12,
-                       tabPanel(p("Risk of bias across studies"),
-                                plotOutput("Rob_summary")
-                       ),
-                       tabPanel(p("Risk of bias in individual studies"),
-                                plotOutput("Rob_traffic_light")
-                       )
-                )
-              )
-      ),
-      
-      tabItem(tabName = "gofer",
-              fillPage(    tags$style(type = "text/css", "#gofer {height: calc(100vh - 80px) !important;}"),
-                           use_waitress(),
[…]

### 2020-05-06 manuscript/R/loa_maker.R

@@ -1,37 +1,0 @@
-#' Results of meta-analysis
-#'@rdname loa_maker
-#'@name loa_maker
-#'
-#'@return dataframe
-
-#' @export
-#' 
-loa_maker <- function(bias,V_bias,logs2,V_logs2) {
-  bias_row=meta(bias, V_bias)
-  logs2_row=meta(logs2, V_logs2)
-  bias_mean <- bias_row[2]
-  sd2_est <- exp(logs2_row[2])
-  tau_est <- bias_row[3]
-  LOA_L <- bias_mean - 2*sqrt(sd2_est + tau_est)
-  LOA_U <- bias_mean + 2*sqrt(sd2_est + tau_est)
-  m <- bias_row[1]
-  tcrit <- qt(1-.05/2,m-1)
-  B1 <- sd2_est^2/(sd2_est + tau_est)
-  B2 <- tau_est^2/(sd2_est + tau_est)
-  wt <- 1/V_bias
-  S1 <- sum(wt)
-  S2 <- sum(wt^2)
-  S3 <- sum(wt^3)
-  A0 <- 2*(m-1)/(S1-S2/S1)^2
-  A1 <- 4/(S1 - S2/S1)
-  A2 <- 2*(S2-2*S3/S1+S2^2/S1^2)/(S1-S2/S1)^2
-  V_logT2 <- A0/tau_est^2 + A1/tau_est + A2
-  V_logT2 <- 2/sum((V_bias + tau_est)^(-2))
-  V_LOA_mod <- bias_row[4] + B1*logs2_row[4] + B2*V_logT2
-  V_LOA_rve <- bias_row[5] + B1*logs2_row[5] + B2*V_logT2
-  CI_L_mod <- LOA_L - tcrit*sqrt(V_LOA_mod)
-  CI_U_mod <- LOA_U + tcrit*sqrt(V_LOA_mod)
-  CI_L_rve <- LOA_L - tcrit*sqrt(V_LOA_rve)
-  CI_U_rve <- LOA_U + tcrit*sqrt(V_LOA_rve)
-  data.frame(m, bias_mean, sd2_est, tau_est, LOA_L, LOA_U, CI_L_mod, CI_U_mod, CI_L_rve, CI_U_rve)
-}

### 2020-05-06 manuscript/R/meta.R

@@ -1,20 +1,0 @@
-#' Intermediate function for calculating meta-analysis
-#'@rdname meta
-#'@name meta
-
-#' @export
-#' 
-meta <-  function(Te,V_T){
-m <- length(Te)
-wt_FE=1/V_T
-T_FE <- sum(Te*wt_FE)/sum(wt_FE)
-Q <- sum(wt_FE*(Te - T_FE)^2)
-S1 <- sum(wt_FE)
-S2 <- sum(wt_FE^2)
-o2 <- (Q - (m - 1))/(S1 - S2/S1)
-wt_RE <- 1/(V_T + o2)
-T_RE <- sum(Te*wt_RE)/sum(wt_RE)
-V_T_RE_mod <- 1/sum(wt_RE)
-V_T_RE_rve <- (m/(m-1))*sum(wt_RE^2*(Te - T_RE)^2)/(sum(wt_RE))^2
-c(m,T_RE,o2,V_T_RE_mod, V_T_RE_rve)
-}

### 2020-05-06 manuscript/figures/fig-one.R

@@ -1,5 +1,15 @@
-fig <- ggprisma::ggprisma(retrieved = 131, included = 18, duplicates = 35, full_text = 23, wrong_intervention = 3, wrong_comparator = 2, wrong_design = 1, awaiting_classification = 2)
+fig <- ggprisma::ggprisma(retrieved = 131, included = 16, 
+                          duplicates = 35, full_text = 23, 
+                          wrong_intervention = 5, 
+                          wrong_comparator = 2, 
+                          wrong_design = 1, 
+                          awaiting_classification = 2)
 
-ggsave(plot = fig, device = "pdf", filename = "manuscript/figures/fig-one.pdf")
+ggsave(plot = fig, device = "pdf", filename = "manuscript/figures/fig-one.pdf",
+       height = 234, width = 174, units = "mm")
+
+ggplot2::ggsave(plot = fig, device = "png", filename = "manuscript/figures/fig-one.png",
+       height = 234, width = 174, units = "mm", dpi=600)
+
 
 ggsave(plot = fig, device = "tiff", filename = "manuscript/figures/fig-one.tiff", width=7.5, height=7, units='in', dpi=600, compression = 'lzw')

### 2020-05-06 manuscript/figures/fig-two.R

@@ -1,6 +1,51 @@
+### curves
+library(ggplot2)
 library(gofer)
-gofer <- gofer::gofer(data = data_core, ma_effect = ma_core$effect_estimate,
-                      ma_lower =  ma_core$lower_limit, ma_upper = ma_core$upper_limit, 
-                      data_age = data_core_age, grade_rating = "Moderate")
-ggplot2::ggsave(gofer, device = "tiff", filename = "fig-two.tiff",
-                height=14, width=20, units = "in")
+bias=data_core$bias
+s2_unb = data_core$s2
+pooled_bias = primary$bias_mean
+pooled_sd = primary$sd2_est
+pooled_tau2 = primary$tau_est
+pooled_sd = sqrt(pooled_sd^2 + pooled_tau2)
+
+LOA_l = primary$LOA_L
+LOA_u = primary$LOA_U
+LOA_l_CI = primary$CI_L_rve
+LOA_u_CI = primary$CI_U_rve
+g <- ggplot(data.frame(x=seq(-20,20,length=200)), aes(x=x)) + 
+  stat_function(fun=dnorm, args = list(bias[1], sd=sqrt(s2_unb[1])), colour = "cornflowerblue", size=0.6, alpha = 0.5) 
+
+for (i in 2:length(bias)){
+  g <- g + stat_function(fun=dnorm, args = list(bias[i], sd=sqrt(s2_unb[i])), color = "cornflowerblue", size = 0.6, alpha = 0.5)
+} 
+
+g <- g + stat_function(fun=dnorm, args = list(pooled_bias, pooled_sd), colour ="lightcoral", alpha = 0.05) + 
+  stat_function(fun=dnorm, args = list(pooled_bias, pooled_sd), colour = NA, geom="area", fill="lightcoral", alpha = 0.6) + 
+  scale_x_continuous(limits = c(-3.5,3.5), breaks = c(-2, -1, 0, 1, 2)) + 
+  labs(x = expression('Difference between core and ZHF temperature measurements in'*~degree*C*''),
+       caption = "Blue curves are distributions of the differences between measurements from zero-heat-flux sensors and core\ntemperature measurements in individual studies. The red curve is the distribution of the pooled estimate.")+
+  scale_y_continuous(name = "Density \n", limits = c(0,2.5)) +  
[…]

### 2020-05-06 manuscript/figures/rob_plots.R

@@ -1,0 +1,24 @@
+library(tidyverse)
+library(gofer)
+library(robvis)
+library(magrittr)
+RoB <- data_core %>%
+  dplyr::bind_rows(data_SL) %>%
+  dplyr::bind_rows(data_NPA) %>%
+  dplyr::select(Study, RoB_selection, RoB_spoton, RoB_comparator, RoB_flow) %>%
+  dplyr::mutate(RoB_overall = dplyr::if_else(RoB_selection == "low" &
+                                               RoB_spoton == "low" &
+                                               RoB_comparator == "low" &
+                                               RoB_flow == "low", "low", "high"))
+
+RoB[RoB == "unclear"] <- "some concerns"
+
+rob_summary(data = RoB, tool = "QUADAS-2", weighted = FALSE)
+
+ggsave(device = "png", filename = "manuscript/figures/rob-summary.png")
+
+
+rob_traffic_light(data = RoB, tool = "QUADAS-2")
+
+ggsave(device = "pdf", filename = "manuscript/figures/fig2.pdf",
+       height = 234, width = 174, units = "mm")

### 2020-05-06 manuscript/figures/table-1.R

@@ -1,24 +1,0 @@
-gt <- df %>% 
-  rename(" " = Comparison, "Mean bias" = bias_mean, "Variance" = sd2_est, 
-         "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, 
-         "Upper bound for 95% limits of agreement" = LOA_U, 
-         "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, 
-         "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve) %>% 
-  gt() %>%
-  tab_header(
-    title = "Table 1. Results of meta-analyses"  )  %>%
-  tab_spanner(
-    label = "Population limits of agreement",
-    columns = vars(
-      `Outer confidence interval for lower 95% limits of agreement`, `Outer confidence interval for upper 95% limits of agreement`)
-  )
-
-gtsave(data = gt, filename = "table_gt.pdf", vwidth = 600)
-
-library(flextable)
-df %>% %>% 
-  rename(" " = Comparison, "Mean bias" = bias_mean, "Variance" = sd2_est, 
-         "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, 
-         "Upper bound for 95% limits of agreement" = LOA_U, 
-         "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, 
-         "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve) %>% flextable()

### 2020-05-06 manuscript/manuscript.Rmd
officedown

@@
 library(ggprisma) # https://github.com/awconway/ggprisma
-library(kableExtra)
 library(knitr)

### 2020-05-06 manuscript/manuscript.Rmd
dockerfile for dockerhub

@@
 data_NPA$comparison <- sub("NPA", "Nasopharyngeal", data_NPA$comparison) 
+data_NPA$Study <- sub("West, 2018", "West, 2019", data_NPA$Study)
+
 data_core$comparison <- sub("PA", "Pulmonary artery", data_core$comparison) 
@@
 data_core$patients <- sub("Laparosopic Surgery", "Laparoscopy Surgery", data_core$patients)
+
+data_NPA_age <- gofer::data_NPA_age
+data_NPA_age$Study <- sub("West, 2015", "West, 2019", data_NPA_age$Study)
+
+data_NPA <- data_NPA_age %>% 
+  tidyr::pivot_wider(names_from = c(age_type, age_measure),
+                    values_from = age) %>% 
+  dplyr::rename(mean_age = mean_sd_average,
+         lower_mean = mean_sd_lower,
+         upper_mean = mean_sd_upper,
+         median_age = median_iqr_average,
+         lower_IQR = median_iqr_lower,
+         upper_IQR = median_iqr_upper) %>% 
+  left_join(data_NPA)
+
+data_SL_age <- gofer::data_SL_age
+data_SL_age$Study <- sub("West, 2015", "West, 2019", data_SL_age$Study)
+
+data_SL$Study <- sub("West, 2018", "West, 2019", data_SL$Study)
+
+data_SL <- data_SL_age %>% 
+  tidyr::pivot_wider(names_from = c(age_type, age_measure),
+                    values_from = age) %>% 
+  dplyr::rename(mean_age = mean_sd_average,
+         lower_mean = mean_sd_lower,
+         upper_mean = mean_sd_upper,
+         median_age = median_iqr_average,
+         lower_IQR = median_iqr_lower,
+         upper_IQR = median_iqr_upper) %>% 
+  left_join(data_SL)
 
@@
 ft <- merge_at(ft, part = "body", i=~Study=="West", j = "temp_range")
+
+ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "patients")
+ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "perc_male")
+ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "age")
+ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "code")
+ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "temp_range")
+ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "n")
+ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "N")
 

### 2020-05-06 manuscript/manuscript.Rmd
include figs param

@@
 always_allow_html: true
+params:
+  include_figs: false
 ---
@@
 library(dplyr)
+library(ggplot2)
+library(robvis)
 library(ggprisma) # https://github.com/awconway/ggprisma
@@
 ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "temp_range")
-ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "n")
-ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "N")
+# ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "n")
+# ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "N")
 
@@
 ft <- merge_at(ft, part = "body", i=~Study=="Pesonen", j = "temp_range")
-ft <- merge_at(ft, part = "body", i=~Study=="Pesonen", j = "n")
-ft <- merge_at(ft, part = "body", i=~Study=="Pesonen", j = "N")
+# ft <- merge_at(ft, part = "body", i=~Study=="Pesonen", j = "n")
+# ft <- merge_at(ft, part = "body", i=~Study=="Pesonen", j = "N")
 
@@
 ft <- merge_at(ft, part = "body", i=~Study=="Makinen", j = "temp_range")
-ft <- merge_at(ft, part = "body", i=~Study=="Makinen", j = "N")
+# ft <- merge_at(ft, part = "body", i=~Study=="Makinen", j = "N")
 
@@
 ```
+
+\pagebreak
+
+```{r fig.cap="Fig. 1", include=params$include_figs, eval=params$include_figs}
+ggprisma::ggprisma(retrieved = 131, included = 16, 
+                          duplicates = 35, full_text = 23, 
+                          wrong_intervention = 5, 
+                          wrong_comparator = 2, 
+                          wrong_design = 1, 
+                          awaiting_classification = 2)
+```
+
+\pagebreak
+
+```{r fig.cap="Fig. 2", include=params$include_figs, eval=params$include_figs}
+RoB <- data_core %>%
+  dplyr::bind_rows(data_SL) %>%
+  dplyr::bind_rows(data_NPA) %>%
+  dplyr::select(Study, RoB_selection, RoB_spoton, RoB_comparator, RoB_flow) %>%
+  dplyr::mutate(RoB_overall = dplyr::if_else(RoB_selection == "low" &
+                                               RoB_spoton == "low" &
+                                               RoB_comparator == "low" &
+                                               RoB_flow == "low", "low", "high"))
+RoB[RoB == "unclear"] <- "some concerns"
+robvis::rob_traffic_light(data = RoB, tool = "QUADAS-2")
+```
+
+\pagebreak
+
+```{r fig.cap="Fig. 3", include=params$include_figs, eval=params$include_figs}
+bias=data_core$bias
+s2_unb = data_core$s2
+pooled_bias = primary$bias_mean
+pooled_sd = primary$sd2_est
+pooled_tau2 = primary$tau_est
+pooled_sd = sqrt(pooled_sd^2 + pooled_tau2)
+
+LOA_l = primary$LOA_L
+LOA_u = primary$LOA_U
+LOA_l_CI = primary$CI_L_rve
+LOA_u_CI = primary$CI_U_rve
+g <- ggplot(data.frame(x=seq(-20,20,length=200)), aes(x=x)) + 
+  stat_function(fun=dnorm, args = list(bias[1], sd=sqrt(s2_unb[1])), colour = "cornflowerblue", size=0.6, alpha = 0.5)
+
+for (i in 2:length(bias)){
+  g <- g + stat_function(fun=dnorm, args = list(bias[i], sd=sqrt(s2_unb[i])), color = "cornflowerblue", size = 0.6, alpha = 0.5)
+}
+
+g <- g + stat_function(fun=dnorm, args = list(pooled_bias, pooled_sd), colour ="lightcoral", alpha = 0.05) + 
+  stat_function(fun=dnorm, args = list(pooled_bias, pooled_sd), colour = NA, geom="area", fill="lightcoral", alpha = 0.6) + 
+  scale_x_continuous(limits = c(-3.5,3.5), breaks = c(-2, -1, 0, 1, 2)) + 
+  labs(x = expression('Difference between core and ZHF temperature measurements in'*~degree*C*''),
+       caption = "Blue curves are distributions of the differences between measurements from zero-heat-flux sensors and core\ntemperature measurements in individual studies.
+The red curve is the distribution of the pooled estimate.")+
+  scale_y_continuous(name = "Density \n", limits = c(0,2.5)) +  
+  #labs(title = "\nOuter confidence intervals for pooled limits of agreement\n\n  Pooled limits of agreement")+
+  theme(plot.title = element_text(hjust = 0.5, margin = margin(t=10, b=-32), size=10),
+        axis.text=element_text(hjust = 0.5, size=10),                                                                        
+        axis.title=element_text(hjust = 0.5, size=10),
+        axis.line=element_line(colour="black", size=0.2),
+        panel.background = element_blank(),
+        axis.ticks = element_blank(), 
+        plot.caption = element_text(hjust = 0)) #+ 
+#CI lines that extend to arrow tips
+# geom_segment(aes(x=LOA_u, y=0, xend=LOA_u, yend=2.25), size = 0.3, linetype="dashed")+ 
+# geom_segment(aes(x=LOA_l, y=0, xend=LOA_l, yend=2.25), size = 0.3, linetype="dashed")+
+# geom_segment(aes(x=LOA_u_CI, y=0, xend=LOA_u_CI, yend=2.48), size = 0.3)+
+# geom_segment(aes(x=LOA_l_CI, y=0, xend=LOA_l_CI, yend=2.48), size = 0.3)#+
+# 
+# geom_segment(aes(x=0, y=2.48, xend=LOA_u_CI, yend=2.48), size = 0.4, arrow = arrow(length = unit(0.03, "npc")))+ #R arrow high
+# geom_segment(aes(x=0, y=2.48, xend=LOA_l_CI, yend=2.48), size = 0.4, arrow = arrow(length = unit(0.03, "npc")))+ #L arrow high
+# geom_segment(aes(x=0, y=2.25, xend=LOA_u, yend=2.25), size = 0.4,  arrow = arrow(length = unit(0.03, "npc")))+ #R arrow low
+# geom_segment(aes(x=0, y=2.25, xend=LOA_l, yend=2.25), size = 0.4,  arrow = arrow(length = unit(0.03, "npc"))) #L arrow low
+g
+
+```

### 2020-05-08 manuscript/manuscript.Rmd
release for zenodo

--- 2020-05-06 manuscript/manuscript.Rmd
@@
       - --lua-filter=Extras/author-info-blocks.lua
-always_allow_html: true
+params:
+  include_figs: false
 ---
@@
 library(flextable)
+library(officer)
+library(officedown)
 ```
@@
 
-The range of uncertainty in the accuracy of the zero-heat-flux thermometer should be taken into account when using this device to inform clinical decision-making.
+The range of uncertainty in the accuracy of a thermometer should be taken into account when using this device to inform clinical decision-making.
 Clinicians should therefore consider the potential that a temperature measurement from a 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System could be as much as 1°C higher or lower than core temperature.
@@
 
-Code availability: All data used in the meta-analyses is available [here](https://github.com/awconway/zhf-review).
+Code availability: All data used in the meta-analyses is available [here](https://github.com/awconway/zhf-review) and archived [here]().
 
@@
 Continuous core temperature monitoring is commonly used within perioperative and intensive care settings.
-Thermoregulatory dysfunction is associated with the induction of anesthesia and can lead to adverse outcomes including cardiac arrhythmia, altered hemostasis and increased risk of surgical site infection.[@frank1997perioperative; @kurz1996perioperative; @michelson1994reversible; @rohrer1992effect] The pulmonary artery catheter is the reference standard for continuous core temperature monitoring, however, the invasive nature of this method renders an increased risk of bloodstream infections and damage to surrounding tissue.[@hadian2006evidence] Although clinically accurate relative to pulmonary artery temperature measurements, surrogate measures of core temperature at esophageal, rectal, and bladder locations remain mildly invasive interventions.
+Thermoregulatory dysfunction is associated with the induction of anesthesia and can lead to adverse outcomes including cardiac arrhythmia, altered hemostasis and increased risk of surgical site infection.[@frank1997perioperative; @kurz1996perioperative; @michelson1994reversible; @rohrer1992effect] The pulmonary artery catheter is the reference standard for continuous core temperature monitoring, however, the invasive nature of this method renders an increased risk of bloodstream infections and damage to surrounding tissue.[@hadian2006evidence] Although accurate relative to pulmonary artery temperature measurements, surrogate measures of core temperature at esophageal, rectal, and bladder locations remain mildly invasive interventions.
 
-Zero-heat-flux thermometry is an alternative non-invasive method that allows for continuous monitoring of core temperature.
-Zero-heat-flux sensors are placed on the lateral surface of the forehead and is initially warmed to equilibrate the temperature of the skin surface to the underlying core tissues.
-Equipped with a thermal insulator, the zero-heat-flux sensor eliminates heat loss to the environment to allow for changes in core temperature to be directly reflected by a change in skin surface temperature.[@eshraghi2014] Originally developed in the 1970s, zero-heat-flux technology was recently implemented in the the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System (3M^TM^, St Paul, MN), as a single-use, disposable sensor.
+Zero-heat-flux thermometry is an alternative non-invasive method that allows for continuous temperature monitoring from the skin surface.
+Unlike other commonly used non-invasive thermometers such as infrared aural canal and temporal devices, the zero-heat-flux device does not apply a correction factor.
+As such, it is classified as an indirect *measurement* of core temperature, not an indirect *estimate*.[@riley2018inadvertent]  Zero-heat-flux thermometers consist of a thermal insulator positioned between two thermistors, which are covered by a heating component.
+The heater is initially warmed to equilibrate with skin surface temperature.
+By eliminating heat loss to the environment, skin surface temperature closely reflects the temperature at a depth of about 1 to 2 cm below the location of the thermometer.[@eshraghi2014]  It has been confirmed that zero-heat-flux thermometers can provide an accurate substitute for core temperature monitoring.[@Sessler_2008]  A comprehensive review of this method of temperature measurement, which was originally developed in the 1970s, is available.[@yamakage2003deep]
+
+A new generation of zero-heat-flux thermometers are now approved for use within perioperative and intensive care settings.
+The accuracy of temperature measurements from this latest generation of devices has been investigated in multiple studies over the last five years.
+The 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System (3M^TM^, St Paul, MN) was the zero-heat-flux device used in most of these studies.
 This device was previously known as the SpotOn Temperature Monitoring System.
-Another device on the market is the T-core sensor from Dräger.
-
-The agreement between temperature measurements from zero-heat-flux thermometers and core as well as other peripheral thermometers has been investigated in multiple studies over the last five years.
-The 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System, has been the zero-heat-flux device used in most of these recent studies.
+It is a single-use, disposable sensor, which is recommended to be positioned on the lateral surface of the forehead, as this is one of the locations in the body where subcutaneous temperature approximates core temperature.
 Appraisal and synthesis of the results would aid clinicians in deciding the appropriate circumstances in which this particular zero-heat-flux thermometer may be used.
-We aimed to determine if 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System has clinically acceptable accuracy and precision relative to established core and peripheral temperature measurement devices.
+We aimed to determine if the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System has clinically acceptable accuracy and precision relative to established core and peripheral temperature measurement devices.
 Accuracy is defined as the average difference between temperature measurements from the zero-heat-flux and comparator device and precision as the variance (standard deviation) in the differences.
@@
 
-\pagebreak
-
 ## Results
@@
 
-Detailed characteristics of included studies is displayed in Table 1.
-The primary comparison of the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System versus core temperature measurements (eg, arterial, bladder, esophageal or rectal) consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies.[@Boisson_2018; @Carvalho_2019; @Dahyot_Fizelier_2017; @eshraghi2014; @G_mez_Romero_2019; @idei2016; @Jack_2019; @Kato_2015; @kollmann2019validation; @M_kinen_2016; @Morettini_2019; @Pesonen_2018; @Schell_Chaple_2018; @Tachibana_2019; @G_mez_Romero_2019] In total, data from `r primary$Participants` participants with `r format(primary$Measurements, scientfic=F)` paired measurements were included in this comparison (two studies did not report the total number of measurements included in their analysis).
+A summary of the characteristics of included studies is displayed in Table 1.
+The primary comparison of the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System versus core temperature measurements (eg, arterial, bladder, esophageal or rectal) consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies.[@Boisson_2018; @Carvalho_2019; @Dahyot_Fizelier_2017; @eshraghi2014; @G_mez_Romero_2019; @idei2016; @Jack_2019; @Kato_2015; @kollmann2019validation; @M_kinen_2016; @Morettini_2019; @Pesonen_2018; @Schell_Chaple_2018; @Tachibana_2019] In total, data from `r primary$Participants` participants with `r format(primary$Measurements, scientfic=F)` paired measurements were included in this comparison (two studies did not report the total number of measurements included in their analysis).
 The sensitivity analysis for the primary comparison with only studies that were assessed as low risk of bias across all domains included `r low_risk$Comparisons` comparisons from `r low_risk$Studies` studies that enrolled `r low_risk$Participants` participants with `r low_risk$Measurements` paired measurements (two studies did not report the total number of measurements included in their analysis).
@@
 
-Table 1 presents results of the primary, sensitivity and all subgroup analyses for the primary comparison as well as secondary comparisons.
+Table 2 presents results of the primary, sensitivity and all subgroup analyses for the primary comparison as well as secondary comparisons.
 The pooled estimate for the mean bias between the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System and core temperature measurements was `r primary$bias_mean`°C.
@@
 The amount of between-study heterogeneity is displayed graphically in the density plot in Figure 3.
-The quality of evidence for the primary comparison was downgraded to low quality due to concerns about study limitations and inconsistency.
+The quality of evidence for the primary comparison was downgraded to moderate quality due to concerns about study limitations.
 Population limits of agreement for the sensitivity analysis restricted to studies rated as having low risk of bias across all the domains of the QUADAS-2 were similar to the primary analysis (`r low_risk$Measurements` measurements; `r low_risk$Participants` participants; `r low_risk$Studies` studies).
@@
 It should be noted that we did not include studies that used the Temple Touch Pro because it is not strictly a zero-heat-flux device.
-This is a new thermometer that is similar to the zero-heat-flux device in that it is placed cutaneously, but the underlying technology is different.[@evron2017evaluation] Likewise, studies that evaluated the Drager Tcore device were not included because this review focused specifically on the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System.
+This is a new thermometer that is similar to the zero-heat-flux device in that it is placed cutaneously, but the underlying technology is different.[@evron2017evaluation] Likewise, studies that evaluated the Dräger Tcore device were not included because this review focused specifically on the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System.
 
@@
 The evidence from this review should be considered in the context of other information about the reliability and ease of use of this device.
+For example, the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System permits use of the same temperature monitoring device to be used throughout the whole perioperative care pathway.
+As such, use of this device during the pre and post-operative period to replace indirect estimates of core temperature, such as infrared tympanic and temporal devices, which are not recommended for use in surgical patients[@riley2018inadvertent] yet are commonly used because of convenience, may be an advantage.
+
+Finally, our initial protocol was focused on the accuracy of zero-heat-flux temperature measurements in general, not the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System specifically.
+A decision was made after data extraction and analysis was conducted to revise our inclustion criteria and include only studies that reported on the accuracy of the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System for this particular report.
+This decision was made because of the potential that differences in the technology integrated into zero-heat-flux devices produced by different manufacturers (i.e.
+3M^TM^ Bair Hugger^TM^ Temperature Monitoring System and the Dräger Tcore) will influence estimates about the accuracy of zero-heat-flux devices overall.
+Although revising the inclusion criteria must be considered a limitation, this decision permitted a more targeted evaluation of the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System and easier interpretation of results.
 
@@
 
-\pagebreak
+<!---BLOCK_MULTICOL_START--->
 
-### Table 1: Study Characteristics
+<!---BLOCK_STOP--->
+
+<!--BLOCK_LANDSCAPE_START--->
+
+## Table 1: Study Characteristics
 
@@
   dplyr::mutate(N= tidyr::replace_na(N, 0)) %>% 
-    dplyr::mutate(lower_temp= tidyr::replace_na(lower_temp, 0)) %>% 
-  dplyr::mutate(upper_temp= tidyr::replace_na(upper_temp, 0)) %>% 
     dplyr::mutate(age = ifelse(!is.na(mean_age), 
@@
     dplyr::mutate(temp_range = glue::glue("{lower_temp}-{upper_temp}")) %>%
-
-     dplyr::select(Year, Study, code, patients, perc_male, age, comparison, n, N, 
+    dplyr::mutate(n1=n) %>% 
+  dplyr::mutate(N1=N) %>% 
+     dplyr::select(Year, Study, code, patients, perc_male, age, comparison, n,n1, N,N1, 
            temp_range) %>%
@@
   value = as_paragraph(as_image( 
-    src = flagon::flags("US", filetype = "png"),
+    src = "Extras/flags/US.png",
     width = .20, height = .15))
@@
   value = as_paragraph(as_image( 
-    src = flagon::flags("FI", filetype = "png"),
+    src = "Extras/flags/FI.png",
     width = .20, height = .15))
@@
   value = as_paragraph(as_image( 
-    src = flagon::flags("FR", filetype = "png"),
+    src = "Extras/flags/FR.png",
     width = .20, height = .15))
@@
   value = as_paragraph(as_image( 
-    src = flagon::flags("BE", filetype = "png"), 
+    src = "Extras/flags/BE.png", 
     width = .20, height = .15))
@@
   value = as_paragraph(as_image( 
-    src = flagon::flags("ES", filetype = "png"), 
-    width = .20, height = .15))
-)
-
-ft <- compose(ft, i=~code=="BE", j = "code",
-  value = as_paragraph(as_image( 
-    src = flagon::flags("BE", filetype = "png"), 
+    src = "Extras/flags/ES.png", 
     width = .20, height = .15))
@@
   value = as_paragraph(as_image( 
-    src = flagon::flags("GB", filetype = "png"), 
+    src = "Extras/flags/GB.png", 
     width = .20, height = .15))
@@
   value = as_paragraph(as_image( 
-    src = flagon::flags("JP", filetype = "png"), 
+    src = "Extras/flags/JP.png", 
     width = .20, height = .15))
@@
   value = as_paragraph(as_image( 
-    src = flagon::flags("IT", filetype = "png"), 
+    src = "Extras/flags/IT.png", 
     width = .20, height = .15))
@@
   value = as_paragraph(as_image( 
-    src = flagon::flags("DE", filetype = "png"), 
+    src = "Extras/flags/DE.png", 
     width = .20, height = .15))
@@
   value = as_paragraph(as_image( 
-    src = flagon::flags("CA", filetype = "png"), 
+    src = "Extras/flags/CA.png", 
     width = .20, height = .15))
@@
 
-ft <- compose( ft, j = "n",   value = as_paragraph(as_chunk(format(n)), "    ",
+ft <- compose( ft, j = "n1",   value = as_paragraph(
   minibar(value = n, barcol = "#930093")
@@
 
-ft <- compose( ft, j = "N",   value = as_paragraph(as_chunk(format(N)), "    ",
+ft <- compose( ft, j = "N1",   value = as_paragraph(
   lollipop(rangecol = "white",positivecol ="#930093", value = log(N), min=0, max=log(max(N)))
@@
     src = "figures/sex.png",
-    width = .20, height = .15)),
+    width = .4, height = .3)),
   part="header"
@@
   fix_border_issues() %>% 
-  add_header_row(values = c("Study","Participants", "Temperature measurements"),  colwidths = c(4, 2 , 4)) %>% 
+  add_header_row(values = c("Study","Participants", "Temperature measurements"),  colwidths = c(4, 2 , 6)) %>% 
   align(align = "center", part = "header") %>% 
@@
   color(i=1, j=5:6, part="header", color="white")  %>% 
-  bg(i=1, j=7:10, part="header", bg="#930093") %>% 
-  color(i=1, j=7:10, part="header", color="white")  %>% 
+  bg(i=1, j=7:12, part="header", bg="#930093") %>% 
+  color(i=1, j=7:12, part="header", color="white")  %>% 
   empty_blanks() %>% 
@@
                     patients = "", age= "Age (years)",
-                    comparison = "", n = "Participants",
-                    N = "Measurements", temp_range = "Range (°C)") %>% 
+                    comparison = "", n1 = "Participants",
+                    N1 = "Measurements", temp_range = "Range (°C)",
+                    n="", N="") %>% 
   border_remove() %>% 
@@
             border = officer::fp_border(color="black", width = 1))  %>% 
-  bg(j=~comparison + temp_range + n+N, bg="lightgray") %>% 
+  bg(j=7:12, bg="lightgray") %>% 
   hline( i =2, part = "header", 
@@
   width(j="comparison",width = 1.18) %>%
-  width(j="n",width = 1.75) %>%
-  width(j="N",width = 1.81) %>%
-  width(j="temp_range",width = 0.65)
+  width(j="n",width = 0.38) %>%
+  width(j="n1",width = 1.16) %>%
+  width(j="N",width = 0.63) %>%
+  width(j="N1",width = 1.19) %>% 
+  width(j="temp_range",width = 0.65) %>% 
+  footnote(i =2, j = 6,
+               value = as_paragraph(
+                "mean (standard deviation) or median [interquartile range]"
+               ),
+               ref_symbols = "a",
+               part = "header")
 
@@
 
-```{r }
+```{r tab.style='table-flex'}
   ma <- list(primary, low_risk, ICU, OT,  NPA,SL, conflict)
@@
 ```
+
+<!---BLOCK_LANDSCAPE_STOP--->

### 2020-05-08 manuscript/manuscript.Rmd
R1 submitted

@@
 
-Code availability: All data used in the meta-analyses is available [here](https://github.com/awconway/zhf-review) and archived [here]().
+Code availability: All data used in the meta-analyses is available [here](https://github.com/awconway/zhf-review) and archived [here](https://doi.org/10.5281/zenodo.3817610).
 

### 2020-05-20 manuscript/manuscript.Rmd
R2 for JCMC

@@
   dplyr::filter(comparison == "NPA")
-
-data_SL <- data %>% 
-  dplyr::filter(comparison == "Sublingual")
+# 
+# data_SL <- data %>% 
+#   dplyr::filter(comparison == "Sublingual")
 
 #eshragi overall
+
 data_core <- data %>% 
+    dplyr::filter(comparison=="PA"|
+                    comparison=="Bladder"|
+                    comparison=="Eso" | 
+                    comparison =="Rectal"|
+                    comparison =="Ax"|
+                    comparison =="Iliac" | 
+                    comparison == "NOPA" |
+                    (Study=="Iden, 2015"& comparison == "NPA")) %>%
+  dplyr::filter(comments != "Intraoperative, off cardiopulmonary bypass" & comments != "Postoperative")
+
+data_core_no_npa <- data %>% 
   dplyr::filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
@@
 data_core_op <- data %>% #eshragi intraop
-    dplyr::filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
+    dplyr::filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac"|
+                                        comparison == "NOPA" |
+                    (Study=="Iden, 2015"& comparison == "NPA")) %>%
   dplyr::filter (clinical_setting=="Intraoperative")
@@
 data_core_icu <- data %>% #eshragi postop
-      dplyr::filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
+      dplyr::filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac" |
+                                          comparison == "NOPA" |
+                    (Study=="Iden, 2015"& comparison == "NPA")) %>%
   dplyr::filter(clinical_setting=="ICU" | clinical_setting=="Postoperative")
@@
 NPA  <- format_results(data_NPA)
+core_no_npa <- format_results(data_core_no_npa)
 ```
@@
 ```{r SL, include=FALSE}
-SL  <- format_results(data_SL)
+# SL  <- format_results(data_SL)
 ```
@@
 
-Eighteen studies were included.
+Sixteen studies were included.
 The primary meta-analysis of zero-heat-flux versus core temperature consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies.
@@
 A systematic review was conducted.
-The primary comparison for this review was zero-heat-flux temperature measured using the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System versus temperature measured from a core site, which we defined as temperature measured at either an arterial, esophageal, bladder or rectal site.
-Secondary comparisons were made between temperatures measured using the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System and temperatures taken at peripheral sites.
+The primary comparison for this review was zero-heat-flux temperature measured using the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System versus temperature measured from a core site, which we defined as temperature measured at either an arterial, esophageal, bladder, rectal, nasopharyngeal or oropharyngeal site.
 
@@
 This was achieved by using weights proportional to the number of participants, not the total number of measurements.
-The R statistical program was used to conduct all analyses.[@R2018] All data and R code used in the meta-analyses is available [here](https://github.com/awconway/zhf-review).
+The R statistical program was used to conduct all analyses.[@R2018] All data and R code used in the meta-analyses is available [here](https://github.com/awconway/zhf-review) and archived [here](https://doi.org/10.5281/zenodo.3817610).
 
@@
 In several studies, results were reported for multiple groups of participants, therefore in the meta-analysis each of these groups was treated as a separate 'comparison'.[@Boisson_2018; @Dahyot_Fizelier_2017; @Schell_Chaple_2018; @M_kinen_2016] Other studies reported multiple sets of results, whereby analyses were conducted between zero-heat-flux and various comparator devices used on the same participant.
-These instances were also treated as a separate 'comparison' if the comparator devices were a part of separate meta-analysis groups.[@West_2019; @Pesonen_2018; @M_kinen_2016; @Iden_2015] One study reported intraoperative, postoperative and overall results for the same participants[@eshraghi2014].
+These instances were also treated as a separate 'comparison' if the comparator devices were a part of separate meta-analysis groups.[@West_2019; @Pesonen_2018; @M_kinen_2016; @Iden_2015] One study used both nasopharyngeal and oropharyngeal temperature as comparators.[@West_2019] Both combined and separate estimates were reported.
+We used the combined estimate in our primary analysis and the estimate for just the nasopharyngeal temperatures in a subgroup analysis.
+One study reported intraoperative, postoperative and overall results for the same participants[@eshraghi2014].
 Only the paired measurements from the overall results were included in the main and low risk bias analyses, leaving paired measurements exclusively from the intraoperative and postoperative timepoints to be included in respective meta-analyses subgroups.
-
 The conventionally cited clinically acceptable agreement between zero-heat-flux and comparator devices is 0.5°C.[@eshraghi2014] It was deemed that outer confidence bounds for 95% limits of agreement between zero-heat-flux and core temperature measurements (termed as ‘population limits of agreement’) outside of these bounds would be clinically unacceptable.
@@
 We also conducted a sensitivity analysis for the primary comparison (zero-heat-flux versus temperature measurement at core site) excluding studies that received funding from industry.
+Probe insertion distance for temperature measurements from the nasopharynx and oropharynx may impact accuracy.[@Lim_2016] For this reason, we also conducted a separate analysis excuding these comparators and an analysis of the studies that compared temperature measurements from the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System with nasopharyngeal temperature.
 As clinicians would be interested in the accuracy of zero-heat-flux relative within the clinical setting in which they use it, we conducted subgroup analyses for the primary comparison according to clinical setting of the study (either intraoperative or intensive care unit).
@@
 A summary of the characteristics of included studies is displayed in Table 1.
-The primary comparison of the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System versus core temperature measurements (eg, arterial, bladder, esophageal or rectal) consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies.[@Boisson_2018; @Carvalho_2019; @Dahyot_Fizelier_2017; @eshraghi2014; @G_mez_Romero_2019; @idei2016; @Jack_2019; @Kato_2015; @kollmann2019validation; @M_kinen_2016; @Morettini_2019; @Pesonen_2018; @Schell_Chaple_2018; @Tachibana_2019] In total, data from `r primary$Participants` participants with `r format(primary$Measurements, scientfic=F)` paired measurements were included in this comparison (two studies did not report the total number of measurements included in their analysis).
+The primary comparison of the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System versus core temperature measurements consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies.[@Boisson_2018; @Carvalho_2019; @Dahyot_Fizelier_2017; @eshraghi2014; @G_mez_Romero_2019; @idei2016; @Jack_2019; @Kato_2015; @kollmann2019validation; @M_kinen_2016; @Morettini_2019; @Pesonen_2018; @Schell_Chaple_2018; @Tachibana_2019; @West_2019; @Iden_2015] In total, data from `r primary$Participants` participants with `r format(primary$Measurements, scientfic=F)` paired measurements were included in this comparison (two studies did not report the total number of measurements included in their analysis).
 The sensitivity analysis for the primary comparison with only studies that were assessed as low risk of bias across all domains included `r low_risk$Comparisons` comparisons from `r low_risk$Studies` studies that enrolled `r low_risk$Participants` participants with `r low_risk$Measurements` paired measurements (two studies did not report the total number of measurements included in their analysis).
@@
 Nasopharyngeal thermometers were used as the comparator devices in `r NPA$Studies` studies, with `r NPA$Measurements` paired measurements from `r NPA$Participants` participants.
-Sublingual thermometers were used as the comparator devices in `r SL$Studies` studies that reported `r SL$Measurements` paired measurements from `r SL$Participants` participants.
 Supplementary information presented in the study [webpage](https://zhf-info.netlify.app) provides comprehensive summaries of the studies included in each of these meta-analyses.
@@
 
-### Primary comparison: 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System versus core thermometers
+### Primary comparison
 
-Table 2 presents results of the primary, sensitivity and all subgroup analyses for the primary comparison as well as secondary comparisons.
+Table 2 presents results of the primary, sensitivity and all subgroup analyses.
 The pooled estimate for the mean bias between the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System and core temperature measurements was `r primary$bias_mean`°C.
@@
 The quality of evidence for the primary comparison was downgraded to moderate quality due to concerns about study limitations.
+
+### Sensitivity analyses
+
 Population limits of agreement for the sensitivity analysis restricted to studies rated as having low risk of bias across all the domains of the QUADAS-2 were similar to the primary analysis (`r low_risk$Measurements` measurements; `r low_risk$Participants` participants; `r low_risk$Studies` studies).
@@
 The evidence rating for this sensitivity analysis was downgraded to low quality though, due to concerns about study limitations, inconsistency and imprecision.
+
+To investigate if results were sensitive to our decision about which  temperature monitoring sites to include in the primary analysis, we conducted a separate analysis excluding any naso/oropharyngeal comparisons.
+Results were similar to the primary analysis (`r glue::glue("mean bias {core_no_npa$bias_mean}°C with population limits of agreement from {core_no_npa$CI_L_rve} to {core_no_npa$CI_U_rve}°C)")`.
+The mean bias between 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System and nasopharyngeal temperature measurements in meta-analysis of results from `r NPA$Studies` studies was `r NPA$bias_mean`°C.
+Population limits of agreement were `r NPA$CI_L_rve`°C to `r NPA$CI_U_rve`°C.
+We downgraded the quality of evidence to low, again due to concerns about imprecision and study limitations.
+
+## Subgroup analyses
 
@@
 
-### Secondary comparisons: 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System versus peripheral thermometers
-
-Temperature measurements from the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System  were compared with sublingual and nasopharyngeal temperature measurements in several studies included in this review.
-The mean bias between 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System and nasopharyngeal temperature measurements in meta-analysis of results from `r NPA$Studies` studies was `r NPA$bias_mean`°C.
-Population limits of agreement were `r NPA$CI_L_rve`°C to `r NPA$CI_U_rve`°C.
-We downgraded the quality of evidence to low, again due to concerns about imprecision and study limitations.
-The mean bias between the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System and sublingual temperature measurements in meta-analysis of results from `r SL$Studies` studies was `r SL$bias_mean`°C.
-Due to the limited number of studies and measurements, population limits of agreement were extremely wide, spanning outside physiologically plausible range for temperature.
-As such, they are not reported.
-The quality of evidence for this comparison was rated as very low quality due to serious concerns about imprecision.
-
 \pagebreak
@@
 
-This systematic review showed that a temperature measurement from a 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System device could be as much as 1°C higher or lower than core temperature.
+This systematic review showed that a temperature measurement from a 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System device could be as much as about 1°C higher or lower than core temperature.
 These results may have important implications for practice.
@@
 
-Subgroup analyses revealed insights to direct future research.
+The accuracy of 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System has been evaluated in various intraoperative contexts as well as in the intensive care unit setting.
+Our subgroup analyses did not indicate that the accuracy of this temperature monitoring device was any more effective in a particular setting and revealed insights to direct future research.
 There were fewer participants included in the subgroup of studies conducted in the Intensive Care Unit compared to those conducted during surgery.
@@
 Additional studies are required to increase confidence in the accuracy of 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System device in this setting, where continuous temperature monitoring is often required.
-
-Although comparisons with core temperature are the most important to evaluate, we included studies that compared 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System and peripheral temperature monitoring devices in our review because clinicians may be interested to determine if this new technology is sufficiently accurate to replace other ways to non-invasively monitor temperature.
-Also, there may be situations where it is standard practice for only peripheral temperature monitoring to be used.
-In these circumstances, it is not practical to expose research participants to the potential risks of invasive core temperature monitoring for the purpose of evaluating the new temperature monitoring device.
-Whether or not the zero-heat-flux thermometer is sufficiently accurate to be used in place of nasopharyngeal thermometers is unclear.
-Population limits of agreement calculated from four studies were broad, spanning from 1°C less than zero-heat-flux temperature to one degree higher.
-Further studies are therefore required.
+Also of note, only two studies included in our systematic review included pediatric patients.
+Additional studies to evaluate the accuracy of this device in children may be warranted to increase confidence.
 
@@
 By using robust variance estimation, weights for pooling estimates in the meta-analysis become proportional to the number of patients, not the total number of measurements.[@tipton2017framework]
-
-The accuracy of 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System has been evaluated in various intraoperative contexts as well as in the intensive care unit setting.
-Our subgroup analyses did not indicate that the accuracy of this temperature monitoring device was any more effective in a particular setting.
-Only two studies included in our systematic review included pediatric patients.
-Additional studies to evaluate the accuracy of this device in children may be warranted to increase confidence.
 
@@
 For example, the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System permits use of the same temperature monitoring device to be used throughout the whole perioperative care pathway.
-As such, use of this device during the pre and post-operative period to replace indirect estimates of core temperature, such as infrared tympanic and temporal devices, which are not recommended for use in surgical patients[@riley2018inadvertent] yet are commonly used because of convenience, may be an advantage.
+As such, replacing indirect estimates of core temperature, such as infrared tympanic and temporal devices, may be an advantage of the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System.
+Indirect estimates of core temperature are not recommended for use in surgical patients, yet are commonly used because of convenience.[@riley2018inadvertent]
 
@@
 ```{r }
-data_NPA <- gofer::data_NPA
-data_SL <- gofer::data_SL
+# data_NPA <- gofer::data_NPA
+# data_SL <- gofer::data_SL
 data_core <- gofer::data_core
-data_NPA$comparison <- sub("NPA", "Nasopharyngeal", data_NPA$comparison) 
-data_NPA$Study <- sub("West, 2018", "West, 2019", data_NPA$Study)
-
+# data_NPA$comparison <- sub("NPA", "Nasopharyngeal", data_NPA$comparison) 
+# data_NPA$Study <- sub("West, 2018", "West, 2019", data_NPA$Study) 
+data_core$comparison <- sub("NPA", "Nasopharyngeal", data_core$comparison) 
+data_core$comparison <- sub("NOPA", "Naso or oropharyngeal", data_core$comparison)
 data_core$comparison <- sub("PA", "Pulmonary artery", data_core$comparison) 
@@
 
-data_NPA_age <- gofer::data_NPA_age
-data_NPA_age$Study <- sub("West, 2015", "West, 2019", data_NPA_age$Study)
-
-data_NPA <- data_NPA_age %>% 
-  tidyr::pivot_wider(names_from = c(age_type, age_measure),
-                    values_from = age) %>% 
-  dplyr::rename(mean_age = mean_sd_average,
-         lower_mean = mean_sd_lower,
-         upper_mean = mean_sd_upper,
-         median_age = median_iqr_average,
-         lower_IQR = median_iqr_lower,
-         upper_IQR = median_iqr_upper) %>% 
-  left_join(data_NPA)
-
-data_SL_age <- gofer::data_SL_age
-data_SL_age$Study <- sub("West, 2015", "West, 2019", data_SL_age$Study)
-
-data_SL$Study <- sub("West, 2018", "West, 2019", data_SL$Study)
-
-data_SL <- data_SL_age %>% 
-  tidyr::pivot_wider(names_from = c(age_type, age_measure),
-                    values_from = age) %>% 
-  dplyr::rename(mean_age = mean_sd_average,
-         lower_mean = mean_sd_lower,
-         upper_mean = mean_sd_upper,
-         median_age = median_iqr_average,
-         lower_IQR = median_iqr_lower,
-         upper_IQR = median_iqr_upper) %>% 
-  left_join(data_SL)
+# data_NPA_age <- gofer::data_NPA_age
+# data_NPA_age$Study <- sub("West, 2015", "West, 2019", data_NPA_age$Study) 
+# 
+# data_NPA <- data_NPA_age %>% 
+#   tidyr::pivot_wider(names_from = c(age_type, age_measure),
+#                     values_from = age) %>% 
+#   dplyr::rename(mean_age = mean_sd_average,
+#          lower_mean = mean_sd_lower,
+#          upper_mean = mean_sd_upper,
+#          median_age = median_iqr_average,
+#          lower_IQR = median_iqr_lower,
+#          upper_IQR = median_iqr_upper) %>% 
+#   left_join(data_NPA) 
+# 
+# data_SL_age <- gofer::data_SL_age
+# data_SL_age$Study <- sub("West, 2015", "West, 2019", data_SL_age$Study) 
+# 
+# data_SL$Study <- sub("West, 2018", "West, 2019", data_SL$Study) 
+# 
+# data_SL <- data_SL_age %>% 
+#   tidyr::pivot_wider(names_from = c(age_type, age_measure),
+#                     values_from = age) %>% 
+#   dplyr::rename(mean_age = mean_sd_average,
+#          lower_mean = mean_sd_lower,
+#          upper_mean = mean_sd_upper,
+#          median_age = median_iqr_average,
+#          lower_IQR = median_iqr_lower,
+#          upper_IQR = median_iqr_upper) %>% 
+#   left_join(data_SL)
 
 ft <- data_core %>% 
-    dplyr::bind_rows(data_SL) %>%
-      dplyr::bind_rows(data_NPA) %>%
+    # dplyr::bind_rows(data_SL) %>%
+    #   dplyr::bind_rows(data_NPA) %>%
     dplyr::arrange(Study) %>% 
@@
 ```{r tab.style='table-flex'}
-  ma <- list(primary, low_risk, ICU, OT,  NPA,SL, conflict)
-names(ma) <- c("Primary", "Low risk studies", "Intensive Care Unit", 
-               "Surgery", "Nasopharyngeal", "Sublingual",
-               "Studies not funded by industry")
+  ma <- list(primary, low_risk,core_no_npa, NPA, conflict, ICU, OT)
+names(ma) <- c("Primary", 
+               "Low risk studies",  
+               "Core (excluding nasopharyngeal and oropharyngeal)", 
+               "Nasopharyngeal", 
+               "Studies not funded by industry",
+               "Intensive Care Unit", 
+               "Surgery")
 df <- dplyr::bind_rows(ma, .id="Comparison")
@@
 df %>%
-  mutate(CI_U_rve = dplyr::na_if(CI_U_rve, 5109.68)) %>% 
-    mutate(CI_L_rve = dplyr::na_if(CI_L_rve, -5110.03)) %>% 
   rename(" " = Comparison, "Mean bias" = bias_mean,
@@
                part = "header") %>% 
-    footnote(i =6, j = 11:12,
-               value = as_paragraph(
-                "Population limits of agreement were extremely wide, spanning outside the physiologically plausible range for temperature."
-               ),
-               ref_symbols = "f",
-               part = "body") %>% 
   add_header_row(values = c("","","","","","","","","","", "Population LoA"),  colwidths = c(rep(1,10, by=1), 2))   %>% 
